\documentclass[a4paper,10pt]{letter}

% ------------------------------------------------------------
% Packages
% ------------------------------------------------------------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}

% ------------------------------------------------------------
% Sender information
% ------------------------------------------------------------
\address{%
    Omar Iskandarani\\
    Independent Researcher\\
    Groningen, The Netherlands\\
    ORCID: 0009-0006-1686-3961\\
    \href{mailto:info@omariskandarani.com}{info@omariskandarani.com}
}

\signature{Omar Iskandarani}

\date{\today}

% ------------------------------------------------------------
% Document
% ------------------------------------------------------------
\begin{document}

    \begin{letter}{%
        Editors\\
        \textit{AIP Advances}
    }

\opening{Dear Editors,}

\textbf{Re: Response to Editorial Comments}\\
Manuscript ID: \textbf{ADV26-AR-00433-T}\\
Title: \textit{Delay-induced mode discreteness in nonlinear ring systems}

\vspace{1em}

Thank you for the opportunity to revise our manuscript. We appreciate the editorial feedback and have carefully revised the manuscript accordingly.

The revised version addresses all requested points:

\begin{itemize}[leftmargin=1.5em]
    \item The language has been clarified and conservative wording has been adopted throughout.
    \item Overstatements and priority-related claims have been softened where appropriate.
    \item Analogies to transport-barrier concepts are now explicitly framed as heuristic rather than derived.
    \item The manuscript has been carefully proofread for clarity, consistency, and presentation.
\end{itemize}

No changes to the core results or conclusions were required.

A marked-up manuscript highlighting all changes is provided alongside the clean revised version, in accordance with the journal’s submission requirements.

\vspace{1em}

Thank you for your time and consideration.

\closing{Sincerely,}

    \end{letter}

\end{document}