\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{enumitem}

\title{Uniqueness of the Minimal Finite-Cell Variational Reduction:\\
A Derivation Target for the Fine-Structure-Scale Pressure Closure}

\author{Omar Iskandarani\\
Independent Researcher, Appingedam, The Netherlands}

\date{\today}

\newcommand{\LK}{\mathcal L_K}
\newcommand{\Harm}{\mathcal H}
\newcommand{\Kcell}{\mathcal K_{\rm cell}}
\newcommand{\Eeff}{E_{\rm eff}}
\newcommand{\EpNLS}{E_p^{\rm NLS}}
\newcommand{\alphacell}{\alpha_{\rm cell}}

\begin{document}
\maketitle

\begin{abstract}
The companion papers isolate a dimensionless fine-structure-scale closure based
on the ideal-trefoil ropelength, a spherical pressure cell, and a finite-cell
BEM/NLS stationary point.  The remaining question is whether the coefficients
\(N_p=4\), \(\sigma=11/3\), \(\chi_R=2\), and \(q_\phi=1\) are merely closure
choices or consequences of a more restrictive variational reduction.  This note
states and proves a conditional uniqueness theorem: under \(SO(3)\) covariance,
locality on the spherical cell boundary, positive quadratic order, volume and
centre-displacement pressure constraints, inner/outer pressure reciprocity, and
selection of the leading \(1/r\) exterior phase field, the minimal finite-cell
variational reduction uniquely gives
\[
  N_p=4,\qquad
  \sigma=\frac{11}{3},\qquad
  \chi_R=2,\qquad
  q_\phi=1.
\]
Consequently,
\[
  \EpNLS
  =
  \frac{16\pi}{3}\LK
  \left(1-\frac{11}{48\LK^2}\right)
\]
is derived within the stated finite-cell variational reduction.  The result is
not claimed to be a complete first-principles derivation from the full
microscopic field equations; rather, it identifies the precise reduction
assumptions under which the pressure-cell closure is unique.
\end{abstract}

\section{Purpose and status}

The preceding companion papers separate three levels of claim.  The first is
an algebraic closure audit.  The second is a spherical/NLS pressure-cell
construction.  The third is a finite-cell BEM/NLS stationary-point calculation
and conditional far-field consistency test.  The present note supplies the
missing logical bridge between a free closure model and a derived effective
model: it proves uniqueness of the minimal finite-cell variational reduction
under explicitly stated axioms.

The status of the result is therefore
\[
  \boxed{\text{derived within the unique minimal finite-cell variational reduction}.}
\]
It is not, by itself,
\[
  \boxed{\text{derived from the full microscopic dynamics without reduction assumptions}.}
\]
That stronger statement would require deriving the axioms below directly from
the underlying field theory.

\section{Axioms of the minimal finite-cell reduction}

Let the finite cell be represented by a spherical boundary \(S^2\), with
outward unit normal \(\mathbf n\), pressure field \(p\), dimensionless shell
thickness \(\eta=a/R_{\rm cell}\), cell-radius ratio
\(\chi_R=R_{\rm cell}/L_K\), and exterior phase field \(u\).  The minimal
quadratic reduction is assumed to satisfy:
\begin{enumerate}[label=A\arabic*.]
\item \(SO(3)\) covariance on the spherical boundary.
\item Locality at quadratic order on \(S^2\).
\item Positive quadratic energy for stable boundary perturbations.
\item Pressure constraints only for total compression and centre displacement:
\[
  \int_{S^2}p\,d\Omega=P_0,\qquad
  \int_{S^2}p\,\mathbf n\,d\Omega=\mathbf P_1.
\]
\item Isotropic NLS/GP shell-gradient response at second order.
\item Reciprocal inner/outer pressure balance at leading scale order.
\item Leading far-field coupling carried only by the exterior \(1/r\) harmonic
phase mode.
\end{enumerate}

These assumptions define the class in which the uniqueness statement is made.

\section{The finite-cell effective action}

At quadratic order the effective action separates into
\[
  \mathcal A_{\rm eff}
  =
  \mathcal A_p[p]
  +
  \mathcal A_{\rm shell}[\eta]
  +
  A_\chi(\chi_R)
  +
  \mathcal A_\phi[u].
\]
The four pieces are fixed below by the axioms, up to an overall normalization
that cancels in the dimensionless coefficient gates.

\section{Theorem 1: constrained pressure minimization gives \(N_p=4\)}

Consider
\[
  \mathcal A_p[p]
  =
  \frac12
  \int_{S^2}
  |\nabla_{S^2}p|^2\,d\Omega
\]
subject to
\[
  \int_{S^2}p\,d\Omega=P_0,
  \qquad
  \int_{S^2}p\,\mathbf n\,d\Omega=\mathbf P_1.
\]
Introducing Lagrange multipliers \(\lambda_0\) and
\(\boldsymbol{\lambda}_1\), the Euler--Lagrange equation is
\[
  -\Delta_{S^2}p
  =
  \lambda_0+\boldsymbol{\lambda}_1\cdot\mathbf n.
\]
The constant function belongs to \(\Harm_0\), and the coordinate functions
\(n_x,n_y,n_z\) span \(\Harm_1\).  Hence the minimal pressure subspace is
\[
  \mathcal P_{\rm min}
  =
  \Harm_0\oplus\Harm_1.
\]
Since
\[
  \dim\Harm_\ell=2\ell+1,
\]
one obtains
\[
  N_p
  =
  \dim\Harm_0+\dim\Harm_1
  =
  1+3
  =
  4.
\]
This proves uniqueness of \(N_p=4\) inside the lowest \(SO(3)\)-closed pressure
subspace satisfying the volume and centre-displacement constraints.  Modes
\(\ell\ge2\) represent quadrupolar and higher shape deformations and are not
required by the constraints.

\section{Theorem 2: isotropic NLS/GP shell variation gives \(\sigma=11/3\)}

Let
\[
  \eta=\frac{a}{R_{\rm cell}}.
\]
The volume Jacobian for a relative inward shell displacement is
\[
  \frac{V(R-a)}{V(R)}
  =
  (1-\eta)^3
  =
  1-3\eta+3\eta^2+O(\eta^3).
\]
After the first-order displacement is absorbed into the equilibrium radius, the
second-order volume contribution is
\[
  \sigma_{\rm vol}=3.
\]
The isotropic NLS/GP gradient term contributes through the transverse
projector
\[
  P_\perp=I-\hat{\mathbf r}\hat{\mathbf r}.
\]
Using
\[
  \langle \hat r_i\hat r_j\rangle_{S^2}
  =
  \frac13\delta_{ij},
\]
one gets
\[
  \langle P_\perp\rangle_{S^2}
  =
  \frac23 I.
\]
Equivalently,
\[
  \langle\sin^2\theta\rangle_{S^2}
  =
  \frac{\int_0^\pi \sin^2\theta\,\sin\theta\,d\theta}
       {\int_0^\pi \sin\theta\,d\theta}
  =
  \frac23.
\]
Thus the second-order shell coefficient is
\[
  \sigma
  =
  \sigma_{\rm vol}+\sigma_\perp
  =
  3+\frac23
  =
  \frac{11}{3}.
\]

\section{Theorem 3: reciprocal pressure stationarity gives \(\chi_R=2\)}

Let
\[
  \chi_R=\frac{R_{\rm cell}}{L_K}.
\]
The leading outer pressure-extension cost is proportional to \(\chi_R\), while
the inner crowding/compliance cost is reciprocal and proportional to the number
of pressure sectors.  Inner/outer reciprocity therefore fixes the minimal
scale action to
\[
  A_\chi(\chi_R)
  =
  \chi_R+\frac{N_p}{\chi_R}.
\]
Stationarity gives
\[
  \frac{dA_\chi}{d\chi_R}
  =
  1-\frac{N_p}{\chi_R^2}
  =
  0,
\]
so
\[
  \chi_R=\sqrt{N_p}=2.
\]
Equivalently, if
\[
  A_\chi=\chi_R+\frac{\lambda_\chi}{\chi_R},
\]
then
\[
  \lambda_\chi=N_p=4.
\]
This is unique in the leading-order class of reciprocal, scale-homogeneous
inner/outer pressure actions.  If additional terms such as \(\chi_R^2\),
\(\chi_R^{-2}\), or \(\log\chi_R\) are admitted at the same order, uniqueness is
lost; such terms are excluded by the minimal scale-reciprocity axiom.

\section{Theorem 4: the exterior phase Hessian fixes \(q_\phi=1\)}

An exterior harmonic field has the multipole expansion
\[
  u(r,\theta,\phi)
  =
  \sum_{\ell,m}
  a_{\ell m}
  \frac{Y_{\ell m}(\theta,\phi)}{r^{\ell+1}}.
\]
Only \(\ell=0\) gives a \(1/r\) field.  The \(\ell=1\) sector begins at
\(r^{-2}\), and all \(\ell\ge2\) modes are shorter-ranged.  Therefore the
leading far-field charge is the constant boundary phase, i.e. the unique
\(H^0(S^2)\) mode.  Since \(S^2\) is connected,
\[
  q_\phi=\dim H^0(S^2)=1.
\]
For the exterior monopole
\[
  u(r)=\frac{\phi}{r},
\]
one has
\[
  \int_{r\ge1}
  |\nabla u|^2\,d^3x
  =
  \int_1^\infty
  4\pi r^2\frac{\phi^2}{r^4}\,dr
  =
  4\pi\phi^2.
\]
Thus
\[
  \Lambda_\phi=4\pi\Kcell.
\]
The unit \(H^0\) one-cell phase Hessian gives
\[
  \Lambda_\phi=\frac{\Eeff}{2},
\]
and therefore
\[
  \Kcell
  =
  \frac{\Eeff}{8\pi}.
\]

\section{Resulting pressure scale}

Combining Theorems 1--3,
\[
  E_p^{(0)}
  =
  N_p\frac{4\pi}{3}\LK
  =
  \frac{16\pi}{3}\LK.
\]
Moreover,
\[
  \eta_K
  =
  \frac{1}{2\chi_R\LK}
  =
  \frac{1}{4\LK}.
\]
With \(\sigma=11/3\),
\[
  \sigma\eta_K^2
  =
  \frac{11}{3}\frac{1}{16\LK^2}
  =
  \frac{11}{48\LK^2}.
\]
Therefore
\[
  \boxed{
  \EpNLS
  =
  \frac{16\pi}{3}\LK
  \left(
  1-\frac{11}{48\LK^2}
  \right).
  }
\]
Theorem 4 then gives the far-field stiffness relation
\[
  \Kcell=\frac{\Eeff}{8\pi},
\]
so that the leading two-cell interaction has coefficient
\[
  \alphacell
  =
  \frac{1}{4\pi\Kcell}
  =
  \frac{2}{\Eeff}.
\]

\section{Falsification and robustness checks}

The uniqueness theorem depends on the minimal axioms.  The following checks
test those axioms rather than the algebra:
\begin{enumerate}
\item include the \(\ell=2\) pressure sector and verify that it enters only as a
higher-order shape correction;
\item replace \(P_\perp\) by a weighted transverse projector and verify that
isotropic NLS/GP reduction fixes the weight to unity;
\item replace \(A_\chi=\chi_R+N_p/\chi_R\) by
\(a\chi_R+bN_p/\chi_R\) and verify that inner/outer reciprocity enforces
\(a=b\);
\item compute the one-cell phase Hessian directly from the full finite-cell
operator and verify \(\Lambda_\phi=\Eeff/2\).
\end{enumerate}

\section{Conclusion}

The four coefficient gates are not free once the minimal finite-cell
variational reduction is imposed.  The pressure constraints uniquely select
\(\Harm_0\oplus\Harm_1\) and hence \(N_p=4\); the isotropic shell second
variation gives \(\sigma=11/3\); reciprocal inner/outer pressure stationarity
gives \(\chi_R=2\); and the exterior \(1/r\) phase field gives \(q_\phi=1\) and
\(\Kcell=\Eeff/(8\pi)\).  The resulting fine-structure-scale pressure closure
is therefore derived within this unique minimal variational reduction.  The
remaining task is to derive the reduction axioms themselves from the full
microscopic field equations.

\begin{thebibliography}{9}

\bibitem{MorseFeshbach1953}
P. M. Morse and H. Feshbach,
\emph{Methods of Theoretical Physics},
McGraw--Hill, New York (1953).

\bibitem{ArfkenWeberHarris2013}
G. B. Arfken, H. J. Weber, and F. E. Harris,
\emph{Mathematical Methods for Physicists}, 7th ed.,
Academic Press, Oxford (2013).
ISBN: 978-0123846549.

\bibitem{Pitaevskii1961}
L. P. Pitaevskii,
``Vortex Lines in an Imperfect Bose Gas,''
\emph{Soviet Physics JETP} \textbf{13}, 451--454 (1961).

\bibitem{RobertsGrant1971}
P. H. Roberts and J. Grant,
``Motions in a Bose Condensate. I. The Structure of the Large Circular Vortex,''
\emph{Journal of Physics A: General Physics} \textbf{4}, 55--72 (1971).
DOI: 10.1088/0305-4470/4/1/306.

\bibitem{Saffman1992}
P. G. Saffman,
\emph{Vortex Dynamics},
Cambridge University Press, Cambridge (1992).
ISBN: 978-0521477390.

\bibitem{Evans2010}
L. C. Evans,
\emph{Partial Differential Equations}, 2nd ed.,
American Mathematical Society, Providence, RI (2010).
ISBN: 978-0821849743.

\end{thebibliography}

\end{document}
