\documentclass[a4paper,10pt]{letter}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\usepackage[margin=1in]{geometry}

\signature{Omar Iskandarani\\
Independent Researcher, Groningen\\
The Netherlands\\
ORCID: 0009-0006-1686-3961\\
Email: \href{mailto:info@omariskandarani.com}{info@omariskandarani.com}}

\address{Omar Iskandarani\\
Vinkenstraat 86A\\
9713 TK Groningen\\
The Netherlands}

\date{\today}

\begin{document}

    \begin{letter}\noindent Editor, \emph{AIP Advances}\\
    AIP Publishing\\[6pt]

    \noindent\textbf{Re: Transfer submission from \emph{Chaos} (MS \#CHA26-AR-00183)}\\
    \textbf{Manuscript title:} \emph{Delay-Induced Mode Selection in Circulating Feedback Systems}

    \medskip
    \noindent Dear Editor,

    \noindent I am submitting the above manuscript to \emph{AIP Advances} via the AIP transfer pathway from
    \emph{Chaos: An Interdisciplinary Journal of Nonlinear Science} (Manuscript \#CHA26-AR-00183).
    The \emph{Chaos} editorial decision dated 02-Feb-2026 recommended transfer to \emph{AIP Advances} on scope/fit grounds.

    \medskip
    \noindent The manuscript develops a reduced delay-differential phase model for circulating feedback loops and shows that
    finite transit time alone can enforce a discrete set of stable operating frequencies through dynamical stability selection,
    without invoking spatial standing-wave boundary conditions. The mechanism is applicable across physical platforms where
    looped propagation and feedback are present (e.g., optical/electronic ring systems, delayed control loops, and distributed
    oscillator networks).

        \medskip
        \noindent\textbf{Related submission disclosure.}
        This manuscript is conceptually related to a separate manuscript of mine previously submitted to \emph{AIP Advances} titled
        \emph{``Delay-Induced Pattern Formation as a Route to Mode Discreteness in Nonlinear Ring Systems.''}
        That companion manuscript is not currently under consideration at \emph{AIP Advances}.
        It treats spatiotemporal pattern formation in extended/nonlocal ring settings, whereas the present manuscript isolates the minimal
        phase-locked circulating mode-selection mechanism in a reduced effective model. The two manuscripts have distinct primary results
        and are intended to be complementary rather than overlapping.

    \medskip
    \noindent This work has not been published elsewhere and is not under consideration by any other journal.
    No external funding supported this research. Data sharing is not applicable because no new datasets were created or analyzed.

    \medskip
    \noindent Sincerely,\\
    Omar Iskandarani



    \end{letter}

\end{document}