\documentclass[a4paper,10pt]{letter}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\usepackage[margin=1in]{geometry}
\usepackage{amstext}

% Sender info
\signature{Omar Iskandarani\\
Independent Researcher, Groningen,\\ The Netherlands\\
ORCID: 0009-0006-1686-3961\\
Email: \href{mailto:info@omariskandarani.com}{info@omariskandarani.com}}
\address{Omar Iskandarani\\
Vinkenstraat 86A,\\
9713TK Groningen, \\The Netherlands}

\date{\today}

\begin{document}

    \begin{letter}{Editors\\\textit{Foundations of Physics}}
        \opening{Dear Editor,}

        I am pleased to submit the manuscript \textit{Electromagnetism as Propagating Torsion in a Hydrodynamic Vacuum: A Geometric Unification via Cartan Structure Equations} for consideration in \textit{Foundations of Physics}.

        While standard QED treats gauge fields as abstract entities, our work provides a rigorous geometric derivation of Maxwell's equations from the kinematics of a structured vacuum substrate. We show that the electromagnetic field strength is mathematically isomorphic to spacetime torsion in a teleparallel geometry. This approach not only clarifies the ontology of the photon but yields a novel, falsifiable prediction regarding vacuum magneto-optics that distinguishes this framework from standard vacuum polarization.

        \textbf{Why \textit{Foundations of Physics}.}
        This work aligns closely with the journal's mission to explore the conceptual and fundamental bases of physical laws. It addresses the ontological nature of the vacuum and the photon, proposing a geometric unification that bridges fluid mechanics, Cartan geometry, and gauge theory. Furthermore, it moves beyond pure interpretation by deriving a concrete experimental discriminator—the  \textbf{Vacuum Verdet Constant}—which predicts a linear-in-$B$ Faraday rotation distinct from the quadratic effects of Euler-Heisenberg QED.

        \textbf{Compliance.}
        The manuscript is original, not under consideration elsewhere, and all authorship/affiliation information is complete. Conflicts of interest: none. Data and code are available via the cited Zenodo record(s).

        Thank you for your consideration.

        \closing{Sincerely,}

    \end{letter}
\end{document}