%! Author = Omar Iskandarani
%! Companion to Swirl-String-Theory Canon-v0.8.1 (included from \texttt{SST\_CANON-v0.8.1.tex} before the manual bibliography).

\section{Research-track sectors migrated from the main canon}

\noindent
This companion document collects those sectors that remain useful for continuity and future development but are too long, too provisional, or too phenomenology-specific for the core body of \textit{Swirl-String-Theory\_Canon-v0.8.1}. Their migration out of the main canon is editorial rather than negative: each subsection remains part of the broader SST research program, but none is required for the minimal logical closure of the core canon.

\medskip
\noindent
\textbf{Editorial note (v0.8.1):} the maximal swirl tension sector ($F_{\rm swirl}^{\max}$, Rydberg bridge identities, Gibbons-class maximum-tension comparison, and the threefold interpretation table) is developed in the core document under \verb|SST_CANON-v0.8.1.tex|, subsection \texttt{Maximal Swirl Tension} (label \texttt{sec:Fmax}); it is not duplicated here.

\medskip








\subsection{Thermodynamic Radiation Interface}
A recurring legacy idea is that a local swirl-energy density may define an effective temperature field and thereby an emergent radiation sector. Let
\begin{align}
    T_{\mathrm{eff}} = T_{\mathrm{eff}}\big(\rhoE,\, \omega,\, \SwirlClock\big)
\end{align}
denote an unspecified constitutive relation. A minimal legacy interface then asks whether Planck-type spectra can emerge from a medium whose local excitation scale is set by $T_{\mathrm{eff}}$.

\textbf{[ORTHODOX]}: blackbody spectra are governed by Planck's law once a valid temperature variable is defined.

\textbf{[SPECULATIVE]}: SST does not yet derive the constitutive relation above, so this sector remains a research program rather than canonically closed physics.

\subsection{Minimal Coupling Interface to QED}
Early research notes repeatedly explored whether an effective vector potential could be built from circulation variables. The most conservative placeholder takes the form
\begin{align}
    \nabla \rightarrow \nabla - i\frac{m}{\hbar}A_{\mathrm{eff}},
    \qquad
    A_{\mathrm{eff}} = \chi \, v,
\end{align}
where $\chi$ is a scalar weight and $v$ is the local carrier velocity field.

\textbf{[ORTHODOX]}: minimal coupling is the standard gateway from free to gauge-coupled wave dynamics.

\textbf{[SPECULATIVE]}: the above substitution is only an analogy template unless a full gauge-covariant derivation is supplied.

\subsection{Ribbon-Invariant Chirality Refinement}
The older canon layers also suggested using the Calugareanu--White--Fuller relation
\begin{align}
    Lk = Tw + Wr
\end{align}
as a refinement of the knot-based matter/antimatter dictionary.

\textbf{[ORTHODOX]}: this is a standard geometric identity for framed curves and ribbons.

\textbf{[DERIVED]}: it can be used internally to separate writhe-dominated from twist-dominated realizations of the same coarse knot class.

\textbf{[SPECULATIVE]}: the mapping from $\operatorname{sign}(Tw)$ or related chirality measures to particle/antiparticle sectors remains a model hypothesis.

\subsection{Particle-Candidate Mapping Layer}
\textbf{[SPECULATIVE] Working dictionary:} a minimal knot/composition mapping retained from earlier SST work is summarized in Table~\ref{tab:particle-candidates}. This table is organizational rather than definitive; it records the current topological assignments used by the mass and taxonomy program.

\begin{table}[h]
\centering
\begin{tabular}{lll}
\hline
Knot class / composition & Candidate & Status / role \\
\hline
$3_1$ & electron & baseline lepton calibration \\
$T(2,5)$ or equivalent higher torus class & muon & lepton hierarchy candidate \\
$T(2,7)$ or equivalent higher torus class & tau & lepton hierarchy candidate \\
$5_2 + 5_2 + 6_1$ & proton & composite baryon candidate \\
analogous nearby composite class & neutron & composite baryon candidate \\
\hline
\end{tabular}
\caption{Minimal knot-class to particle-candidate summary retained as a research-track dictionary.}
\label{tab:particle-candidates}
\end{table}

\textbf{[CRITICAL NOTE]}: Table~\ref{tab:particle-candidates} is a working dictionary only. A full canonical assignment requires an explicit invariant set and a mass-functional comparison program.

\subsection{Hydrodynamic Exchange and the Pauli Barrier}
\textbf{[ORTHODOX]}: for two thin filamentary loops $C_1$ and $C_2$ in an incompressible medium, the Biot--Savart interaction energy is
\begin{align}
    E_{\mathrm{int}}
    =
    \frac{\rhoF\Gamma_1\Gamma_2}{4\pi}
    \oint_{C_1}\oint_{C_2}
    \frac{d\ell_1\cdot d\ell_2}{\norm{r_1-r_2}}.
\end{align}

\textbf{[DERIVED]}: if two identical electron-candidate loops are forced into the same spatial state, regularization at the core radius $\rc$ yields the overlap penalty
\begin{align}
    V_{\mathrm{Pauli}}(d)
    \approx
    \frac{\rhoF\Gamma_0^2}{4\pi}
    \iint
    \frac{d\ell_1\cdot d\ell_2}{\sqrt{\norm{r_1(\theta_1)-r_2(\theta_2)+d}^2+\rc^2}},
\end{align}
with maximal-overlap scale
\begin{align}
    V_{\mathrm{Pauli}}^{\max}
    \approx
    \frac{\rhoF\Gamma_0^2}{4\pi}\left(\frac{L}{\rc}\right)\mathcal{O}(1).
\end{align}

Using the canonical values
\begin{align}
    \rhoF &= 7.0\times 10^{-7}\ \mathrm{kg\,m^{-3}}, \\
    \rc &= 1.40897017\times 10^{-15}\ \mathrm{m}, \\
    \Gamma_0 &= 2\pi \rc\,\vnorm \approx 9.6836\times 10^{-9}\ \mathrm{m^2\,s^{-1}},
\end{align}
and $L\sim 2\pi a_0$ at the hydrogenic scale, one obtains the benchmark estimate
\begin{align}
    V_{\mathrm{Pauli}}^{\max} \sim 1.23\times 10^{-18}\ \mathrm{J} \sim 7.6\ \mathrm{eV}.
\end{align}

\textbf{[CRITICAL NOTE]}: this is retained as a canonical scale benchmark, not yet as a closed theorem. Its role is to show that the exclusion-energy estimate falls in an atomically relevant window rather than at obviously pathological scales.

\subsection{Numerical Benchmark Layer}
\textbf{[DERIVED] Computational-program requirement:} earlier SST work contained explicit benchmark tables for particle and atomic masses. In v0.8.1, the benchmark layer is retained as a reproducibility requirement rather than as a stand-alone authority claim.

\begin{table}[h]
\centering
\begin{tabular}{lllll}
\hline
Particle & $m_{\mathrm{exp}}$ (MeV) & $m_{\mathrm{SST}}$ (MeV) & rel. error & mode class \\
\hline
e & 0.51099895 & 0.51099895 & 0 & predictive/closure \\
$\mu$ & 105.6583745 & \dots & \dots & predictive candidate \\
$\tau$ & 1776.86 & \dots & \dots & predictive candidate \\
p & 938.272088 & \dots & \dots & predictive or closure \\
n & 939.565420 & \dots & \dots & predictive or closure \\
\hline
\end{tabular}
\caption{Benchmark summary structure to be populated from canonical scripts and archived CSV output.}
\end{table}

\textbf{[CRITICAL NOTE]}: a future v0.8.x benchmark appendix should include the exact script or package path used for generation, archived CSV outputs, mode definitions (predictive vs. exact-closure), and uncertainty propagation on canonical constants and geometric factors.

\subsection{Helicity-by-base archive (diagnostic layer)}
\textbf{[DERIVED] Archive role:} the SST helicity-by-base outputs are retained as a measurable balance diagnostic for taxonomy support, not as an independent law.
Define the midpoint-distance diagnostic
\begin{align}
    \Delta_H(K)=\abs{\widehat{\mathcal{H}}_{b}(K)+\frac{1}{2}},
\end{align}
where $\widehat{\mathcal{H}}_{b}(K)$ is the archived normalized helicity-like base indicator for class $K$.

Near-balanced values with $\Delta_H(K)\ll 1$ indicate candidate dark or quasi-dark sectors only when symmetry and instability filters are also satisfied.

\textbf{[CRITICAL NOTE]}: no single helicity-like scalar is sufficient for sector assignment; classifier decisions remain conjunction rules over symmetry, helicity balance, and low-order stability content.

\textbf{[CANON WORKFLOW NOTE]}: if SST-labelled and parallel VAM-labelled helicity outputs are numerically identical, the SST-labelled archive is the only required source for canon workflows.

\subsection{Trefoil-closure archive (benchmark discipline)}
\textbf{[DERIVED] Benchmark role:} ideal-trefoil robustness sweeps, final-best-estimate tables, and theorem-style reports are retained as benchmark-discipline infrastructure.

\textbf{[CRITICAL NOTE]}: practical best-estimate closure and theorem-level closure are distinct.
A result may remain useful for calibration while still failing strict theorem-level tail or postcheck requirements.

\textbf{[REQUIRED METADATA]}: benchmark reports should include explicit pass/fail logic, postchecks, extrapolation summaries, and local-curve diagnostics so that closure claims are auditable.

\subsection{\texorpdfstring{$\phi_{3_1}$}{phi3_1} transform archive (deferred)}
\textbf{[SPECULATIVE] Status:} retained as research-track spectral evidence for later zeta/spectral programs.

\textbf{[SCOPE RULE]}: this archive is not part of the current dark-sector or galactic canonization closure path in v0.8.x.

\subsection{Gauge-Sector Roadmap}
\textbf{[SPECULATIVE] Structural roadmap:} a retained minimal statement of the gauge program is
\begin{align}
    g_{\mathrm{eff}} = su(3) \oplus su(2) \oplus u(1),
\end{align}
with effective gauge phases organized as holonomy data of multi-director transport.

A minimal phase-based representation is
\begin{align}
    A^a_{\mu}(x) = \partial_{\mu}\theta^a(x),
\end{align}
and clock coupling acts as a common phase reference,
\begin{align}
    \theta^a(x) \mapsto \theta^a(x)+q^a\chi(x)
    \quad\Rightarrow\quad
    A^a_{\mu}\mapsto A^a_{\mu}+q^a\partial_{\mu}\chi.
\end{align}

\textbf{[CRITICAL NOTE]}: the gauge layer is retained only as a roadmap statement. Running couplings, anomaly cancellation, and realistic mixing matrices remain open work.

\section{Dark-sector and galactic canonization execution package (v0.8.x)}
\label{sec:dark-sector-execution-package}

\subsection{Stage-0 freeze: topology toolkit and benchmark protocol}
\textbf{[DERIVED] Scope freeze:} the mandatory topology toolkit for v0.8.x canonization is fixed to:
\begin{enumerate}
    \item Gauss linking integral,
    \item helicity in ideal fluids,
    \item thin-tube helicity reduction,
    \item Hopf invariant,
    \item basic torus-knot invariants $(c,b,g)$,
    \item Calugareanu--White--Fuller relation $Lk=Tw+Wr$.
\end{enumerate}

\textbf{[DERIVED] Notation freeze:} one notation family is used in this package:
\[
\rhoF,\quad v_\theta(r),\quad p_{\mathrm{swirl}}(r),\quad
\mathcal{H}(K),\quad N_u^{(1)}(K),\quad \Gamma,\quad \kappa,\quad \SwirlClock.
\]
No parallel symbol aliases are introduced for the same quantity.

\textbf{[DERIVED] Mandatory benchmark protocol template:}
\begin{enumerate}
    \item \textbf{Inputs:} canonical constants, topology identifiers, profile parameters, and dataset/version tags.
    \item \textbf{Procedure:} exact script or package path, run command, and branch/commit hash.
    \item \textbf{Outputs:} archived CSV files with fixed column schema and an attached metadata note.
    \item \textbf{Uncertainty:} first-order propagation for calibrated constants and sensitivity sweep on profile parameters.
    \item \textbf{Rerun:} deterministic rerun steps and acceptance tolerances.
\end{enumerate}

\textbf{[CANON WORKFLOW NOTE]}: every promoted quantitative claim in this package is invalid without an explicit input-to-CSV trace.

\subsection{Stage-1 freeze: dark-sector Euler pressure anchor}
\textbf{[ORTHODOX] Euler radial balance (steady, axisymmetric, azimuthal-dominant):}
\begin{align}
    \frac{1}{\rhoF}\frac{dp_{\mathrm{swirl}}}{dr}
    =
    \frac{v_\theta(r)^2}{r}.
    \label{eq:exec_swirl_pressure}
\end{align}

\textbf{[DERIVED] Flat-tail limit (constant tail speed):}
\begin{align}
    v_\theta(r)\to v_0
    \quad\Longrightarrow\quad
    p_{\mathrm{swirl}}(r)
    =
    p_0 + \rhoF v_0^2\ln\!\left(\frac{r}{r_0}\right).
\end{align}

\textbf{[DERIVED] Assumption block:}
incompressible, inviscid, stationary, axisymmetric, azimuthal-dominant flow, with validity restricted to regions where radial drift and stratification corrections are subleading.

\textbf{[DERIVED] Dimensional check:}
\[
\left[\frac{1}{\rhoF}\frac{dp}{dr}\right]
=
\frac{\mathrm{kg\,m^{-2}\,s^{-2}}}{\mathrm{kg\,m^{-3}}}
=
\mathrm{m\,s^{-2}}
=
\left[\frac{v^2}{r}\right].
\]

\textbf{[SPECULATIVE] SST interpretation:}
Eq.~\eqref{eq:exec_swirl_pressure} is interpreted as a classifier/driver layer for dark-sector support. This interpretation is model-level and separate from the orthodox derivation.

\textbf{[DERIVED] Attached observables/falsifiers:}
\begin{enumerate}
    \item Rotation-curve consistency after pressure reconstruction from archived $v_\theta(r)$ data.
    \item Null falsifier: systematic mismatch in the reconstructed pressure gradient sign or scale across validated radial windows.
\end{enumerate}

\subsection{Stage-2 freeze: measurable dark taxonomy}
\textbf{[DERIVED] Minimal classifier variables:}
symmetry class (including amphichirality status), chirality sign/state, helicity-balance indicator $\Delta_H(K)$, and low-order instability count $N_u^{(1)}(K)$.

\textbf{[DERIVED] Decision rules (symmetry-first, then stability-filtered):}
\begin{align}
    \text{Dark}
    &:\ \text{amphichiral candidate}
    \ \wedge\
    \Delta_H(K)\ll 1
    \ \wedge\
    N_u^{(1)}(K)=0,\\
    \text{Quasi-dark}
    &:\ \text{near-balanced symmetry/helicity}
    \ \wedge\
    0 < N_u^{(1)}(K)\le 2,\\
    \text{Visible}
    &:\ \text{chiral-dominant and/or helicity-unbalanced sectors}.
\end{align}

\textbf{[DERIVED] Ambiguity tie-break:}
if classes overlap, choose the class with the strongest conjunction score in the order
\[
\text{symmetry gate} \rightarrow \text{helicity balance gate} \rightarrow \text{stability gate}.
\]

\textbf{[DERIVED] Baseline templates and falsifiers:}
\begin{itemize}
    \item \textbf{Visible baseline:} trefoil-like chiral template; falsifier = persistent amphichiral-plus-balanced signature under validated data updates.
    \item \textbf{Quasi-dark baseline:} Borromean-type weak-coupling template; falsifier = stable zero-instability assignment across independent scans.
    \item \textbf{Dark baseline:} figure-eight/amphichiral template; falsifier = robust nonzero chirality or high-instability assignment.
\end{itemize}

\textbf{[CANON WORKFLOW NOTE]}:
amphichiral $\Rightarrow$ dark remains a classifier proposal tested against observables, not a closed theorem.

\subsection{Stage-3 freeze: galactic law branch gate and closure route}
\textbf{[DERIVED] Branch-gate decision:} Branch A (legacy profile refine) is selected for current v0.8.x closure because it preserves tested limits while allowing benchmark traceability.

Working profile:
\begin{align}
    v_\theta(r)
    =
    \frac{C_{\mathrm{core}}}{\sqrt{1+(r_c/r)^2}}
    +
    C_{\mathrm{tail}}\left(1-e^{-r/r_c}\right).
\end{align}

\textbf{[DERIVED] Required checks:}
small-$r$ behavior, flat-tail behavior, parameter semantics, and pressure reconstruction via Eq.~\eqref{eq:exec_swirl_pressure}.

\textbf{[DERIVED] Failure modes:}
\begin{enumerate}
    \item non-physical parameter combinations (wrong sign or unstable growth),
    \item failure to satisfy tail-limit behavior in benchmark windows,
    \item inability to reconstruct a consistent pressure profile from the same archived inputs.
\end{enumerate}

\subsection{Stage-4 freeze: probe falsification map}
\textbf{[DERIVED]} probe classes are fixed as astrophysical, laboratory pressure/swirl analog, HV-coil/thrust-inspired, optical/torsional coupling, and null dark-sector tests.

\begin{table}[h]
\centering
\begin{tabular}{p{2.7cm}p{3.1cm}p{2.5cm}p{2.2cm}p{2.2cm}}
\hline
Probe class & Equation under test & Null-result meaning & Primary confounder & Expected sign/trend \\
\hline
Astrophysical rotation curves & Eq.~\eqref{eq:exec_swirl_pressure} + profile closure & weakens pressure-law applicability window & baryonic-model bias & reconstructed $dp/dr$ consistent with $v_\theta^2/r$ \\
Lab swirl analog & Euler radial balance scaling & weakens scale-transfer claim & viscosity/edge forcing & monotone pressure rise with imposed swirl \\
HV-coil/thrust-inspired & circulation-pressure bridge claims & kills quantized-bridge claim if no scaling & EM/thermal artifacts & response tracks circulation proxy \\
Optical/torsional coupling & swirl-clock bridge signatures & weakens coupling interpretation & detector drift/noise & phase/timing shift with controlled swirl proxy \\
Null dark tests & taxonomy conjunction rules & kills classifier branch if conjunction fails & mislabelled topology class & class score decreases under contradictory diagnostics \\
\hline
\end{tabular}
\caption{Frozen equation-to-probe map for falsification-first workflow in the v0.8.x dark-sector program.}
\label{tab:exec-probe-map}
\end{table}

\textbf{[CANON WORKFLOW NOTE]}: probe outcomes can support or reject already-stated equations, but they do not replace derivation-level closure.

\subsection{Promotion snapshot after execution}
\textbf{[DERIVED]} post-freeze status in this package:
\begin{itemize}
    \item Item 6 (topology toolkit): CANON-ready in scope and notation.
    \item Item 5 (benchmark protocol): CANON-CANDIDATE pending repository-wide protocol reuse.
    \item Item 1 (Euler pressure anchor): CANON-CANDIDATE with explicit assumptions, limits, and falsifier path.
    \item Item 2 (dark taxonomy): BRIDGE with measurable classifier gates and falsifiers.
    \item Item 3 (galactic swirl law): BRIDGE with branch gate closed and benchmark route fixed.
    \item Item 4 (probe map): CANON-BRIDGE with equation/null-result mapping frozen.
\end{itemize}

%===========================================================

\section{Candidate CANON-v0.8.x Modules from Swirl-Flux, Envelope, and Reconnection Analysis}
    \label{app:sst_v08_candidate_modules}

% --- SST macro prelude ---
    \providecommand{\swirlarrow}{%
        \mathchoice{\mkern-2mu\scriptstyle\boldsymbol{\circlearrowleft}}%
        {\mkern-2mu\scriptstyle\boldsymbol{\circlearrowleft}}%
        {\mkern-2mu\scriptscriptstyle\boldsymbol{\circlearrowleft}}%
        {\mkern-2mu\scriptscriptstyle\boldsymbol{\circlearrowleft}}%
    }
    \providecommand{\vswirl}{\mathbf{v}_{\!\swirlarrow}}
    \providecommand{\rhoF}{\rho_{\!f}}
    \providecommand{\rhoE}{\rho_{\!E}}
    \providecommand{\rhoM}{\rho_{\!m}}
    \providecommand{\rhocore}{\rho_{\mathrm{core}}}
    \providecommand{\rc}{r_c}
    \providecommand{\Fswirlmax}{F_{\mathrm{swirl}}^{\max}}
    
    \subsection{Status Classification}
        
        The following modules are proposed as CANON-v0.8.x candidates.
        
        \begin{enumerate}
            \item The Schrödinger kinetic coefficient is retained as an effective
            envelope stiffness,
            \[
                \mathcal S_e=\frac{\hbar^2}{2M_e}.
            \]
            The replacement \(-\vswirl^2\nabla^2/2\) is rejected on dimensional grounds.
            
            \item The Meissner effect is interpreted as macroscopic swirl-flux phase
            locking in a coherent paired condensate.
            
            \item R/T wave--string interaction is represented by conservation of
            radiative pseudomomentum plus vorticity impulse.
            
            \item Reconnection is excluded in the ideal sector but allowed in
            measurement, decay, and dissipative sectors, where helicity is redistributed
            between topology, writhe, twist, radiation, and dissipation.
        \end{enumerate}
    
    \subsection{Envelope Stiffness and the Rejection of the \texorpdfstring{\(\vswirl^2\nabla^2\)}{vswirl2 Laplacian} Kinetic Term}
        
        For an effective R/T envelope amplitude \(\Psi(\mathbf r,t)\), the kinetic
        coefficient must have dimension \(\mathrm{J\,m^2}\). The correct envelope
        stiffness is therefore
        \[
            \mathcal S_e
            \equiv
            \frac{\hbar^2}{2M_e},
            \qquad
            [\mathcal S_e]=\mathrm{J\,m^2}.
        \]
        The effective low-energy envelope equation is
        \[
            i\hbar\frac{\partial\Psi}{\partial t}
            =
            \left[
                -\mathcal S_e\nabla^2
            +
            V_{\mathrm{SST}}(\mathbf r,t)
            \right]\Psi .
        \]
        The operator \(-\vswirl^2\nabla^2/2\) is not a Schrödinger kinetic energy
        operator because
        \[
            \left[\vswirl^2\nabla^2\right]
            =
            \frac{\mathrm{m^2}}{\mathrm{s^2}}\frac{1}{\mathrm{m^2}}
            =
            \mathrm{s^{-2}},
        \]
        which is not an energy.
        
        For tunneling through a one-dimensional effective SST barrier,
        \[
            T
            \sim
            \exp\left(
                    -2\int_{x_1}^{x_2}\kappa_{\mathrm{SST}}(x)\,dx
            \right),
        \]
        where
        \[
            \kappa_{\mathrm{SST}}(x)
            =
            \sqrt{
                \frac{V_{\mathrm{SST}}(x)-E}{\mathcal S_e}
            }
            =
            \sqrt{
                \frac{2M_e\left[V_{\mathrm{SST}}(x)-E\right]}{\hbar^2}
            }.
        \]
        This is dimensionally consistent because
        \[
            \left[
                \frac{V-E}{\mathcal S_e}
            \right]
            =
            \mathrm{m^{-2}},
            \qquad
            [\kappa_{\mathrm{SST}}]=\mathrm{m^{-1}}.
        \]
    
    \subsection{Numerical Bridge Anomaly}
        
        A numerically close but dimensionally non-identical bridge is
        \[
            \mathcal B_e
            =
            \frac{\Fswirlmax \rc^3}
            {5\lambda_c\|\vswirl\|}.
        \]
        Using
        \[
            \lambda_c=\frac{h}{M_e c},
        \]
        one obtains
        \[
            \frac{\hbar^2}{2M_e}
            =
            6.10426431\times10^{-39}\,\mathrm{J\,m^2},
        \]
        whereas
        \[
            \mathcal B_e
            =
            6.12394931\times10^{-39}\,\mathrm{J\,s}.
        \]
        The numerical ratio is
        \[
            \frac{\mathcal B_e}{\mathcal S_e}\bigg|_{\mathrm{SI\ numbers}}
            =
            1.00322479.
        \]
        This is classified as a Research Track numerical bridge, not a canonical
        identity, because
        \[
            [\mathcal B_e]=\mathrm{J\,s}
            \neq
            \mathrm{J\,m^2}=[\mathcal S_e].
        \]
        
        The dimensionally meaningful relation is instead
        \[
            5\lambda_c\|\vswirl\|
            =
            5\alpha\frac{h}{2M_e},
        \]
        with both sides having dimension \(\mathrm{m^2\,s^{-1}}\).
    
    \subsection{Swirl-Flux Locking and the Meissner Effect}
        
        For a coherent paired electronic condensate of mass \(2M_e\) and charge
        \(q_{\mathrm{pair}}=-2e\), phase single-valuedness gives
        \[
            \oint_{\partial\Sigma}
            \left(
                2M_e\mathbf v_{\mathrm{pair}}
                +
                q_{\mathrm{pair}}\mathbf A
            \right)\cdot d\boldsymbol\ell
            =
            nh .
        \]
        Since \(q_{\mathrm{pair}}=-2e\),
        \[
            2M_e\Gamma_{\mathrm{pair}}
            -
            2e\Phi_B
            =
            nh .
        \]
        Thus
        \[
            \Phi_B
            =
            \frac{M_e}{e}\Gamma_{\mathrm{pair}}
            -
            n\frac{h}{2e}.
        \]
        In magnitude,
        \[
            |\Phi_B|
            =
            \left|
                n\Phi_0
            -
                \frac{M_e}{e}\Gamma_{\mathrm{pair}}
            \right|,
            \qquad
            \Phi_0=\frac{h}{2e}.
        \]
        For a non-rotating coherent bulk,
        \[
            \Gamma_{\mathrm{pair}}\to 0,
        \]
        and therefore
        \[
            |\Phi_B|=n\Phi_0.
        \]
        The Meissner effect is then interpreted in SST as exclusion of non-quantized
        magnetic flux from a phase-locked coherent R/T condensate.
    
    \subsection{R/T Pseudomomentum--Impulse Exchange}
        
        For a closed R/T interaction domain,
        \[
            \frac{d}{dt}
            \left(
                \mathbf P_R+\mathbf I_T
            \right)
            =
            0.
        \]
        Here \(\mathbf P_R\) denotes radiative R-phase pseudomomentum and
        \(\mathbf I_T\) denotes T-phase vorticity impulse,
        \[
            \mathbf I_T
            =
            \frac{\rhoF}{2}
            \int_{\Omega}
            \mathbf x\times\boldsymbol\omega\,d^3x .
        \]
        The dimension is
        \[
            [\mathbf I_T]
            =
            \mathrm{kg\,m\,s^{-1}},
        \]
        so \(\mathbf I_T\) is a true momentum-like quantity.
        
        For a thin circular swirl string of circulation \(\Gamma\) and radius \(R\),
        \[
            \mathbf I_T
            =
            \rhoF\Gamma\pi R^2\hat{\mathbf n}.
        \]
        The core circulation scale is
        \[
            \Gamma_0
            =
            2\pi \rc\|\vswirl\|
            =
            9.68361920\times10^{-9}\,\mathrm{m^2\,s^{-1}}.
        \]
    
    \subsection{Reconnection and Helicity Redistribution}
        
        In the ideal sector, topology is conserved:
        \[
            \frac{D\mathcal K}{Dt}=0,
        \]
        under the assumptions
        \[
            \nabla\cdot\mathbf v=0,
            \qquad
            \nu=0,
            \qquad
            \mathrm{barotropic},
            \qquad
            \mathrm{no\ reconnection}.
        \]
        In the dissipative, measurement, or decay sector, reconnection is allowed:
        \[
            \frac{D\mathcal K}{Dt}\neq0.
        \]
        The helicity budget is written
        \[
            \Delta H_{\mathrm{topology}}
            +
            \Delta H_{\mathrm{writhe}}
            +
            \Delta H_{\mathrm{twist}}
            +
            \Delta H_{\mathrm{radiative}}
            =
            -\Delta H_{\mathrm{diss}}.
        \]
        In the weak-dissipation limit,
        \[
            \Delta H_{\mathrm{topology}}
            +
            \Delta H_{\mathrm{writhe}}
            +
            \Delta H_{\mathrm{twist}}
            +
            \Delta H_{\mathrm{radiative}}
            \approx
            0.
        \]
        For filamentary structures,
        \[
            H_{\mathrm{centerline}}
            =
            \sum_{i\neq j}
            \Gamma_i\Gamma_j\mathrm{Lk}_{ij}
            +
            \sum_i
            \Gamma_i^2
            \left(
                \mathrm{Wr}_i+\mathrm{Tw}_i
            \right).
        \]
    
    \subsection{Spherical Pressure Envelopes}
        
        For inviscid incompressible SST flow,
        \[
            \nabla p_{\mathrm{SST}}
            =
            \rhoF(\mathbf v\cdot\nabla)\mathbf v .
        \]
        For an azimuthal swirl profile \(v_\theta(r)\),
        \[
            \frac{dp}{dr}
            =
            \rhoF\frac{v_\theta^2(r)}{r}.
        \]
        If
        \[
            v_\theta(r)=\frac{\Gamma}{2\pi r},
        \]
        then
        \[
            \frac{dp}{dr}
            =
            \rhoF\frac{\Gamma^2}{4\pi^2r^3},
        \]
        and hence
        \[
            p(r)
            =
            p_\infty
            -
            \frac{\rhoF\Gamma^2}{8\pi^2r^2}.
        \]
        Therefore
        \[
            \Delta p(r)
            =
            p_\infty-p(r)
            =
            \frac{\rhoF\Gamma^2}{8\pi^2r^2}
            =
            \frac{1}{2}\rhoF v_\theta^2(r).
        \]
        
        At the canonical swirl speed,
        \[
            \frac{1}{2}\rhoF\|\vswirl\|^2
            =
            4.18774392\times10^5\,\mathrm{Pa}.
        \]
        At the core-density stress scale,
        \[
            \rhocore\|\vswirl\|^2
            =
            4.65848920\times10^{30}\,\mathrm{Pa}.
        \]
        The canonical maximum swirl force is recovered as
        \[
            \Fswirlmax
            =
            \rhocore\|\vswirl\|^2\pi\rc^2
            =
            29.053507\,\mathrm{N}.
        \]
    
    \subsection{Golden-Layer Scaling}
        
        The universal rule
        \[
            E_n=\varphi^nE_0
        \]
        is rejected as too strong. The weaker Research Track ansatz is
        \[
            E_{K,k}
            =
            E_K^{(0)}\varphi^{-2k},
            \qquad
            k\in\mathbb Z_{\ge0}.
        \]
        Here \(K\) labels a knot family and \(k\) labels a relaxation layer inside
        that family.
    
    \subsection{Non-Holonomic Gravity Claims}
        
        Podkletnov-type anti-gravity claims are not adopted as Canon. At most, the
        formal analogy
        \[
            \mathrm{non\mbox{-}holonomic\ twist}
            \longleftrightarrow
            \mathrm{foliation\ twist/vorticity}
        \]
        may be retained in a historical or speculative appendix.
        No experimental anti-gravity claim is inferred.
        
        \begin{thebibliography}{99}
            
            \bibitem{LondonLondon1935}
            F. London and H. London,
            ``The Electromagnetic Equations of the Supraconductor,''
            \textit{Proceedings of the Royal Society A},
            vol. 149, no. 866, pp. 71--88, 1935.
            DOI: \texttt{10.1098/rspa.1935.0048}.
            
            \bibitem{Tinkham1996}
            M. Tinkham,
            \textit{Introduction to Superconductivity},
            2nd ed.,
            McGraw--Hill, New York, 1996.
            ISBN: \texttt{978-0486435039}.
            
            \bibitem{Onsager1949}
            L. Onsager,
            ``Statistical hydrodynamics,''
            \textit{Il Nuovo Cimento},
            vol. 6, Suppl. 2, pp. 279--287, 1949.
            DOI: \texttt{10.1007/BF02780991}.
            
            \bibitem{Feynman1955}
            R. P. Feynman,
            ``Application of Quantum Mechanics to Liquid Helium,''
            in \textit{Progress in Low Temperature Physics},
            vol. 1, pp. 17--53, Elsevier, 1955.
            DOI: \texttt{10.1016/S0079-6417(08)60077-3}.
            
            \bibitem{Vinen2004}
            W. F. Vinen,
            ``The Physics of Superfluid Helium,''
            CERN Yellow Reports / Lecture Notes, 2004.
            Permalink: \texttt{https://cds.cern.ch/record/808382/files/p363.pdf}.
            
            \bibitem{BuhlerMcIntyre2005}
            O. B{\"u}hler and M. E. McIntyre,
            ``Wave capture and wave--vortex duality,''
            \textit{Journal of Fluid Mechanics},
            vol. 534, pp. 67--95, 2005.
            DOI: \texttt{10.1017/S0022112005004374}.
            
            \bibitem{KlecknerIrvine2013}
            D. Kleckner and W. T. M. Irvine,
            ``Creation and dynamics of knotted vortices,''
            \textit{Nature Physics},
            vol. 9, pp. 253--258, 2013.
            DOI: \texttt{10.1038/nphys2560}.
            
            \bibitem{KlecknerKauffmanIrvine2016}
            D. Kleckner, L. H. Kauffman, and W. T. M. Irvine,
            ``How superfluid vortex knots untie,''
            \textit{Nature Physics},
            vol. 12, pp. 650--655, 2016.
            DOI: \texttt{10.1038/nphys3679}.
            
            \bibitem{KellerCheviakov2024}
            J. M. Keller and A. F. Cheviakov,
            ``Exact spherical vortex-type equilibrium flows in fluids and plasmas,''
            \textit{Fundamental Plasma Physics},
            vol. 11, article 100063, 2024.
            DOI: \texttt{10.1016/j.fpp.2024.100063}.
            
            \bibitem{Brickman1969}
            N. F. Brickman,
            ``Rotating Superconductors,''
            \textit{Physical Review},
            vol. 184, pp. 460--470, 1969.
            DOI: \texttt{10.1103/PhysRev.184.460}.
        
        \end{thebibliography}
        
        
        
% ============================================================
% Appendix: Mode-Locked Swirl-Coil Excitation
% Canon v0.8.1 insertion block
% ============================================================

% Safe local macro guards; harmless if the Canon preamble already defines these.
\providecommand{\swirlarrow}{\mathchoice{\mkern-2mu\scriptstyle\boldsymbol{\circlearrowleft}}{\mkern-2mu\scriptstyle\boldsymbol{\circlearrowleft}}{\mkern-2mu\scriptscriptstyle\boldsymbol{\circlearrowleft}}{\mkern-2mu\scriptscriptstyle\boldsymbol{\circlearrowleft}}}
\providecommand{\vswirl}{\mathbf{v}_{\!\swirlarrow}}
\providecommand{\rhoF}{{\rho_{\!f}}}
\providecommand{\rhoE}{\rho_{\!E}}
\providecommand{\rhoM}{\rho_{\!m}}
\providecommand{\rc}{{r_c}}
\providecommand{\vnorm}{\lVert \mathbf{v}_{\!\boldsymbol{\circlearrowleft}} \rVert}

\section{Mode-Locked Swirl-Coil Excitation and \texorpdfstring{$\vnorm=f\Delta x$}{v=f dx} Metrology}
\label{sec:appendix_mode_locked_swirl_coil}

\textbf{Status.} \textbf{[RESEARCH TRACK / CANON-CANDIDATE]}.
This appendix formulates a falsifiable experimental protocol for testing whether externally driven multi-phase coil geometries can inject coherent swirl modes into a bounded measurement region. The construction is not assumed as a new force law. It is a mode-selection and metrology rule for identifying when the canonical characteristic swirl speed
\begin{equation}
\vnorm = 1.09384563\times 10^{6}\,\mathrm{m\,s^{-1}}
\end{equation}
is sampled by a laboratory-scale frequency--length product.

\subsection{Motivation}

The basic dimensional identity
\begin{equation}
\vnorm = f\,\Delta x
\label{eq:appendix_swirl_speed_frequency_length}
\end{equation}
has the units of speed and is therefore not, by itself, a dynamical claim. Its SST use is metrological: a driven system is said to probe a swirl-resonant channel only when a temporal frequency $f$ and a geometrically defined spatial period $\Delta x$ satisfy Eq.~\eqref{eq:appendix_swirl_speed_frequency_length} within experimental bandwidth.

For a circular or quasi-circular coil, the relevant spatial period is generally not an arbitrary external distance. It is the azimuthal wavelength selected by the coil radius and spatial mode number. Hence the physical coil radius enters the resonance condition directly.

\subsection{Ring-mode closure condition}

Let $R_{\mathrm{coil}}$ be the effective radius of the active winding, $f_0$ the electrical base frequency, $n\in\mathbb{N}$ the temporal harmonic, and $m\in\mathbb{Z}\setminus\{0\}$ the azimuthal spatial mode number around the coil. The spatial wavelength of mode $m$ along the coil circumference is
\begin{equation}
\Delta x_m
=
\frac{2\pi R_{\mathrm{coil}}}{|m|}.
\label{eq:appendix_spatial_period}
\end{equation}
The (n)-th temporal harmonic has frequency
\begin{equation}
f_n = n f_0.
\end{equation}
The dimensionless swirl-lock parameter is therefore
\begin{equation}
\boxed{
\eta_{n,m}
=
\frac{f_n \Delta x_m}{\vnorm}
=
\frac{n f_0}{\vnorm}
\frac{2\pi R_{\mathrm{coil}}}{|m|}
}.
\label{eq:appendix_eta_nm}
\end{equation}
A ring mode is swirl-locked when
\begin{equation}
\boxed{\eta_{n,m}=1.}
\label{eq:appendix_eta_lock}
\end{equation}
Equivalently, the resonant coil radius for a given $(n,m,f_0)$ is
\begin{equation}
\boxed{
R_{\mathrm{coil}}^{(n,m)}
=
\frac{|m|\,\vnorm}{2\pi n f_0}
}.
\label{eq:appendix_resonant_radius}
\end{equation}

\paragraph{Dimensional check.}
\[
[R_{\mathrm{coil}}]
=
\frac{\mathrm{m\,s^{-1}}}{\mathrm{s^{-1}}}
=
\mathrm{m}.
\]
Thus Eq.~\eqref{eq:appendix_resonant_radius} is dimensionally well-defined.

\subsection{Numerical calibration examples}

For the canonical value
\[
\vnorm = 1.09384563\times10^6\,\mathrm{m\,s^{-1}},
\]
and a base drive frequency
\[
f_0 = 150\,\mathrm{kHz},
\]
the first three $m=1$ radius locks are
\begin{align}
R_{\mathrm{coil}}^{(1,1)}
&=
\frac{1.09384563\times10^6}{2\pi(1)(150000)}
=
1.1606\,\mathrm{m},
\\
R_{\mathrm{coil}}^{(2,1)}
&=
0.5803\,\mathrm{m},
\\
R_{\mathrm{coil}}^{(3,1)}
&=
0.3869\,\mathrm{m}.
\end{align}
For a smaller experimental coil with
\[
R_{\mathrm{coil}}=0.150\,\mathrm{m},
\]
the $(n=3,\ m=1)$ lock frequency is
\begin{equation}
f_0
=
\frac{\vnorm}{2\pi n R_{\mathrm{coil}}}
=
\frac{1.09384563\times10^6}
{2\pi(3)(0.150)}
=
3.8687\times10^5\,\mathrm{Hz}.
\end{equation}
Hence a $0.150\,\mathrm{m}$ coil driven at $150\,\mathrm{kHz}$ does not satisfy the $(n=3,m=1)$ ring-lock condition. Its lock parameter is
\begin{equation}
\eta_{3,1}
=
\frac{3(150000)\,2\pi(0.150)}
{1.09384563\times10^6}
=
0.3877.
\end{equation}
This is sub-resonant for the $(3,1)$ ring mode, although it may still couple to different $(n,m)$ channels.

\subsection{Three-phase selection rule}

Consider a three-phase coil drive with phase index $q=0,1,2$. If the $q$-th phase is shifted by $2\pi q/3$, the discrete phase sum for temporal harmonic $n$ and spatial azimuthal mode $m$ is
\begin{equation}
T_{n,m}^{(3\phi)}
=
\frac{1}{3}
\left|
\sum_{q=0}^{2}
\exp!\left[
i q \frac{2\pi}{3}(m-n)
\right]
\right|.
\label{eq:appendix_three_phase_factor}
\end{equation}
The exact selection rule is
\begin{equation}
\boxed{
T_{n,m}^{(3\phi)}
=
\begin{cases}
1, & m\equiv n \pmod{3},\\
0, & m\not\equiv n \pmod{3}.
\end{cases}
}
\label{eq:appendix_three_phase_rule}
\end{equation}
Thus a three-phase winding does not merely ``add power''; it filters the allowed temporal--spatial mode pairs.

\subsection{Double-stack phase-shift filter}

Let the coil be built as two vertically separated stacks, with the second stack rotated azimuthally by
\begin{equation}
\delta = 30^\circ = \frac{\pi}{6}.
\end{equation}
Let $\psi$ denote the electrical inter-stack phase offset. The two-stack spatial filter is
\begin{equation}
L_m(\delta,\psi)
=
\left|
1+\exp[i(m\delta+\psi)]
\right|.
\label{eq:appendix_stack_filter}
\end{equation}
For equal stack polarity and zero additional electrical offset $(\psi=0)$, the destructive condition is
\begin{equation}
m\delta=(2q+1)\pi,
\qquad q\in\mathbb{Z}.
\end{equation}
With $\delta=\pi/6$, this gives
\begin{equation}
\boxed{
m = 6,18,30,\ldots
}
\end{equation}
Therefore a $30^\circ$ double-stack geometry exactly suppresses the sixth azimuthal spatial harmonic and its odd multiples in this idealized equal-amplitude model.

\subsection{Golden-duty PWM spectrum}

Let the duty cycle be the inverse golden-square fraction
\begin{equation}
d = \varphi^{-2}
=
\left(\frac{1+\sqrt{5}}{2}\right)^{-2}
=
0.381966011\ldots .
\end{equation}
For an ideal unipolar rectangular pulse train, the magnitude of the $n$-th Fourier coefficient, ignoring the DC normalization convention, is proportional to
\begin{equation}
P_n(d)
=
\left|
\frac{\sin(\pi n d)}{\pi n}
\right|.
\label{eq:appendix_pwm_spectrum}
\end{equation}
For $d=\varphi^{-2}$, the first seven relative amplitudes normalized to $P_1$ are approximately
\begin{center}
\begin{tabular}{c|c|c}
\hline
$n$ & $P_n(d)$ & $P_n(d)/P_1(d)$ \\
\hline
1 & 0.296675 & 1.000 \\
2 & 0.107508 & 0.362 \\
3 & 0.046948 & 0.158 \\
4 & 0.079273 & 0.267 \\
5 & 0.017794 & 0.060 \\
6 & 0.042102 & 0.142 \\
7 & 0.038864 & 0.131 \\
\hline
\end{tabular}
\end{center}
Thus golden-duty PWM strongly suppresses the fifth harmonic, but does not by itself null the sixth and seventh harmonics. In the proposed three-phase double-stack geometry, the suppression of the fifth, sixth, and seventh bands must be understood as a composite filter effect:
\begin{equation}
\boxed{
\mathcal{C}_{n,m}
=
P_n(d)\,
T_{n,m}^{(3\phi)}\,
S_m(\mathrm{P40},+11,-9)\,
L_m(\delta,\psi)\,
G_m(k_nR_{\mathrm{coil}})
}.
\label{eq:appendix_composite_filter}
\end{equation}
Here:
\begin{itemize}
\item $P_n(d)$ is the PWM harmonic amplitude;
\item $T_{n,m}^{(3\phi)}$ is the three-phase selection factor;
\item $S_m(\mathrm{P40},+11,-9)$ is the spatial winding factor of the SawShape path;
\item $L_m(\delta,\psi)$ is the double-stack filter;
\item $G_m(k_nR_{\mathrm{coil}})$ is the geometric near-field coupling factor.
\end{itemize}
The wave number of the $n$-th temporal harmonic is
\begin{equation}
k_n
=
\frac{2\pi n f_0}{\vnorm}.
\end{equation}

\subsection{SawShape winding factor for \texorpdfstring{$\mathrm{P40},+11,-9$}{P40,+11,-9}}

For a discrete winding on $N=40$ angular sites, define the node angle
\begin{equation}
\theta_j=\frac{2\pi p_j}{40},
\qquad p_j\in\mathbb{Z}/40\mathbb{Z}.
\end{equation}
A SawShape path with alternating skip sequence $(+11,-9)$ can be represented by
\begin{equation}
p_{j+1}
=
p_j + s_j
\pmod{40},
\qquad
s_j\in\{+11,-9\}.
\end{equation}
The normalized spatial Fourier factor is then
\begin{equation}
\boxed{
S_m(\mathrm{P40},+11,-9)
=
\left|
\frac{1}{N_s}
\sum_{j=0}^{N_s-1}
w_j
\exp(-i m \theta_j)
\right|
}.
\label{eq:appendix_sawshape_factor}
\end{equation}
Here $w_j$ encodes segment weight, orientation, current direction, layer index, and local segment length. This factor is experimentally accessible: it can be inferred by measuring the spatial FFT of the near-field magnetic map over a circular sampling path.

\subsection{Canonical interpretation}

The proposed coil does not directly generate a canonical force. Instead, it prepares a structured, rotating, mode-filtered boundary condition for the local field. In SST language, the coil acts as a laboratory-scale swirl-mode injector.

The relevant energy-density comparison is
\begin{equation}
\rhoE
=
\frac{1}{2}\rhoF \vnorm^2.
\end{equation}
Using
\[
\rhoF = 7.0\times10^{-7}\,\mathrm{kg\,m^{-3}},
\qquad
\vnorm = 1.09384563\times10^{6}\,\mathrm{m\,s^{-1}},
\]
one obtains
\begin{equation}
\rhoE
=
\frac{1}{2}
(7.0\times10^{-7})
(1.09384563\times10^{6})^2
=
4.187\times10^{5}\,\mathrm{J\,m^{-3}}.
\end{equation}
The corresponding mass-equivalent density is
\begin{equation}
\rhoM
=
\frac{\rhoE}{c^2}
=
\frac{4.187\times10^{5}}
{(2.99792458\times10^{8})^2}
=
4.659\times10^{-12}\,\mathrm{kg\,m^{-3}}.
\end{equation}
These values should be understood as canonical scale references, not as a claim that a laboratory coil reaches the full canonical swirl speed in ordinary electromagnetic matter.

\subsection{Experimental falsification protocol}

A coil experiment is SST-relevant only if it passes the following null hierarchy.

\begin{enumerate}
\item \textbf{Electrical null:} repeat with identical RMS current and power but randomized phase ordering.
\item \textbf{Geometric null:} replace SawShape $(\mathrm{P40},+11,-9)$ by a symmetry-preserving circular winding with the same resistance and inductance.
\item \textbf{Duty-cycle null:} compare $d=0.381966$ against $d=0.500$, $d=0.333$, and $d=0.250$ at fixed RMS current.
\item \textbf{Stack null:} compare $30^\circ$ double-stack shift against $0^\circ$, $15^\circ$, $45^\circ$, and $60^\circ$.
\item \textbf{Mode-lock scan:} sweep $f_0$ and test whether anomalous coherence peaks occur at
\[
f_0^{(n,m)}
=
\frac{|m|\,\vnorm}{2\pi n R_{\mathrm{coil}}}.
\]
\item \textbf{Environmental null:} repeat in still air, shielded enclosure, and, where safely possible, reduced pressure to remove ion wind and acoustic coupling.
\item \textbf{Force-decomposition null:} decompose any measured force into electromagnetic, thermal, acoustic, EHD, and mechanical vibration contributions before assigning a residual.
\end{enumerate}

Only a residual signal satisfying both
\begin{equation}
\eta_{n,m}\approx 1
\end{equation}
and
\begin{equation}
\mathcal{C}_{n,m}\neq 0
\end{equation}
is admissible as an SST research-track candidate.

\subsection{Vorticity-force decomposition layer}

Any measured force must first be written schematically as
\begin{equation}
\mathbf{F}_{\mathrm{meas}}
=
\mathbf{F}_{\mathrm{EM}}
+
\mathbf{F}_{\mathrm{EHD}}
+
\mathbf{F}_{\mathrm{thermal}}
+
\mathbf{F}_{\mathrm{acoustic}}
+
\mathbf{F}_{\mathrm{mechanical}}
+
\mathbf{F}_{\omega}
+
\mathbf{F}_{\mathrm{res}} .
\label{eq:appendix_force_budget}
\end{equation}
Here $\mathbf{F}_{\omega}$ denotes force reconstructed from ordinary vorticity transport and impulse balance. Only the remaining term $\mathbf{F}_{\mathrm{res}}$, after conventional reconstruction and uncertainty propagation, can be tested against the SST mode-locking rule. The canonical research criterion is therefore
\begin{equation}
\boxed{
\mathbf{F}_{\mathrm{res}}
=
\mathbf{F}_{\mathrm{res}}(\eta_{n,m},\mathcal{C}_{n,m})
\quad\text{with a peak near}\quad
\eta_{n,m}=1.
}
\end{equation}

\subsection{Recommended measured observables}

The minimum observable set is:
\begin{enumerate}
\item drive current $I_A(t),I_B(t),I_C(t)$;
\item voltage $V_A(t),V_B(t),V_C(t)$;
\item real input power $P_{\mathrm{in}}(t)$;
\item local magnetic field map $\mathbf{B}(\mathbf{x},t)$;
\item pickup-coil FFT around the active circumference;
\item accelerometer spectrum on the coil frame;
\item air temperature and pressure field if operated in air;
\item force sensor output with synchronized phase reference.
\end{enumerate}
A positive SST candidate requires a phase-stable spectral feature at a predicted $(n,m)$ lock that disappears under at least one of the symmetry-breaking null tests.

\subsection{Conclusion}

The 3-phase SawShape $(\mathrm{P40},+11,-9)$ double-stack coil with $30^\circ$ inter-stack rotation and $d=\varphi^{-2}$ PWM is canonically useful as a mode-filtered swirl-excitation apparatus. Its SST value is not that it assumes a new force, but that it makes the frequency--length criterion
\[
\vnorm=f\Delta x
\]
experimentally precise.

The essential design rule is
\[
\eta_{n,m}
=
\frac{n f_0}{\vnorm}
\frac{2\pi R_{\mathrm{coil}}}{|m|}
\approx 1,
\]
with observable coupling only when
\[
\mathcal{C}_{n,m}
=
P_n(d)\,
T_{n,m}^{(3\phi)}\,
S_m(\mathrm{P40},+11,-9)\,
L_m(\delta,\psi)\,
G_m(k_nR_{\mathrm{coil}})
\]
is nonzero. This converts the coil concept into a falsifiable SST metrology protocol.

% ============================================================
% Optional bibliography additions, if not already present
% ============================================================
%
% Add these entries to the existing thebibliography environment only if needed.
%
% \bibitem{Bracewell2000}
% R.~N. Bracewell,
% \newblock \emph{The Fourier Transform and Its Applications},
% \newblock 3rd ed., McGraw--Hill (2000).
%
% \bibitem{Balanis2016}
% C.~A. Balanis,
% \newblock \emph{Antenna Theory: Analysis and Design},
% \newblock 4th ed., Wiley (2016).
%
% \bibitem{KlecknerIrvine2013}
% D.~Kleckner and W.~T.~M. Irvine,
% \newblock Creation and dynamics of knotted vortices,
% \newblock \emph{Nature Physics} \textbf{9} (2013), 253--258,
% \newblock DOI: 10.1038/nphys2560.
%
% \bibitem{Gehlert2023}
% P.~Gehlert, I.~Andreu-Angulo, and H.~Babinsky,
% \newblock Vortex force decomposition---forces associated with individual elements of a vorticity field,
% \newblock \emph{Experiments in Fluids} \textbf{64} (2023), 112,
% \newblock DOI: 10.1007/s00348-023-03654-3.


% ==========================================================
% SST CANON v0.8.1 -- Research Track Appendices
% Four appendices extracted from knot/vorticity literature review
% Insert after \appendix in SST_CANON-v0.8.1.tex.
% Assumes the v0.8.1 macro prelude is already loaded.
% ==========================================================

\section{Research Appendix: Non-Abelian Topological Charge for Protected Swirl Strings}
\label{app:nonabelian_topological_charge}

\paragraph{Canon status.}
\textbf{[SPECULATIVE] Research Track.}
This appendix does not promote a new particle assignment to canon. It records a canon-compatible extension of the SST topology sector: knot type and helicity may be insufficient to determine dynamical stability when reconnection and strand-crossing moves are allowed. A non-Abelian coloring invariant may supply an additional obstruction to decay.

\subsection{Motivation}
The current SST knot sector uses geometric and topological descriptors such as crossing number, ropelength, helicity, chirality, and hyperbolic-volume proxies. A minimal effective form is
\begin{equation}
    E_{\rm eff}[K]
    = \alpha C(K)+\beta L(K)+\gamma \mathcal H(K),
    \label{eq:sst_eff_energy_old}
\end{equation}
where $C(K)$ is a crossing-complexity proxy, $L(K)$ is a ropelength or length proxy, and $\mathcal H(K)$ denotes helicity or helicity-derived topological data.

Recent work on non-Abelian topological defects shows that some linked structures cannot be removed by local reconnections and strand crossings because the strands carry non-commuting elements of an order-parameter fundamental group. This suggests that SST should distinguish two layers:
\begin{enumerate}
    \item the geometric knot type $K$ of the swirl string centerline;
    \item an internal topological coloring $q$ valued in a discrete or continuous group $G$.
\end{enumerate}

\subsection{Group-colored swirl-string sector}
Let a colored swirl-string configuration be denoted
\begin{equation}
    \mathcal K_G=(K,q),
\end{equation}
where
\begin{equation}
    q: \pi_1\!\left(\mathbb R^3\setminus K\right)\longrightarrow G
    \label{eq:coloring_homomorphism}
\end{equation}
assigns a group element to each Wirtinger generator of the complement. For a diagram with arc generators $a_i$, the coloring must satisfy the usual crossing consistency relations. In SST language, $q(a_i)$ labels an internal director or phase-sector attached to a local swirl-string strand.

\textbf{[ORTHODOX] Constraint.}
For a non-Abelian group $G$, strand exchange is obstructed when the corresponding labels do not commute:
\begin{equation}
    [q(a_i),q(a_j)]
    = q(a_i)q(a_j)q(a_i)^{-1}q(a_j)^{-1}
eq e_G.
    \label{eq:noncommuting_obstruction}
\end{equation}

\textbf{[SPECULATIVE] SST interpretation.}
Equation~\eqref{eq:noncommuting_obstruction} is interpreted as a local reconnection barrier in the swirl medium. If two strands belong to non-commuting internal sectors, a direct crossing or reconnection requires an additional defect cord or phase bridge. In SST terms this is a candidate mechanism for topological protection beyond ordinary helicity conservation.

\subsection{Protected-sector invariant}
Define a protection marker
\begin{equation}
    \mathcal P_G(\mathcal K_G)=
    \begin{cases}
        1, & \text{if no allowed local reconnection/crossing sequence reduces }\mathcal K_G\text{ to the trivial sector},\\[0.3em]
        0, & \text{otherwise.}
    \end{cases}
    \label{eq:protection_marker}
\end{equation}
The marker $\mathcal P_G$ is not an energy term by itself. It is a sector label. Energetically, it enters as a barrier rule:
\begin{equation}
    \Delta E_{\rm rec}(\mathcal K_G\rightarrow \mathcal K'_G)=
    \begin{cases}
        <\infty, & Q_G(\mathcal K_G)=Q_G(\mathcal K'_G),\\[0.3em]
        \infty \text{ or macroscopically large}, & Q_G(\mathcal K_G)\neq Q_G(\mathcal K'_G),
    \end{cases}
    \label{eq:nonabelian_barrier_rule}
\end{equation}
where $Q_G$ is a conserved coloring invariant under the permitted move set.

A useful research-track extension of Eq.~\eqref{eq:sst_eff_energy_old} is therefore
\begin{equation}
    E_{\rm eff}^{(G)}[\mathcal K_G]
    = \alpha C(K)+\beta L(K)+\gamma \mathcal H(K)
    + \Delta_G\,\mathcal P_G(\mathcal K_G),
    \label{eq:nonabelian_extended_energy}
\end{equation}
where $\Delta_G$ is not a fitted mass term but a symbolic protection scale measuring the minimum energy required to violate or bypass the coloring constraint.

\subsection{Dimensional check}
The quantities $C(K)$, $\mathcal H(K)$ after normalization, $Q_G$, and $\mathcal P_G$ are dimensionless. Therefore $\alpha$, $\gamma$, and $\Delta_G$ must carry units of energy if Eq.~\eqref{eq:nonabelian_extended_energy} is used as an energy functional. If instead $E_{\rm eff}$ is a dimensionless scoring functional, all coefficients are dimensionless and must later be multiplied by an SST energy scale such as $\rhoE V_K$.

\subsection{Minimal falsifier}
If two SST candidate particles have the same $(C,L,\mathcal H)$ but different observed stability, the model predicts that a missing internal sector label exists:
\begin{equation}
    (C_1,L_1,\mathcal H_1)=(C_2,L_2,\mathcal H_2),
    \qquad
    \tau_1\neq \tau_2
    \quad\Rightarrow\quad
    Q_G(\mathcal K_1)\neq Q_G(\mathcal K_2).
\end{equation}
Failure to find such a sector in simulation or experiment would demote this appendix from Research Track to rejected model branch.

\section{Research Appendix: Reconnection Decay as a Stability Falsifier}
\label{app:reconnection_decay_falsifier}

\paragraph{Canon status.}
\textbf{[ORTHODOX] Constraint + [SPECULATIVE] SST interpretation.}
This appendix records a negative constraint on SST. A single-component Gross--Pitaevskii-like medium with permitted reconnections does not automatically protect knotted filaments. Therefore, SST particle stability requires additional structure beyond generic phase-defect topology.

\subsection{Baseline statement}
In a dissipative or reconnection-permitting medium, knotted filament topology can decay. The relevant orthodox lesson is not that SST is false, but that topology alone is insufficient unless the move set is restricted by the dynamics.

Let $K(t)$ denote the topology of a swirl-string centerline. A reconnection path is a sequence
\begin{equation}
    K_0 \longrightarrow K_1 \longrightarrow \cdots \longrightarrow K_N,
    \label{eq:reconnection_path}
\end{equation}
where each arrow is a local reconnection or strand-crossing event. If $K_N$ is an unlink or collection of unknotted loops, then $K_0$ is dynamically unprotected under that move set.

\subsection{SST stability criterion}
SST should not claim that every closed filament is stable. A canon-compatible stability criterion is
\begin{equation}
    \tau_{\rm life}(K)
    \sim \tau_0\exp\!\left(\frac{\Delta E_{\rm rec}(K)}{E_{\rm drive}}\right),
    \label{eq:sst_lifetime_barrier}
\end{equation}
where $\Delta E_{\rm rec}(K)$ is the lowest reconnection barrier out of the topological sector, and $E_{\rm drive}$ is the effective environmental or internal driving energy available to trigger reconnection.

The stable-particle condition is therefore not merely
\begin{equation}
    K\neq \bigcirc,
\end{equation}
but rather
\begin{equation}
    \Delta E_{\rm rec}(K)\gg E_{\rm drive}
    \quad\text{and/or}\quad
    Q_G(K)\neq Q_G(\bigcirc).
    \label{eq:sst_stability_condition}
\end{equation}

\subsection{Relation to Chronos--Kelvin transport}
For ideal SST evolution without reconnection or external source, the Chronos--Kelvin invariant remains
\begin{equation}
    \frac{D}{Dt}\left(R^2\omega\right)=0.
\end{equation}
Reconnection is precisely a non-ideal event where this transport law is locally invalid or discontinuous. Thus a $\kappa$-type transition in the canon may be interpreted as the event layer at which topology can change.

\textbf{[SPECULATIVE] Identification.}
A reconnection event is an SST Kairos event when it changes the topological sector:
\begin{equation}
    \kappa:\quad K_i\rightarrow K_{i+1},
    \qquad
    Q_G(K_i)\neq Q_G(K_{i+1})
    \quad\text{or}\quad
    \mathcal H(K_i)\neq \mathcal H(K_{i+1}).
\end{equation}

\subsection{Dimensionless diagnostic}
Define the stability ratio
\begin{equation}
    \Xi_{\rm rec}(K)
    = \frac{\Delta E_{\rm rec}(K)}{E_{\rm tube}(K)}.
    \label{eq:xi_reconnection}
\end{equation}
For a slender swirl tube, the standard leading envelope energy scale is
\begin{equation}
    E_{\rm tube}(K)
    \simeq
    \frac{\rhoF\Gamma^2}{4\pi}\,\ell_K\ln\!\left(\frac{R}{\rc}\right),
    \label{eq:slender_tube_energy_scale}
\end{equation}
where $\Gamma$ is circulation, $\ell_K$ is centerline length, and $R$ is the outer cutoff. The units check:
\begin{equation}
    [\rhoF\Gamma^2\ell_K]
    = \frac{\mathrm{kg}}{\mathrm m^3}\frac{\mathrm m^4}{\mathrm s^2}\mathrm m
    = \mathrm{kg}\,\mathrm m^2\mathrm s^{-2}=\mathrm J.
\end{equation}

A practical SST classification rule is
\begin{equation}
    \Xi_{\rm rec}(K)\lesssim 1 \Rightarrow \text{hydrodynamically fragile},
    \qquad
    \Xi_{\rm rec}(K)\gg 1 \Rightarrow \text{candidate stable T-phase state}.
\end{equation}

\subsection{Minimal simulation protocol}
A candidate SST knot assignment should be tested under three levels of dynamics:
\begin{enumerate}
    \item single-component phase-defect evolution;
    \item constrained incompressible evolution without reconnection;
    \item multi-director or non-Abelian colored evolution with reconnection rules.
\end{enumerate}
Only states stable under the third protocol should be promoted as particle candidates.

\section{Research Appendix: Fractional Torus-Phase Winding and Swirl-Clock Phase}
\label{app:fractional_torus_phase}

\paragraph{Canon status.}
\textbf{[SPECULATIVE] Research Track.}
This appendix records a bridge between coordinated rotational phase mechanics and SST R-phase torsional packets. It does not assert that optical polarization knots are literal SST particles. It supplies a useful mathematical template for phase winding, internal rotation, and torus-knot closure.

\subsection{Coordinated phase generator}
Let $\theta$ be an external azimuthal coordinate and let $\phi$ be an internal director angle. A coordinated rotation acts as
\begin{equation}
    \theta\mapsto \theta+\alpha,
    \qquad
    \phi\mapsto \phi+\gamma\alpha.
\end{equation}
The generator has the schematic form
\begin{equation}
    J_\gamma = L_{\rm orb}+\gamma S_{\rm int},
    \label{eq:jgamma_sst}
\end{equation}
where $L_{\rm orb}$ shifts external azimuthal phase and $S_{\rm int}$ shifts internal swirl-director phase.

For two commensurate internal frequencies $p\Omega$ and $q\Omega$ carrying azimuthal mode numbers $m_1$ and $m_2$, the coordinated-winding parameter is
\begin{equation}
    \gamma
    =\frac{m_2p-m_1q}{p+q}.
    \label{eq:gamma_fractional_winding}
\end{equation}
The corresponding torus-winding pair is
\begin{equation}
    (m,n)=\left(m_2p-m_1q,\;p+q\right).
    \label{eq:torus_pair_fractional_phase}
\end{equation}
If $\gcd(m,n)=1$, the internal lobe trajectory is a single $(m,n)$ torus knot. If $d=\gcd(m,n)>1$, the trajectory splits into $d$ linked components.

\subsection{SST phase-action translation}
To avoid notation conflict with the Swirl-Clock factor $\SwirlClock$, define a phase-action field $\mathscr S(\vec x,t)$. In an R-phase torsional packet, write the reduced phase on a toroidal carrier as
\begin{equation}
    \Theta(\theta,\phi,t)
    = n\phi-m\theta-\Omega t.
    \label{eq:sst_torus_phase}
\end{equation}
The closure condition is
\begin{equation}
    \oint d\Theta = 2\pi N,
    \qquad N\in\mathbb Z.
    \label{eq:phase_closure_condition}
\end{equation}
The phase-action field may be represented locally as
\begin{equation}
    \mathscr S(\vec x,t)=\hbar_{\rm SST}\,\Theta(\vec x,t),
    \label{eq:phase_action_relation}
\end{equation}
so that the circulation quantization condition becomes
\begin{equation}
    \oint \nabla\mathscr S\cdot d\vec\ell
    =2\pi N\hbar_{\rm SST}.
    \label{eq:phase_action_quantization}
\end{equation}

\subsection{Connection to Swirl-Clock modulation}
The local Swirl-Clock factor remains the kinematic clock factor
\begin{equation}
    \SwirlClock
    =\sqrt{1-\frac{\lVert\vswirl\rVert^2}{c^2}}.
    \label{eq:swirl_clock_factor_appendix}
\end{equation}
The phase-action field controls wave-like periodicity, while $\SwirlClock$ controls local clock rate. The research-track bridge is that a stable R-phase packet may require simultaneous closure of both:
\begin{align}
    \oint \nabla\mathscr S\cdot d\vec\ell &=2\pi N\hbar_{\rm SST},\label{eq:phase_closure}\\
    \frac{D}{Dt}\left(R^2\omega\right)&=0.\label{eq:kelvin_closure}
\end{align}

\textbf{[SPECULATIVE] Interpretation.}
Equation~\eqref{eq:gamma_fractional_winding} suggests a route to fractional internal winding without fractional circulation. The circulation quantum remains integer-valued, but the internal phase orientation can return only after multiple external turns. This may be useful for modeling R-phase torsional photons, spin-orbit-like packet structure, or generation-family phase layering.

\subsection{Dimensional check}
The variables $m,n,p,q,N$ and $\gamma$ are dimensionless. The phase $\Theta$ is dimensionless. Therefore $\mathscr S=\hbar_{\rm SST}\Theta$ has units of action, and Eq.~\eqref{eq:phase_action_quantization} has units of action because $\nabla\mathscr S\cdot d\vec\ell$ has units $({\rm J\,s\,m^{-1}}){\rm m}={\rm J\,s}$.

\section{Research Appendix: Topological Fluid Mechanics and the SST Energy Functional}
\label{app:tfm_energy_functional}

\paragraph{Canon status.}
\textbf{[ORTHODOX] Mathematical background + [SPECULATIVE] SST synthesis.}
This appendix records the topological-fluid mechanics background behind the SST knot-energy program. The orthodox part is that ideal incompressible flow preserves topology and helicity under the usual assumptions. The speculative part is the identification of selected relaxed knot classes with particle sectors.

\subsection{Frozen-field topology}
In an ideal incompressible medium, topology is transported by the flow map. For SST this supports the use of closed swirl strings as dynamically persistent structures under non-reconnecting evolution.

The primary invariants are
\begin{align}
    \Gamma &= \oint_C \vswirl\cdot d\vec\ell,\label{eq:gamma_appendix}\\
    \mathcal H &= \int_V \vswirl\cdot\vec\omega\,d^3x,\label{eq:helicity_appendix}\\
    \vec\omega &= \nabla\times\vswirl.\label{eq:vorticity_appendix}
\end{align}
For linked tubes with circulations $\Gamma_i$, the leading topological helicity decomposition is
\begin{equation}
    \mathcal H
    \simeq
    \sum_i \Gamma_i^2\,SL_i
    +2\sum_{i<j}Lk_{ij}\Gamma_i\Gamma_j,
    \label{eq:helicity_link_decomposition}
\end{equation}
where $SL_i$ is self-linking and $Lk_{ij}$ is Gauss linking number.

\subsection{Energy relaxation under topological constraints}
For a slender swirl tube, the leading hydrodynamic energy scale is
\begin{equation}
    E_{\rm env}
    \simeq
    \frac{\rhoF\Gamma^2}{4\pi}\,\ell_K\ln\!\left(\frac{R}{\rc}\right),
    \label{eq:env_energy_tfm}
\end{equation}
where $\ell_K$ is the tube centerline length. The core contribution can be represented by a line-tension term
\begin{equation}
    E_{\rm core}\simeq T_{\rm core}\ell_K.
    \label{eq:core_line_tension}
\end{equation}
Near contacts and curvature corrections may be encoded by
\begin{equation}
    E_{\rm geom}[K]
    =T_{\rm core}\ell_K
    +\frac{\rhoF\Gamma^2}{4\pi}\ell_K\ln\!\left(\frac{R}{\rc}\right)
    +\beta_{\kappa}\int_K \kappa_s^2\,ds
    +\beta_{\rm nc}\,C_{\rm near}(K).
    \label{eq:geometric_energy_functional}
\end{equation}
Here $\kappa_s$ is centerline curvature and $C_{\rm near}$ is a near-contact or crossing-complexity proxy.

\subsection{Reduction to the SST normal form}
After nondimensionalization by a reference energy $E_0$, Eq.~\eqref{eq:geometric_energy_functional} reduces to the canon-style scoring form
\begin{equation}
    \frac{E_{\rm geom}[K]}{E_0}
    \leadsto
    \alpha C(K)+\beta L(K)+\gamma\mathcal H(K)+\cdots.
    \label{eq:tfm_to_sst_eff}
\end{equation}
This justifies the SST normal form as a coarse-grained energy-ordering tool, not as a finished mass theorem.

\subsection{Canon discipline}
The functional in Eq.~\eqref{eq:tfm_to_sst_eff} should be used as follows:
\begin{enumerate}
    \item \textbf{[ORTHODOX]} Use $\Gamma$, $\mathcal H$, $Lk$, writhe, twist, and ropelength as established geometric/topological descriptors.
    \item \textbf{[DERIVED]} Within a chosen tube model, derive the units and leading energy scaling from $\rhoF$, $\Gamma$, $\ell_K$, and $\rc$.
    \item \textbf{[SPECULATIVE]} Only after this, map a relaxed topological class to an SST particle sector.
\end{enumerate}

\subsection{Minimal falsifier}
If two distinct knots have the same SST particle assignment but relax to incompatible energy minima or different protected sectors under the same admissible dynamics, the assignment must be split or rejected:
\begin{equation}
    K_1\sim_{\rm SST}K_2
    \quad\text{but}\quad
    \min E[K_1]\neq \min E[K_2]
    \quad\Rightarrow\quad
    \text{taxonomy refinement required.}
\end{equation}

% ----------------------------------------------------------
% Bibliography entries to merge into the main thebibliography
% ----------------------------------------------------------

\begin{thebibliography}{99}

\bibitem{Annala2022ProtectedVortexKnots}
T.~Annala, R.~Zamora-Zamora, and M.~M{\"o}tt{\"o}nen,
``Topologically protected vortex knots and links,''
\emph{Communications Physics} \textbf{5}, 309 (2022).
DOI: \href{https://doi.org/10.1038/s42005-022-01071-2}{10.1038/s42005-022-01071-2}.

\bibitem{Kleckner2016SuperfluidKnotsUntie}
D.~Kleckner, L.~H.~Kauffman, and W.~T.~M.~Irvine,
``How superfluid vortex knots untie,''
\emph{Nature Physics} \textbf{12}, 650--655 (2016).
DOI: \href{https://doi.org/10.1038/nphys3679}{10.1038/nphys3679}.

\bibitem{Pisanty2018FractionalKnotsLight}
E.~Pisanty, G.~Jim{\'e}nez, V.~Vicu{\~n}a-Hern{\'a}ndez, A.~Pic{\'o}n, A.~Celi, J.~P.~Torres, and M.~Lewenstein,
``Knotting fractional-order knots with the polarization state of light,''
\emph{arXiv:1808.05193} (2018).
Permalink: \href{https://arxiv.org/abs/1808.05193}{arXiv:1808.05193}.

\bibitem{Ricca1998KnotFluidMechanics}
R.~L.~Ricca,
``Applications of knot theory in fluid mechanics,''
\emph{Banach Center Publications} \textbf{42}, 321--346 (1998).
Permalink: \href{https://eudml.org/doc/252224}{EuDML:252224}.

\bibitem{Moffatt1969HelicityKnottedness}
H.~K.~Moffatt,
``The degree of knottedness of tangled vortex lines,''
\emph{Journal of Fluid Mechanics} \textbf{35}, 117--129 (1969).
DOI: \href{https://doi.org/10.1017/S0022112069000991}{10.1017/S0022112069000991}.

\bibitem{ArnoldKhesin1998TopologicalMethods}
V.~I.~Arnold and B.~A.~Khesin,
\emph{Topological Methods in Hydrodynamics},
Springer (1998).
DOI: \href{https://doi.org/10.1007/978-1-4612-0645-3}{10.1007/978-1-4612-0645-3}.

\end{thebibliography}

% ============================================================
% SST CANON-v0.8.1 Research-Track Appendix Pack
% Topic: Resonance Selection, Time Kernels, Swirl Impedance,
%        and Layered Relaxation in Swirl--String Theory
% Status: [RESEARCH-TRACK], not main-canon proof.
% ============================================================

% --- Minimal macro safety for standalone insertion ---
\providecommand{\vswirl}{\mathbf{v}_{\!\boldsymbol{\circlearrowleft}}}
\providecommand{\vnorm}{\lVert \mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert}
\providecommand{\rhoF}{\rho_{\!f}}
\providecommand{\rhoE}{\rho_{\!E}}
\providecommand{\rhoM}{\rho_{\!m}}
\providecommand{\rhocore}{\rho_{\text{core}}}
\providecommand{\rc}{r_c}
\providecommand{\omC}{\omega_C}
\providecommand{\Fswirlmax}{F_{\text{swirl}}^{\max}}

% ============================================================


\section{Resonance Selection Principle}
    \label{sec:resonance-selection-principle}
    
    \noindent
    \textbf{Status:} [RESEARCH-TRACK; candidate Canon principle].
    
    A swirl-string state \(K\) is assigned a causal response function
    \(\chi_K(\omega)\). An external perturbation \(F(t)\), with Fourier
    spectrum \(\widetilde F(\omega)\), excites the state \(K\) with amplitude
    \begin{equation}
        \mathcal A_K[F]
        =
        \int_0^\infty
        \widetilde F(\omega)\,
        \chi_K(\omega)\,
        d\omega .
    \end{equation}
    The excitation probability is
    \begin{equation}
        P_K[F]
        =
        |\mathcal A_K[F]|^2 .
    \end{equation}
    
    For isolated narrow resonances, the response function may be written as
    \begin{equation}
        \chi_K(\omega)
        =
        \sum_n
        \frac{B_{Kn}\gamma_{Kn}}
        {\omega-\omega_{Kn}+i\gamma_{Kn}},
    \end{equation}
    where \(\omega_{Kn}\) are internal swirl-string eigenfrequencies,
    \(\gamma_{Kn}\) are linewidths, and \(B_{Kn}\) are coupling weights.
    
    The natural SST frequency scale is
    \begin{equation}
        \Omega_{\rm SST}
        =
        \frac{\lVert \mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert}{r_c},
    \end{equation}
    so that internal modes may be parametrized by
    \begin{equation}
        \omega_{Kn}
        =
        \eta_{Kn}\Omega_{\rm SST},
    \end{equation}
    with dimensionless mode factors \(\eta_{Kn}\).
    
    This principle unifies delay-loop selection, Swirl-Clock phase-locking,
    mode-locking, and knot-state excitation as instances of one spectral
    overlap law.
    
    
\section{Resonance Selection Principle for Swirl--String Excitation}
    \label{app:resonance-selection-principle}
    
    \subsection*{Status and purpose}
        
        \noindent
        \textbf{Status:} [RESEARCH-TRACK].
        This appendix promotes the frequency-overlap idea from a specific beam--swirl model to a general SST excitation principle. It is not a proof of nuclear activation or fusion enhancement. It is a controlled response ansatz compatible with the Canon-v0.8.1 language of swirl strings, mode selection, circulation, helicity, and Kelvin-compatible dynamics.
    
    \subsection*{Claim}
        
        A swirl-string state \(K\) is excited most efficiently when the spectrum of an external perturbation overlaps the internal response spectrum of \(K\). Define a normalized external spectral density
        \begin{equation}
            p_{\mathrm{ext}}(\omega)\ge 0,
            \qquad
            \int_0^\infty p_{\mathrm{ext}}(\omega)\,d\omega = 1,
            \label{eq:p_ext_normalized}
        \end{equation}
        where \(p_{\mathrm{ext}}\) has units of seconds, because \(d\omega\) has units \(\mathrm{s}^{-1}\). Let the dimensionless response function of the swirl-string state be
        \begin{equation}
            R_K(\omega)
            =
            \sum_{n}
            B_{Kn}
            \frac{\gamma_{Kn}^{2}}
            {(\omega-\omega_{Kn})^{2}+\gamma_{Kn}^{2}},
            \label{eq:RK_lorentzian}
        \end{equation}
        where:
        \begin{itemize}
            \item \(\omega_{Kn}\) is the \(n\)-th internal mode frequency,
            \item \(\gamma_{Kn}\) is the corresponding linewidth,
            \item \(B_{Kn}\) is a dimensionless coupling weight.
        \end{itemize}
        
        The dimensionless excitation yield is then
        \begin{equation}
            \boxed{
                \mathcal{Y}_K
                =
                \int_0^\infty
                p_{\mathrm{ext}}(\omega)\,
                R_K(\omega)\,
                d\omega
            }
            \qquad
            [\mathrm{RESEARCH\text{-}TRACK}].
            \label{eq:SST_resonance_yield}
        \end{equation}
    
    \subsection*{Dimensional check}
        
        Since
        \[
            [p_{\mathrm{ext}}]=\mathrm{s},
            \qquad
            [d\omega]=\mathrm{s}^{-1},
            \qquad
            [R_K]=1,
        \]
        we obtain
        \[
            [\mathcal{Y}_K]
            =
            \mathrm{s}\cdot 1 \cdot \mathrm{s}^{-1}
            =
            1.
        \]
        Thus \(\mathcal{Y}_K\) is a dimensionless excitation efficiency.
    
    \subsection*{Canonical scale}
        
        The natural SST angular-frequency scale is
        \begin{equation}
            \Omega_{\mathrm{SST}}
            =
            \frac{\vnorm}{\rc}.
            \label{eq:Omega_SST_scale}
        \end{equation}
        Using the Canon values
        \[
            \vnorm = 1.09384563\times10^{6}\ \mathrm{m\,s^{-1}},
            \qquad
            \rc = 1.40897017\times10^{-15}\ \mathrm{m},
        \]
        gives
        \begin{equation}
            \Omega_{\mathrm{SST}}
            =
            7.76344066\times10^{20}\ \mathrm{s^{-1}}.
            \label{eq:Omega_SST_numeric}
        \end{equation}
        The corresponding cycle period is
        \begin{equation}
            T_{\mathrm{SST}}
            =
            \frac{2\pi}{\Omega_{\mathrm{SST}}}
            =
            8.09329985\times10^{-21}\ \mathrm{s}.
            \label{eq:T_SST_numeric}
        \end{equation}
    
    \subsection*{Interpretation}
        
        Equation~\eqref{eq:SST_resonance_yield} does not assert that all nuclear, atomic, or particle transitions are already derived in SST. It states a weaker and safer rule:
        
        \begin{quote}
            External excitation is strongest when the perturbing spectrum overlaps an allowed internal swirl-string response spectrum.
        \end{quote}
        
        This principle can later be specialized to:
        \begin{itemize}
            \item radiative transitions,
            \item qubit-like R/T phase transitions,
            \item knot-mode excitation,
            \item delayed mode selection,
            \item controlled response experiments in optical, plasma, or condensed-matter analogues.
        \end{itemize}
    
    \subsection*{Falsifiability}
        
        For a fixed target state \(K\), SST predicts that changing the spectral center \(\omega_0\) of a narrow-band perturbation should change the activation yield according to \(R_K(\omega_0)\), up to normalization and detector response. If no resonance-like dependence appears after controlling for beam power, fluence, and thermal effects, then Eq.~\eqref{eq:SST_resonance_yield} is falsified as a useful excitation law.

% ============================================================
\section{Time-Domain Kernel Form of Swirl--String Response}
    \label{app:time-domain-kernel-response}
    
    \subsection*{Status and purpose}
        
        \noindent
        \textbf{Status:} [RESEARCH-TRACK].
        This appendix converts the frequency-domain selection rule into a time-domain response law. It is intended to connect SST mode selection to pulsed experiments, delay-loop systems, and Swirl-Clock phase locking.
    
    \subsection*{Pulse-response formulation}
        
        Let \(f(t)\) be a real external driving pulse. A Gaussian-windowed monochromatic pulse may be written as
        \begin{equation}
            f(t)
            =
            f_0
            \exp\!\left(-\frac{t^2}{2\tau_p^2}\right)
            \cos(\omega_0 t+\phi_0),
            \label{eq:gaussian_drive_pulse}
        \end{equation}
        where \(\tau_p\) is the pulse duration and \(\omega_0\) is the carrier angular frequency.
        
        Let \(k_K(t)\) be the causal impulse-response kernel of the swirl-string state \(K\), with
        \begin{equation}
            k_K(t<0)=0.
        \end{equation}
        The induced response is
        \begin{equation}
            \boxed{
                s_K(t)
                =
                \int_{-\infty}^{t}
                f(t')\,k_K(t-t')\,dt'
            }
            \qquad
            [\mathrm{ORTHODOX\ form;\ RESEARCH\text{-}TRACK\ SST\ interpretation}].
            \label{eq:SST_convolution_response}
        \end{equation}
    
    \subsection*{Frequency-domain equivalence}
        
        With the Fourier convention
        \[
            \hat f(\omega)
            =
            \int_{-\infty}^{\infty}
            f(t)e^{i\omega t}\,dt,
        \]
        the convolution theorem gives
        \begin{equation}
            \hat s_K(\omega)
            =
            \hat f(\omega)\,\chi_K(\omega),
            \label{eq:frequency_response_chi}
        \end{equation}
        where \(\chi_K(\omega)\) is the complex response function of the swirl-string state. The measurable spectral response is proportional to
        \begin{equation}
            R_K(\omega)
            \propto
            |\chi_K(\omega)|^2.
            \label{eq:response_modulus}
        \end{equation}
    
    \subsection*{Bandwidth--duration relation}
        
        A Gaussian pulse obeys the scaling
        \begin{equation}
            \Delta\omega\,\tau_p \sim 1.
            \label{eq:time_bandwidth_relation}
        \end{equation}
        Therefore:
        \begin{itemize}
            \item short pulses have broad spectra and can excite many nearby modes;
            \item long pulses have narrow spectra and selectively excite one mode;
            \item coherent excitation requires phase stability over at least one internal response time.
        \end{itemize}
        
        For the canonical SST scale,
        \[
            T_{\mathrm{SST}} = 8.09329985\times10^{-21}\ \mathrm{s}.
        \]
        Thus, a pulse with duration \(\tau_p\gg T_{\mathrm{SST}}\) is narrow relative to the core-scale carrier, whereas \(\tau_p\lesssim T_{\mathrm{SST}}\) is broadband at the canonical core scale.
    
    \subsection*{Connection to Swirl Clock}
        
        If the internal phase of a swirl string is denoted by \(\theta_K(t)\), then a resonant perturbation can be represented as a phase-locking term
        \begin{equation}
            \frac{d\theta_K}{dt}
            =
            \omega_K
            +
            \epsilon\,f(t)\sin(\omega_0 t-\theta_K),
            \label{eq:phase_locking_response}
        \end{equation}
        where \(\epsilon\) is a coupling parameter. Phase locking occurs when
        \begin{equation}
            |\omega_0-\omega_K| \lesssim \epsilon |f_0|.
            \label{eq:locking_condition}
        \end{equation}
        This gives a direct bridge between frequency-selective excitation and Swirl-Clock synchronization.
    
    \subsection*{Falsifiability}
        
        For a given \(K\), changing only the pulse duration \(\tau_p\) while keeping total pulse energy fixed should alter the response through the bandwidth \(\Delta\omega\). A null result after controlling for heating and total fluence would falsify this time-domain response model.

% ============================================================
\section{Swirl Impedance and Mode Linewidth}
    \label{app:swirl-impedance-linewidth}
    
    \subsection*{Status and critical correction}
        
        \noindent
        \textbf{Status:} [RESEARCH-TRACK].
        The earlier expression
        \[
            Z_{\mathrm{eff}} \sim \frac{P_{\mathrm{core}}\rc}{\vnorm\hbar}
        \]
        should \emph{not} be canonised as written. Its dimensions are
        \[
            \left[
                \frac{P_{\mathrm{core}}\rc}{\vnorm\hbar}
            \right]
            =
            \mathrm{m^{-3}},
        \]
        so it is not an impedance and not dimensionless.
        
        A Canon-compatible replacement is to define either:
        
        \begin{enumerate}
            \item a dimensionless rigidity ratio,
            \item or an acoustic-like pressure-to-speed impedance.
        \end{enumerate}
    
    \subsection*{Dimensionless swirl-rigidity ratio}
        
        Let \(V_K\) be the effective active volume of a swirl-string configuration and \(P_K\) the pressure scale associated with its deformation. Define
        \begin{equation}
            \boxed{
                \Pi_K(\omega)
                =
                \frac{P_K V_K}{\hbar\omega}
            }
            \qquad
            [\mathrm{RESEARCH\text{-}TRACK}].
            \label{eq:dimensionless_swirl_rigidity}
        \end{equation}
        This compares stored mechanical energy \(P_KV_K\) to the quantum energy scale \(\hbar\omega\). It is dimensionless:
        \[
            [P_KV_K]=\mathrm{J},
            \qquad
            [\hbar\omega]=\mathrm{J}.
        \]
    
    \subsection*{Acoustic-like swirl impedance}
        
        An alternative intensive impedance is
        \begin{equation}
            \boxed{
                Z_{\mathrm{swirl}}
                =
                \frac{P_K}{v_K}
            }
            \label{eq:swirl_acoustic_impedance}
        \end{equation}
        with units
        \[
            [Z_{\mathrm{swirl}}]
            =
            \frac{\mathrm{kg\,m^{-1}\,s^{-2}}}{\mathrm{m\,s^{-1}}}
            =
            \mathrm{kg\,m^{-2}\,s^{-1}},
        \]
        the same units as acoustic impedance. This object measures resistance to velocity-driven pressure excitation.
    
    \subsection*{Connection to linewidth and quality factor}
        
        A resonant mode with angular frequency \(\omega_K\) and quality factor \(Q_K\) has linewidth
        \begin{equation}
            \gamma_K
            =
            \frac{\omega_K}{2Q_K}.
            \label{eq:linewidth_quality_factor}
        \end{equation}
        A minimal phenomenological relation is
        \begin{equation}
            Q_K
            =
            Q_0\,\Pi_K^\eta,
            \qquad
            \eta>0,
            \label{eq:Q_rigidity_ansatz}
        \end{equation}
        so that larger stored-energy rigidity produces narrower response lines.
    
    \subsection*{Numerical check using canonical scales}
        
        Using
        \[
            \Fswirlmax = 29.053507\ \mathrm{N},
            \qquad
            \rc = 1.40897017\times10^{-15}\ \mathrm{m},
        \]
        define the core pressure scale
        \begin{equation}
            P_{\max}
            =
            \frac{\Fswirlmax}{\pi \rc^2}
            =
            4.65848920\times10^{30}\ \mathrm{Pa}.
            \label{eq:Pmax_numeric}
        \end{equation}
        For a horn-torus active volume
        \begin{equation}
            V_{\mathrm{horn}}
            =
            2\pi^2 \rc^3
            =
            5.52122107\times10^{-44}\ \mathrm{m^3},
            \label{eq:horn_volume_numeric}
        \end{equation}
        the stored pressure energy is
        \begin{equation}
            P_{\max}V_{\mathrm{horn}}
            =
            2.57205487\times10^{-13}\ \mathrm{J}.
            \label{eq:pressure_energy_numeric}
        \end{equation}
        At the canonical angular frequency
        \[
            \Omega_{\mathrm{SST}}
            =
            7.76344066\times10^{20}\ \mathrm{s^{-1}},
        \]
        we have
        \begin{equation}
            \hbar\Omega_{\mathrm{SST}}
            =
            8.18710572\times10^{-14}\ \mathrm{J}
            =
            510998.946\ \mathrm{eV}.
            \label{eq:hbarOmega_numeric}
        \end{equation}
        Therefore,
        \begin{equation}
            \Pi_{\mathrm{horn}}
            =
            \frac{P_{\max}V_{\mathrm{horn}}}
            {\hbar\Omega_{\mathrm{SST}}}
            =
            3.14159235
            \approx \pi.
            \label{eq:Pi_horn_numeric}
        \end{equation}
    
    \subsection*{Interpretation}
        
        Equation~\eqref{eq:Pi_horn_numeric} is not yet a derivation of a particle mass or coupling constant. It is a useful dimensional coincidence produced by canonical SST scales and the horn-torus active-volume choice. It should be labelled:
        \[
            \boxed{
                \text{[CALIBRATED / RESEARCH-TRACK NUMERICAL STRUCTURE]}
            }
        \]
        until derived from the SST action or from a topological minimization principle.
    
    \subsection*{Falsifiability}
        
        If \(\Pi_K\) controls linewidth, then families of analog swirl-string excitations should satisfy
        \[
            \gamma_K \propto \omega_K \Pi_K^{-\eta}.
        \]
        A measured absence of correlation between active-volume rigidity and linewidth would falsify Eq.~\eqref{eq:Q_rigidity_ansatz}.

% ============================================================
\section{Layered Relaxation and Multi-Mode Decay}
    \label{app:layered-relaxation}
    
    \subsection*{Status and warning}
        
        \noindent
        \textbf{Status:} [RESEARCH-TRACK].
        This appendix preserves the useful part of the delayed-decay idea: a multi-layer swirl-string system may relax through multiple modes. It explicitly rejects the naive identification
        \[
            \tau_i = \frac{r_i}{\vnorm}
        \]
        with observed delayed-neutron group lifetimes. For nuclear-scale radii, this gives \(\tau_i\sim 10^{-21}\ \mathrm{s}\), whereas delayed-neutron groups are macroscopic nuclear decay times. Therefore direct radial-transit mapping is dimensionally possible but physically wrong in scale.
    
    \subsection*{General multi-mode relaxation}
        
        If a perturbed swirl-string state has several metastable channels, its observable relaxation can be expanded as
        \begin{equation}
            \boxed{
                A(t)
                =
                \sum_{i=1}^{N}
                A_i
                e^{-t/\tau_i}
                \cos(\omega_i t+\phi_i)
            }
            \qquad
            [\mathrm{ORTHODOX\ form;\ RESEARCH\text{-}TRACK\ SST\ interpretation}].
            \label{eq:multimode_relaxation}
        \end{equation}
        The non-oscillatory limit is
        \begin{equation}
            A(t)
            =
            \sum_{i=1}^{N}
            A_i e^{-t/\tau_i}.
            \label{eq:multigroup_decay}
        \end{equation}
    
    \subsection*{Pole interpretation}
        
        Equation~\eqref{eq:multimode_relaxation} corresponds to a response function with poles
        \begin{equation}
            \omega
            =
            \omega_i
            -
            \frac{i}{\tau_i}.
            \label{eq:response_poles}
        \end{equation}
        Thus, each decay time \(\tau_i\) is a lifetime of a response pole, not necessarily a physical radial crossing time.
    
    \subsection*{Allowed SST interpretation}
        
        In SST, a layered or nested swirl-string configuration may contain:
        \begin{itemize}
            \item a core-scale response,
            \item a sheath-scale response,
            \item a linking/helicity response,
            \item a global Swirl-Clock phase response.
        \end{itemize}
        The decay constants \(\tau_i\) should therefore be treated as \emph{effective metastable relaxation times}. A safe parametrization is
        \begin{equation}
            \tau_i
            =
            \frac{Q_i}{\omega_i},
            \label{eq:tau_Q_over_omega}
        \end{equation}
        where \(Q_i\) is the quality factor of the \(i\)-th mode.
    
    \subsection*{Critical scale check}
        
        For the canonical core scale,
        \begin{equation}
            \tau_c
            =
            \frac{\rc}{\vnorm}
            =
            1.28808868\times10^{-21}\ \mathrm{s}.
            \label{eq:core_crossing_time_numeric}
        \end{equation}
        Therefore, an observed lifetime of \(1\ \mathrm{s}\) would require
        \begin{equation}
            Q
            \sim
            \omega_i\tau_i
            \sim
            7.76\times10^{20}.
            \label{eq:large_Q_warning}
        \end{equation}
        Such a huge \(Q\)-factor is not impossible as a formal metastability parameter, but it cannot be interpreted as a simple geometric shell crossing.
    
    \subsection*{Experimental analogy}
        
        Multi-exponential decay models are common in nuclear delayed-neutron kinetics and in linear response theory. SST may use this only as an analogy unless a topological barrier calculation derives the \(Q_i\) or \(\tau_i\) values independently.
    
    \subsection*{Falsifiability}
        
        The layered relaxation ansatz predicts that perturbing a structured target should produce reproducible decay constants \(\tau_i\) independent of total pulse amplitude, provided the response remains linear. If the apparent \(\tau_i\) vary strongly with drive amplitude, heating, or detector threshold, the model is likely observing instrumental or thermal relaxation rather than swirl-string metastability.

% ============================================================
\section{Summary of Canon Placement}
    \label{app:canon-placement-summary}
    
    The four additions should be placed as follows:
    
    \begin{center}
        \begin{tabular}{|p{0.25\linewidth}|p{0.22\linewidth}|p{0.42\linewidth}|}
            \hline
            \textbf{Appendix} & \textbf{Canon status} & \textbf{Recommended placement} \\
            \hline
            Resonance Selection Principle &
            [RESEARCH-TRACK] strong candidate &
            CANON-v0.8.1 companion appendix; possible future main-canon principle after validation. \\
            \hline
            Time-Domain Kernel Response &
            [RESEARCH-TRACK] strong candidate &
            Near Swirl Clock, delay-mode selection, or quantum-response sections. \\
            \hline
            Swirl Impedance and Linewidth &
            [RESEARCH-TRACK] with corrected dimensions &
            Use as a response/linewidth ansatz; do not canonise the older dimensionally incorrect formula. \\
            \hline
            Layered Relaxation &
            [RESEARCH-TRACK] analogy only &
            Keep as metastable multi-mode response; reject direct delayed-neutron shell-crossing interpretation. \\
            \hline
        \end{tabular}
    \end{center}

% ============================================================
    \begin{thebibliography}{99}
        
        \bibitem{Kubo1957}
        R. Kubo. (1957).
        \textit{Statistical-Mechanical Theory of Irreversible Processes. I. General Theory and Simple Applications to Magnetic and Conduction Problems}.
        Journal of the Physical Society of Japan \textbf{12}, 570--586.
        doi: \href{https://doi.org/10.1143/JPSJ.12.570}{10.1143/JPSJ.12.570}.
        
        \bibitem{BreitWigner1936}
        G. Breit and E. Wigner. (1936).
        \textit{Capture of Slow Neutrons}.
        Physical Review \textbf{49}, 519--531.
        doi: \href{https://doi.org/10.1103/PhysRev.49.519}{10.1103/PhysRev.49.519}.
        
        \bibitem{Batchelor1967}
        G. K. Batchelor. (1967).
        \textit{An Introduction to Fluid Dynamics}.
        Cambridge University Press.
        
        \bibitem{Saffman1992}
        P. G. Saffman. (1992).
        \textit{Vortex Dynamics}.
        Cambridge University Press.
        doi: \href{https://doi.org/10.1017/CBO9780511624063}{10.1017/CBO9780511624063}.
        
        \bibitem{Helmholtz1858}
        H. von Helmholtz. (1858).
        \textit{\"Uber Integrale der hydrodynamischen Gleichungen, welche den Wirbelbewegungen entsprechen}.
        Journal f\"ur die reine und angewandte Mathematik \textbf{55}, 25--55.
        doi: \href{https://doi.org/10.1515/crll.1858.55.25}{10.1515/crll.1858.55.25}.
        
        \bibitem{Kelvin1867}
        W. Thomson, Lord Kelvin. (1867).
        \textit{On Vortex Atoms}.
        Proceedings of the Royal Society of Edinburgh \textbf{6}, 94--105.
        
        \bibitem{Onsager1949}
        L. Onsager. (1949).
        \textit{Statistical Hydrodynamics}.
        Il Nuovo Cimento \textbf{6}, 279--287.
        doi: \href{https://doi.org/10.1007/BF02780991}{10.1007/BF02780991}.
        
        \bibitem{Feynman1955}
        R. P. Feynman. (1955).
        \textit{Application of Quantum Mechanics to Liquid Helium}.
        In C. J. Gorter (ed.), \textit{Progress in Low Temperature Physics}, Vol. 1, pp. 17--53.
        North-Holland.
        doi: \href{https://doi.org/10.1016/S0079-6417(08)60077-3}{10.1016/S0079-6417(08)60077-3}.
        
        \bibitem{Bracewell2000}
        R. N. Bracewell. (2000).
        \textit{The Fourier Transform and Its Applications}.
        3rd ed., McGraw--Hill.
        
        \bibitem{Keepin1965}
        G. R. Keepin. (1965).
        \textit{Physics of Nuclear Kinetics}.
        Addison-Wesley.
        
        \bibitem{Dhibar2018}
        M. Dhibar, I. Mazumdar, G. Anil Kumar, S. P. Weppner, A. K. Rhine Kumar, S. M. Patel, and P. B. Chavan. (2018).
        \textit{Study of \(^{12}\mathrm C(p,p'\gamma)^{12}\mathrm C\) reaction}.
        arXiv:1806.02126.
        \href{https://arxiv.org/abs/1806.02126}{https://arxiv.org/abs/1806.02126}.
        
        \bibitem{Rose2018}
        P. B. Rose Jr. et al. (2018).
        \textit{High-energy gamma rays resulting from low-energy nuclear reactions}.
        Physical Review C \textbf{97}, 064305.
        doi: \href{https://doi.org/10.1103/PhysRevC.97.064305}{10.1103/PhysRevC.97.064305}.
    
    \end{thebibliography}



\section{Research Track: Nested Vortex--Antivortex States as Entropy-Minimizing Swirl Structures}
    
    \subsection{Motivation}
        
        Consider a coherent swirl structure consisting of an outer circulation region
        with vorticity $\omega_{\mathrm{out}}>0$ and an embedded inner core with
        opposite vorticity
        
        \[
            \omega_{\mathrm{in}}<0.
        \]
        
        Such configurations appear naturally in fluid dynamics, magnetic flux ropes,
        and vortex-ring interactions.
        
        Within SST, opposite swirl chirality corresponds to opposite temporal
        orientation of the Swirl Clock:
        
        \[
            S_t^{\circlearrowleft}
            \quad\leftrightarrow\quad
            \text{matter},
        \]
        
        \[
            S_t^{\circlearrowright}
            \quad\leftrightarrow\quad
            \text{antimatter}.
        \]
    
    \subsection{Helicity Cancellation}
        
        The total helicity may be decomposed as
        
        \[
            H_{\mathrm{tot}}
            =
            H_{\mathrm{out}}
            +
            H_{\mathrm{in}}.
        \]
        
        Because the embedded structure carries opposite chirality,
        
        \[
            H_{\mathrm{in}}<0.
        \]
        
        Hence
        
        \[
            |H_{\mathrm{tot}}|
            <
            |H_{\mathrm{out}}|.
        \]
        
        The configuration therefore possesses reduced net topological complexity.
    
    \subsection{Entropy Hypothesis}
        
        We introduce the conjecture
        
        \[
            S_{\mathrm{top}}
            \propto
            |H|,
        \]
        
        where $S_{\mathrm{top}}$ denotes topological entropy.
        
        Consequently,
        
        \[
            S_{\mathrm{top}}^{\mathrm{nested}}
            <
            S_{\mathrm{top}}^{\mathrm{single}},
        \]
        
        suggesting that nested vortex--antivortex states may represent preferred
        low-energy attractors of the swirl medium.
    
    \subsection{Status}
        
        \textbf{Research Track.}
        
        Not yet derived from the canonical SST Lagrangian.
        Proposed as a candidate mechanism for stability enhancement and
        matter--antimatter coexistence.
    
    
    \section{Research Track: Helicity Conversion and Torsional Radiation}
    
    \subsection{Motivation}
        
        Experiments and simulations of knotted vortex structures indicate that
        reconnection events frequently preserve a substantial fraction of helicity.
        
        Rather than disappearing, helicity is redistributed between knotting,
        linking, writhe, and twist.
    
    \subsection{Helicity Partition}
        
        Write total helicity as
        
        \[
            H
            =
            H_{\mathrm{knot}}
            +
            H_{\mathrm{twist}}
            +
            H_{\mathrm{link}}.
        \]
        
        During reconnection:
        
        \[
            H_{\mathrm{knot}}
            \downarrow
        \]
        
        while
        
        \[
            H_{\mathrm{twist}}
            \uparrow .
        \]
        
        Thus
        
        \[
            H_{\mathrm{tot}}
            \approx
            \mathrm{const}.
        \]
    
    \subsection{SST Interpretation}
        
        Within SST, mass-bearing T-phase structures correspond to localized knot
        helicity.
        
        Radiative R-phase excitations correspond to propagating torsional modes.
        
        We therefore conjecture
        
        \[
            H_{\mathrm{knot}}
            \rightarrow
            H_{\mathrm{twist}}
            \rightarrow
            \gamma_R ,
        \]
        
        where $\gamma_R$ denotes an R-phase torsional pulse.
    
    \subsection{Mass--Radiation Conversion Chain}
        
        The proposed conversion pathway is
        
        \[
            M
            \leftrightarrow
            H_{\mathrm{knot}}
            \leftrightarrow
            H_{\mathrm{twist}}
            \leftrightarrow
            \gamma_R.
        \]
        
        In this picture:
        
        \begin{itemize}
            \item stable particles store helicity as topology,
            \item reconnections release helicity as torsional twist,
            \item torsional twist propagates as photon-like R-phase radiation.
        \end{itemize}
    
    \subsection{Connection to Photon Ontology}
        
        This hypothesis is consistent with the SST identification
        
        \[
            \text{photon}
            =
            \text{torsional R-phase pulse},
        \]
        
        and provides a possible mechanism for
        
        \begin{itemize}
            \item particle decay,
            \item annihilation,
            \item radiation emission,
            \item energy transport.
        \end{itemize}
    
    \subsection{Falsifiable Prediction}
        
        If the hypothesis is correct, vortex reconnection experiments should show
        
        \[
            \Delta H_{\mathrm{knot}}
            \approx
            -
            \Delta H_{\mathrm{twist}}
        \]
        
        with emitted torsional wave packets carrying the missing helicity.
    
    \subsection{Status}
        
        \textbf{Research Track.}
        
        Motivated by helicity-conservation studies in knotted vortex systems.
        Requires derivation from the SST radiation sector.
    
    
    \section{Research Track: Kairos Surfaces as Chirality Transition Layers}
    
    \subsection{Definition}
        
        The Temporal Ontology introduces the Kairos event
        
        \[
            \kappa,
        \]
        
        representing an irreversible topological transition.
        
        We extend this concept spatially.
        
        Let
        
        \[
            \omega(\mathbf{x})=0
        \]
        
        define a surface separating opposite chiral domains:
        
        \[
            \omega>0
            \quad\leftrightarrow\quad
            S_t^{\circlearrowleft},
        \]
        
        \[
            \omega<0
            \quad\leftrightarrow\quad
            S_t^{\circlearrowright}.
        \]
        
        We define the locus
        
        \[
            \Sigma_\kappa
            =
            \{
            \mathbf{x}
            \;|\;
            \omega(\mathbf{x})=0
            \}
        \]
        
        as a \emph{Kairos Surface}.
    
    \subsection{Physical Interpretation}
        
        Across $\Sigma_\kappa$ the swirl orientation reverses sign.
        
        The surface therefore acts as a boundary between distinct temporal sectors.
        
        \[
            S_t^{\circlearrowleft}
            \longleftrightarrow
            S_t^{\circlearrowright}.
        \]
        
        Such regions may act as:
        
        \begin{itemize}
            \item annihilation interfaces,
            \item vortex reconnection sites,
            \item phase-transition boundaries,
            \item chirality-conversion layers.
        \end{itemize}
    
    \subsection{Kairos Criterion}
        
        A local Kairos transition is conjectured whenever
        
        \[
            \omega
            \rightarrow
            0
        \]
        
        and
        
        \[
            \nabla\omega
            \neq
            0.
        \]
        
        The gradient supplies a preferred transition direction.
    
    \subsection{Status}
        
        \textbf{Research Track.}
        
        Consistent with the Temporal Ontology but not yet derived from the SST field
        equations.

\section{Euler-Decomposed Swirl Gravity and Probe Transport}
\label{sec:appendix_euler_probe_transport}

\subsection{Purpose and status}
    This appendix separates the canonical scalar pressure acceleration from
    orientation-dependent transverse transport effects. The pressure law is retained
    as the canon-level bridge, while Magnus-type terms are treated as probe-level
    corrections.

\subsection{Canonical pressure acceleration}
    \begin{align}
        \mathbf{a}_{P}
        =
        -\frac{1}{\rho_{\!f}}\nabla p_{\mathrm{swirl}}.
    \end{align}

\subsection{Euler decomposition}
    For an incompressible inviscid background flow,
    \begin{align}
        \frac{\partial \mathbf{u}}{\partial t}
        +
        \boldsymbol{\omega}\times\mathbf{u}
        +
        \nabla\left(\frac{u^2}{2}\right)
        =
        -\frac{1}{\rho_{\!f}}\nabla p_{\mathrm{swirl}}.
    \end{align}

\subsection{Filament Magnus transport}
    For a circulation-carrying swirl-string probe $K$,
    \begin{align}
        \mathbf{F}_{\mathrm{M}}^{(K)}
        =
        \int_K
        \rho_{\!f}\Gamma_K
        \mathbf{T}(s)\times
        \left[
            \mathbf{U}_K(s)-\mathbf{u}(\mathbf{X}(s))
        \right]ds.
    \end{align}

\subsection{Curvature self-transport}
    In the local-induction approximation,
    \begin{align}
        \mathbf{f}_{\kappa}
        \simeq
        -\frac{\rho_{\!f}\Gamma_K^2}{4\pi}
        \Lambda_K\kappa\,\mathbf{N}.
    \end{align}

\subsection{Status}
    The scalar pressure term is canon-level. The Magnus and curvature terms are
    research-track transport corrections until a universal coupling law for
    macroscopic matter is derived.
    
    % ============================================================
% Research Track Appendix: Swirl--Electromagnetic Normalization
% ============================================================
    

\section{Research Track: Swirl--Electromagnetic Normalization by Vorticity}
\label{app:research_swirl_em_vorticity}

% ------------------------------------------------------------
% Local macro safety block
% ------------------------------------------------------------
\providecommand{\swirlarrow}{\boldsymbol{\circlearrowleft}}
\providecommand{\vswirl}{\mathbf{v}_{\!\boldsymbol{\circlearrowleft}}}
\providecommand{\vnorm}{\lVert\mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert}
\providecommand{\rhoF}{\rho_{\!f}}
\providecommand{\rhoE}{\rho_{\!E}}
\providecommand{\rhoM}{\rho_{\!m}}
\providecommand{\rc}{r_c}
\providecommand{\Fmax}{F_{\max}^{\rm swirl}}

\subsection{Purpose and Status}
    
    This appendix records a research-track extension of Swirl--String Theory
    (SST) in which electromagnetic field variables are interpreted as
    SI-normalized coarse-grained measures of swirl kinematics.  The result is
    not proposed as a replacement of Maxwell's equations at the level of
    observed electrodynamics.  Instead, it is a constitutive bridge between
    the SST swirl-medium variables and the ordinary electromagnetic variables
    \(\mathbf{E}\), \(\mathbf{B}\), \(\mathbf{A}\), \(\mathbf{D}\), and
    \(\mathbf{H}\).
    
    The central observation is that a dimensionally correct identification of
    the vector potential is obtained by scaling the local swirl velocity by the
    electron mass-to-charge ratio:
    \begin{equation}
        \boxed{
            \mathbf{A}_{\rm SI}
            =
            \frac{m_e}{e}\,
            \vswirl
        } .
        \label{eq:swirl_vector_potential_bridge}
    \end{equation}
    Since \([\mathbf{A}]={\rm kg\,m\,C^{-1}\,s^{-1}}\) and
    \([(m_e/e)\vswirl]={\rm kg\,C^{-1}}\cdot{\rm m\,s^{-1}}\), this equation
    has the correct SI units.
    
    The associated magnetic field is then
    \begin{equation}
        \boxed{
            \mathbf{B}_{\rm SST}
            =
            \nabla\times\mathbf{A}_{\rm SI}
            =
            \frac{m_e}{e}\,
            \boldsymbol{\omega}
        },
        \qquad
        \boldsymbol{\omega}
        =
        \nabla\times\vswirl .
        \label{eq:B_from_vorticity}
    \end{equation}
    This is the cleanest form of the statement that magnetic flux arises from
    structured vorticity, not merely from charge flow.  The charge-current
    description remains the effective macroscopic description; the SST
    interpretation places the microscopic origin of the magnetic field in
    quantized circulation and vorticity.

\subsection{Why Direct Vorticity Source Terms Are Rejected}
    
    Earlier trial equations attempted to write vorticity as an additional
    source term directly inside Maxwell's equations, for example terms of the
    schematic form
    \begin{equation}
        \nabla\cdot\mathbf{E}
        \sim
        \frac{\rho}{\varepsilon_0}
        +
        \frac{F_{\max}\omega}{\vnorm \rc^2},
        \qquad
        \nabla\times\mathbf{B}
        \sim
        \mu_0\mathbf{J}
        +
        \frac{\vnorm\hbar}{q\rc^2}\boldsymbol{\Omega}.
        \label{eq:rejected_direct_source_terms}
    \end{equation}
    These forms are not retained as canonical equations because the added
    terms do not generally have the SI dimensions required by Maxwell's
    source equations.  In particular,
    \(\nabla\cdot\mathbf{E}\) has units
    \({\rm V\,m^{-2}}\), while the proposed vorticity-force expression does
    not reduce to this unit without an additional calibrated constitutive
    coefficient.  Likewise, the Ampere--Maxwell equation requires units of
    \({\rm T\,m^{-1}}\), not a force-per-charge expression multiplied by an
    unfixed vorticity vector.
    
    Therefore, the research-track correction is:
    
    \begin{quote}
        Vorticity should not be inserted as an uncalibrated extra Maxwell source.
        It should enter through a constitutive identification of the potential and
        field variables.
    \end{quote}
    
    The retained bridge is thus Eq.~\eqref{eq:swirl_vector_potential_bridge},
    not Eq.~\eqref{eq:rejected_direct_source_terms}.

\subsection{Electric Field from Time-Dependent Swirl}
    
    With the vector potential bridge established, the electric field follows
    from the usual potential relation:
    \begin{equation}
        \boxed{
            \mathbf{E}_{\rm SST}
            =
            -\frac{\partial\mathbf{A}_{\rm SI}}{\partial t}
            -
            \nabla\Phi_{\rm SST}
            =
            -\frac{m_e}{e}
            \frac{\partial\vswirl}{\partial t}
            -
            \nabla\Phi_{\rm SST}
        } .
        \label{eq:E_from_time_dependent_swirl}
    \end{equation}
    Here \(\Phi_{\rm SST}\) is the SI-normalized scalar potential associated
    with compressive, pressure-like, or boundary-induced swirl response.  In
    strictly incompressible regions, \(\Phi_{\rm SST}\) should be interpreted
    as an effective potential imposed by boundary constraints, topology, and
    coarse-grained pressure balance rather than by local volume compression.
    
    Equation~\eqref{eq:E_from_time_dependent_swirl} gives the SST analogue of
    Faraday induction: time-varying swirl produces an electric field.  Taking
    the curl gives
    \begin{equation}
        \nabla\times\mathbf{E}_{\rm SST}
        =
        -
        \frac{\partial}{\partial t}
        \left(
            \nabla\times\mathbf{A}_{\rm SI}
        \right)
        =
        -
        \frac{\partial\mathbf{B}_{\rm SST}}{\partial t},
        \label{eq:faraday_from_swirl}
    \end{equation}
    since \(\nabla\times\nabla\Phi_{\rm SST}=0\).  Thus the ordinary Faraday
    law is preserved exactly.

\subsection{Maxwell Equations as Effective Medium Equations}
    
    The correct research-track formulation is to retain Maxwell's equations
    in their macroscopic form while adding swirl-induced polarization and
    magnetization terms:
    \begin{align}
        \nabla\cdot\mathbf{D}_{\rm SST}
        &=
        \rho_{\rm free},
        \label{eq:SST_gauss_D}
        \\
        \nabla\cdot\mathbf{B}_{\rm SST}
        &=
        0,
        \label{eq:SST_gauss_B}
        \\
        \nabla\times\mathbf{E}_{\rm SST}
        &=
        -
        \frac{\partial\mathbf{B}_{\rm SST}}{\partial t},
        \label{eq:SST_faraday}
        \\
        \nabla\times\mathbf{H}_{\rm SST}
        &=
        \mathbf{J}_{\rm free}
        +
        \frac{\partial\mathbf{D}_{\rm SST}}{\partial t}.
        \label{eq:SST_ampere}
    \end{align}
    The constitutive relations are
    \begin{align}
        \mathbf{D}_{\rm SST}
        &=
        \varepsilon_0\mathbf{E}_{\rm SST}
        +
        \mathbf{P}_{\rm swirl},
        \label{eq:D_constitutive_swirl}
        \\
        \mathbf{H}_{\rm SST}
        &=
        \frac{1}{\mu_0}\mathbf{B}_{\rm SST}
        -
        \mathbf{M}_{\rm swirl}.
        \label{eq:H_constitutive_swirl}
    \end{align}
    Here \(\mathbf{P}_{\rm swirl}\) and \(\mathbf{M}_{\rm swirl}\) encode the
    coarse-grained response of bound swirl structures, knot cores, circulating
    R-phase modes, and boundary-induced polarization.
    
    This formulation has an important advantage: it does not violate the
    observed Maxwell structure.  It instead interprets charge and current as
    effective descriptions of deeper circulation and vorticity organization.

\subsection{Core-Scale Calibration and the QED Critical Field}
    
    At the SST core scale the characteristic angular vorticity scale is
    \begin{equation}
        \Omega_{\rm core}
        =
        \frac{\vnorm}{\rc}.
        \label{eq:omega_core}
    \end{equation}
    Using the canonical SST values
    \begin{equation}
        \vnorm
        =
        1.09384563\times10^{6}\ {\rm m\,s^{-1}},
        \qquad
        \rc
        =
        1.40897017\times10^{-15}\ {\rm m},
    \end{equation}
    one obtains
    \begin{equation}
        \Omega_{\rm core}
        =
        7.76344066\times10^{20}\ {\rm s^{-1}}.
        \label{eq:omega_core_numeric}
    \end{equation}
    The corresponding SST magnetic field scale is
    \begin{equation}
        B_{\rm core}^{\rm SST}
        =
        \frac{m_e}{e}\Omega_{\rm core}.
        \label{eq:Bcore_sst}
    \end{equation}
    Numerically,
    \begin{equation}
        \frac{m_e}{e}
        =
        5.68563010\times10^{-12}\ {\rm kg\,C^{-1}},
    \end{equation}
    and therefore
    \begin{equation}
        \boxed{
            B_{\rm core}^{\rm SST}
            =
            4.41400519\times10^{9}\ {\rm T}
        } .
        \label{eq:Bcore_numeric}
    \end{equation}
    
    This is not an arbitrary scale.  The standard QED critical magnetic field
    is
    \begin{equation}
        B_{\rm QED}
        =
        \frac{m_e^2c^2}{e\hbar}
        =
        4.41400522\times10^{9}\ {\rm T}.
        \label{eq:Bqed}
    \end{equation}
    Thus
    \begin{equation}
        \frac{B_{\rm core}^{\rm SST}}{B_{\rm QED}}
        =
        0.999999993.
        \label{eq:Bcore_Bqed_ratio}
    \end{equation}
    The equality follows analytically from the SST Compton-core relation
    \begin{equation}
        \lambda_c
        =
        \frac{2\pi c\rc}{\vnorm},
        \label{eq:compton_core_relation}
    \end{equation}
    together with the standard identity
    \begin{equation}
        \lambda_c
        =
        \frac{2\pi\hbar}{m_ec}.
    \end{equation}
    Equating these two expressions gives
    \begin{equation}
        \frac{\vnorm}{\rc}
        =
        \frac{m_ec^2}{\hbar}.
        \label{eq:omega_core_compton}
    \end{equation}
    Substitution into Eq.~\eqref{eq:Bcore_sst} yields
    \begin{equation}
        B_{\rm core}^{\rm SST}
        =
        \frac{m_e}{e}
        \frac{m_ec^2}{\hbar}
        =
        \frac{m_e^2c^2}{e\hbar}
        =
        B_{\rm QED}.
        \label{eq:Bcore_equals_Bqed}
    \end{equation}
    
    This is the strongest numerical result of this appendix: the SI-normalized
    vorticity bridge naturally reproduces the Schwinger/QED magnetic field
    scale at the SST core.
    
    The associated electric field scale is
    \begin{equation}
        E_{\rm core}^{\rm SST}
        =
        cB_{\rm core}^{\rm SST}
        =
        1.32328547\times10^{18}\ {\rm V\,m^{-1}},
        \label{eq:Ecore_numeric}
    \end{equation}
    which matches the usual Schwinger electric field
    \begin{equation}
        E_{\rm Schwinger}
        =
        \frac{m_e^2c^3}{e\hbar}.
        \label{eq:Schwinger_field}
    \end{equation}

\subsection{Corrected Maximum Force Relation}
    
    The same calibration fixes the correct factor in the SST maximum-force
    relation.  The expression
    \begin{equation}
        \frac{\vnorm\hbar}{\rc^2}
    \end{equation}
    has units of force, but it is twice the canonical force scale.  The
    consistent relation is
    \begin{equation}
        \boxed{
            \Fmax
            =
            \frac{\vnorm\hbar}{2\rc^2}
        } .
        \label{eq:Fmax_corrected}
    \end{equation}
    Using the canonical constants gives
    \begin{equation}
        \Fmax
        =
        29.0535098\ {\rm N},
    \end{equation}
    in agreement with the canonical value
    \begin{equation}
        F_{\max}^{\rm swirl}
        \simeq
        29.053507\ {\rm N}.
    \end{equation}
    The electron rest energy relation is then
    \begin{equation}
        \boxed{
            m_ec^2
            =
            2\Fmax \rc
        } .
        \label{eq:electron_energy_force_core}
    \end{equation}
    Equivalently,
    \begin{equation}
        m_e
        =
        \frac{2\Fmax\rc}{c^2}.
    \end{equation}
    Numerically,
    \begin{equation}
        \frac{2F_{\max}^{\rm swirl}\rc}{c^2}
        =
        9.10938\times10^{-31}\ {\rm kg},
    \end{equation}
    which matches the electron mass within the stated calibration precision.

\subsection{Photon and R-Phase Normal Modes}
    
    A second research-track result is that photon frequency should not be
    introduced through an ad hoc energy-density law of the form
    \begin{equation}
        u(r,\omega,T)
        \propto
        \frac{F_{\max}\omega^3}{\vnorm r^2}
        \frac{1}{\exp(\hbar\omega/k_BT)-1}.
        \label{eq:rejected_photon_density}
    \end{equation}
    This expression is not retained as a fundamental energy density because
    its bare prefactor does not have the units of energy per volume without
    additional geometric or constitutive factors.
    
    Instead, the research-track photon sector is formulated as a normal-mode
    condition on a closed or quasi-closed R-phase path:
    \begin{equation}
        \boxed{
            k_n
            =
            \frac{2\pi n}{L_{\rm eff}(K)},
            \qquad
            \omega_n
            =
            c_\gamma k_n
            =
            \frac{2\pi n c_\gamma}{L_{\rm eff}(K)}
        } .
        \label{eq:photon_frequency_topological_path}
    \end{equation}
    Here \(L_{\rm eff}(K)\) is the effective optical/swirl path length of the
    supporting configuration \(K\), and \(c_\gamma\) is the propagation speed
    of the R-phase excitation.  In the vacuum limit one expects
    \(c_\gamma=c\).  For a circular ring of radius \(R\),
    \begin{equation}
        L_{\rm eff}=2\pi R,
    \end{equation}
    so that
    \begin{equation}
        \boxed{
            \omega_n
            =
            \frac{n c_\gamma}{R}
        } .
        \label{eq:ring_photon_frequency}
    \end{equation}
    This gives a clean formulation of the statement:
    
    \begin{quote}
        Photon frequency depends on the supporting swirl-ring or path structure.
    \end{quote}
    
    For knotted, linked, or boundary-deformed paths, \(L_{\rm eff}(K)\) may
    include writhe, torsion, self-linking, and medium-response corrections:
    \begin{equation}
        L_{\rm eff}(K)
        =
        L(K)
        +
        \Delta L_{\rm writhe}
        +
        \Delta L_{\rm torsion}
        +
        \Delta L_{\rm boundary}
        +
        \Delta L_{\rm medium}.
        \label{eq:effective_path_length_decomposition}
    \end{equation}
    This places the photon sector in the same mathematical family as the SST
    delay-loop and mode-selection principles.

\subsection{Kelvin Impulse Bridge}
    
    For a thin circular swirl ring with circulation \(\Gamma\), major radius
    \(R\), and core radius \(a\), the classical ring scalings are
    \begin{align}
        E_{\rm ring}
        &=
        \frac{1}{2}\rhoF\Gamma^2 R
        \left[
            \ln\left(\frac{8R}{a}\right)-\alpha_{\rm ring}
        \right],
        \label{eq:ring_energy}
        \\
        P_{\rm ring}
        &=
        \rhoF\Gamma\pi R^2,
        \label{eq:ring_impulse}
        \\
        V_{\rm ring}
        &=
        \frac{\Gamma}{4\pi R}
        \left[
            \ln\left(\frac{8R}{a}\right)-\beta_{\rm ring}
        \right].
        \label{eq:ring_velocity}
    \end{align}
    These relations provide a bridge between Kelvin's impulse theory and an
    SST momentum assignment.  A research-track identification may be written
    as
    \begin{equation}
        \boxed{
            \hbar k
            \leftrightarrow
            \eta_I P_{\rm swirl}
        },
        \qquad
        P_{\rm swirl}
        =
        \rhoF\Gamma\pi R^2.
        \label{eq:hbar_k_kelvin_impulse_bridge}
    \end{equation}
    The coefficient \(\eta_I\) is not a free fit parameter in the final
    theory.  It must be determined from the same SI-normalization that fixes
    Eqs.~\eqref{eq:swirl_vector_potential_bridge}--\eqref{eq:Bcore_equals_Bqed},
    or from an independently specified R-phase normalization.
    
    This suggests a useful research direction:
    
    \begin{quote}
        Planck momentum may correspond to normalized Kelvin impulse of a circulating
        R-phase excitation.
    \end{quote}

\subsection{Topology, Helicity, and Reconnection}
    
    The ideal SST sector assumes conservation of circulation, linkage, and
    helicity in the absence of reconnection.  This corresponds to the
    Helmholtz--Kelvin regime:
    \begin{equation}
        \frac{D\Gamma}{Dt}=0,
        \qquad
        \frac{D\mathcal{H}}{Dt}=0,
        \qquad
        \mathcal{H}
        =
        \int
        \vswirl\cdot\boldsymbol{\omega}\,d^3x.
        \label{eq:helicity_conservation}
    \end{equation}
    In this ideal sector, knot class is preserved.
    
    However, laboratory and numerical studies of knotted and linked fluid
    structures show that reconnection can transfer helicity between linking,
    twist, and writhe.  Therefore, SST should distinguish two regimes:
    
    \begin{align}
        \text{Ideal sector:}
        \quad
        &K(t)=K(0),
        \qquad
        \Gamma=\text{constant},
        \qquad
        \mathcal{H}=\text{constant},
        \label{eq:ideal_topology_sector}
        \\
        \text{Transition sector:}
        \quad
        &K_i\rightarrow K_j,
        \qquad
        \Delta\mathcal{H}
        =
        \Delta\mathcal{L}
        +
        \Delta\mathcal{T}
        +
        \Delta\mathcal{W},
        \label{eq:transition_topology_sector}
    \end{align}
    where \(\mathcal{L}\), \(\mathcal{T}\), and \(\mathcal{W}\) denote
    linking, twist, and writhe contributions respectively.
    
    This is relevant for the SST interpretation of measurement, decay, and
    mode conversion.  A stable particle-like excitation belongs to the ideal
    sector.  A decay or transition corresponds to a controlled failure of
    ideal topological conservation, usually through reconnection or boundary
    interaction.

\subsection{Pressure Envelopes and Spherical Equilibrium}
    
    The electromagnetic bridge above should be kept distinct from the
    pressure-envelope sector of SST.  The pressure sector is governed by the
    Bernoulli-type swirl balance
    \begin{equation}
        p
        +
        \frac{1}{2}\rhoF\vnorm^2
        =
        p_0,
        \label{eq:bernoulli_swirl_pressure}
    \end{equation}
    or, for a perturbation,
    \begin{equation}
        \Delta p
        =
        -
        \frac{1}{2}\rhoF
        \Delta\left(\vnorm^2\right).
        \label{eq:pressure_defect}
    \end{equation}
    This pressure defect can generate attraction-like behavior in the
    gravitational/swirl-clock sector.  It should not be confused with the
    magnetic vorticity bridge
    \begin{equation}
        \mathbf{B}_{\rm SST}
        =
        \frac{m_e}{e}\boldsymbol{\omega}.
    \end{equation}
    
    Thus the research-track separation is:
    
    \begin{align}
        \text{EM-like sector:}
        \quad
        &\mathbf{A}_{\rm SI}
        =
        \frac{m_e}{e}\vswirl,
        \qquad
        \mathbf{B}_{\rm SST}
        =
        \frac{m_e}{e}\boldsymbol{\omega},
        \label{eq:em_sector_summary}
        \\
        \text{pressure/gravity sector:}
        \quad
        &\Delta p
        =
        -
        \frac{1}{2}\rhoF
        \Delta(\vnorm^2),
        \qquad
        d\tau/dt
        =
        \sqrt{1-\vnorm^2/c^2}.
        \label{eq:pressure_gravity_sector_summary}
    \end{align}

\subsection{Negative-Temperature and Entropy Analogy}
    
    A further research-track idea is that bounded swirl ensembles may possess
    entropy-ordering behavior analogous to negative-temperature vortex states.
    This is not required for the electromagnetic normalization, but it may be
    useful in the classification of high-energy knot ensembles.
    
    A possible entropy functional is
    \begin{equation}
        S_{\rm swirl}
        =
        k_B\ln\Omega_{\rm topo}(E,\Gamma,\mathcal{H}),
        \label{eq:swirl_entropy}
    \end{equation}
    where \(\Omega_{\rm topo}\) counts accessible configurations at fixed
    energy, circulation, and helicity.  A negative-temperature-like regime
    would satisfy
    \begin{equation}
        \frac{\partial S_{\rm swirl}}{\partial E}
        <
        0.
        \label{eq:negative_temperature_condition}
    \end{equation}
    Such a regime would describe increasing order with increasing energy,
    for example through clustering, alignment, or coherent large-scale swirl
    organization.  This idea should remain in the research track until it is
    connected to a concrete SST Hamiltonian and a well-defined finite phase
    space.

\subsection{Research Claims Retained}
    
    The following claims are retained for research-track development:
    
    \begin{enumerate}
        \item Magnetic field strength can be SI-normalized as vorticity:
        \[
            \mathbf{B}_{\rm SST}
            =
            \frac{m_e}{e}\boldsymbol{\omega}.
        \]
        
        \item The vector potential is the SI-normalized swirl velocity:
        \[
            \mathbf{A}_{\rm SI}
            =
            \frac{m_e}{e}\vswirl.
        \]
        
        \item The core-scale SST magnetic field equals the QED critical field:
        \[
            B_{\rm core}^{\rm SST}
            =
            B_{\rm QED}
            =
            \frac{m_e^2c^2}{e\hbar}.
        \]
        
        \item The associated electric field equals the Schwinger scale:
        \[
            E_{\rm core}^{\rm SST}
            =
            cB_{\rm core}^{\rm SST}
            =
            \frac{m_e^2c^3}{e\hbar}.
        \]
        
        \item Photon frequency should be modeled by normal-mode closure:
        \[
            \omega_n
            =
            \frac{2\pi n c_\gamma}{L_{\rm eff}(K)}.
        \]
        
        \item Kelvin impulse may provide the bridge to photon momentum:
        \[
            \hbar k
            \leftrightarrow
            \eta_I\rhoF\Gamma\pi R^2.
        \]
        
        \item Reconnection belongs to a separate transition sector and should
        not be mixed with ideal knot conservation.
    \end{enumerate}

\subsection{Claims Not Retained as Canonical}
    
    The following statements are not retained as canonical equations:
    
    \begin{enumerate}
        \item Direct insertion of uncalibrated vorticity terms into Maxwell
        source equations.
        
        \item The statement that charge is unnecessary in all electromagnetic
        phenomena.  In this appendix charge remains the effective macroscopic
        source variable.
        
        \item The claim that Podkletnov-type gravitational shielding is
        established evidence for SST.  Such material may be mentioned only as
        speculative historical motivation, not as support for the canon.
        
        \item Photon energy-density laws containing
        \(F_{\max}\omega^3/(\vnorm r^2)\) without a complete dimensional and
        geometric derivation.
    \end{enumerate}

\subsection{Minimal Experimental Tests}
    
    The vorticity-normalization bridge suggests several falsifiable directions.
    
    \paragraph{1. Structured plasmonic or polaritonic media.}
        If electromagnetic fields are coupled to structured circulation-like
        degrees of freedom, then anisotropic or hyperbolic media should show
        geometry-dependent emission and propagation consistent with an effective
        path length \(L_{\rm eff}(K)\).
    
    \paragraph{2. Superfluid or quantum-fluid circulation.}
        Quantized circulation structures should generate measurable effective
        magnetization only when the system contains charged, spinful, or
        electromagnetically coupled degrees of freedom.  A neutral inviscid fluid
        alone should not emit ordinary electromagnetic fields unless an additional
        coupling channel exists.
    
    \paragraph{3. Ring-resonator delay tests.}
        The photon/R-phase normal-mode law predicts that frequency selection
        should scale as
        \[
            \omega_n
            \propto
            \frac{1}{L_{\rm eff}}.
        \]
        Boundary deformation, writhe-like path changes, or torsional loading
        should shift the selected resonances.
    
    \paragraph{4. Core-scale extrapolation.}
        The equality
        \[
            B_{\rm core}^{\rm SST}=B_{\rm QED}
        \]
        is not directly reachable in ordinary laboratory magnetic fields, but it
        can be tested indirectly by checking whether the same normalization
        reproduces Compton, Schwinger, and electron-rest-energy scales without
        additional tuning.

\subsection{Numerical Verification Table}

Using the canonical SST constants
\[
    \vnorm=1.09384563\times10^6\ {\rm m\,s^{-1}},
    \qquad
    \rc=1.40897017\times10^{-15}\ {\rm m},
\]
one obtains:

\begin{center}
    \begin{tabular}{lll}
        \hline
        Quantity & Expression & Numerical value \\
        \hline
        Core angular scale &
        \(\Omega_{\rm core}=\vnorm/\rc\) &
        \(7.76344066\times10^{20}\ {\rm s^{-1}}\) \\
        
        Mass-charge ratio &
        \(m_e/e\) &
        \(5.68563010\times10^{-12}\ {\rm kg\,C^{-1}}\) \\
        
        SST core magnetic field &
        \((m_e/e)\Omega_{\rm core}\) &
        \(4.41400519\times10^9\ {\rm T}\) \\
        
        QED critical magnetic field &
        \(m_e^2c^2/(e\hbar)\) &
        \(4.41400522\times10^9\ {\rm T}\) \\
        
        Ratio &
        \(B_{\rm core}^{\rm SST}/B_{\rm QED}\) &
        \(0.999999993\) \\
        
        SST electric field scale &
        \(cB_{\rm core}^{\rm SST}\) &
        \(1.32328547\times10^{18}\ {\rm V\,m^{-1}}\) \\
        
        Circulation quantum &
        \(2\pi\rc\vnorm\) &
        \(9.68361920\times10^{-9}\ {\rm m^2\,s^{-1}}\) \\
        
        Corrected force ceiling &
        \(\vnorm\hbar/(2\rc^2)\) &
        \(29.0535098\ {\rm N}\) \\
        
        Electron mass from force &
        \(2F_{\max}^{\rm swirl}\rc/c^2\) &
        \(9.10938\times10^{-31}\ {\rm kg}\) \\
        \hline
    \end{tabular}
\end{center}

\subsection{Conclusion}

The strongest result of this appendix is the SI-normalized vorticity
bridge
\[
    \mathbf{A}_{\rm SI}
    =
    \frac{m_e}{e}\vswirl,
    \qquad
    \mathbf{B}_{\rm SST}
    =
    \frac{m_e}{e}\boldsymbol{\omega}.
\]
It preserves Maxwell's equations as effective field equations, avoids
dimensionally invalid source terms, and reproduces the QED critical field
at the SST core scale.  For this reason it is suitable for inclusion in
the research-track sections of CANON-v0.8.x.

The proposed canonical status is:

\begin{center}
    \begin{tabular}{ll}
        \hline
        Result & Status \\
        \hline
        \(\mathbf{A}_{\rm SI}=(m_e/e)\vswirl\) & Research Track, strong candidate \\
        \(\mathbf{B}_{\rm SST}=(m_e/e)\boldsymbol{\omega}\) & Research Track, strong candidate \\
        \(B_{\rm core}^{\rm SST}=B_{\rm QED}\) & Numerically verified calibration result \\
        Direct vorticity source terms in Maxwell equations & Rejected / not canonical \\
        Photon frequency from \(L_{\rm eff}(K)\) & Research Track, compatible with delay-loop sector \\
        Kelvin impulse to \(\hbar k\) bridge & Research Track, unresolved normalization \\
        Negative-temperature swirl entropy & Speculative Research Track \\
        \hline
    \end{tabular}
\end{center}