\documentclass[a4paper,10pt]{letter}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\usepackage[margin=1in]{geometry}

\signature{Omar Iskandarani\\
Independent Researcher, Groningen\\
The Netherlands\\
ORCID: 0009-0006-1686-3961\\
Email: \href{mailto:info@omariskandarani.com}{info@omariskandarani.com}}

\address{Omar Iskandarani\\
Vinkenstraat 86A\\
9713 TK Groningen\\
The Netherlands}

\date{\today}

\begin{document}

    \begin{letter}{Point-by-Point Response to Technical Check\\
    \textit{Manuscript ID: f96b55e0-2fa2-4532-81cd-7b60d86b81da v1.0}\\
    \textbf{Title: Phase Locking and Discrete Mode Selection in Closed Circulation Loops}}

    \opening{Dear Editorial Support,}

    Thank you for the technical check and for identifying the required corrections. I have revised the manuscript accordingly. Please find the point-by-point response below.

    \medskip
    \noindent\textbf{1. Funding Declaration}\\
    \textbf{Comment:} Please provide a Funding Declaration in the manuscript. If there was no Funding, please state so.\\
    \textbf{Response:} Added a Declarations section to the manuscript, including a Funding subsection stating that no specific funding was received for this work.

    \medskip
    \noindent\textbf{2. Author Name Consistency}\\
    \textbf{Comment:} Some Author Names provided in the submission system are not provided in the manuscript (Omar Iskandarani). Please make sure the information in the manuscript and in the submission system is identical, including the order in which authors are mentioned.\\
    \textbf{Response:} Revised the manuscript front matter to use the Springer-compatible author metadata structure. The author name now appears as Omar Iskandarani, matching the submission system.

    \medskip
    \noindent\textbf{3. Abstract}\\
    \textbf{Comment:} Please provide an Abstract in the manuscript.\\
    \textbf{Response:} Confirmed and retained the abstract in the manuscript using the Springer-compatible \texttt{\string\abstract\{...\}} front matter format.

    \medskip
    Additionally, I corrected the manuscript front matter formatting to ensure compatibility with the Springer template metadata parsing (author/affiliation/email/abstract structure).

    No scientific content was changed.

    \closing{Sincerely,}

    \end{letter}

\end{document}