%! Author  = Omar Iskandarani
%! Date    = June 2026
%! ORCID   = 0009-0006-1686-3961
%! Target  = Physical Review A / European Physical Journal Plus

% ============================================================
%  Closure Requirements for a Compton-Core Vortex-Filament Scaling Model:
%  What Is Fixed Algebraically and What Requires New Dynamics
% ============================================================

\documentclass[aps,pra,preprint,longbibliography,nofootinbib]{revtex4-2}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{siunitx}
\usepackage[colorlinks=true,
            linkcolor=blue!60!black,
            citecolor=blue!60!black,
            urlcolor=blue!60!black]{hyperref}
\usepackage{cleveref}
\usepackage{microtype}

% ── Theorem environments ─────────────────────────────────────
\newtheorem{postulate}{Postulate}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\newtheorem{closure}{Closure}

% ── Notation ─────────────────────────────────────────────────
% Circulatory arrow subscript (reads as "circulatory flow")
\newcommand{\rotarrow}{%
  \mathchoice{\mkern-2mu\scriptstyle\boldsymbol{\circlearrowleft}}%
             {\mkern-2mu\scriptstyle\boldsymbol{\circlearrowleft}}%
             {\mkern-2mu\scriptscriptstyle\boldsymbol{\circlearrowleft}}%
             {\mkern-2mu\scriptscriptstyle\boldsymbol{\circlearrowleft}}}

\newcommand{\vc}{\mathbf{v}_{\rotarrow}}        % circulatory velocity (vector)
\newcommand{\vnorm}{\lVert\mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert} % magnitude

\newcommand{\rhof}{\rho_{\!f}}                   % background fluid density
\newcommand{\rhoE}{\rho_{\!E}}                   % kinetic energy density
\newcommand{\rhom}{\rho_{\!m}}                   % mass-equivalent density
\newcommand{\rhocore}{\rho_{\mathrm{core}}}      % core density
\newcommand{\rc}{r_c}                            % core radius
\newcommand{\Stv}{S_t}                           % relativistic time-dilation factor
\newcommand{\omC}{\omega_C}                      % Compton angular frequency
\newcommand{\lc}{\lambda_c}                      % Compton wavelength
\newcommand{\Rinf}{R_\infty}                     % Rydberg constant
\newcommand{\Tc}{\mathcal{T}_c}                  % vortex line tension at core
\newcommand{\Fgr}{F_{\mathrm{gr}}}              % gravitational tension scale c^4/4G
\newcommand{\Gz}{\Gamma_0}                       % circulation quantum
\newcommand{\Et}{\mathcal{E}_0}                    % zeroth-order topological aspect ratio
\newcommand{\LK}{\mathcal{L}_K}                     % ropelength of the knot
\newcommand{\AK}{A_K}                                % Biot--Savart logarithmic coefficient
\newcommand{\Xsph}{\Xi_{\mathrm{sph}}}             % spherical pressure-cell factor
\newcommand{\chiR}{\chi_R}                         % spherical cell radius coefficient
% ─────────────────────────────────────────────────────────────

\begin{document}

\title{Closure Requirements for a Compton-Core Vortex-Filament Scaling Model:\\
       What Is Fixed Algebraically and What Requires New Dynamics}

\author{Omar Iskandarani}
\thanks{ORCID: \href{https://orcid.org/0009-0006-1686-3961}{0009-0006-1686-3961}}
\affiliation{Independent Researcher, Groningen, The Netherlands}
\email{info@omariskandarani.com}
\date{June 2026}

% ─────────────────────────────────────────────────────────────

\begin{abstract}
We analyze which parts of a Compton-core vortex-filament model of the
electron are fixed algebraically and which parts require additional
physical closure.  The core postulate identifies the angular rotation
rate of the core with the electron Compton frequency,
$\Omega_{\mathrm{core}}=\omega_C=m_e c^2/\hbar$.  This postulate alone
only gives $\lVert \mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert=\omega_C r_c$;
it does not determine the characteristic circulation speed, the
fine-structure constant, the line tension, or the core density.  To close
the model one must add: (i) a spectroscopic speed closure equivalent to
using the Rydberg constant or $\alpha$ as input; (ii) a core-diameter
energy normalization for the line tension; and (iii) a thin-wall
Laplace-pressure closure for the density.  With these assumptions the
scales
$\lVert \mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert=(\pi\hbar cR_\infty/m_e)^{1/2}$,
$r_c=\lVert \mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert/\omega_C=r_e/2$,
$\Gamma_0=2\pi r_c\lVert \mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert$,
$\mathcal{T}_c=m_ec^2/(2r_c)$, and
$\rho_{\mathrm{core}}=m_ec^2/(2\pi\lVert \mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert^2r_c^3)$
follow consistently.  We therefore do not claim a first-principles
derivation of $\alpha$ or of $\rho_{\mathrm{core}}$.  Instead we identify
the minimal missing ingredients required for such a derivation and give
phenomenological test templates in terms of a short-range potential
correction or an electron form factor.

As a controlled extension, we also state and analyze an explicit spherical
pressure-cell closure.  This extension contains two distinct numerical
statements.  The value obtained by inserting the retrospective aspect scale
$\Et=274.074996$ is a calibrated consistency check and is not used as evidence
for a non-circular prediction.  The companion BEM/NLS-shell calculation gives
the non-CODATA conditional certificate
\[
  \alpha_{\rm cell}^{-1}=137.035953(28),
\]
where the uncertainty is run-to-run scatter.  The parameter-light leading
observation remains
\[
  \alpha_{\rm lead}^{-1}
  =
  \frac{8\pi}{3}\mathcal L_{3_1}
  =
  137.1547,
\]
which is within \(8.7\times10^{-4}\) of CODATA.  The conversion of the derived
sector count \(N_p=4\) into the pressure prefactor \(16\pi/3\), the
normalization \(w_\perp=1\) required for \(11/48\), and the physical far-field
identification remain explicitly model-dependent gates.  We therefore use
``fine-structure scale'' for the extension unless the far-field interaction law
is separately assumed or derived.

\end{abstract}

\maketitle

% =============================================================
\section{Introduction}
\label{sec:intro}
% =============================================================

Localized vortex-filament models of particle-like excitations trace
their lineage to Helmholtz and Kelvin~\cite{Helmholtz1867,Kelvin1867}
and continue to appear in topological soliton theory~\cite{FaddeevNiemi1997},
analogue-gravity models~\cite{Barcelo2005}, and superfluid-vacuum
analogies~\cite{Volovik2003}.  Such models require at least a core
radius, a characteristic circulation speed, a circulation, a line
tension, and an effective core density.  The central issue is not
whether these quantities can be written in terms of known constants;
they can.  The issue is which relations are independent physical
postulates and which are merely algebraic rewritings of standard
spectroscopic data.

The present paper therefore adopts a deliberately conservative aim.  We
ask what follows from a Compton-core hypothesis, what additionally must
be supplied to close the model, and what would be required to turn the
closure into a first-principles derivation.  The result is a hierarchy of
assumptions rather than a claimed derivation of the fine-structure
constant.  In particular, the relation between the circulation speed and
$\alpha$ is treated as a spectroscopic speed closure equivalent to using
$R_\infty$ as input.  Likewise, the line tension and the density require
separate mechanical closure assumptions.

This distinction is essential.  The Compton-core postulate gives only
$\lVert \mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert=\omega_C r_c$.
It does not by itself fix either
$\lVert \mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert$ or $r_c$.
A genuine derivation of the speed would require an independent dynamical
calculation of the electromagnetic coupling, or equivalently of
$\alpha$, without importing $R_\infty$.  A genuine derivation of the line
tension would require a specified core-energy functional.  A genuine
derivation of the density would require a specified interface model or
stress tensor.  These requirements are made explicit below.  For reproducibility and
referee auditability, Appendix~\ref{app:assumptions} gives the complete
assumption ledger; Appendix~\ref{app:bs_pressure} proves the Biot--Savart
pressure-balance theorem used for local core closure;
Appendix~\ref{app:spherical_geometry} derives the spherical pressure-cell
Jacobian used in the closure factor; Appendix~\ref{app:alpha_theorem}
states the resulting conditional fine-structure closure theorem;
Appendix~\ref{app:numerics} records the numerical convergence and
robustness requirements, while Appendix~\ref{app:sensitivity} gives the
sensitivity and falsification checks.  Historical numerical coincidences are
omitted from the submission version because they are not evidentiary steps in
the closure analysis.  A companion spherical/NLS pressure-cell paper
derives the pressure scale \(E_p^{\rm NLS}\) and shell stiffness
\(\kappa_{\rm NLS}^{\rm shell}\), while a companion BEM/NLS finite-cell
paper numerically extracts the stationary aspect eigenvalue \(E_\star\).
Those results are not assumed in the algebraic closure analysis below; they
address precisely the new dynamics identified here as missing.  The accompanying
supplementary script
\texttt{reproduce\_alpha\_cell\_closure.py} implements the minimal numerical
audit pipeline used in this paper: Fourier ideal-trefoil loading,
Biot--Savart cutoff-energy scanning, extraction of $A_K$, the
no-contact check $a_{\rm nc}/r_c=\sqrt{4\pi A_K}$, and the final
spherical-cell evaluation of $\alpha_{\rm cell}$; see
Appendix~\ref{app:numerics} for the reproducibility protocol.


We also record a more ambitious closure candidate motivated by the
ideal-trefoil robustness tests.  In that candidate the local Biot--Savart
logarithmic coefficient is assigned the conjectured slender-core asymptote
$1/(4\pi)$, giving the core-radius closure $a=r_c$, while the remaining
small correction to a zeroth-order topological aspect ratio is attributed
to the spherical pressure response of the surrounding irrotational cell.
The aspect scale $\Et=274.074996$ is not derived in this paper; it is a
conjectured external aspect eigenvalue whose independent derivation is an
open problem.  Since $\alpha_{\rm cell}\simeq2/\Et$ at leading order,
this input fixes the first four to five significant figures of the final
number.  The spherical-cell construction should therefore be read as a
conditional closure/reproduction, not as a first-principles derivation from
a complete microscopic action.

Throughout we use SI units, with $\hbar=h/(2\pi)$, $m_e$, $c$, and $e$
carrying their CODATA 2022 recommended meanings~\cite{MohrTaylor2022}.
CODATA 2022 is based on a least-squares adjustment of data available
through 31 December 2022~\cite{MohrTaylor2022}.  We denote the
circulatory velocity field by $\mathbf{v}_{\!\boldsymbol{\circlearrowleft}}$
and its magnitude by
$\vnorm=\lVert \mathbf{v}_{\!\boldsymbol{\circlearrowleft}}\rVert$.

% =============================================================
\section{The Compton-Core Postulate}
\label{sec:postulate}
% =============================================================

\begin{postulate}[Compton-core hypothesis]
\label{post:compton}
The vortex core undergoes solid-body rotation at the electron
Compton angular frequency,
\begin{equation}
  \Omega_{\mathrm{core}} = \omC \equiv \frac{m_e c^2}{\hbar}.
  \label{eq:postulate}
\end{equation}
The magnitude of the circulatory velocity at the core boundary
of radius $\rc$ is therefore
\begin{equation}
  \vnorm = \omC\,\rc.
  \label{eq:vc_rc_link}
\end{equation}
\end{postulate}

\begin{remark}[Physical motivation]
\label{rem:motivation}
For a solid-body rotating core of radius $\rc$ and angular
velocity $\Omega$, the tangential speed at the boundary is
$\vnorm = \Omega\,\rc$.
The Compton frequency $\omC = m_e c^2/\hbar$ is the natural
frequency associated with the electron rest energy: it is the
frequency at which one quantum $\hbar\omC = m_e c^2$ is stored.
Postulate~\ref{post:compton} is the simplest resonance condition
consistent with the electron rest energy as the core-energy scale,
and it provides a geometric link between the rotation rate and the
core boundary.
It is a hypothesis about the core dynamics, not a consequence of
standard quantum electrodynamics, and it is testable: any
independent measurement of $\rc$ inconsistent with
$\rc = \vnorm/\omC$ (where $\vnorm$ is determined by
Sec.~\ref{sec:derived}) falsifies the postulate.
\end{remark}

% =============================================================
\section{The Spectroscopic Speed Closure}
\label{sec:rydberg}
% =============================================================

\subsection{Equivalence of $R_\infty$ and $\alpha$ as inputs}

The Rydberg constant satisfies
\begin{equation}
  R_\infty = \frac{\alpha^2 m_e c}{2h}
           = \frac{\alpha^2 m_e c}{4\pi\hbar}.
  \label{eq:Rydberg_standard}
\end{equation}
Thus $R_\infty$ and $\alpha$ carry the same information once
$\{m_e,c,h\}$ are specified.  Using $R_\infty$ instead of $\alpha$ is
therefore not an independent derivation of $\alpha$; it is a convenient
spectroscopic parametrization of the same dimensionless input.

\begin{closure}[Spectroscopic speed closure]
\label{cl:speed}
The characteristic circulation speed is related to the electromagnetic
coupling by
\begin{equation}
  \tilde\alpha \equiv \frac{2\vnorm}{c},
  \qquad
  R_\infty = \frac{\tilde\alpha^2 m_e c}{2h}.
  \label{eq:speed_closure}
\end{equation}
Equivalently,
\begin{equation}
  R_\infty = \frac{\vnorm^2 m_e}{\pi\hbar c}
           = \frac{\vnorm^2\omega_C}{\pi c^3}.
  \label{eq:rydberg_core}
\end{equation}
\end{closure}

\begin{remark}[What would be needed to derive the speed]
\label{rem:derive_speed}
Closure~\ref{cl:speed} is the strongest non-geometric input in the
model.  A first-principles derivation would require a dynamical
calculation of the dimensionless coupling
\begin{equation}
  \tilde\alpha = \mathcal{F}[\mathcal{I}_1,\mathcal{I}_2,\ldots],
  \label{eq:alpha_from_dynamics_placeholder}
\end{equation}
where the invariants $\mathcal{I}_i$ are defined by an explicit
field-theoretic or hydrodynamic action.  Unless Eq.~\eqref{eq:alpha_from_dynamics_placeholder}
can be evaluated without using $R_\infty$, atomic spectra, or the
CODATA value of $\alpha$, the speed remains calibrated rather than
derived.
\end{remark}

% =============================================================
\section{Closure of the Characteristic Speed}
\label{sec:derivation}
% =============================================================

Using Closure~\ref{cl:speed},
\begin{equation}
  \Rinf = \frac{\vnorm^2\,\omC}{\pi c^3}
  \quad\Longrightarrow\quad
  \vnorm^2 = \frac{\pi\,\hbar\,c\,\Rinf}{m_e}.
  \label{eq:vc_solve}
\end{equation}

\begin{proposition}[Characteristic circulation speed]
\label{prop:vc}
Given Closure~\ref{cl:speed} and the measured $\Rinf$,
\begin{equation}
  \boxed{
    \vnorm = \sqrt{\frac{\pi\,\hbar\,c\,\Rinf}{m_e}}
  }
  \label{eq:vc}
\end{equation}
is the unique positive closure value for the tangential
circulation speed.
The inputs are $\{m_e, c, \hbar, \Rinf\}$; since
$\Rinf \equiv \alpha^2 m_e c/(2h)$, this is equivalent to using
$\alpha$ as input.  The result is therefore calibrated by spectroscopy,
not predicted independently.
\end{proposition}

\subsubsection*{Dimensional check}
\[
  \Bigl[\sqrt{\hbar\,c\,\Rinf/m_e}\Bigr]
  = \sqrt{
      \frac{\mathrm{J{\cdot}s\cdot m{\cdot}s^{-1}\cdot m^{-1}}}
           {\mathrm{kg}}
    }
  = \sqrt{\mathrm{m^2\,s^{-2}}} = \mathrm{m\,s^{-1}}. \checkmark
\]

\subsubsection*{Numerical value}
$\vnorm = \SI{1.093\,845\,631\,5e6}{\meter\per\second}$
\quad(from CODATA 2022~\cite{MohrTaylor2022}).

% =============================================================
\section{Derived Mechanical Scales}
\label{sec:derived}
% =============================================================

The following scales follow algebraically from
Proposition~\ref{prop:vc} and Postulate~\ref{post:compton},
each with a direct classical-hydrodynamic interpretation.

% ------- 4.1 Core radius ------------------------------------
\subsection{Core radius and its relation to the classical electron radius}
\label{sec:rc}

\begin{equation}
  \rc = \frac{\vnorm}{\omC} = \frac{\vnorm\,\hbar}{m_e c^2}
      = \SI{1.408\,970\,16e-15}{\meter}.
  \label{eq:rc}
\end{equation}

\begin{remark}[Relation to the classical electron radius]
\label{rem:re}
The classical electron radius is
\begin{equation}
  r_e = \frac{e^2}{4\pi\varepsilon_0 m_e c^2}
      = \frac{\alpha\hbar}{m_e c}
      = \SI{2.817\,940\,3e-15}{\meter}.
  \label{eq:re}
\end{equation}
From \eqref{eq:rc} and $\alpha = 2\vnorm/c$ (established below),
$\rc = \alpha\hbar/(2m_e c) = r_e/2$.
We emphasize that $\rc$ is an \emph{effective model parameter},
not a claim about the physical extent of the electron.
The classical radius $r_e$ itself plays an analogous role in QED
— appearing in Thomson cross-sections, Compton scattering, and
vacuum polarization — without implying a physical "size."
Experimental upper bounds on the electron's spatial extent
(from $g{-}2$ and high-energy scattering measurements,
$r \lesssim \SI{1e-18}{\meter}$~\cite{PDG2022}) constrain the
\emph{point-like} quantum-mechanical extent of the charge
distribution, not the scale at which an effective vortex-core
model is constructed.
For a toroidal idealization in which the tube centre lies at distance
$R = \rc$ from the symmetry axis and the tube has minor radius
$a = \rc$ (horn-torus geometry), the outer boundary lies at
$R+a=2\rc=r_e$.  This gives a geometric interpretation of the
factor-of-two relation, but it is not evidence that the electron charge
has a resolved radius $r_e$.
\end{remark}

% ------- 4.2 Fine-structure constant -------------------------
\subsection{Fine-structure constant as input equivalence}
\label{sec:alpha}

\begin{proposition}[Algebraic equivalence of $\alpha$ and $\vnorm$]
\label{prop:alpha}
The ratio $\tilde\alpha \equiv 2\vnorm/c$
satisfies $\tilde\alpha = \alpha$ (the CODATA fine-structure
constant) because Closure~\ref{cl:speed} was imposed.
This is not a derivation of $\alpha$ from independent physics
but the algebraic consequence of $\Rinf \equiv \alpha^2 m_e c/(2h)$
combined with \eqref{eq:vc}.
\end{proposition}

\begin{proof}
$\tilde\alpha = (2/c)(\pi\hbar c\Rinf/m_e)^{1/2}$.
Substituting $\Rinf = \alpha^2 m_e c/(4\pi\hbar)$:
$\tilde\alpha = (2/c)(\alpha^2 c^2/4)^{1/2} = \alpha$. \qed
\end{proof}

Numerically, $\tilde\alpha = \num{7.297\,352\,567\,1e-3}$
versus CODATA $\alpha = \num{7.297\,352\,569\,3e-3}$;
the residual $3\times10^{-10}$ is the propagated uncertainty
from $\Rinf$ (relative uncertainty \SI{1.9e-12}{}) combined with
the rounding of $\{m_e, c, \hbar\}$.
It is a precision-consistency check, not a prediction.

% ------- 4.3 Circulation quantum ----------------------------
\subsection{Circulation quantum}
\label{sec:Gamma0}

The line integral of velocity around the core boundary defines the
circulation,
\begin{equation}
  \Gz \equiv \oint \vc\cdot d\mathbf{l}
           = 2\pi\,\rc\,\vnorm
           = \frac{2\pi\vnorm^2}{\omC}
           = \SI{9.683\,619e-9}{\meter\squared\per\second}.
  \label{eq:Gamma0}
\end{equation}
The ratio $\Gz/\kappa = \alpha^2/4 \approx \num{1.33e-5}$,
where $\kappa = h/m_e$ is the Onsager-Feynman quantum~\cite{Onsager1949,Feynman1955},
showing that the present circulation is smaller by $\alpha^2/4$.

% ------- 4.4 Vortex line tension ---------------------------
\subsection{Vortex line tension}
\label{sec:Tc}

The \emph{vortex line tension} is the energy stored in the core per
unit filament length~\cite{Saffman1992}.  It is not fixed by
Postulate~\ref{post:compton}.  We therefore introduce a separate
normalization closure.

\begin{closure}[Core-diameter energy normalization]
\label{cl:tension}
One electron rest-energy quantum is assigned to a filament segment of
length $2\rc$:
\begin{equation}
  \Tc \equiv \frac{m_e c^2}{2\rc} = \frac{\hbar\omC}{2\rc}.
  \label{eq:Tc_def}
\end{equation}
\end{closure}

The physical content of Closure~\ref{cl:tension} is that the core stores
one quantum of Compton energy $m_e c^2=\hbar\omega_C$ per core-diameter
length.  A first-principles derivation would require an explicit
energy functional whose on-shell line energy equals Eq.~\eqref{eq:Tc_def}.

\begin{corollary}[Line tension in fundamental constants]
\label{cor:Tc}
\begin{equation}
  \Tc = \frac{m_e c^2}{2\rc}
      = \frac{m_e^2 c^3}{\tilde\alpha\,\hbar}
      = \SI{29.053\,51}{\newton}.
  \label{eq:Tc}
\end{equation}
\end{corollary}

\begin{remark}[Disambiguation from the gravitational tension scale]
\label{rem:Fgr}
The quantity $\Fgr \equiv c^4/(4G)$ defines the maximum force
transmissible without forming a causal horizon in general
relativity~\cite{Gibbons2002,Schiller2006}.
It and $\Tc$ share the dimension of force (energy per unit length),
but are conceptually distinct:
$\Tc$ is a mechanical property of the vortex core, while $\Fgr$ is
a causal upper bound from spacetime physics.
Numerically $\Tc \approx \SI{29}{\newton}$ versus
$\Fgr \approx \SI{3e43}{\newton}$.
Their ratio
\begin{equation}
  \frac{\Tc}{\Fgr} = \frac{4\alpha_g}{\tilde\alpha}
                   \approx \num{9.60e-43},
  \label{eq:tension_ratio}
\end{equation}
where $\alpha_g = Gm_e^2/(\hbar c) \approx \num{1.752e-45}$,
involves only fundamental constants and has no free parameters.
\end{remark}

% ------- 4.5 Core mass density --------------------------------
\subsection{Core mass density from Laplace-pressure balance}
\label{sec:rhocore}

The density is also not fixed by the Compton-core postulate.  We close
it with a thin-wall pressure-balance model.

\begin{closure}[Thin-wall Laplace-pressure closure]
\label{cl:laplace}
For a cylindrical core of radius $\rc$ and line tension $\Tc$, define an
effective wall tension
\begin{equation}
  \gamma \equiv \frac{\Tc}{2\pi\rc}.
  \label{eq:wall_tension}
\end{equation}
The corresponding cylindrical Laplace pressure is
\begin{equation}
  P_L = \frac{\gamma}{\rc} = \frac{\Tc}{2\pi\rc^2}.
  \label{eq:Laplace}
\end{equation}
We then impose the mechanical balance
\begin{equation}
  \frac{1}{2}\rhocore\vnorm^2 = \frac{\Tc}{2\pi\rc^2}.
  \label{eq:pressure_balance}
\end{equation}
\end{closure}

Closure~\ref{cl:laplace} is a thin-interface assumption.  It is not a
generic theorem of vortex dynamics; other core stress tensors or outer
cutoffs would change the numerical coefficient.

\begin{corollary}[Core density]
\label{cor:rho}
Solving~\eqref{eq:pressure_balance} and substituting
\eqref{eq:Tc_def}:
\begin{equation}
  \boxed{
    \rhocore = \frac{\Tc}{\pi\rc^2\vnorm^2}
             = \frac{m_e c^2}{2\pi\,\vnorm^2\,\rc^3}.
  }
  \label{eq:rhocore}
\end{equation}
Numerically, $\rhocore = \SI{3.893\,4e18}{\kilogram\per\cubic\meter}$.
\end{corollary}

\subsubsection*{Dimensional check}
$[m_e c^2/(\vnorm^2\rc^3)]
= \mathrm{kg\,m^2\,s^{-2}\,/\,(m^2\,s^{-2}\cdot m^3)}
= \mathrm{kg\,m^{-3}}$. \checkmark

\begin{remark}[Status of the density result]
\label{rem:noncircular}
Equation~\eqref{eq:rhocore} is non-circular only because
Closure~\ref{cl:tension} fixes $\Tc$ before Closure~\ref{cl:laplace} is
applied.  It is nevertheless not a first-principles density derivation.
It is the density implied by the chosen tension normalization and the
chosen thin-wall pressure law.

For comparison, the usual local-induction estimate for the line energy
of a vortex filament contains a circulation, a density, and typically a
logarithmic dependence on an outer length scale~\cite{Saffman1992}.
Therefore, any future derivation of $\rhocore$ from a hydrodynamic action
must specify the core profile, the outer cutoff or renormalization rule,
and the stress tensor.  Without those ingredients, Eq.~\eqref{eq:rhocore}
should be read as a closure consequence, not as an independent prediction.
\end{remark}

% ------- 4.6 Geometric gate identity -------------------------
\subsection{Geometric gate identity}
\label{sec:gate}

\begin{lemma}[Geometric gate]
\label{lem:gate}
\begin{equation}
  \frac{\lc}{\pi\rc} = \frac{4}{\tilde\alpha} \approx 548.14,
  \label{eq:gate}
\end{equation}
where $\lc = h/(m_ec)$ is the electron Compton wavelength.
\end{lemma}

\begin{proof}
$\lc = 2\pi\hbar/(m_ec)$; $\rc = \tilde\alpha\hbar/(2m_ec)$:
$\lc/(\pi\rc) = 4/\tilde\alpha$. \qed
\end{proof}

This dimensionless ratio is pure algebra; it is a geometric property
of the length scales $\lc$ and $\rc$ and does not encode additional
physical content.

% =============================================================
\section{Derivation Chain and Hydrodynamic Interpretation}
\label{sec:chain}
% =============================================================

The complete derivation chain is:
\begin{equation}
  \underbrace{m_e,\;c,\;\hbar,\;R_\infty}_{\text{standard inputs}}
  \;\xrightarrow{\;\text{Closure\;\ref{cl:speed}}\;}
  \vnorm
  \;\xrightarrow{\;\text{Post.\;\ref{post:compton}}\;}
  \rc
  \xrightarrow{}
  \Gz
  \;\xrightarrow{\;\text{Closure\;\ref{cl:tension}}\;}
  \Tc
  \;\xrightarrow{\;\text{Closure\;\ref{cl:laplace}}\;}
  \rhocore.
  \label{eq:chain}
\end{equation}
The classical-hydrodynamic interpretation of each scale is:

\medskip
\begin{tabular}{@{}ll@{}}
$\vnorm = \omC\rc$ & tangential speed at solid-body core boundary \\
$\rc = \vnorm/\omC$ & core radius from solid-body rotation \\
$\Gz = 2\pi\rc\vnorm$ & circulation (line integral of velocity) \\
$\Tc = m_e c^2/(2\rc)$ & line tension from core-diameter energy closure \\
$\rhocore$ & core density from thin-wall pressure-balance closure \\
\end{tabular}

% =============================================================
\section{Status Table}
\label{sec:status}
% =============================================================

\begin{table}[h]
\centering
\caption{Epistemic status of all quantities.  ``Closure'' denotes an
explicit model assumption beyond the Compton-core postulate; ``Algebraic''
denotes a consequence of earlier rows.}
\label{tab:status}
\begin{tabular}{llll}
\toprule
Quantity & Symbol & Status & Note \\
\midrule
Compton frequency  & $\omC = m_e c^2/\hbar$     & Standard def.  & \cite{MohrTaylor2022} \\
Core rotation rate & $\Omega_{\rm core}=\omC$   & Postulate       & Post.~\ref{post:compton} \\
Rydberg/FSC input  & $\Rinf\equiv\alpha$        & Empirical input & \eqref{eq:Rydberg_standard} \\
Speed relation     & $2\vnorm/c=\tilde\alpha$   & Closure         & Closure~\ref{cl:speed} \\
Circ.\ speed       & $\vnorm$                   & Calibrated      & Prop.~\ref{prop:vc} \\
Core radius        & $\rc = r_e/2$              & Post.+closure   & \eqref{eq:rc} \\
Circulation        & $\Gz$                      & Algebraic       & \eqref{eq:Gamma0} \\
Line tension       & $\Tc$                      & Closure         & Closure~\ref{cl:tension} \\
Core density       & $\rhocore$                 & Closure result  & Closure~\ref{cl:laplace} \\
Geom.\ gate        & $\lc/(\pi\rc)$             & Algebraic       & Lemma~\ref{lem:gate} \\
Trefoil log coeff. & $\AK$                      & Numerical/asymptotic ansatz & App.~\ref{app:numerics} \\
Aspect scale       & $\Et=274.074996$          & Conjectural input & App.~\ref{app:assumptions} \\
Cell-radius coeff. & $\chiR=2$                  & Closure choice & App.~\ref{app:sensitivity} \\
Spherical cell factor & $\Xsph$                 & Closure candidate & App.~\ref{app:spherical_geometry} \\
Cell reproduction for FSC & $\alpha_{\rm cell}$ & Conditional     & App.~\ref{app:alpha_theorem} \\
Background density & $\rhof$                    & Open            & needs independent coupling \\
Topological state  & knot type $K$              & Open            & not determined here \\
\bottomrule
\end{tabular}
\end{table}

% =============================================================
\section{What Would Be Required for a First-Principles Derivation}
\label{sec:requirements}
% =============================================================

The preceding sections define a consistent closure hierarchy.  A full
derivation would require replacing each closure by a dynamical equation.
The minimal requirements are as follows.

\subsection{Independent derivation of the speed or fine-structure constant}

One must specify an action or Hamiltonian containing both the
circulatory degrees of freedom and the electromagnetic coupling, for
example schematically
\begin{equation}
  S = \int d^4x\,\mathcal{L}\bigl[\mathbf{v}_{\!\boldsymbol{\circlearrowleft}},
  \rho, A_\mu, \psi;\Pi_i\bigr],
  \label{eq:needed_action}
\end{equation}
with dimensionless parameters or topological invariants $\Pi_i$.  The
model must then predict
\begin{equation}
  \alpha = \mathcal{F}(\Pi_i),
  \qquad
  \vnorm = \frac{\alpha c}{2},
  \label{eq:needed_alpha}
\end{equation}
without using $R_\infty$, atomic spectra, or the CODATA value of
$\alpha$.  This is the missing step if the goal is to derive the speed
rather than calibrate it.


\subsection{Candidate spherical pressure-cell closure for the fine-structure constant}
\label{sec:spherical_cell}

This subsection gives a concrete closure candidate for the missing step in
Eq.~\eqref{eq:needed_alpha}.  It is deliberately separated from the
algebraic closure chain above.  The result is conditional: if the spherical
pressure-cell functional below is the correct coarse-grained outer-cell
functional, and if the external aspect input $\Et$ is accepted, then the
model reproduces the numerical fine-structure scale.  If either ingredient
is not derived from the full dynamics, the result remains a conjectural
closure.  The full assumption ledger, pressure theorem, spherical-cell
Jacobian, numerical checks, and sensitivity analysis are given in
Appendices~\ref{app:assumptions}--\ref{app:sensitivity}.

Let $K$ denote the ideal trefoil.  The local irrotational contribution to
the Biot--Savart energy of a slender filament is written in the normalized
form
\begin{equation}
  E_{\rm BS}(a)
  = \rhof \Gz^2 L_K
    \left[\AK\log\!\left(\frac{L_K}{a}\right)+a_K\right],
  \label{eq:bs_log_energy}
\end{equation}
where $a$ is the tube radius, $L_K$ is the physical centerline length, and
$\AK$ is the logarithmic local-induction coefficient.  The normal pressure
on a tube wall of area $2\pi aL_K$ is
\begin{equation}
  P_{\rm irr}(a)
  = -\frac{1}{2\pi aL_K}\frac{\partial E_{\rm BS}}{\partial a}
  = \frac{\rhof\Gz^2\AK}{2\pi a^2}.
  \label{eq:pirr_from_bs}
\end{equation}
Balancing this against the core dynamic pressure
\begin{equation}
  P_{\rm core}=\frac{1}{2}\rhof\vnorm^2
  \label{eq:pcore_dynamic}
\end{equation}
and using $\Gz=2\pi r_c\vnorm$ gives
\begin{equation}
  \frac{a}{r_c}=\sqrt{4\pi\AK}.
  \label{eq:anc_from_AK}
\end{equation}
Thus the conjectured slender-core asymptotic value $\AK=1/(4\pi)$ is
exactly the no-contact core-radius closure $a=r_c$.  This is also the
closure convention used in the numerical robustness script, where
$a_{\rm nc}=r_c\sqrt{4\pi A_K}$ and the stationary roots are solved in
$x=a/r_c$ rather than directly at meter scale.  Finite-resolution numerical
runs need not equal $1/(4\pi)$ exactly; the use of $1/(4\pi)$ below is an
asymptotic ansatz, not a fitted finite-resolution value.

The remaining question is whether the dimensionless speed ratio can be
predicted.  We introduce a zeroth-order topological aspect ratio $\Et$ and
write
\begin{equation}
  \alpha_{\rm cell}=\frac{2}{\mathcal E_{\rm eff}},
  \qquad
  \mathcal E_{\rm eff}=\Et(1-\delta_{\rm cell}).
  \label{eq:alpha_cell_def}
\end{equation}
At leading order, $\alpha_{\rm cell}\simeq2/\Et$.  Consequently the
choice of $\Et$ determines the first four to five significant figures of
the final value, while the pressure-cell correction below operates only at
relative order $\Et^{-2}\sim10^{-5}$.  In the present manuscript $\Et$ is
therefore classified as a conjectured external aspect eigenvalue, not as a
quantity derived from the pressure-cell calculation itself.  A fundamental
version of the model must derive $\Et$ independently, as discussed in
Sec.~\ref{sec:requirements} and Appendix~\ref{app:assumptions}.

The local trefoil calculation supplies the asymptotic factor
$\pi^2\AK\to\pi/4$.  The spherical cell supplies the finite-volume
correction multiplying this local factor.  Let
\begin{equation}
  \LK\equiv \frac{L_K}{D_K}
  \label{eq:ropelength_def}
\end{equation}
be the dimensionless ropelength of the ideal trefoil, and define the
small spherical shell parameter
\begin{equation}
  \eta_K\equiv\frac{1}{4\LK}.
  \label{eq:etaK_def}
\end{equation}
More generally one may write the spherical control radius as
$R_{\rm cell}=\chiR L_K$.  Then
\begin{equation}
  \eta_K(\chiR)=\frac{a}{R_{\rm cell}}
  =\frac{1}{2\chiR\LK} .
  \label{eq:etaK_chiR}
\end{equation}
The numerical closure below uses $\chiR=2$, giving
$\eta_K=1/(4\LK)$.  The choice $\chiR=2$ is a model closure, not derived
in this paper; Appendix~\ref{app:sensitivity} records the associated
sensitivity.

We now postulate the minimal dimensionless pressure-cell Gibbs functional
\begin{equation}
  \mathcal G_{\rm sph}(q;\eta_K)
  = \frac{K_{\rm sph}}{2}\,q^2
    -K_{\rm sph}\left(1+3\eta_K+\eta_K^2\right)q,
  \qquad K_{\rm sph}>0,
  \label{eq:spherical_gibbs}
\end{equation}
where $q$ is the dimensionless multiplier of the local trefoil correction
$\pi^2\AK/\Et^2$.  This is a virtual-work/enthalpy closure: the quadratic
term penalizes departure from the isotropic cell response, and the linear
term is the coarse-grained pressure work performed by the shifted spherical
control surface.  The three forcing terms are assigned as follows: $1$ is
the local tube-pressure contribution, $3\eta_K$ is the first variation of
a spherical volume element $V\propto R^3$, and $\eta_K^2$ is the leading
quadratic curvature-shell response retained after removing the purely
local wall term already accounted for by $\AK$.  The combination is still a
closure rule.  A more general weighted form is analyzed in
Appendix~\ref{app:sensitivity}; only a primitive stress-tensor derivation
could promote Eq.~\eqref{eq:spherical_gibbs} to a first-principles result.

\begin{proposition}[Spherical pressure-cell closure]
\label{prop:spherical_alpha}
For the functional~\eqref{eq:spherical_gibbs}, the unique stationary and
stable pressure-cell multiplier is
\begin{equation}
  \Xsph(\chiR)=1+3\eta_K(\chiR)+\eta_K(\chiR)^2 .
  \label{eq:Xi_sph_general_main}
\end{equation}
For the closure choice $\chiR=2$, this becomes
\begin{equation}
  \Xsph=1+3\eta_K+\eta_K^2
       =1+\frac{3}{4\LK}+\frac{1}{16\LK^2}.
  \label{eq:Xi_sph}
\end{equation}
Consequently, if the corrected aspect ratio is
\begin{equation}
  \mathcal E_{\rm eff}
  =\Et\left[1-\frac{\pi}{4}\frac{\Xsph}{\Et^2}
       +O(\Et^{-4},\LK^{-3})\right],
  \label{eq:Eeff_spherical}
\end{equation}
then the predicted coupling is
\begin{equation}
  \boxed{
  \alpha_{\rm cell}
  =\frac{2}{\Et\left[1-\dfrac{\pi}{4\Et^2}
      \left(1+\dfrac{3}{4\LK}+\dfrac{1}{16\LK^2}\right)\right]}
  } .
  \label{eq:alpha_spherical_prediction}
\end{equation}
\end{proposition}

\begin{proof}
Stationarity gives
\begin{equation}
  \frac{\partial \mathcal G_{\rm sph}}{\partial q}
  =K_{\rm sph}\left[q-\left(1+3\eta_K+\eta_K^2\right)\right]=0,
  \label{eq:gibbs_stationarity}
\end{equation}
so $q=\Xsph$.  Since
\begin{equation}
  \frac{\partial^2 \mathcal G_{\rm sph}}{\partial q^2}=K_{\rm sph}>0,
  \label{eq:gibbs_stability}
\end{equation}
the stationary point is a strict minimum.  Substituting
$\AK=1/(4\pi)$ into the local finite-core factor $\pi^2\AK/\Et^2$ gives
$(\pi/4)/\Et^2$.  Multiplication by the stable spherical-cell response
$\Xsph$ yields Eq.~\eqref{eq:Eeff_spherical}, and
$\alpha_{\rm cell}=2/\mathcal E_{\rm eff}$ gives
Eq.~\eqref{eq:alpha_spherical_prediction}.
\end{proof}

For numerical orientation, take
\begin{equation}
  \Et=274.074996,
  \qquad
  \LK=16.371498,
  \qquad
  \chiR=2 .
  \label{eq:numerical_E0_LK}
\end{equation}
Here $\Et$ is a conjectured external aspect input.  The value
$\LK=16.371498$ is the ropelength of the ideal trefoil with tube diameter
$D_K=1$ used in the numerical ideal-trefoil run and is taken from the Knot
Atlas ideal-knot Fourier data file~\cite{KnotAtlasIdeal}; the rigorous
mathematical ropelength framework is reviewed in Ref.~\cite{Cantarella2002}.  Then
\begin{align}
  \eta_K &= 1.52704413\times10^{-2},
  &\Xsph &= 1.04604451,
  \label{eq:Xi_numbers}\\
  \mathcal E_{\rm eff} &= 274.071998421,
  &\alpha_{\rm cell}^{-1} &= 137.035999211 .
  \label{eq:alpha_cell_numbers}
\end{align}
Compared with the CODATA 2022 value of $\alpha$, this numerical value is
within $2.4\times10^{-10}$ fractionally.  This level of agreement should
not be overinterpreted.  The dominant zeroth-order scale is supplied by
$\Et$, because $\alpha_{\rm cell}\simeq2/\Et$; the spherical-cell factor
only supplies the residual $10^{-5}$ finite-core correction.  Thus the
extension is a conditional reproduction given $\Et$, $\chiR$, and
$\LK$, not yet a derivation from a complete microscopic action.  Its
falsifiable content is the pair of coefficients $3/(4\LK)$ and
$1/(16\LK^2)$ together with the radius choice $\chiR=2$; changing the
pressure-cell geometry changes the prediction.

\subsection{Independent derivation of the line tension}

A line tension must follow from an energy functional.  For a cylindrical
core profile this would require an expression of the form
\begin{equation}
  \mathcal{T}_{\rm dyn}
  = \int_0^{R_{\rm out}}2\pi r\,dr\,
    \left[\frac{1}{2}\rho(r)v_\theta(r)^2
    +U(\rho,\nabla\rho)+\mathcal{E}_{\rm int}(r)\right],
  \label{eq:needed_tension}
\end{equation}
plus a renormalization prescription for the outer scale $R_{\rm out}$.
Closure~\ref{cl:tension} is derived only if
\begin{equation}
  \mathcal{T}_{\rm dyn}=\frac{m_ec^2}{2r_c}
  \label{eq:tension_target}
\end{equation}
follows as the stationary on-shell value.

\subsection{Independent derivation of the density}

The density requires a stress-balance calculation.  A sufficient route is
to define a radial stress tensor $\sigma_{ij}$ and show that the normal
stress jump at the core wall gives
\begin{equation}
  \Delta P = \sigma_{rr}^{\rm(out)}-\sigma_{rr}^{\rm(in)}
           = \frac{\gamma}{r_c},
  \qquad
  \gamma = \frac{\partial E}{\partial A},
  \label{eq:needed_laplace}
\end{equation}
with $\gamma=\mathcal{T}_c/(2\pi r_c)$ as a consequence rather than a
definition.  Only then does $\rho_{\mathrm{core}}$ become dynamically
predicted.

\subsection{Independent low-energy observable}

Finally, the model must produce an observable correction.  A generic
low-energy parametrization is
\begin{equation}
  F_e(q^2)=1-\frac{1}{6}\langle r^2\rangle_{\rm eff}q^2+\mathcal{O}(q^4),
  \qquad
  \langle r^2\rangle_{\rm eff}=\chi r_c^2,
  \label{eq:form_factor_template}
\end{equation}
where $\chi$ must be predicted.  Equivalently, the theory may predict a
short-range potential correction
\begin{equation}
  \Delta V_\eta(r)=
  \eta\,\frac{e^2}{4\pi\varepsilon_0 r}\,f(r/r_c),
  \qquad f(0)\;\mathrm{finite},\quad f(x\gg1)\to0,
  \label{eq:potential_template}
\end{equation}
where $\eta$ and $f$ must be fixed by the model.  Without such a
coefficient or shape function, the core scale is not experimentally
sharp.

% =============================================================
\section{Phenomenological Tests and Falsifiers}
\label{sec:falsifiers}
% =============================================================

The present closure model does not yet make a parameter-free prediction
for atomic spectra.  It does, however, define test templates that become
falsifiable once the coefficients in Eqs.~\eqref{eq:form_factor_template}
and~\eqref{eq:potential_template} are fixed.

\medskip
\noindent\textbf{(i) Spectroscopic potential test.}
For any specified $\Delta V_\eta(r)$, hydrogenic energy shifts are
\begin{equation}
  \Delta E_{n\ell}
  = \int_0^\infty |R_{n\ell}(r)|^2\,\Delta V_\eta(r)\,r^2\,dr.
  \label{eq:lamb_template}
\end{equation}
Existing bound-state QED calculations already account for the Lamb
shift to high precision~\cite{Bethe1947,Karshenboim2005}.  Therefore,
any order-unity $\eta$ producing an unobserved shift is excluded.  If the
model predicts $\eta\ll1$, the corresponding bound must be stated.

\medskip
\noindent\textbf{(ii) Form-factor test.}
If the model predicts $\chi$ in Eq.~\eqref{eq:form_factor_template}, then
scattering data constrain the effective charge response.  The scale
$r_c\simeq\SI{1.409e-15}{\meter}$ cannot be interpreted naively as a
resolved electron radius; it is only observable through the predicted
coupling coefficient $\chi$.

\medskip
\noindent\textbf{(iii) Tension-ratio diagnostic.}
The ratio
\begin{equation}
  \frac{\Tc}{\Fgr}=\frac{4\alpha_g}{\tilde\alpha}
  \label{eq:tension_ratio_diagnostic}
\end{equation}
is a useful dimensionless diagnostic, but not by itself a falsifiable
prediction.  It becomes testable only after a concrete analogue-system
mapping identifies the measured mechanical tension and the analogue
causal-horizon scale.

% =============================================================
\section{Numerical Summary}
\label{sec:numerical}
% =============================================================

The numerical values in Table~\ref{tab:numbers} are accompanied by the
standalone supplementary script
\texttt{reproduce\_alpha\_cell\_closure.py}.  The script is not used as a
substitute for the assumptions in Appendix~\ref{app:assumptions}; it is
only a reproducibility aid for the Biot--Savart coefficient extraction,
the local closure ratio, and the spherical-cell numerical evaluation
described in Appendix~\ref{app:numerics}.

\begin{table}[h]
\centering
\caption{Numerical values of all closed quantities from CODATA 2022
inputs~\cite{MohrTaylor2022}.
The fourth column gives the propagated fractional uncertainty from $\Rinf$
(\num{1.9e-12}) where applicable; dashes indicate quantities with no
CODATA counterpart.}
\label{tab:numbers}
\begin{tabular}{llll}
\toprule
Quantity & Symbol & Value & Prop.\ unc.\ from $\Rinf$ \\
\midrule
Circ.\ speed   & $\vnorm$ & \SI{1.093\,845\,63e6}{\m\per\s}      & $\sim\num{1e-12}$ \\
Core radius    & $\rc$    & \SI{1.408\,970\,16e-15}{\meter}       & $\sim\num{1e-12}$ \\
$\tilde\alpha$ &          & \num{7.297\,352\,567e-3}              & $\sim\num{1e-12}$ \\
Circulation    & $\Gz$    & \SI{9.683\,619e-9}{\m\squared\per\s}  & — \\
Line tension   & $\Tc$    & \SI{29.053\,51}{\newton}               & — \\
Core density   & $\rhocore$& \SI{3.893\,4e18}{\kg\per\m\cubed}    & — \\
Geom.\ gate    & $4/\tilde\alpha$ & \num{548.14}               & $\sim\num{1e-12}$ \\
Spherical-cell FSC & $\alpha_{\rm cell}^{-1}$ & \num{137.035999211} & closure-systematic \\
Spherical factor & $\Xsph$ & \num{1.04604451} & closure-systematic \\
\bottomrule
\end{tabular}
\end{table}

% =============================================================

\section{Derived-label policy for companion results}
\label{sec:derived-label-policy}

This section records the updated status after the post-review gate scripts.  The
companion results should still be read as a hierarchy of derived, conditional,
and open steps rather than as a single first-principles derivation of QED
\(\alpha\).

The following gates have strengthened.

First, the pressure-sector count is now derived inside the spherical finite-cell
surface variation.  For a boundary perturbation
\[
  r(\Omega)=R[1+\epsilon f(\Omega)]
\]
at fixed volume, the surface-area second variation gives
\[
  \delta^2 A
  =
  \frac{R^2}{2}
  \int_{S^2}\left(|\nabla_{S^2}f|^2-2f^2\right)d\Omega .
\]
For \(f=Y_{\ell m}\),
\[
  k_\ell=\ell(\ell+1)-2=(\ell-1)(\ell+2).
\]
Thus \(\ell=1\) is the three-dimensional translation/centre-displacement
zero-mode sector, \(\ell\ge2\) are positive-stiffness shape modes, and
\(\ell=0\) is the scalar compression sector.  Therefore
\[
  \mathcal P_{\rm min}=\mathcal H_0\oplus\mathcal H_1,
  \qquad
  N_p=1+3=4
\]
is derived within the spherical finite-cell surface reduction.

The perturbative and nonlinear robustness checks now strengthen this statement.
The perturbative finite-core audit uses the first positive shape-mode gap
\(k_2=4\) and verifies that corrections at the finite-core scale
\[
  \eta_K=\frac{1}{4\mathcal L_K}=1.52703116982\times10^{-2}
\]
are far below the half-gap criterion.  The nonlinear star-shaped solve uses
\[
  r(\Omega)=\exp\!\left(\sum_{\ell=2}^{\ell_{\max}}\sum_m
  a_{\ell m}Y_{\ell m}(\Omega)\right)
\]
with exact volume rescaling.  For \(\ell_{\max}=6\), the
\(\ell\ge2\) sector contains 45 real modes; 300 random samples per amplitude
at \(\eta_K,0.05,0.10,0.25,0.50,1.00\) found no negative fixed-volume area
excess, and 20 L-BFGS-B minimizations from amplitude-one random starts returned
to the spherical solution with
\[
  \max\lVert a_{\ell m}^{\rm final}\rVert=5.830157\times10^{-7}.
\]
The global topological loophole is closed, within the finite-perimeter pressure
cell class, by the Euclidean isoperimetric inequality
\[
  P(\Omega)^3\ge 36\pi V(\Omega)^2,
\]
with equality only for a ball.  Thus non-star-shaped, disconnected, and
higher-genus admissible cells cannot lower the fixed-volume perimeter below the
sphere.  Self-intersecting immersed surfaces are not admissible reduced
boundaries of a pressure cell; if counted with multiplicity, they cannot
improve the isoperimetric bound.


Second, the radius action has a stronger SST-internal support.  The
Laplace-matching script evaluates
\[
  P_{\rm kin}=\frac12\rho_{\rm core}
  \lVert\mathbf v_{\!\boldsymbol{\circlearrowleft}}\rVert^2
  =
  2.329244600448\times10^{30}\ {\rm Pa},
\]
and
\[
  P_{\rm Laplace}=\frac{F_{\rm swirl}^{\max}}{2\pi r_c^2}
  =
  2.329244600448\times10^{30}\ {\rm Pa}.
\]
Hence \(\mu=P_{\rm in}/P_{\rm out}=1\) in the leading reciprocal pressure
model, giving
\[
  A_\chi=\chi_R+\frac{N_p}{\chi_R},
  \qquad
  \chi_R=\sqrt{N_p}=2,
  \qquad
  \lambda_\chi=4 .
\]
This is derived within the Laplace-matched reciprocal pressure model, subject
to excluding same-order nonreciprocal corrections such as \(\log\chi_R\),
\(\chi_R^2\), or \(\chi_R^{-2}\).

Third, the finite-shell coefficient is now localized to one explicit
normalization gate.  The GP/NLS core-profile audit solves the radial vortex
profile and derives
\[
  \sigma_{\rm vol}=3,
  \qquad
  \langle\sin^2\theta\rangle_{S^2}=\frac23.
\]
Thus
\[
  \sigma=3+\frac23 w_\perp .
\]
For the unweighted isotropic GP/NLS shell normalization \(w_\perp=1\),
\[
  \sigma=\frac{11}{3},
  \qquad
  \frac{\sigma}{4\chi_R^2}=\frac{11}{48}
  \quad(\chi_R=2).
\]
The script confirms the angular identity, but the status of \(w_\perp=1\) is
not derived from the primitive GP/NLS core dynamics.  In fact, the supplied
relaxed-core proxy \texttt{derive\_relaxed\_gp\_core\_hessian\_wperp.py}
returns \(w_\perp\simeq2.076\) in its smoke test, not \(1\).  Therefore
\(11/48\) should be read as a coefficient derived only after imposing the
unweighted isotropic shell normalization \(w_\perp=1\).  At the
primitive-equation level, \(w_\perp=1\) remains an open gate and the current
proxy is a warning sign rather than a confirmation.

Fourth, the exterior Hodge/phase part and the interior phase budget now have a
stronger status.  For a connected spherical cell boundary,
\[
  q_\phi=\dim H^0(S^2)=1,
\]
and the exterior constant phase mode obeys
\[
  \int_{r\ge R}|\nabla(\phi R/r)|^2\,d^3x=4\pi R\phi^2,
  \qquad
  \Lambda_\phi=4\pi R\mathcal K_{\rm cell}.
\]
The interior phase-Hessian chain is now closed within the canonical linearized
normal-mode reduction.  In Madelung/GP variables, the density perturbation and
phase are canonically conjugate; after diagonalization each normal mode has
\[
  H_k=\frac12p_k^2+\frac12\omega_k^2q_k^2,
\]
so its cycle-averaged phase/flow and pressure/compression budgets are equal:
\[
  M_\phi=M_p=\frac{E_{\rm eff}}{2}.
\]
Together with the radial optimum \(n_{\rm eff}(r)\propto r^{-2}\) and the
accessible-area projection \(M_{\rm acc}=M_\phi(R-a)^2/R^2\), this gives
\[
  \Lambda_\phi=\frac{E_{\rm eff}}{2R^2}.
\]
For the normalized cell \(R=1\),
\[
  \Lambda_\phi=\frac{E_{\rm eff}}{2},
  \qquad
  \mathcal K_{\rm cell}=\frac{E_{\rm eff}}{8\pi}.
\]
The remaining qualification is physical rather than algebraic: the
\(E_{\rm eff}\) used in the pressure-cell chain must be identified with the
cycle-averaged quadratic energy of the same canonical interior mode family.

The strongest current classification is therefore
\[
  N_p=4
  \quad[\text{derived in spherical surface spectrum; stable under perturbative, nonlinear star-shaped, and finite-perimeter global-topology checks}],
\]
\[
  A_\chi=\chi_R+\frac{N_p}{\chi_R}
  \quad[\text{derived in Laplace-matched reciprocal pressure model}],
\]
\[
  \frac{11}{48}
  \quad[\text{conditional on the unweighted shell normalization }w_\perp=1],
\]
and
\[
  \mathcal K_{\rm cell}=\frac{E_{\rm eff}}{8\pi}
  \quad[\text{derived inside the canonical normal-mode reduction, with the }E_{\rm eff}\text{ bridge explicitly assumed}].
\]
A complete first-principles derivation of the electromagnetic fine-structure
constant still requires a microscopic derivation of \(w_\perp=1\) and the
physical bridge identifying \(E_{\rm eff}\) with the cycle-averaged quadratic
energy of that same canonical interior mode family.




\subsection*{Major-revision claim-status correction}

The companion audit distinguishes three levels that must not be conflated.  First,
\(N_p=4\) is the strongest derived result: it follows from the spherical surface
spectrum and is stable under perturbative, nonlinear star-shaped, and
finite-perimeter global-topology checks.  Second, the pressure prefactor
\[
  \frac{16\pi}{3}=N_p\frac{4\pi}{3}
\]
still contains the sector-volume normalization \(4\pi/3\) per pressure sector
per unit ropelength.  The present manuscripts motivate this normalization but
do not yet derive it from a pressure-cell variational principle.  Third, the
precision-supplying coefficient
\[
  \frac{11}{48}
\]
requires \(w_\perp=1\).  Since the relaxed GP-core proxy gives
\(w_\perp\simeq2.076\), this coefficient is conditional and should not be used
as a primitive-derived input until the discrepancy is resolved.

Accordingly, the retrospective value
\(\alpha_{\rm cell}^{-1}=137.035999211\) is a calibrated consistency check.
The non-CODATA BEM/NLS value \(\alpha_{\rm cell}^{-1}=137.035953(28)\) is a
conditional finite-cell certificate, and the untuned leading relation
\((8\pi/3)\mathcal L_{3_1}=137.1547\) is the appropriate parameter-light
headline.

\subsection*{Code evidence for the updated gate status}

The supporting scripts and outputs are stored in \texttt{../code/} relative to
the \texttt{Manuscripts} directory.  The relevant reproducibility files are:
\begin{itemize}
\item \texttt{../code/derive\_pressure\_mode\_cutoff\_surface\_spectrum.py}
and \texttt{../code/outputs\_surface\_mode\_cutoff/};
\item \texttt{../code/test\_finite\_core\_nonspherical\_shape\_corrections.py}
and \texttt{../code/outputs\_finite\_core\_shape/};
\item \texttt{../code/solve\_nonlinear\_shape\_stability.py} and
\texttt{../code/outputs\_nonlinear\_shape\_stability\_lmax6\_opt/};
\item \texttt{../code/derive\_gp\_core\_profile\_second\_variation.py} and
\texttt{../code/outputs\_gp\_core\_profile\_second\_variation/};
\item \texttt{../code/derive\_relaxed\_gp\_core\_hessian\_wperp.py} and
\texttt{../code/outputs\_relaxed\_gp\_wperp/};
\item \texttt{../code/derive\_pressure\_self\_duality\_from\_laplace\_matching.py}
and \texttt{../code/outputs\_laplace\_self\_duality/};
\item \texttt{../code/solve\_one\_cell\_hodge\_phase\_hessian.py} and
\texttt{../code/outputs\_hodge\_phase\_hessian/};
\item \texttt{../code/derive\_phase\_pressure\_exchange\_self\_duality.py} and
\texttt{../code/outputs\_phase\_pressure\_self\_duality/}.
\end{itemize}

\section{Discussion}

The post-review gate calculations sharpen the closure status.  The previous
delay-stability route did not cleanly retain the \(\ell=1\) sector with default
parameters; it has therefore been superseded by the fixed-volume surface
spectrum, which gives \(k_\ell=(\ell-1)(\ell+2)\) and derives
\(N_p=4\) in the spherical finite-cell reduction.  The pressure self-duality is
also strengthened by the equality of the SST kinetic and Laplace pressures.
The remaining nontrivial open target is now the microscopic normalization
\(w_\perp=1\).  The interior phase-Hessian identity
\(\Lambda_\phi=E_{\rm eff}/2\) is derived within the canonical normal-mode
phase--pressure reduction, subject to the stated physical bridge for
\(E_{\rm eff}\).


The fourth companion note gives the uniqueness theorem for the finite-cell
variational reduction: constrained \(S^2\) pressure minimization, isotropic
NLS/GP shell variation, reciprocal radius stationarity, and exterior
\(H^0(S^2)\) phase selection.  This is the strongest current justification for
the phrase ``derived within the minimal finite-cell variational reduction.''


The companion Paper~II appendix gives the pressure-sector and finite-shell
arguments that turn the coefficients \(16\pi/3\), \(11/48\), and
\(\chi_R=2\) into consequences of the minimal shell model.  The companion
Paper~III appendix gives the far-field \(H^0(S^2)\) argument that isolates the
single \(1/r\) phase mode.  The present paper keeps these results separated from
the algebraic audit so that the epistemic status of each step remains explicit.

\label{sec:discussion}
% =============================================================

The central result is a closure analysis, not a first-principles
derivation.  The Compton-core postulate fixes the relation between
rotation rate, speed, and radius.  The Rydberg anchor fixes the speed
only because it is equivalent to the fine-structure constant.  The line
tension and density then follow only after two further mechanical
closures are imposed.

This organization removes the circularity in the stronger claim that
$\alpha$ or $\rho_{\mathrm{core}}$ had been derived.  The paper instead
identifies exactly where new dynamics would be required.  The most
important missing piece is an independent derivation of
$\tilde\alpha=2\vnorm/c$ from a specified interaction functional.  The
second missing piece is an on-shell core-energy calculation yielding
$\mathcal{T}_c=m_ec^2/(2r_c)$.  The third is a stress-balance derivation
of the thin-wall Laplace law.

The spherical pressure-cell construction of Sec.~\ref{sec:spherical_cell}
shows one explicit route by which the speed closure could become
predictive: the local trefoil coefficient fixes $a=r_c$, and the
spherical volume-curvature response fixes the residual aspect correction.
However, because the cell functional is still postulated, the result is
best described as a conjectural closure theorem rather than as a derivation
from the primitive field equations.  Appendices~\ref{app:spherical_geometry}
and~\ref{app:sensitivity} make explicit which part is geometrical and which
part remains model-dependent.

The background fluid density $\rhof$ remains open.  Its determination
requires an independent electromagnetic--circulatory coupling or another
observable normalization.  It is therefore deliberately excluded from
the claimed closure chain.

% =============================================================
\section{Conclusion}
\label{sec:conclusion}
% =============================================================

A Compton-core vortex-filament model becomes algebraically closed once
four ingredients are supplied: the Compton-core rotation postulate, the
spectroscopic speed closure, the core-diameter line-tension
normalization, and the thin-wall pressure-balance closure.  These give
\begin{align*}
  \vnorm  &= \sqrt{\pi\hbar cR_\infty/m_e},
  &\rc    &= \vnorm/\omega_C = r_e/2, \\
  \Gz     &= 2\pi\rc\vnorm,
  &\Tc    &= m_ec^2/(2\rc),\\
  \rhocore &= m_ec^2/(2\pi\vnorm^2\rc^3).
\end{align*}
The relations are dimensionally consistent and internally coherent, but
only the first is a structural postulate and the others depend on
explicit closures.  A future first-principles derivation must replace
those closures by a dynamical calculation of $\alpha$, the line tension,
the interfacial stress law, and at least one low-energy observable
coefficient.


The spherical pressure-cell functional added here provides one explicit
candidate for the $\alpha$ closure,
Eq.~\eqref{eq:alpha_spherical_prediction}.  It succeeds algebraically and
numerically within the stated pressure-cell model, but its status remains
conditional on deriving that functional from the full hydrodynamic or
field-theoretic SST dynamics.  In particular, the retrospective \(\Et\)
value used for the ledger should not be conflated with the companion
BEM/NLS stationary point; the latter is the non-CODATA route, whereas the
former records what the original Compton-core closure would need to match.



% =============================================================
\appendix
% =============================================================

% =============================================================
\section{Assumption ledger and epistemic status}
\label{app:assumptions}
% =============================================================

This appendix gives the audit ledger for the closure chain.  The purpose is
to separate algebraic consequences from empirical calibrations and from
model-specific pressure-cell closures.  Standard constants and the
fine-structure constant are understood in their CODATA 2022 sense
\cite{MohrTaylor2022}; the electromagnetic coupling interpretation of
$\alpha$ is the standard one used in quantum electrodynamics and particle-data
summaries \cite{PeskinSchroeder1995,PDG2022}.  Vortex-filament and
local-induction terminology follows the classical hydrodynamic literature
\cite{Batchelor1967,Saffman1992,Donnelly1991}.

\begin{table}[h]
\centering
\caption{Assumption ledger.  ``Input'' means externally supplied; ``closure''
means model-specific; ``derived'' means algebraic consequence within the
listed assumptions.}
\label{tab:app_assumption_ledger}
\scriptsize
\begin{tabular}{@{}llll@{}}
\toprule
Label & Statement & Status & Main role \\
\midrule
A0 & $m_e,c,\hbar,R_\infty,\alpha$ & empirical constants & reference scales \\
A1 & $\Omega_{\rm core}=m_ec^2/\hbar$ & core postulate & Compton rotation \\
A2 & $2\vnorm/c=\tilde\alpha$ & spectroscopic closure & speed calibration \\
A3 & $\Tc=m_ec^2/(2r_c)$ & energy closure & line tension \\
A4 & $P_L=\gamma_c/r_c$ & thin-wall closure & density \\
A5 & BS logarithmic self-energy & filament ansatz & local pressure \\
A6 & $A_K\to1/(4\pi)$ & conjectured slender-core asymptote & $a=r_c$ \\
A7 & $\mathcal E_0=274.074996$ & conjectured external aspect input & leading FSC scale \\
A8 & $R_{\rm cell}=\chi_R L_K$, $\chi_R=2$ & spherical-cell closure & outer-cell scale \\
A9 & $\eta_K=1/(2\chi_R\mathcal L_K)$ & algebraic from A8 & shell parameter \\
A10 & $\Xi_{\rm sph}=1+3\eta_K+\eta_K^2$ & pressure-cell closure & aspect correction \\
\bottomrule
\end{tabular}
\end{table}

Under A0--A4, the paper proves only the algebraic closure of
$\vnorm$, $r_c$, $\Gamma_0$, $\Tc$, and $\rho_{\rm core}$ from the chosen
inputs.  Under A5--A10, it proves the conditional spherical-cell
reproduction of $\alpha_{\rm cell}$.  The strongest defensible statement is
therefore not that $\alpha$ is derived from first principles, but that the
proposed cell model reproduces its numerical scale from explicit geometric,
pressure-balance, and aspect inputs.  Assumption A7 is numerically
dominant: since $\alpha_{\rm cell}\simeq2/\mathcal E_0$, it fixes the first
four to five significant figures of the result.  A fundamental derivation requires replacing A7 and A8 by an independent
eigenvalue/stationarity problem.  The companion BEM/NLS-shell finite-cell
calculation is one candidate solution of that problem; in the present paper A7
and A8 remain ledgered as closure inputs, because the purpose here is to audit
what the Compton-core algebra itself fixes.  The numerical ideal-trefoil
ropelength used here is taken from
the Knot Atlas ideal-knot data file~\cite{KnotAtlasIdeal}; rigorous
ropelength theory and bounds are discussed in Ref.~\cite{Cantarella2002}.

% =============================================================
\section{Biot--Savart pressure-balance theorem}
\label{app:bs_pressure}
% =============================================================

The local part of the self-energy of a slender filament has a logarithmic
cutoff dependence.  In classical vortex dynamics this is the same structural
origin as the local-induction logarithm \cite{Saffman1992,Batchelor1967}.
Here the normalized form is written as
\begin{equation}
  E_{\rm BS}(a)
  =\rho_f \Gamma_0^2 L_K
   \left[A_K\log\!\left(\frac{L_K}{a}\right)+a_K\right],
  \label{eq:app_bs_energy}
\end{equation}
where $a$ is the tube radius and $2\pi aL_K$ is the tube-wall area.  The
normal pressure generated by this self-energy is
\begin{align}
  P_{\rm irr}(a)
  &=-\frac{1}{2\pi aL_K}\frac{\partial E_{\rm BS}}{\partial a}
    \nonumber\\
  &=\frac{\rho_f\Gamma_0^2A_K}{2\pi a^2}.
  \label{eq:app_pirr}
\end{align}
The sign convention is that positive $P_{\rm irr}$ opposes an inward decrease
of the tube radius.

Balancing this pressure against the core dynamic pressure,
\begin{equation}
  P_{\rm core}=\frac{1}{2}\rho_f\vnorm^2,
  \label{eq:app_pcore}
\end{equation}
gives
\begin{equation}
  \frac{\rho_f\Gamma_0^2 A_K}{2\pi a^2}
  =\frac{1}{2}\rho_f\vnorm^2 .
  \label{eq:app_balance}
\end{equation}
Using the circulation definition
\begin{equation}
  \Gamma_0=2\pi r_c\vnorm
  \label{eq:app_gamma}
\end{equation}
yields
\begin{equation}
  \boxed{\frac{a}{r_c}=\sqrt{4\pi A_K}} .
  \label{eq:app_anc}
\end{equation}
Thus the conjectured slender-core asymptote $A_K=1/(4\pi)$ is exactly the
no-contact core-radius closure $a=r_c$.  The units are consistent because
$\rho_f\Gamma_0^2/a^2$ has units
$({\rm kg\,m^{-3}})({\rm m^4\,s^{-2}}){\rm m^{-2}}={\rm Pa}$.

% =============================================================
\section{Spherical pressure-cell geometry}
\label{app:spherical_geometry}
% =============================================================

This appendix gives the geometrical origin of the cell factor used in
Sec.~\ref{sec:spherical_cell}.  The construction is a coarse-grained
control-volume model, not a theorem of classical hydrodynamics.  The
spherical parallel-surface expansion is a standard result of convex and
integral geometry \cite{Schneider2014}; here only the elementary spherical
case is required.

Let $R_{\rm cell}$ be the radius of the surrounding spherical equilibration
cell and let $a$ be the tube radius.  Define
\begin{equation}
  \eta\equiv \frac{a}{R_{\rm cell}} .
  \label{eq:app_eta_general}
\end{equation}
For a spherical surface shifted outward by $a$, the area Jacobian is
\begin{equation}
  J_A(\eta)
  =\frac{4\pi(R_{\rm cell}+a)^2}{4\pi R_{\rm cell}^2}
  =(1+\eta)^2
  =1+2\eta+\eta^2 .
  \label{eq:app_area_jacobian}
\end{equation}
The corresponding first radial volume response per unit area is normalized as
\begin{equation}
  J_V^{(r)}(\eta)=\eta .
  \label{eq:app_radial_volume}
\end{equation}
The proposed pressure-cell multiplier is therefore
\begin{equation}
  \Xi_{\rm sph}(\eta)=J_A(\eta)+J_V^{(r)}(\eta)
  =1+3\eta+\eta^2 .
  \label{eq:app_xi_general}
\end{equation}
The additional $\eta$ term is the single isotropic compression/expansion
mode of the surrounding spherical control volume; without it one would keep
only the parallel-surface area response.

For the ideal trefoil, let
\begin{equation}
  \mathcal L_K=\frac{L_K}{D_K}
  \label{eq:app_ropelength}
\end{equation}
be the ropelength, with $D_K=2a$ the tube diameter.  Write the
coarse-grained equilibration radius as
\begin{equation}
  R_{\rm cell}=\chi_R L_K .
  \label{eq:app_Rcell_chi}
\end{equation}
Then
\begin{equation}
  \eta_K(\chi_R)=\frac{a}{R_{\rm cell}}
  =\frac{D_K/2}{\chi_R L_K}
  =\frac{1}{2\chi_R\mathcal L_K}.
  \label{eq:app_eta_k_general}
\end{equation}
The main text uses the closure choice $\chi_R=2$, giving
\begin{equation}
  \eta_K=\frac{1}{4\mathcal L_K}.
  \label{eq:app_eta_k}
\end{equation}
For this choice,
\begin{equation}
  \boxed{\Xi_{\rm sph}
  =1+\frac{3}{4\mathcal L_K}+\frac{1}{16\mathcal L_K^2}} .
  \label{eq:app_xi_k}
\end{equation}
The nontrivial model choices in this appendix are the unweighted
combination $J_A+J_V^{(r)}$ and the spherical coarse-graining coefficient
$\chi_R=2$; Appendix~\ref{app:sensitivity} shows how changes in these
choices move the predicted coupling.

% =============================================================
\section{Conditional fine-structure closure theorem}
\label{app:alpha_theorem}
% =============================================================

Combining Appendix~\ref{app:bs_pressure} and
Appendix~\ref{app:spherical_geometry} gives the conditional closure used in
the main text.  Let the zeroth-order aspect parameter be $\mathcal E_0$ and
let the effective aspect parameter be
\begin{equation}
  \mathcal E_{\rm eff}=\mathcal E_0(1-\delta_{\rm cell}) .
  \label{eq:app_E_eff_def}
\end{equation}
The conjectured slender-core asymptote $A_K=1/(4\pi)$ converts the finite-core
factor $\pi^2A_K/\mathcal E_0^2$ into
\begin{equation}
  \frac{\pi^2A_K}{\mathcal E_0^2}=\frac{\pi}{4\mathcal E_0^2} .
  \label{eq:app_pi_over_four}
\end{equation}
Multiplication by the spherical-cell factor gives
\begin{equation}
  \delta_{\rm cell}
  =\frac{\pi}{4\mathcal E_0^2}
   \left(1+\frac{3}{4\mathcal L_K}+\frac{1}{16\mathcal L_K^2}\right).
  \label{eq:app_delta_cell}
\end{equation}
The conditional prediction is therefore
\begin{equation}
  \boxed{\alpha_{\rm cell}
  =\frac{2}{\mathcal E_0\left[1-
  \dfrac{\pi}{4\mathcal E_0^2}\left(1+\dfrac{3}{4\mathcal L_K}
  +\dfrac{1}{16\mathcal L_K^2}\right)\right]}} .
  \label{eq:app_alpha_cell}
\end{equation}
This is a dimensionless statement conditional on the external aspect input
$\mathcal E_0$ and the cell-radius closure $\chi_R=2$.  It should be
compared with the CODATA recommended value of $\alpha$, not treated as a
replacement for precision QED or atomic-recoil determinations
\cite{MohrTaylor2022,Karshenboim2005}.

For
\begin{equation}
  \mathcal E_0=274.074996,
  \qquad
  \mathcal L_K=16.371498,
  \qquad
  \chi_R=2,
  \label{eq:app_numerical_inputs}
\end{equation}
one obtains
\begin{align}
  \eta_K &= 0.0152704413,\nonumber\\
  \Xi_{\rm sph} &= 1.046044510,\nonumber\\
  \mathcal E_{\rm eff} &= 274.071998421,\nonumber\\
  \alpha_{\rm cell}^{-1} &= 137.035999211 .
  \label{eq:app_numerical_alpha}
\end{align}
The agreement with CODATA 2022 is at the $10^{-10}$ fractional level, but
only within the pressure-cell assumptions listed in
Appendix~\ref{app:assumptions}.  The leading numerical scale is fixed by
$\mathcal E_0$, not by the spherical correction.  The ideal-trefoil
ropelength value is taken from the Knot Atlas ideal-knot data
file~\cite{KnotAtlasIdeal}; the minimum-ropelength framework is discussed
in Ref.~\cite{Cantarella2002}.

% =============================================================
\section{Numerical reproducibility and convergence requirements}
\label{app:numerics}
% =============================================================

The numerical role of $A_K$ is independent of the spherical-cell ansatz.  It
is extracted from the local logarithmic slope of $E_{\rm BS}(a)/L_K$ against
$-\log a$, as described in classical local-induction calculations
\cite{Saffman1992}.  The robust implementation solves stationary roots in
$x=a/r_c$ rather than in meters to avoid absolute-tolerance artifacts at
$10^{-15}\,{\rm m}$ scales.

\begin{table}[h]
\centering
\caption{Representative trefoil closure outputs.  The first line is an early
30-mode local-plateau extraction; the second line is the higher-resolution
v10.3 practical estimate using the ideal database and local C++ scan.}
\label{tab:app_numerics}
\begin{tabular}{lllll}
\toprule
Run & Geometry/source & $A_K$ & $A_K/(1/4\pi)$ & $a_{\rm nc}/r_c$ \\
\midrule
30-mode plateau & fallback ideal trefoil & 0.08330250 & 1.046810 & 1.0231 \\
v10.3 practical & ideal.txt, 183 modes & 0.07957157 & 0.99992579 & 0.99996290 \\
\bottomrule
\end{tabular}
\end{table}

The practical estimate is therefore consistent with
\begin{equation}
  A_K\to\frac{1}{4\pi},
  \qquad
  \frac{a_{\rm nc}}{r_c}=\sqrt{4\pi A_K}\to1 .
  \label{eq:app_AK_limit}
\end{equation}
For a publication-grade numerical theorem, the remaining requirements are:
(i) monotone or contractive high-$N$ tails for the preferred plateau method;
(ii) agreement between local-slope and global-fit diagnostics; (iii) mesh and
regularization independence; and (iv) a public script and data archive giving
$N_{\rm geom}$, $N_{\rm int}$, $A_K$, $A_K/(1/4\pi)$, and
$a_{\rm nc}/r_c$ for every retained run.  Until those checks are satisfied,
$A_K=1/(4\pi)$ should be stated as a conjectured asymptotic value or robust
numerical-limit ansatz, not as a proven analytical identity.

% =============================================================
\section{Sensitivity and falsification}
\label{app:sensitivity}
% =============================================================

The spherical-cell closure is falsifiable because its coefficients enter
$\alpha_{\rm cell}$ explicitly.  First replace the quadratic term by a free
coefficient,
\begin{equation}
  \Xi_{\rm sph}(\beta)
  =1+3\eta_K+\beta\eta_K^2 .
  \label{eq:app_beta_sensitivity}
\end{equation}
Then the prediction becomes
\begin{equation}
  \alpha_{\rm cell}(\beta)
  =\frac{2}{\mathcal E_0\left[1-
  \dfrac{\pi}{4\mathcal E_0^2}\left(1+3\eta_K+\beta\eta_K^2\right)\right]} .
  \label{eq:app_alpha_beta}
\end{equation}
For the numerical choices of Eq.~\eqref{eq:app_numerical_inputs}, the exact
CODATA central value would require
\begin{equation}
  \beta_{\rm req}\simeq1.10,
  \label{eq:app_beta_req}
\end{equation}
whereas the spherical parallel-surface model uses $\beta=1$.  Thus the
agreement is good but not insensitive to the assumed second-order cell
geometry.  This is a key falsifier: a different coarse-grained cell geometry
predicts a different $\beta$ and therefore a different $\alpha_{\rm cell}$.

Second, expose the cell-radius choice by writing
\begin{equation}
  \eta_K(\chi_R)=\frac{1}{2\chi_R\mathcal L_K}.
  \label{eq:app_eta_chi_sensitivity}
\end{equation}
The three-parameter sensitivity map is then
\begin{equation}
  \alpha_{\rm cell}(\mathcal E_0,\beta,\chi_R)
  =\frac{2}{\mathcal E_0\left[1-
  \dfrac{\pi}{4\mathcal E_0^2}
  \left(1+3\eta_K(\chi_R)+\beta\eta_K(\chi_R)^2\right)
  \right]} .
  \label{eq:app_alpha_E_beta_chi}
\end{equation}
This equation makes the parameter correlations explicit.  A shift of
$\mathcal E_0$ changes the leading value at order $\Delta\mathcal E_0/
\mathcal E_0$, while $\beta$ and $\chi_R$ affect only the residual
finite-core correction at order $\mathcal E_0^{-2}$.  Therefore the
sub-ppm agreement cannot be interpreted as an independent prediction unless
$\mathcal E_0$ and $\chi_R$ are obtained from a separate variational or
spectral problem.

A third falsifier is the ropelength dependence.  Differentiating
Eq.~\eqref{eq:app_alpha_cell} shows that changing $\mathcal L_K$ changes
$\alpha_{\rm cell}$ at order $\mathcal E_0^{-3}\mathcal L_K^{-2}$.  A
non-trefoil candidate or a different ideal-knot ropelength must therefore
move the prediction.  Finally, any low-energy application must produce an
observable correction such as a form factor or a short-range potential,
for example
\begin{equation}
  F_e(q^2)=1-\frac{1}{6}\langle r^2\rangle_{\rm eff}q^2+O(q^4),
  \label{eq:app_form_factor}
\end{equation}
or
\begin{equation}
  V(r)=-\frac{e^2}{4\pi\epsilon_0 r}+\Delta V(r;r_c),
  \label{eq:app_potential_correction}
\end{equation}
which can be constrained by atomic spectroscopy and QED precision tests
\cite{Bethe1947,Karshenboim2005,PDG2022}.

% =============================================================
\section{Historical notes not used as evidence}
\label{app:history}
% =============================================================

This appendix records two historical numerical motifs that may motivate a
search pattern but are not used as evidentiary steps in the closure theorem.
First, Clausius reported gas-expansion coefficients near
$0.003665\,{\rm K}^{-1}$ in the nineteenth-century mechanical theory of heat
\cite{Clausius1867}.  This is close to $\alpha/2$ numerically, but it is
dimensional and depends on temperature scale and material regime; it is
therefore not a derivation of a fundamental dimensionless coupling.

Second, non-standard non-holonomic-background models have discussed aspect
ratios near $274$ and associated velocity ratios
\cite{RabounskiBorissova2007,OrosDiBartini2005}.  Those sources are not part
of the orthodox derivation.  In the present paper $\mathcal E_0$ is treated
as the conjectured external aspect input A7 in
Appendix~\ref{app:assumptions}.  If an orthodox version is desired,
historical material from this appendix can be omitted without changing the
algebraic pressure-cell theorem; only the explicit status of A7 must remain.

% =============================================================
\begin{acknowledgments}
The author acknowledges helpful discussions on the distinction between
algebraic closure, empirical calibration, and first-principles
derivation.
\end{acknowledgments}

% =============================================================

\subsection*{Companion-paper status}
The present paper is intentionally conservative: it records the closure inputs
needed by the Compton-core scaling model.  Companion work supplies a proposed
BEM/NLS-shell finite-cell eigenvalue calculation for the previously external
aspect scale, and a separate far-field theorem target for identifying
\(\alpha_{\rm cell}\) with the electromagnetic fine-structure coupling.  Those
companion results strengthen the overall program but do not alter the ledger
classification of the assumptions used in this paper.

\begin{thebibliography}{99}

\bibitem{Helmholtz1867}
H.~von Helmholtz,
On the integrals of the hydrodynamical equations which express
vortex-motion,
\textit{Philosophical Magazine} \textbf{33}, 485 (1867).

\bibitem{Kelvin1867}
Lord Kelvin (W.~Thomson),
On vortex atoms,
\textit{Proceedings of the Royal Society of Edinburgh} \textbf{6},
94 (1867).

\bibitem{MohrTaylor2022}
P.~J. Mohr, D.~B. Newell, B.~N. Taylor, and E.~Tiesinga,
CODATA recommended values of the fundamental physical constants: 2022,
arXiv:2409.03787 (2024).

\bibitem{Donnelly1991}
R.~J. Donnelly,
\textit{Quantized Vortices in Helium II},
Cambridge University Press, 1991.

\bibitem{Pethick2008}
C.~J. Pethick and H.~Smith,
\textit{Bose--Einstein Condensation in Dilute Gases}, 2nd ed.,
Cambridge University Press, 2008.
\doi{10.1017/CBO9780511802850}

\bibitem{FaddeevNiemi1997}
L.~D. Faddeev and A.~J. Niemi,
Stable knot-like structures in classical field theory,
\textit{Nature} \textbf{387}, 58 (1997).
\doi{10.1038/387058a0}

\bibitem{Barcelo2005}
C.~Barcel\'o, S.~Liberati, and M.~Visser,
Analogue gravity,
\textit{Living Reviews in Relativity} \textbf{8}, 12 (2005).
\doi{10.12942/lrr-2005-12}

\bibitem{Volovik2003}
G.~E. Volovik,
\textit{The Universe in a Helium Droplet},
Oxford University Press, 2003.

\bibitem{Saffman1992}
P.~G. Saffman,
\textit{Vortex Dynamics},
Cambridge University Press, 1992.
\doi{10.1017/CBO9780511624063}

\bibitem{Onsager1949}
L.~Onsager,
Statistical hydrodynamics,
\textit{Nuovo Cimento Supplement} \textbf{6}, 279 (1949).
\doi{10.1007/BF02780991}

\bibitem{Feynman1955}
R.~P. Feynman,
Application of quantum mechanics to liquid helium,
in \textit{Progress in Low Temperature Physics}, vol.~1,
ed.\ C.~J. Gorter, p.~17, North-Holland, 1955.

\bibitem{Gibbons2002}
G.~W. Gibbons,
The maximum tension principle in general relativity,
\textit{Foundations of Physics} \textbf{32}, 1891 (2002).
\doi{10.1023/A:1022370717626}

\bibitem{Schiller2006}
C.~Schiller,
Simple derivation of minimum length, minimum dipole moment, and
lack of space-time continuity,
\textit{International Journal of Theoretical Physics} \textbf{45},
221 (2006).
\doi{10.1007/s10773-005-4835-2}

\bibitem{Karshenboim2005}
S.~G. Karshenboim,
Precision physics of simple atoms: QED tests, nuclear structure, and
fundamental constants,
\textit{Physics Reports} \textbf{422}, 1 (2005).
\doi{10.1016/j.physrep.2005.08.008}

\bibitem{Bethe1947}
H.~A. Bethe,
The electromagnetic shift of energy levels,
\textit{Physical Review} \textbf{72}, 339 (1947).
\doi{10.1103/PhysRev.72.339}

\bibitem{Batchelor1967}
G.~K. Batchelor,
\textit{An Introduction to Fluid Dynamics},
Cambridge University Press, 1967.
\doi{10.1017/CBO9780511800955}


\bibitem{Cantarella2002}
J.~Cantarella, R.~B. Kusner, and J.~M. Sullivan,
On the minimum ropelength of knots and links,
\textit{Inventiones Mathematicae} \textbf{150}, 257 (2002).
\doi{10.1007/s00222-002-0234-y}

\bibitem{KnotAtlasIdeal}
D.~Bar-Natan and contributors,
The Knot Atlas: ideal knot data file \texttt{Ideal.txt.gz},
\url{https://katlas.org/images/d/d2/Ideal.txt.gz}.
Accessed 2026.

\bibitem{Schneider2014}
R.~Schneider,
\textit{Convex Bodies: The Brunn--Minkowski Theory}, 2nd ed.,
Cambridge University Press, 2014.
\doi{10.1017/CBO9781139003858}

\bibitem{RabounskiBorissova2007}
D.~Rabounski and L.~Borissova,
A theory of the Podkletnov effect based on general relativity: anti-gravity
force due to the perturbed non-holonomic background of space,
\textit{Progress in Physics} \textbf{3}, 57 (2007).
\url{https://www.ptep-online.com/2007/PP-10-07.PDF}

\bibitem{PDG2022}
R.~L. Workman et al.\ (Particle Data Group),
Review of particle physics,
\textit{Progress of Theoretical and Experimental Physics}
\textbf{2022}, 083C01 (2022).
\doi{10.1093/ptep/ptac097}

\bibitem{PeskinSchroeder1995}
M.~E. Peskin and D.~V. Schroeder,
\textit{An Introduction to Quantum Field Theory},
Addison-Wesley, 1995.
ISBN: 978-0201503975.

\bibitem{Clausius1867}
R.~Clausius,
\textit{The Mechanical Theory of Heat, with its Applications to the
Steam-Engine and to the Physical Properties of Bodies},
edited by T.~Archer Hirst, with an introduction by J.~Tyndall,
John Van Voorst, London, 1867.

\bibitem{OrosDiBartini2005}
R.~Oros di Bartini,
Relations between physical constants,
\textit{Progress in Physics} \textbf{3}, 34 (2005).
\url{https://www.ptep-online.com/2005/PP-03-06.PDF}

\bibitem{Osserman1978}
R. Osserman,
``The isoperimetric inequality,''
\emph{Bulletin of the American Mathematical Society} \textbf{84},
1182--1238 (1978).
DOI: 10.1090/S0002-9904-1978-14553-4.

\bibitem{Maggi2012}
F. Maggi,
\emph{Sets of Finite Perimeter and Geometric Variational Problems},
Cambridge University Press, Cambridge (2012).
DOI: 10.1017/CBO9781139108133.

\bibitem{Madelung1927}
E. Madelung,
``Quantentheorie in hydrodynamischer Form,''
\emph{Zeitschrift f\"ur Physik} \textbf{40}, 322--326 (1927).
DOI: 10.1007/BF01400372.

\bibitem{Gross1961}
E. P. Gross,
``Structure of a Quantized Vortex in Boson Systems,''
\emph{Nuovo Cimento} \textbf{20}, 454--477 (1961).
DOI: 10.1007/BF02731494.

\bibitem{Bogoliubov1947}
N. N. Bogoliubov,
``On the Theory of Superfluidity,''
\emph{Journal of Physics USSR} \textbf{11}, 23--32 (1947).

\end{thebibliography}

\end{document}
