
% =====================================================================

% SST Canon Addendum — Overlaps & Synthesis Map (A–I)

% Version tag: v0.3.1+2025-08-27-J (bridging-only; does not modify Core)

% =====================================================================


\section*{ Parameter Dictionary (cross-referencing A–I)}

\begin{align*}

&\textbf{Cutoff / EFT (A):} && E_c\equiv \hbar,\Omega_c=\hbar,|\mathbf v_{!\circlearrowleft}|/r_c.\

&\textbf{Misalignment (A3):} && \xi_{\ae}=v^2/f_{\ae}^2.\

&\textbf{Projector flavour (A4):} && {\hat{\mathbf v}\textit{a,\hat{\mathbf v}\textit{b,\hat{\mathbf v}\textit{c}.\

&\textbf{ASG (B):} && f_g,\ f_y;\quad y}{t,*}^2-y}{b,*}^2=(Q_t^2-Q_b^2),g}{Y,\textit{}^2/;\color{gray}{\text{(SM: }=\tfrac13 g_{Y,}}^2\text{)}}.\

&\textbf{EW kernels (C):} && \Delta\rho,\ \Delta r,\ a_\mu;\quad F_0,\ F^{\textrm C,N}\textit{{1,2}\ (\text{loop polynomials}).\

&\textbf{EJA ladder (D):} && \sqrt m\text{-eigenvalues }{s-\delta,\ s,\ s+\delta},\ \delta^2=3/8.\

&\textbf{R2M2 (E):} && M_f(\mu)=y_f(\mu),\alpha(\mu)\alpha^\dagger(\mu),\ \alpha: S^2\text{ curve }\Gamma;\ \omega\equiv|\mathrm d\alpha/\mathrm d\ln\mu|.\

&\textbf{Safe PS (F):} && G}{\textrm PS},\ v_R,\ N_{Fi},\ A_i=3,\ (\bar\lambda_i)\leftarrow(\lambda_j),\ m_b\simeq(M_F m_t)/(\sqrt2 m_B).\

&\textbf{Sterile/modulino (G):} && (\Delta m^2,\theta)\textit{{41},\ m}{\tilde z}\sim [(M_P R)^2,4\pi^2 R]^{-1} f(\omega),\ m_{3/2}=\omega/R.\

&\textbf{Entanglement (H):} && E^{\perp}\textit{{ud}(\theta_C;y),\ y\equiv (Y^uY^d/\cos^2\theta_W)+\sin^2\theta_W Q_uQ_d.\

&\textbf{Unified flavor (I):} && \mathcal G}{\textrm UFG}(T),\ \text{local groups},\ \text{CP inner/outer};\ T_{\ae}\ (\text{swirl modulus}).

\end{align*}


\section*{ Synthesis Matrix}

\renewcommand{\arraystretch}{1.15}

\begin{tabular}{p{3.1cm}|p{12.3cm}}

\textbf{Theme} & \textbf{Overlap (who constrains whom)}\\hline

\emph{Flavor backbone} & (D) EJA fixes adjacent $\sqrt{m}$ ratios via $s\pm\delta$; (E) R2M2 generates hierarchies/mixings from $\alpha(\mu)$ rotation; (H) EMH selects Cabibbo/mixing minima via $E^{\perp}_{\min}$; (I) local flavor groups set allowed textures/CP via $T_{\ae}$. Together: choose $\Gamma$, $T_{\ae}$, and an interference weight $y$ so that (D) $\Rightarrow$ ratios, (E) $\Rightarrow$ leakage consistent with (D), and (H) $\Rightarrow$ observed small quark vs large lepton mixings.\\

\emph{Top--bottom split} & (B) demands $y_{t}>y_{b}$ by $\Delta y^2 = (Q_t^2 - Q_b^2)g_{Y,*}^2$; (F) generates $m_b\ll m_t$ via $(10,1,1)$ mixing. Compatible if $m_b/m_t\simeq M_F/(\sqrt{2} m_B)$ saturates the required IR split after running from the ASG-determined UV difference.\\

\emph{EW integrity} & (C) $|\Delta\rho|\lesssim 10^{-3}$ on any new doublet; (A3) pNGB misalignment with custodial symmetry preserves $\Delta\rho\approx 0$. Use (C) as a veto on spectrum choices introduced by (E,F,H,I).\\

\emph{Naturalness/EFT} & (A1,A2) cap power growth at $E_c$ and require fine-tuning bookkeeping for any bridging scalar; dovetails with pNGB option in (A3) and with UV safety (F) or gravitational fixed points (B).\\

\emph{Sterile window} & (G) defines a decoupled sterile sector (aetherino), consistent with (C) and (A) since couplings are Planck-suppressed; does not disturb the flavor backbone but offers experimental hooks (FPF).\\

\emph{CP origin} & (E) converts strong $\theta$ to CKM phase through rotation; (I) makes CP inner (exact) at enhancement loci and outer (spontaneously broken) away; both mechanisms can co-exist: R2M2 provides the phase while $T_{\ae}$ controls where CP is protected/broken.\\

\end{tabular}

\section*{Compatibility Lemmas}

\paragraph{Lemma 1 (EJA $\leftrightarrow$ R2M2).} For a fermion species $f$, suppose R2M2 yields (small-angle) leakage
\[
m^{(f)}_2/m^{(f)}_3 \simeq c_f\,\Delta\theta_{23}^2,\quad m^{(f)}_1/m^{(f)}_2 \simeq c'_f\,\Delta\theta_{12}^2.
\]
The EJA ladder (D6) gives
\[
\left(\frac{m^{(f)}_2}{m^{(f)}_3}\right)^{1/2} = \frac{s_f}{s_f+\delta},\qquad \left(\frac{m^{(f)}_1}{m^{(f)}_2}\right)^{1/2} = \frac{s_f-\delta}{s_f}.
\]
Then the two descriptions are mutually consistent if
\begin{equation}
\Delta\theta_{23} = \frac{1}{\sqrt{c_f}}\,\frac{s_f}{s_f+\delta},\qquad \Delta\theta_{12} = \frac{1}{\sqrt{c'_f}}\,\frac{s_f-\delta}{s_f}
\end{equation}
for some real $c_f,c'_f>0$. Thus EJA sets \emph{targets} for the arc-lengths along $\Gamma$; R2M2 supplies them geometrically.

\paragraph{Lemma 2 (EMH $\leftrightarrow$ Cabibbo).} With the two-generation entangling-power kernel (H2), there exists an interference weight $y\in\mathbb{R}$ such that
\[
\left.\frac{\partial E^{\perp}_{ud}}{\partial \theta_C}\right|_{\theta_C=\theta^\star}=0
\]
holds at a desired $\theta^\star\in(0,\pi/4)$. In particular, deforming $y$ away from its SM value by small anisotropies in neutral vs charged-current swirl permeability moves the minimum continuously from $\sim 6^\circ$ toward $\sim 13^\circ$, thereby matching the projector-driven Cabibbo in (A4).

\paragraph{Lemma 3 (ASG $\leftrightarrow$ PS split).} Take $\tan\beta=1$ at the PS scale so $y_t\simeq y_b$. ASG then enforces a UV offset $\Delta y^2 = \tfrac{1}{3} g_{Y,*}^2$. After RG flow and PS vector-like mixing, the IR ratio obeys
\begin{equation}
\frac{m_b}{m_t} \simeq \frac{M_F}{\sqrt{2} m_B}\left[1-\frac{\Delta y^2}{2y_t^2}+\mathcal{O}(\text{running})\right]
\end{equation}
so choosing $M_F/m_B$ fixes $m_b/m_t$ while respecting the ASG-induced inequality $y_t>y_b$.

\paragraph{Lemma 4 (EW integrity under misalignment).} If custodial symmetry is preserved (pNGB map A3 with custodial coset), then new contributions to $\Delta\rho$ vanish at leading order; any extra doublets (C1) must satisfy $|\Delta\rho|\lesssim10^{-3}$. Coupling deviations scale as $\delta g_{hVV}/g_{hVV} = -\tfrac{1}{2}\xi_{\ae}$, hence $\xi_{\ae}\ll1$ suffices to keep both Higgs-coupling and $W$-mass constraints under control.

\section*{ Minimal Canon Workflow (bridging layer)}

\begin{enumerate}
\item \textbf{Choose local flavor groups} per sector via $T_{\ae}$ (I); decide CP inner/outer at that scale.
\item \textbf{Pick a rotation curve} $\Gamma(\mu;a)$ (E) with one curvature parameter $a$; this sets leakages and mixing via small arc lengths.
\item \textbf{Fix EJA targets} by selecting $(s_f,\delta)$ (D) (canonical $\delta^2=3/8$) and equate with the R2M2 arc relations of Lemma~1 to determine $a$ and $c_f,c'_f$.
\item \textbf{Tune Cabibbo} by the EMH selector (H): adjust the interference weight $y$ (swirl permeability) to place the $E^{\perp}_{ud}$ minimum at the desired $\theta_C$.
\item \textbf{Impose ASG/PS} via Lemma~3 for third family, then extend to lighter families with the projector basis (A4) and R2M2 geometry.
\item \textbf{Check EW kernels} (C): $\Delta\rho$, $a_\mu$, and $\Delta r$ for any extra excitations introduced; ensure $\xi_{\ae}$ is small (A3).
\item \textbf{Optionally add a sterile window} (G): record $(\Delta m^2,\theta)$ consistent with cosmology toggles; keep Planck-suppressed couplings to avoid conflicts with (C).
\end{enumerate}

\section*{Tensions \& Resolutions}

\begin{itemize}
\item \textbf{Cabibbo $6^\circ$ vs $13^\circ$.} Resolved by Lemma~2: small $y$-deformations (effective neutral/charged-current balance) shift the EMH minimum to the projector target.
\item \textbf{EJA fixed $\delta$ vs R2M2 flexibility.} Lemma~1 equates EJA ratios to arc lengths, absorbing differences into species coefficients $c_f,c'_f$ (expected from differing $y_f$ normalizations).
\item \textbf{ASG inequality vs PS $\tan\beta=1$.} Lemma~3 shows vector-like mixing accomplishes the IR split while keeping $y_t>y_b$ as required in the UV.
\item \textbf{EW bounds vs new excitations.} Apply the Custodial Integrity Rule (C1) and small $\xi_{\ae}$; veto spectra that overshoot $|\Delta\rho|$.
\end{itemize}

\section*{Dimensional \& Limit Checks}

All synthesis relations are dimensionally consistent: arc lengths are angles, mass ratios are dimensionless, loop kernels dimensionless, and $\xi_{\ae}$ dimensionless. Limits: $\omega\to 0$ (no rotation) $\Rightarrow$ no mixing; $\delta\to 0$ (EJA collapse) $\Rightarrow$ degenerate families; $y\to 0$ (no neutral-current interference) $\Rightarrow$ EMH prefers small Cabibbo.

% =====================================================================
% End of Addendum J
% =====================================================================

\begin{aligned}
&\text{(D6) EJA ratios:} && \frac{\sqrt{m}_{\textrm mid}}{\sqrt{m}_{\textrm heavy}} = \frac{s}{s+\delta},\quad
\frac{\sqrt{m}_{\textrm light}}{\sqrt{m}_{\textrm mid}} = \frac{s-\delta}{s},\quad \delta^2 = \tfrac{3}{8}.\\[4pt]
&\text{(E) Rotating rank-one:} && M_f(\mu) = y_f(\mu)\,\alpha(\mu)\alpha^\dagger(\mu),\quad \alpha:\ S^2\text{ curve},\\
&m_2/m_3 \simeq c_f\,\Delta\theta_{23}^2,\quad m_1/m_2 \simeq c'_f\,\Delta\theta_{12}^2.\\[4pt]
&\text{(H2) EMH kernel:} && 
E^{\perp}_{ud}(\theta_C;y) = 8y^2\left[\frac{\cos^4\theta_C}{(1+2y+4y^2-2y\cos2\theta_C)^2}
+\frac{\sin^4\theta_C}{(1+2y+4y^2+2y\cos2\theta_C)^2}\right].\\[4pt]
&\text{(B3_{\textrm SM}) ASG difference:} && y_{t,*}^2-y_{b,*}^2 = \tfrac{1}{3}g_{Y,*}^2.\\[4pt]
&\text{(F) PS vectorlike split:} && m_b \simeq \dfrac{M_F\,m_t}{\sqrt{2}\,m_B}\quad(\text{at leading order}).\\[4pt]
&\text{(C \& A3) EW/Higgs bounds:} && |\Delta\rho|\lesssim 10^{-3},\quad \delta g_{hVV}/g_{hVV} = -\tfrac{1}{2}\xi_{\ae},\quad \xi_{\ae}\ll1.
\end{aligned}