\documentclass[11pt,a4paper]{article}

% ---------------------------------------------------------------------------
% Orthodox, framework-free manuscript.
% Central result: a NEGATIVE / obstruction result plus one clean non-circular
% leading coincidence. No claim of a first-principles derivation of alpha.
% Verified research scripts are included verbatim in the appendices.
% ---------------------------------------------------------------------------

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage[scaled=0.92]{helvet}
\usepackage{courier}
\usepackage{amsmath,amssymb,amsthm}
% (hbar handled inline via \hslash)
\usepackage{geometry}
\geometry{margin=1.0in}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\usepackage{listings}

% ---- code listing style for appendices --------------------------------------
\definecolor{codegray}{gray}{0.95}
\definecolor{codecomment}{rgb}{0.30,0.45,0.30}
\definecolor{codekw}{rgb}{0.10,0.10,0.65}
\lstdefinestyle{py}{
  language=Python,
  basicstyle=\ttfamily\scriptsize,
  keywordstyle=\color{codekw},
  commentstyle=\color{codecomment}\itshape,
  stringstyle=\color{black},
  backgroundcolor=\color{codegray},
  breaklines=true,
  showstringspaces=false,
  numbers=left,
  numberstyle=\tiny,
  frame=single,
  framesep=4pt,
  columns=fullflexible,
  keepspaces=true,
}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

% epistemic status tags (kept light, in orthodox language)
\newcommand{\established}{\textbf{[established]}}
\newcommand{\derivedmodel}{\textbf{[derived-in-model]}}
\newcommand{\conditional}{\textbf{[conditional]}}
\newcommand{\open}{\textbf{[open]}}

\title{An $\alpha$-free trefoil-ropelength coincidence\\
and the obstruction to part-per-million\\
fine-structure closure}

\author{%
  O.~Iskandarani\\
  \small Independent Researcher, Groningen, The Netherlands\\
  \small ORCID: 0009-0006-1686-3961
}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We study a well-posed finite-cell variational eigenvalue problem for a
finite-core trefoil filament enclosed by a spherical pressure-compliance
boundary, and we examine whether its leading dimensionless eigenvalue can
reproduce the inverse fine-structure constant $\alpha^{-1}$. We report a clean
positive result and a precisely quantified negative one. \emph{Positive:} a
parameter-light geometric quantity built from a single topological invariant, the
ideal trefoil ropelength $\mathcal{L}_{3_1}$, namely
$\tfrac{8\pi}{3}\,\mathcal{L}_{3_1}=137.15471$, lies within
$8.66\times10^{-4}$ ($866$~ppm) of the CODATA value $\alpha^{-1}=137.035999$.
This is a \emph{sub-per-mille}, not a part-per-million, agreement. Its numerical
prefactor $\tfrac{16\pi}{3}=N_p\cdot\tfrac{4\pi}{3}$ contains a mode-count factor
$N_p=4$ that we derive from the finite-cell surface spectrum
$k_\ell=\ell(\ell+1)-2$; the construction uses no electromagnetic input, which we
verify by an explicit provenance audit. \emph{Negative:} closing the residual
$866$~ppm to part-per-million accuracy is \emph{not} a single-coefficient problem.
The conditional second-order coefficient $c_2=11/48$ reaches only $10.5$~ppm, not
ppm-level; exact closure at fixed cell-radius gate requires a transverse shell
weight $w_\perp=1.0675$ (not the round value $1$), whereas an independent
Gross--Pitaevskii core-profile computation returns $w_\perp\approx2.076$, which
\emph{overshoots} to $-157$~ppm on the opposite side. We show that the residual
$10.5$~ppm can be absorbed independently by any of five distinct sub-percent
coefficients (shell weight, cell-radius gate, pressure-sector volume, ropelength
value, or a third-order term), and that part-per-million closure requires the
ropelength to a relative precision $\sim10^{-6}$ that exceeds the precision to
which ideal-knot ropelength is presently known. We conclude that part-per-million
fine-structure closure is, in this construction, underdetermined and effectively
not falsifiable, and that the defensible result is the $\alpha$-free
sub-per-mille leading coincidence with $N_p=4$ derived. All numerical claims are
reproduced by the scripts in the appendices.
\end{abstract}

\paragraph{Epistemic conventions.}
To keep the status of each statement explicit we tag claims as \established{}
(textbook physics/mathematics), \derivedmodel{} (a consequence of the stated
model), \conditional{} (depends on an unproven coefficient choice), or \open{}
(an unresolved gate). The central claim of this paper is a \conditional{}/\open{}
\emph{obstruction}, not a derivation.

\section{Introduction}
\label{sec:intro}

Attempts to obtain dimensionless coupling constants from geometry or topology
have a long and largely cautionary history, and a numerical coincidence between a
geometric quantity and $\alpha^{-1}$ is, on its own, weak evidence for anything.
We therefore frame this work around a precise \emph{negative} question. Given a
finite-cell variational problem whose leading eigenvalue happens to lie close to
$\alpha^{-1}$, can the residual gap be closed using only quantities supplied by
the model's own primitive (field) equation, without inserting a constant chosen
to reproduce the answer? We find that it cannot, and we localise the obstruction
to a single, computable scalar.

The construction is deliberately minimal. A finite-core filament in the shape of
the ideal trefoil $3_1$ is taken as the source; its self-energy is regularised by
a core radius fixed by a no-contact closure condition; the filament is enclosed by
a spherical boundary that supplies a pressure-compliance term; and the
dimensionless cell action is extremised over an aspect parameter $E$. The only
topological input is the ropelength $\mathcal{L}_{3_1}$. We emphasise at the outset
that this quantity is, in the literature, a \emph{numerically computed} object: the
tightest trefoil conformation is obtained by constrained relaxation algorithms
\cite{PieranskiPrzybyl2001IdealTrefoil,PrzybylPieranski2014HighResolutionTrefoil}
and reported as a numerical upper bound
\cite{BaranskaPieranskiRawdon2004RopelengthPolygonal,AshtonCantarellaPiatekRawdon2005SelfContact},
not as a closed-form analytic invariant. This distinction is decisive for the
part-per-million question (Section~\ref{sec:degeneracy}). No empirical value of
$\alpha$, and no electromagnetic constant, enters the construction of the
eigenvalue; we verify this provenance explicitly in
Section~\ref{sec:provenance}.

A central methodological point organises the paper. Even a perfectly closed
second-order calculation would not establish a derivation unless its inputs are
themselves free of $\alpha$. We therefore impose the strict ordering
\begin{equation}
  \underbrace{G_0}_{\text{input provenance}}
  \;\longrightarrow\;
  \underbrace{H_2,\,H_3}_{\text{pressure / phase Hessians}}
  \;\longrightarrow\;
  \alpha_{\mathrm{cell}},
  \label{eq:ordering}
\end{equation}
and we argue that the part-per-million programme is blocked at $G_0$, not at the
Hessians.

Section~\ref{sec:leading} presents the leading geometric value and derives the
mode-count factor $N_p=4$ from the surface spectrum. Section~\ref{sec:bem}
describes the boundary-element eigenvalue and its negative control.
Section~\ref{sec:provenance} records the provenance audit establishing that the
construction is $\alpha$-free. Section~\ref{sec:obstruction} states the
shell-deficit identity, corrects the naive precision target (the round value
$w_\perp=1$ reaches only $10.5$~ppm; exact closure needs $w_\perp=1.0675$), and
shows that the Gross--Pitaevskii proxy overshoots to the opposite side.
Section~\ref{sec:degeneracy} establishes the main negative result: the residual is
absorbed by any of five sub-percent coefficients, so part-per-million closure is
underdetermined. Section~\ref{sec:discussion} summarises the honest status.

\section{The finite-cell construction and its leading value}
\label{sec:leading}

\subsection*{Core regularisation}
The self-energy of a finite-core filament of unit circulation has the standard
slender-body form $E_{\mathrm{BS}}(a)=A_K\,\log(\Lambda/a)+\text{(finite)}$,
where $a$ is the core radius and $A_K$ is the logarithmic Biot--Savart
coefficient. For a smooth slender filament the local-induction theorem gives
\begin{equation}
  A_K \;\longrightarrow\; \frac{1}{4\pi}\,. \qquad \established
  \label{eq:AK}
\end{equation}
A cutoff-energy scan over the ideal-trefoil Fourier curve (Appendix~\ref{app:closure})
reproduces \eqref{eq:AK} as a plateau value, and the no-contact closure
$a_{\mathrm{nc}}/r_c=\sqrt{4\pi A_K}\to 1$ fixes the regularising radius without
reference to any electromagnetic scale.

\subsection*{Leading geometric value}
Within the spherical pressure-cell model the dimensionless aspect eigenvalue
acquires a leading scale set by the ropelength,
\begin{equation}
  E_p^{\mathrm{lead}} \;=\; \frac{16\pi}{3}\,\mathcal{L}_{3_1},
  \qquad
  \mathcal{L}_{3_1}=16.371637,
  \label{eq:Ep}
\end{equation}
so that the associated inverse coupling, defined by $\alpha^{-1}=E/2$, is
\begin{equation}
  \boxed{\;\alpha^{-1}_{\mathrm{lead}}
  \;=\;\frac{8\pi}{3}\,\mathcal{L}_{3_1}
  \;=\;137.15471\;}
  \qquad \derivedmodel
  \label{eq:lead}
\end{equation}
which differs from $\alpha^{-1}_{\mathrm{CODATA}}=137.035999$ by
\begin{equation}
  \frac{\alpha^{-1}_{\mathrm{lead}}-\alpha^{-1}_{\mathrm{CODATA}}}
       {\alpha^{-1}_{\mathrm{CODATA}}}
  \;=\;+8.66\times10^{-4}\;=\;+866~\text{ppm}.
  \label{eq:leaddev}
\end{equation}
We stress that this is a \emph{sub-per-mille} agreement; the part-per-million
language sometimes attached to this construction applies only to the
second-order--corrected value of Sections~\ref{sec:obstruction}--\ref{sec:degeneracy},
not to \eqref{eq:lead}.
The prefactor in \eqref{eq:Ep} factors as $16\pi/3=N_p\cdot 4\pi/3$, where
$4\pi/3$ is the volume of the unit three-ball (the leading pressure sector) and
the mode-count $N_p$ is \emph{not} free:

\begin{definition}[Soft sector]
\label{def:soft}
For the spherical finite-cell surface problem we identify the mode-count $N_p$
with the number of independent surface modes in the \emph{soft sector}, i.e. the
modes whose surface stiffness eigenvalue $k_\ell$ is non-positive ($k_\ell\le0$):
the zero modes ($k_\ell=0$) and any unstable modes ($k_\ell<0$). Strictly
positive-stiffness modes are excluded.
\end{definition}

\begin{proposition}[Surface mode count, \derivedmodel{}]
\label{prop:Np}
The spherical surface stiffness spectrum is
\begin{equation}
  k_\ell \;=\; \ell(\ell+1)-2, \qquad \ell=0,1,2,\dots,
  \label{eq:kspectrum}
\end{equation}
so that $k_0=-2$ (one breathing/compression mode), $k_1=0$ (the three rigid
translation zero modes), and $k_\ell>0$ for $\ell\ge2$. By
Definition~\ref{def:soft} the soft sector is exactly $\ell\in\{0,1\}$, whence
\begin{equation}
  N_p \;=\; \underbrace{1}_{\ell=0}+\underbrace{3}_{\ell=1} \;=\; 4.
\end{equation}
The result is consistent with the isoperimetric inequality and with the nonlinear
shape-stability tests of Appendix~\ref{app:closure}.
\end{proposition}

\noindent We emphasise that Proposition~\ref{prop:Np} is a derivation only
\emph{given} the soft-sector identification of Definition~\ref{def:soft}; that
identification (non-positive stiffness, i.e. zero plus unstable modes) is a
modelling choice, natural but not forced, and we flag it as such rather than
leaving it implicit. The remaining prefactor elements---the sector volume
$4\pi/3$ and the overall factor $\tfrac12$---are \emph{not} derived here; the
former is forced to be the unit-ball volume only at leading order, while its
part-per-million correction is an \open{} quantity entangled with the pressure
Hessian (Section~\ref{sec:degeneracy}). We therefore describe \eqref{eq:lead}
precisely as: a single topological invariant multiplied by a partially-derived
geometric prefactor lands within $866$~ppm of $\alpha^{-1}$.

\begin{remark}[Status of the ropelength input]
\label{rem:benchmark}
A further qualification is essential. The value $\mathcal{L}_{3_1}=16.371637$ is
itself a numerically computed quantity---a relaxation-algorithm result and
numerical upper bound
\cite{PieranskiPrzybyl2001IdealTrefoil,BaranskaPieranskiRawdon2004RopelengthPolygonal,AshtonCantarellaPiatekRawdon2005SelfContact},
not a closed-form analytic invariant. The trefoil ropelength input used here is
therefore treated as a \emph{numerical-geometry benchmark}, not as a theorem-level
$\alpha$-free input. Consequently \eqref{eq:lead} is best read as an $\alpha$-free
numerical coincidence at $866$~ppm rather than as a derived constant; this point
returns with force in Section~\ref{sec:degeneracy}, where it bounds what
part-per-million closure could possibly mean.
\end{remark}

\section{The boundary-element eigenvalue and its negative control}
\label{sec:bem}

To test whether the leading scale \eqref{eq:Ep} corresponds to a genuine
stationary point rather than an imposed value, we discretise the cell action
\begin{equation}
  \mathcal{A}_{\mathrm{tot}}(E)
  \;=\;\tfrac12\,\mathbf{n}^{\!\top} C_{\mathrm{BEM}}(E)\,\mathbf{n}
  \;+\;\mathcal{A}_{\mathrm{pressure}}(E),
  \label{eq:action}
\end{equation}
where $C_{\mathrm{BEM}}(E)$ is a scalar single-layer boundary-element response
matrix on the trefoil tube plus spherical outer boundary, and
$\mathcal{A}_{\mathrm{pressure}}(E)$ is the spherical pressure-compliance term
with scale \eqref{eq:Ep} dressed by the finite-shell correction of
Section~\ref{sec:obstruction}. Extremising \eqref{eq:action} yields a
reproducible interior stationary eigenvalue
\begin{equation}
  E_\star = 274.0749, \qquad
  \text{bracket } [273.93,\,274.12], \qquad \derivedmodel
  \label{eq:Estar}
\end{equation}
classified as an interior minimum. The downstream coupling, computed from
$E_\star$ and the ropelength alone (with closure coefficients $\chi_R=2$,
$\beta=1$; see below), is
\begin{equation}
  \alpha^{-1}_{\mathrm{cell}} = 137.0359, \qquad
  \frac{\alpha_{\mathrm{cell}}-\alpha_{\mathrm{CODATA}}}{\alpha_{\mathrm{CODATA}}}
  = 3.6\times10^{-7}.
  \label{eq:alphacell}
\end{equation}

\paragraph{Negative control \established{}.}
The location \eqref{eq:Estar} is supplied by the pressure-compliance term. With
that term removed (BEM-only action), no interior stationary point exists and the
solver returns \texttt{E0\_not\_derived}. Hence the eigenvalue is not an artefact
of the boundary discretisation alone; equally, the BEM does not generate the scale
$274$ independently of the prescribed pressure scale \eqref{eq:Ep}. The honest
reading is that the BEM \emph{confirms a stationary point at the ropelength-set
scale}, with a working falsification control.

\paragraph{Downstream closure coefficients \conditional{}.}
The map from $E_\star$ to $\alpha^{-1}_{\mathrm{cell}}$ in \eqref{eq:alphacell}
uses
\begin{equation}
  \alpha_{\mathrm{cell}} = \frac{2}{E_{\mathrm{eff}}},\qquad
  E_{\mathrm{eff}} = E_\star\Big(1-\frac{\pi}{4}\,\frac{\xi}{E_\star^2}\Big),\qquad
  \xi = 1+3\eta+\beta\eta^2,\quad
  \eta=\frac{1}{2\chi_R\mathcal{L}_{3_1}},
\end{equation}
with $\chi_R=2$ (the cell-radius gate $R_{\mathrm{cell}}=2\mathcal{L}_K$) and
$\beta=1$. These are \open{} coefficients: $\chi_R=2$ is argued within a minimal
reciprocal-pressure action but not independently established, and $\beta=1$ is a
choice. The part-per-million agreement \eqref{eq:alphacell} is therefore
\conditional{} on $\{\chi_R=2,\beta=1\}$ in addition to the shell weight discussed
next; it should not be read as a prediction.

\section{The second-order correction and the precision target}
\label{sec:obstruction}

The residual $866$~ppm between \eqref{eq:lead} and CODATA is partly absorbed by a
finite-shell correction to the pressure scale,
\begin{equation}
  E_p \;=\; \frac{16\pi}{3}\,\mathcal{L}_{3_1}
  \Big[\,1-\frac{c_2}{\mathcal{L}_{3_1}^2}\,\Big],
  \qquad
  \alpha^{-1}_{\mathrm{cell}} = \frac{8\pi}{3}\mathcal{L}_{3_1}
  \Big[\,1-\frac{c_2}{\mathcal{L}_{3_1}^2}\,\Big],
  \label{eq:shell}
\end{equation}
whose correction coefficient $c_2$ is the crux of this section. The conditional
value $c_2=11/48=0.22917$ used in earlier drafts of this construction does
\emph{not} reach part-per-million accuracy:
\begin{equation}
  c_2=\tfrac{11}{48}\;\Longrightarrow\;
  \alpha^{-1}_{\mathrm{cell}}=137.03744,\qquad
  \frac{\Delta}{\alpha^{-1}_{\mathrm{CODATA}}}=+10.5~\text{ppm}.
  \label{eq:1148}
\end{equation}
Exact agreement instead requires
\begin{equation}
  c_2^{\mathrm{req}}
  =\mathcal{L}_{3_1}^2\Big(1-\frac{\alpha^{-1}_{\mathrm{CODATA}}}{\tfrac{8\pi}{3}\mathcal{L}_{3_1}}\Big)
  =0.231978,
  \label{eq:c2req}
\end{equation}
so that $11/48$ is a convenient rational approximation but not the closure value.

\subsection*{The shell-deficit identity}
\begin{proposition}[Shell-deficit identity, \derivedmodel{}]
\label{prop:sigma}
For the spherical core profile with radial Jacobian
$1-(1-\eta)^3 = 3\eta-3\eta^2+\eta^3$, angular average
$\langle\sin^2\rangle=\tfrac23$ and projector-trace average $\tfrac23$, the total
shell-deficit exponent is
\begin{equation}
  \sigma \;=\; \sigma_{\mathrm{vol}} + \sigma_\perp
        \;=\; 3 + \tfrac{2}{3}\,w_\perp,
  \qquad
  c_2=\frac{\sigma}{4\chi_R^2}=\frac{\sigma}{16}\ (\chi_R=2),
  \label{eq:sigma}
\end{equation}
where $w_\perp$ is the transverse shell weight. The symbolic derivation is
reproduced verbatim in Appendix~\ref{app:shell}.
\end{proposition}

\subsection*{The precision target is not the round value}
Combining \eqref{eq:c2req} with \eqref{eq:sigma} at fixed $\chi_R=2$, exact
closure requires
\begin{equation}
  \sigma^{\mathrm{req}}=16\,c_2^{\mathrm{req}}=3.71165,
  \qquad
  \boxed{\,w_\perp^{\mathrm{req}}=\tfrac32(\sigma^{\mathrm{req}}-3)=1.0675\,}.
  \label{eq:wreq}
\end{equation}
Thus the part-per-million target is \emph{not} the round value $w_\perp=1$ (which
yields only $10.5$~ppm); it is the non-round $1.0675$. The independent
Gross--Pitaevskii (GP) core-profile computation of the same weight
(Appendix~\ref{app:wperp}) returns instead
\begin{equation}
  w_\perp^{\mathrm{GP}} \approx 2.076
  \;\Longrightarrow\;
  \sigma\approx4.38,\quad c_2\approx0.274,\quad
  \alpha^{-1}_{\mathrm{cell}}\approx137.0145,
  \label{eq:wperpGP}
\end{equation}
i.e. an \emph{overshoot} of $-157$~ppm on the opposite side of CODATA. The GP
value is therefore not merely imprecise: it lands on the wrong side of the target,
so no small correction to the GP computation can recover \eqref{eq:wreq}.

\begin{theorem}[Failure of the single-coefficient closure]
\label{thm:obstruction}
Within the finite-cell construction at fixed cell-radius gate $\chi_R=2$,
part-per-million agreement with $\alpha^{-1}$ requires the transverse shell weight
$w_\perp=1.0675$ \eqref{eq:wreq}. The Gross--Pitaevskii core equation, which
governs the same transverse profile, yields $w_\perp\approx2.076$
\eqref{eq:wperpGP}, corresponding to an inverse coupling on the opposite side of
the CODATA value. Hence part-per-million closure cannot be obtained by computing
$w_\perp$ from the primitive equation; the round value $w_\perp=1$ that appears to
``almost'' close the construction is itself only a $10.5$~ppm approximation and
not the closure value.
\end{theorem}

\begin{proof}[Proof (within the model)]
By \eqref{eq:sigma}, $c_2=\sigma/16$ and $\sigma=3+\tfrac23 w_\perp$. Exact
closure requires $c_2=c_2^{\mathrm{req}}=0.231978$ \eqref{eq:c2req}, hence
$\sigma=3.71165$ and $w_\perp=1.0675$. The round value $w_\perp=1$ gives
$c_2=11/48=0.22917$, i.e. $137.03744$ ($+10.5$~ppm). The GP computation
(Appendix~\ref{app:wperp}) returns $w_\perp=2.076$, hence $c_2=0.274$ and
$137.0145$ ($-157$~ppm). The required value $1.0675$ lies between, matching
neither the round value nor the primitive-equation value. \qedhere
\end{proof}

\noindent Theorem~\ref{thm:obstruction} shows the single-coefficient route fails.
The deeper obstruction---why no \emph{combination} of coefficients can be claimed
to close the construction---is the subject of Section~\ref{sec:degeneracy}.

\section{Provenance audit: the construction is non-circular}
\label{sec:provenance}

Because the leading value \eqref{eq:lead} lies close to $\alpha^{-1}$, it is
essential to verify that no empirical electromagnetic quantity enters the
construction. We record the audit explicitly.

\begin{enumerate}
\item The eigenvalue $E_\star$ \eqref{eq:Estar} is extremised from
\eqref{eq:action}; its inputs are the trefoil tube geometry (ropelength and
Fourier coefficients), the spherical boundary, and the pressure scale
\eqref{eq:Ep}--\eqref{eq:shell}. None of these contains $\alpha$, $e$,
$\varepsilon_0$, $\hslash$, $m_e$, or any length fixed through them.
\item The downstream map to $\alpha^{-1}_{\mathrm{cell}}$ uses only $E_\star$,
$\mathcal{L}_{3_1}$, $\chi_R$, $\beta$. No electromagnetic constant appears.
\item The CODATA value of $\alpha$ is used \emph{only} for the comparisons
\eqref{eq:leaddev} and \eqref{eq:alphacell}; it is never an input.
\end{enumerate}
Consequently the obstruction of Theorem~\ref{thm:obstruction} is a statement
internal to a non-circular construction: the leading value is genuinely $\alpha$-free,
and the failure to close to part-per-million is not an artefact of having inserted
$\alpha$ somewhere upstream.

\section{The degeneracy obstruction and the ropelength precision wall}
\label{sec:degeneracy}

Theorem~\ref{thm:obstruction} rules out the single-coefficient ($w_\perp$) route.
We now show a stronger statement: the residual $10.5$~ppm left by the conditional
$c_2=11/48$ value can be absorbed \emph{independently} by any one of several
sub-percent coefficients, so that part-per-million agreement carries no
discriminating power.

\subsection*{Five interchangeable closure routes}
Holding all other quantities fixed, the $10.5$~ppm residual of \eqref{eq:1148} is
removed exactly by each of the following single adjustments:
\begin{center}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{@{}llll@{}}
\toprule
Route & adjust & required value & shift from nominal \\
\midrule
A (shell weight)   & $w_\perp$          & $1.0675$        & $+6.7\%$ vs $1$ \\
B (cell-radius gate)& $\chi_R$          & $1.98784$       & $-0.61\%$ vs $2$ \\
C (sector volume)  & $V_{\mathrm{sect}}$ & $4.188746$      & $-10.5$~ppm vs $4\pi/3$ \\
D (ropelength)     & $\mathcal{L}_{3_1}$ & $16.371465$     & $-10.5$~ppm vs $16.371637$ \\
E (third order)    & $c_3$              & $O(1)$          & via $c_3\eta^3$, $\eta=\tfrac{1}{4\mathcal{L}}$ \\
\bottomrule
\end{tabular}
\end{center}
The numbers are reproduced in the audit script accompanying this paper. Route~E is
quantitatively decisive on its own: with core parameter
$\eta=1/(4\mathcal{L}_{3_1})=0.015270$ one has $\eta^3=3.56\times10^{-6}$, so an
$O(1)$ third-order coefficient shifts $\alpha^{-1}$ by
$\approx 137\cdot\eta^3=3.6$~ppm, and an $O(3)$ coefficient covers the entire
residual. Truncating the shell expansion at second order is therefore not
justified at part-per-million accuracy in the first place.

\begin{theorem}[Degeneracy of part-per-million closure]
\label{thm:degeneracy}
Within the present construction, part-per-million agreement with $\alpha^{-1}$ does
not single out any coefficient: the $10.5$~ppm residual is absorbed independently
by $w_\perp$, $\chi_R$, $V_{\mathrm{sect}}$, $\mathcal{L}_{3_1}$, or $c_3$, each at
the sub-percent (or smaller) level. Consequently no individual coefficient can be
claimed to be ``derived'' by demanding part-per-million closure; the residual lies
within the joint undetermined freedom of the model.
\end{theorem}

\noindent This is an identifiability statement: with five interchangeable
sub-percent knobs, landing within $\sim10$~ppm of $\alpha^{-1}$ is essentially
guaranteed once any one of them is allowed to float, and a fit that closes the gap
provides no evidence that the corresponding coefficient is physically correct.

\subsection*{The ropelength precision wall}
Route~D exposes a sharper, input-level obstacle. The sensitivity of the leading
value to the ropelength is $\partial\alpha^{-1}/\partial\mathcal{L}_{3_1}=8\pi/3$,
so part-per-million ($|\Delta\alpha^{-1}|<1.37\times10^{-4}$) requires
\begin{equation}
  |\Delta\mathcal{L}_{3_1}| \;<\; 1.6\times10^{-5},
  \qquad\text{i.e. a relative precision } \sim10^{-6}.
  \label{eq:Ltol}
\end{equation}
The ideal trefoil ropelength is, however, not a closed-form analytic invariant but
a numerically computed object. The tightest conformation is obtained by
constrained relaxation algorithms (the SONO algorithm
\cite{PieranskiPrzybyl2001IdealTrefoil} and later finite-element refinements
\cite{PrzybylPieranski2014HighResolutionTrefoil}), and the reported values are
numerical \emph{upper bounds}: Ashton, Cantarella, Piatek and Rawdon define
ropelength as the minimum length of unit-diameter tubes in a knot type and report
improved upper bounds for knots up to nine crossings \emph{except} the trefoil,
which remained tied to prior computations
\cite{AshtonCantarellaPiatekRawdon2005SelfContact}; Bara\'nska, Pieranski and
Rawdon discuss explicitly the algorithmic bounding and estimation of smooth-knot
ropelength and compare computation methods
\cite{BaranskaPieranskiRawdon2004RopelengthPolygonal}. Since the input is a
numerical bound rather than a value certified to $\sim10^{-6}$, the tolerance
\eqref{eq:Ltol} cannot be met from the topological input, and part-per-million
closure is \emph{not a topological derivation}, independently of the pressure and
phase Hessians. Equivalently: if $\mathcal{L}_{3_1}=16.371637$ is a numerical
upper bound rather than a certified invariant, then $\tfrac{8\pi}{3}\mathcal{L}_{3_1}$
is a numerical-geometry benchmark (Remark~\ref{rem:benchmark}), not a theorem-level
$\alpha$-free input.

\subsection*{The gate hierarchy}
The two preceding results refine the ordering \eqref{eq:ordering} into a four-gate
hierarchy, only the first element of which is presently met:
\begin{equation}
  \underbrace{G_0}_{\substack{\text{input}\\\text{provenance}}}
  \;\longrightarrow\;
  \underbrace{G_1}_{\substack{\text{identifiability /}\\\text{degeneracy breaking}}}
  \;\longrightarrow\;
  \underbrace{G_2}_{\substack{\text{operator Hessians}\\(H_2,H_3)}}
  \;\longrightarrow\;
  \underbrace{G_3}_{\substack{\text{ppm}\\\text{closure}}},
  \label{eq:gatehierarchy}
\end{equation}
with
$G_0=\{\mathcal{L}_{3_1},N_p,V_{\mathrm{sect}},\chi_R,E_{\mathrm{eff}},\eta\text{-scaling}\}$
and $G_1$ the requirement that no several free sub-percent corrections can absorb
the same residual. Theorem~\ref{thm:degeneracy} shows $G_1$ \emph{fails} at present,
and the ropelength wall shows $G_0$ is not met to ppm tolerance; both block closure
\emph{before} the Hessians $G_2$ become relevant. This inverts the naive picture
$H_2,H_3\to\alpha$: writing the Hessians is not the bottleneck (both are already in
symbolic form); they are necessary downstream gates, not sufficient ones. Moreover
$G_0$ and $G_2$ are not separable at part-per-million order---the sector-volume
correction $\epsilon_V$ (Route~C) and the shell weight $w_\perp$ (Route~A) are both
finite-cell quantities produced by the \emph{same} Hessian, so they cannot be
treated as independent gates. We conclude that the defensible, falsifiable content
of the construction is the $\alpha$-free \emph{sub-per-mille} leading coincidence
\eqref{eq:lead} with $N_p=4$ derived (Proposition~\ref{prop:Np}), and that
part-per-million closure is, at present, both underdetermined ($G_1$) and not
resolvable from the topological input ($G_0$).
\section{Discussion}
\label{sec:discussion}

\paragraph{What we do not claim.}
We do not claim a first-principles derivation of the fine-structure constant. The
leading value \eqref{eq:lead} reproduces $\alpha^{-1}$ only at the sub-per-mille
($866$~ppm) level; its agreement contains one derived element ($N_p=4$,
Proposition~\ref{prop:Np}) and undetermined ones (the sector factor $4\pi/3$ and
the overall $\tfrac12$). The part-per-million figure \eqref{eq:alphacell} is
\conditional{} on $\{\chi_R=2,\beta=1,w_\perp=1.0675\}$, none of which is supplied
by the primitive equation, and by Theorem~\ref{thm:degeneracy} the residual that
these absorb carries no discriminating power. The honest status is therefore: a
non-circular, parameter-light geometric coincidence at sub-per-mille level, plus a
precisely localised demonstration that improving it to part-per-million is
underdetermined.

\paragraph{What would remove the obstruction.}
A genuine part-per-million claim would require the entire input set
$\{\mathcal{L}_{3_1},N_p,V_{\mathrm{sect}},\chi_R,\sigma,c_{3+}\}$ to be fixed
$\alpha$-free, each to the tolerance implied by \eqref{eq:Ltol} and its analogues
($|\Delta\sigma|<4.3\times10^{-3}$, $|\Delta w_\perp|<6.4\times10^{-3}$). At
present $N_p=4$ alone meets this standard. In particular a corrected transverse
core computation would have to return $w_\perp=1.0675$ (not the round $1$, and not
the GP proxy $2.076$) from the primitive equation, \emph{and} the sector volume
and ropelength would have to be pinned independently to $\sim10^{-6}$ relative
precision. We regard the ropelength precision wall \eqref{eq:Ltol} as the most
likely terminal obstruction.

\paragraph{Falsifiability.}
The construction makes checkable statements independent of any interpretation.
\emph{(a)} The surface mode count is $N_p=4$ (Proposition~\ref{prop:Np}); a
finite-element computation of the same surface spectrum returning $N_p\neq4$ would
falsify the prefactor in \eqref{eq:Ep}. \emph{(b)} The transverse shell weight
returned by the GP core profile is $w_\perp\approx2.076$, on the opposite side of
the precision target $1.0675$ (Appendix~\ref{app:wperp}); this is what makes the
single-coefficient closure fail. \emph{(c)} Part-per-million closure is
degenerate (Theorem~\ref{thm:degeneracy}); exhibiting a derivation of all six
inputs to the tolerances above, with no $\alpha$-pinned step, would overturn this
assessment. The coincidence \eqref{eq:lead} itself is not a prediction and is
presented only as the $\alpha$-free leading result.

\paragraph{Status.} The leading sub-per-mille coincidence is \derivedmodel{} up to
the open sector and normalisation factors; part-per-million closure is
\conditional{}/\open{} and, by Theorem~\ref{thm:degeneracy}, underdetermined.

\section*{Data and code availability}
The scripts that reproduce every numerical statement in this paper are included in
the appendices and provided as the files \texttt{reproduce\_alpha\_cell\_closure.py},
\texttt{derive\_gp\_shell\_deficit.py},
\texttt{derive\_relaxed\_gp\_core\_hessian\_wperp.py}, and
\texttt{audit\_ppm\_closure.py}.

\appendix
\section{Symbolic shell-deficit identity \texorpdfstring{$\sigma=3+\tfrac23 w_\perp$}{sigma}}
\label{app:shell}
The following script derives Proposition~\ref{prop:sigma} symbolically (radial
Jacobian, angular averages, and the resulting exponents), and prints the special
cases $w_\perp\in\{0,1,11/10\}$.
\lstinputlisting[style=py]{code/derive_gp_shell_deficit.py}

\section{Gross--Pitaevskii transverse shell weight \texorpdfstring{$w_\perp$}{wperp}}
\label{app:wperp}
The following script computes the relaxed GP core profile and the
transverse-to-scalar Hessian ratio, returning $w_\perp\approx2.076$ and the
associated $\sigma$, and reports the open-gate status.
\lstinputlisting[style=py]{code/derive_relaxed_gp_core_hessian_wperp.py}

\section{Finite-cell closure and the leading value}
\label{app:closure}
The following script performs the cutoff-energy Biot--Savart scan, extracts the
plateau coefficient $A_K\to1/(4\pi)$, applies the no-contact closure, and produces
the spherical-cell summary underlying \eqref{eq:Ep}--\eqref{eq:lead}.
\lstinputlisting[style=py]{code/reproduce_alpha_cell_closure.py}

\section{Part-per-million accounting and the five closure routes}
\label{app:audit}
The following script reproduces every numerical statement in
Sections~\ref{sec:obstruction}--\ref{sec:degeneracy}: the $866$~ppm leading gap,
the required coefficient $c_2^{\mathrm{req}}=0.231978$ and weight
$w_\perp^{\mathrm{req}}=1.0675$, the $10.5$~ppm residual of $c_2=11/48$, the
$-157$~ppm overshoot of the GP proxy, the five interchangeable closure routes
(A--E), and the sensitivity bounds including the ropelength tolerance
\eqref{eq:Ltol}.
\lstinputlisting[style=py]{code/audit_ppm_closure.py}

\begin{thebibliography}{9}
\bibitem{PieranskiPrzybyl2001IdealTrefoil}
  P.~Piera\'nski and S.~Przyby\l,
  \emph{The ideal trefoil knot},
  Phys.~Rev.~E \textbf{64}, 031801 (2001),
  DOI:10.1103/PhysRevE.64.031801; arXiv:physics/0103039.
\bibitem{BaranskaPieranskiRawdon2004RopelengthPolygonal}
  J.~Bara\'nska, P.~Piera\'nski and E.~J.~Rawdon,
  \emph{Ropelength of tight polygonal knots},
  arXiv:physics/0409108 (2004);
  arXiv record: to appear in \emph{Physical and Numerical Models in Knot Theory
  and their Application to the Life Sciences}.
\bibitem{AshtonCantarellaPiatekRawdon2005SelfContact}
  T.~Ashton, J.~Cantarella, M.~Piatek and E.~Rawdon,
  \emph{Self-contact sets for 50 tightly knotted and linked tubes},
  arXiv:math/0508248 (2005).
\bibitem{PrzybylPieranski2014HighResolutionTrefoil}
  S.~Przyby\l\ and P.~Piera\'nski,
  \emph{High resolution portrait of the ideal trefoil knot},
  J.~Phys.~A: Math.~Theor.~\textbf{47}, 285201 (2014),
  DOI:10.1088/1751-8113/47/28/285201; arXiv:1402.5760.
\bibitem{PitaevskiiStringari}
  L.~P.~Pitaevskii and S.~Stringari,
  \emph{Bose--Einstein Condensation},
  (Oxford University Press, Oxford, 2003).
\bibitem{CODATA2022}
  E.~Tiesinga, P.~J.~Mohr, D.~B.~Newell, B.~N.~Taylor,
  \emph{CODATA recommended values of the fundamental physical constants: 2022},
  Rev.~Mod.~Phys. (2024). \textit{[value used: $\alpha^{-1}=137.035999177$]}
\end{thebibliography}

\end{document}
