
\subsection{Quark-Like Twist Knots as Quasi-Unknot Defects}
\label{subsec:rt_quark_twist_quasi_unknot}

\textbf{[RESEARCH TRACK / CANON CANDIDATE]} Twist knots and related clasp knots may be interpreted as quasi-unknot carrier loops with a localized twist/clasp defect. Geometrically such a knot can be stretched so that it resembles an unknot with a central aperture, while topologically remaining nontrivial until a crossing change or reconnection occurs.

A useful diagnostic decomposition is
\begin{align}
    K_{\mathrm{twist}}
    \simeq
    0_1 + \Delta_{\mathrm{clasp}},
\end{align}
where $\Delta_{\mathrm{clasp}}$ denotes a localized topological defect region. Candidate audit quantities are
\begin{align}
    \mathcal{U}_{\mathrm{quasi}},\qquad
    A_{\mathrm{aperture}},\qquad
    f_{\mathrm{clasp}},\qquad
    f_{\kappa,\mathrm{localized}},
\end{align}
standing for quasi-unknot score, central aperture, clasp-localization fraction, and curvature-concentration fraction.

\textbf{[CHARGE PLACEHOLDER]} Fractional quark-like charge should not be assigned to the trefoil. If retained, it is represented as fractional exterior boundary winding,
\begin{align}
    \frac{Q}{e}=q_{\partial},
    \qquad
    q_u=+\frac{2}{3},
    \qquad
    q_d=-\frac{1}{3}.
\end{align}
The topological knot supplies the defect carrier; $q_{\partial}$ supplies the charge-sector bookkeeping.

\subsection{Triple-Gear and Borromean Baryon Analogues}
\label{subsec:rt_triple_gear_borromean_baryons}

\textbf{[MECHANICAL ANALOGUE / NOT A PROOF]} The triple-gear print and Borromean-type links are retained as baryon analogues, not as final particle assignments.

The proton-like analogue is a three-component locked system with nonzero exterior collective rotation,
\begin{align}
    \mathcal{B}_{p}^{\mathrm{gear}}
    =
    (C_1,C_2,C_3;\ q_{\partial}=+1,\ \Theta_{\mathrm{ext}}\neq 0),
\end{align}
where the charge proxy is the boundary winding $q_{\partial}$, not raw pairwise helicity.

The neutron-like analogue is a Borromean or Borromean-adjacent system with no net exterior boundary winding but nontrivial three-component topology,
\begin{align}
    \mathcal{B}_{n}^{\mathrm{Bor}}
    =
    (C_1,C_2,C_3;\ q_{\partial}=0,\ \mu_{123}\neq 0).
\end{align}
This preserves the intuition that the neutron is neutral externally while still carrying internal topological structure.

\textbf{[FALSIFIERS]} The proton analogue fails if the locked triple system has no stable exterior collective phase. The neutron analogue fails if the Borromean sector necessarily induces nonzero exterior boundary winding.

\subsection{Trefoil--Gear Kinematic Non-Equivalence}
\label{subsec:rt_trefoil_gear_kinematic_nonequivalence}

\textbf{[RESEARCH TRACK]} The triple gear and segmented trefoil are not kinematically identical even if they use related printed parts. The gear model measures rotation about a straight axle; the trefoil model measures phase transport along a curved framed tube.

For the gear analogue,
\begin{align}
    \omega_{\mathrm{gear}}
    =
    \frac{1}{5}\,\omega_{\mathrm{core}}
\end{align}
if five full core rotations produce one full gear rotation.

For the segmented trefoil Blender model, the shell/blade winding budget is
\begin{align}
    N_{\mathrm{shell,total}}=10,
    \qquad
    N_{\mathrm{shell,segment}}=\frac{10}{3}.
\end{align}
If the same core-staft mechanism gives five core rotations per segment, then
\begin{align}
    \frac{N_{\mathrm{shell,segment}}}{N_{\mathrm{core,segment}}}
    =
    \frac{10/3}{5}
    =
    \frac{2}{3}.
\end{align}
This $2/3$ is therefore a conditional shell/core kinematic ratio, not a trefoil-electron charge assignment.

\subsection{Higgs-as-Trefoil High-Temperature Hypothesis}
\label{subsec:rt_higgs_trefoil_parked}

\textbf{[PARKED / SPECULATIVE]} The idea that a Higgs-like state is a thermally activated trefoil phase is not canon-ready. A single trefoil is chiral and lepton-like in the current taxonomy, whereas a Higgs-like excitation must behave effectively as a scalar sector.

A viable future version would need at least one of the following mechanisms:
\begin{enumerate}
    \item a trefoil--anti-trefoil paired condensate with scalar effective symmetry,
    \item a high-temperature unframed phase where chirality averages out,
    \item an independent scalar amplitude mode coupled to trefoil attachment without identifying the Higgs with the trefoil itself.
\end{enumerate}
Until such a mechanism is derived, the hypothesis remains outside the canon.

