% =====================================================================
% Springer Nature (sn-jnl) template conversion
% Paper: Kelvin Mode Suppression in Atomic Orbitals: A Vortex-Filament Gap
% Author: Omar Iskandarani
% Date (source): 2025-12-14
% Affiliation: Independent Researcher, Groningen, The Netherlands
% License: © 2025 Omar Iskandarani. All rights reserved.
% DOI: 10.5281/zenodo.18018084
% =====================================================================

% =========================
% 1) Document class choice
% =========================
% \documentclass[referee,pdflatex,sn-mathphys-num]{sn-jnl} % double-spacing option for review
\documentclass[pdflatex,sn-mathphys-num]{sn-jnl}

% =========================
% 2) Core packages (lean)
% =========================
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{bm}
\usepackage{siunitx}
% \usepackage{physics}

% TikZ/PGFPlots (used by your figures)
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{caption}
\pgfplotsset{compat=newest}

% ====================================
% 3) Paper metadata macros (edit here)
% ====================================
\newcommand{\papertitle}{Spectroscopic Constraints on Kelvin-Like Internal Modes in Effective Filament Models of Atomic Bound States}
\newcommand{\papershorttitle}{Kelvin-Like Internal Modes in Atomic Bound States}
\newcommand{\paperdoi}{10.5281/zenodo.18018084}
\newcommand{\paperorcid}{0009-0006-1686-3961}
\newcommand{\paperemail}{info@omariskandarani.com}
\newcommand{\papercity}{Groningen}
\newcommand{\papercountry}{The Netherlands}
\newcommand{\paperkeywords}{Kelvin modes, effective filament models, atomic spectroscopy, excitation gap, low-energy reduction}

\raggedbottom

\begin{document}

% =========================
% 5) Title + author block
% =========================
    \title[\papershorttitle]{\papertitle}

    \author*[1]{\fnm{Omar} \sur{Iskandarani}}\email{\paperemail}
    \affil*[1]{\orgname{Independent Researcher}, \orgaddress{\city{\papercity}, \country{\papercountry}}}

% =========================
% 6) Abstract + keywords
% =========================
    \abstract{%
        We consider effective atomic bound-state models supplemented by an internal helical excitation sector with Kelvin-like dispersion. The central question is whether such an internal sector can remain compatible with precision atomic spectroscopy. We obtain a conditional decoupling bound: if the internal spectrum is separated from the orbital sector by an excitation gap $\Delta_K$, then the induced correction is Boltzmann suppressed, $\delta E_n \propto \exp[-\Delta_K/(k_B T_{\mathrm{eff}})]$, and the low-energy orbital description remains spectroscopically stable. By contrast, ungapped constructions do not enjoy generic exponential protection and therefore require additional suppression mechanisms to remain compatible with spectroscopy. The resulting constraint is conditional on the effective occupation scale $T_{\mathrm{eff}}$, the active mode count $N_K$, and the coupling efficiency $\lambda_n$, and is informative only for models in which that coupling is not itself parametrically tiny. A separate dispersion-based estimate places the onset of the lowest internal mode in a geometry-dependent window spanning roughly $10^2\,\mathrm{eV}$ to $10^3\,\mathrm{eV}$ for the fiducial parameter sweep presented in Appendix~A. Taken together, the spectroscopy bound and the onset estimate delimit a conditional parameter region rather than a unique prediction.%
    }

    \keywords{\paperkeywords}

    \maketitle

% Global dimensionless temperature ratio
    \newcommand{\epsilonK}{\varepsilon_K} % Dimensionless temperature ratio

% ============================================================
    \section{Introduction}\label{sec:intro}
        Hydrodynamic and vortex-based models of matter trace back to Kelvin and Helmholtz \cite{Helmholtz1858,Kelvin1867}. Modern superfluid dynamics and quantum turbulence have renewed interest in vortex filaments as fundamental excitations \cite{Onsager1949,Feynman1955,Barenghi2014}.

        In that broader context, it is natural to ask whether an atomic bound state might admit an \emph{effective} description in which the usual orbital degree of freedom is accompanied by an internal filament-like excitation sector.

        This paper does not attempt to establish such a microscopic picture as fundamental. Its purpose is narrower: to derive a consistency condition. If an internal Kelvin-like sector exists and couples to bound electronic states, then atomic spectroscopy immediately constrains its low-energy behavior. The question is therefore not whether one prefers a filament interpretation, but whether any such internal sector can remain invisible at atomic energies.

        The main result is narrower than a no-go theorem. An ungapped Kelvin-like spectrum does not enjoy any generic exponential protection, so compatibility with spectroscopy requires additional suppression from the density of states, the effective occupation scale, or the coupling to observable line shifts. A gapped spectrum avoids this problem: below the gap, the internal sector is effectively frozen and only a Boltzmann-suppressed correction survives. The paper should therefore be read as establishing a conditional consistency bound for internal-mode completions of atomic bound states rather than as ruling out all ungapped constructions in full generality.

% ============================================================
    \section{Kelvin Waves on Vortex Filaments}\label{sec:kelvin}
        For a thin filament with circulation $\Gamma$ and core radius $\xi$, small-amplitude Kelvin waves satisfy \cite{LordKelvin1880,Barenghi2014}
        \begin{equation}
            \omega(k) \simeq \frac{\Gamma}{4\pi} k^2
            \left[
                \ln\!\left(\frac{1}{|k|\xi}\right) + C_0
            \right],
            \label{eq:kelvin_dispersion}
        \end{equation}
        with $C_0=\mathcal{O}(1)$. For a closed filament of length $L$,
        \begin{equation}
            k_m = \frac{2\pi m}{L}, \quad m=1,2,\dots,\qquad
            \omega_m \propto \frac{\Gamma m^2}{L^2}.
        \end{equation}
        Here the logarithmic factor $\ln\!\bigl(1/(|k_m|\xi)\bigr)+C_0$ has been suppressed only for compactness; it is retained in all explicit estimates below.
        For hydrogenic orbitals $r_n=a_0 n^2$, implying $L_n\sim 2\pi a_0 n^2$, Kelvin frequencies soften rapidly with principal quantum number $n$.

% ============================================================
    \section{Thermodynamic Constraint from Atomic Spectroscopy}\label{sec:constraint}
        Suppose an atomic bound state carries, in addition to its orbital energy $E_n^{(0)}$, an internal contribution from Kelvin-like modes,
        \begin{equation}
            E_n^{\mathrm{eff}}(T_{\mathrm{eff}})
            =
            E_n^{(0)} + \delta E_n(T_{\mathrm{eff}}),
        \end{equation}
        where $T_{\mathrm{eff}}$ is not necessarily a literal thermodynamic temperature, but an effective population scale for the internal sector.

        The key physical assumption is that internal excitation energy can feed into an observed level shift with some efficiency $\lambda_n$. A convenient generic parametrization is
        \begin{equation}
            |\delta E_n(T_{\mathrm{eff}})|
            \le
            \lambda_n \sum_m E_{m,n}\, \nu_{m,n}(T_{\mathrm{eff}}),
            \qquad 0\le \lambda_n \le 1,
            \label{eq:generic_coupling_bound}
        \end{equation}
        where $E_{m,n}$ are internal mode energies and $\nu_{m,n}$ are occupation factors. The present paper does not derive $\lambda_n$ microscopically; rather, it keeps that coupling explicit so that the resulting constraint can be read conditionally.

        In an ungapped sector, low-energy modes can in principle be populated down to arbitrarily small excitation energy, and no generic exponential suppression follows. No specific polynomial correction law is assumed here; the point is only that, without a gap, compatibility with spectroscopy must come from additional structure such as a strongly depleted low-energy density of states, a very small effective occupation scale, or a very weak coupling $\lambda_n$ to observable line shifts. By contrast, once the internal spectrum is gapped, the induced correction acquires Boltzmann suppression, which is the only ingredient needed for the consistency bound derived below.

% ============================================================
    \section{Gapped Kelvin Spectrum}\label{sec:gap}
        The minimal decoupling mechanism is an excitation gap $\Delta_K$ in the internal spectrum, so that all active internal modes satisfy $E_{m,n}\ge\Delta_K$. Nothing in the consistency argument below requires a specific operator realization of that sector; the only assumption needed is a discrete gapped mode family whose low-temperature occupations are Boltzmann suppressed. The microscopic origin of $\Delta_K$ is left open here; in an effective filament picture it may arise from topology, curvature, torsion, core structure, or geometric constraints on admissible excitations \cite{Ricca1996}.

        A separate dimensional consistency check uses the same fiducial regulator and loop scale as Appendix~\ref{app:first_kelvin}. For a filament with circulation $\Gamma$ and core radius $\xi$, the tension $T_f \sim \rho \, \Gamma^2/(4\pi \xi^2)$ sets a characteristic bending energy for the first Kelvin mode. Taking the mode wavelength to be of order the loop length $L$, one obtains $\Delta_K \sim \Gamma^2/(4\pi \xi L)$ up to logarithmic corrections. With $\Gamma = h/m_e$, $\xi \sim 10^{-15}\,\mathrm{m}$, and $L \sim 10^{-10}\,\mathrm{m}$, this gives $\Delta_K = \mathcal{O}(10^2\text{--}10^3\,\mathrm{eV})$. This estimate is not independent of Appendix~\ref{app:first_kelvin}: both use the same $(\xi,L)$ inputs and should be read only as mutually consistent order-of-magnitude checks. Here $\xi$ is a short-distance regularization length for the thin-filament description, not a claim about measured electron size; as Appendix~\ref{app:first_kelvin} shows explicitly, increasing $\xi$ or $L$ softens the onset and can eliminate the desired separation from ordinary atomic energy scales.

% ============================================================
    \section{Low-Temperature Thermodynamics}\label{sec:lowT}
        The dimensionless temperature ratio
        \[
            \epsilonK = \frac{k_B T}{\Delta_K} \ll 1
        \]
        characterizes the low-temperature (Kelvin-frozen) regime. For a discrete gapped mode family, low-temperature occupations satisfy the Boltzmann upper bound
        \begin{equation}
            \nu_{m,n}(T) \lesssim \exp\!\left(-\frac{E_{m,n}}{k_B T}\right)
            \le
            \exp\!\left(-\frac{\Delta_K}{k_B T}\right).
            \label{eq:boltzmann_occ}
        \end{equation}
        Substituting Eq.~\eqref{eq:boltzmann_occ} into the generic coupling bound \eqref{eq:generic_coupling_bound} gives
        \begin{equation}
            |\delta E_n(T)|
            \lesssim
            \lambda_n N_K \Delta_K
            \exp\!\left(-\frac{\Delta_K}{k_B T}\right),
            \label{eq:deltaE_boltzmann}
        \end{equation}
        for a finite or effectively truncated set of active modes. This Boltzmann form, rather than any specific ladder-operator realization, is the only thermodynamic input needed below. For comparison, a single harmonic bosonic mode gives the same asymptotic exponential suppression \cite{Pathria2011}.

        \begin{figure}[htbp]
            \centering
            \begin{tikzpicture}
% MAIN PLOT: Thermal Energy vs Temperature
                \begin{axis}[
                width=12cm,
                height=8cm,
                xlabel={$T$ [K]},
                ylabel={$U(T)$ [arb. units]},
                legend style={at={(0.05,0.95)}, anchor=north west},
                domain=0:1.5,
                samples=100,
                axis lines=left,
                enlargelimits=true,
                grid=both,
                xtick={0.5,1.0,1.5},
                ytick={0,1,2,3,4},
                xlabel style={font=\small},
                ylabel style={font=\small},
                title={Kelvin-Mode Thermal Energy vs Temperature},
                title style={font=\bfseries\small},
                thick
                ]
% No Gap: U ~ T^2
                \addplot[blue,thick] {4*x^2};
                \addlegendentry{Ungapped case: illustrative algebraic example}
% With Gap: U ~ exp(-Δ/T)
                \addplot[red,thick,dashed] {5*exp(-1/x)};
                \addlegendentry{Gapped case: exponential suppression}
                \end{axis}

% INSET: Energy spectrum with gap
                \begin{scope}[shift={(7.8,0.1)}]
                    \begin{axis}[
                    width=4.2cm,
                    height=3.5cm,
                    title={Kelvin Spectrum},
                    title style={font=\bfseries\tiny},
                    xlabel={$k$},
                    ylabel={$E(k)$},
                    axis lines=left,
                    ticks=none,
                    xmin=0, xmax=3.5,
                    ymin=0, ymax=4.5,
                    xtick=\empty,
                    ytick=\empty,
                    clip=false
                    ]
                    \fill[gray!20] (axis cs:0,0) rectangle (axis cs:3.5,1.5);
                    \draw[dashed, gray] (axis cs:0,1.5) -- (axis cs:3.5,1.5);
                    \foreach \x in {0.5,1.0,1.5,2.0,2.5,3.0} {
                        \addplot[only marks, mark=*, red] coordinates {(\x, {1.5 + 0.5*\x})};
                    }
                    \node[align=center,font=\tiny] at (axis cs:1.75,0.75) {No modes\\[-0.3em]($E<\Delta_K$)};
                    \end{axis}
                \end{scope}
            \end{tikzpicture}
            \caption{Comparison of Kelvin-mode thermal energy with and without an excitation gap $\Delta_K$. The ungapped curve is an illustrative algebraic example only and does not assume a universal $T^2$ law. Inset: discrete spectrum with a forbidden band $E<\Delta_K$.}
            \label{fig:kelvin-gap}
        \end{figure}

        \begin{figure}[htbp]
            \centering
            \begin{tikzpicture}
                \begin{axis}[
                width=6cm,
                height=4.5cm,
                title={Kelvin Excitation Spectrum},
                title style={font=\bfseries\tiny},
                xlabel={$k_m$ (mode index)},
                ylabel={$E_m$ [eV]},
                axis lines=left,
                ticks=none,
                xmin=0, xmax=6,
                ymin=0, ymax=800,
                clip=false
                ]
                \pgfmathsetmacro{\DeltaK}{500} % eV gap
                \fill[gray!20] (axis cs:0,0) rectangle (axis cs:6,\DeltaK);
                \draw[dashed, gray!60] (axis cs:0,\DeltaK) -- (axis cs:6,\DeltaK);
                \node[align=center,font=\tiny] at (axis cs:3,250) {Forbidden\\ region};
                \foreach \x in {1,2,3,4,5} {
                    \addplot[only marks, mark=*, red, mark size=2pt] coordinates {(\x, {\DeltaK + 40*\x})};
                }
                \node[anchor=west,font=\tiny] at (axis cs:6,\DeltaK+10) {$\Delta_K$};
                \end{axis}
            \end{tikzpicture}
            \caption{Illustrative Kelvin excitation spectrum with a gap $\Delta_K=\SI{500}{\electronvolt}$. Shaded band: $E<\Delta_K$.}
            \label{fig:kelvin-thermal-suppression}
        \end{figure}

        Equation~\eqref{eq:deltaE_boltzmann} is the operative statement for the induced level shift: a gap produces exponential suppression, while the ungapped case lacks any comparable generic protection.

% ============================================================
    \section{Required Gap Scale}\label{sec:required_gap}
        Let $\delta E_{\mathrm{spec}}$ denote the maximum spectroscopy-compatible correction to a low-lying level. For a finite or effectively truncated active mode set of size $N_K$, Eq.~\eqref{eq:generic_coupling_bound} together with Boltzmann suppression gives the sufficient decoupling condition
        \begin{equation}
            \lambda_n N_K \Delta_K
            \exp\!\left(-\frac{\Delta_K}{k_B T_{\mathrm{eff}}}\right)
            \lesssim
            \delta E_{\mathrm{spec}}.
            \label{eq:general_bound}
        \end{equation}
        Equivalently,
        \begin{equation}
            \frac{\Delta_K}{k_B T_{\mathrm{eff}}}
            \gtrsim
            \ln\!\left(\frac{\lambda_n N_K \Delta_K}{\delta E_{\mathrm{spec}}}\right).
            \label{eq:log_bound}
        \end{equation}
        The dependence on $\lambda_n$, $N_K$, and $\delta E_{\mathrm{spec}}$ is only logarithmic. The numerical non-triviality of Eq.~\eqref{eq:log_bound} therefore depends primarily on the assumed effective occupation scale $T_{\mathrm{eff}}$ and on the coupling efficiency $\lambda_n$: for room-temperature populations or extremely weak coupling, the bound may require only an eV-scale gap, whereas larger $T_{\mathrm{eff}}$ together with non-negligible coupling push the required gap above ordinary atomic binding energies. In the present effective setting, $T_{\mathrm{eff}}$ should be read not as the ambient temperature of a cold atom but as a placeholder for a non-equilibrium internal-mode population scale, such as might arise in strong-field ionization, keV-scale electron scattering, or other driven preparations that transiently populate the internal sector. The present paper does not independently derive a specific range for $T_{\mathrm{eff}}$, nor does it provide a microscopic estimate of $\lambda_n$; accordingly, Eq.~\eqref{eq:log_bound} should be read strictly as a conditional constraint on parameter space rather than as an absolute numerical prediction. The active mode count $N_K$ is likewise model-dependent, but a natural estimate is that it is set by a UV cutoff at wavelengths of order $\xi$, so that $N_K$ is at most of order $L/\xi$ (or smaller after symmetry and coupling selection rules). For the fiducial ratios used in Appendix~\ref{app:first_kelvin}, this gives $N_K \lesssim 10^{3}\text{--}10^{5}$, which shifts Eq.~\eqref{eq:log_bound} only logarithmically and therefore does not alter the order-of-magnitude conclusion. Appendix~\ref{app:first_kelvin} then supplies a fiducial onset estimate for the lowest internal mode using the same regularization variables $(\xi,L)$, so the two results should be read as complementary consistency checks rather than independent determinations of the same scale.

% ============================================================
    \section{Discussion and Outlook}\label{sec:outlook}
        The result of this paper is a conditional consistency bound. Any effective atomic bound-state model endowed with an internal Kelvin-like filament sector faces a sharp spectroscopic requirement: once the parameters $(\lambda_n,N_K,T_{\mathrm{eff}},\Delta_K)$ and the spectroscopic tolerance $\delta E_{\mathrm{spec}}$ are specified, Eq.~\eqref{eq:log_bound} determines whether the internal sector is safely decoupled from observed low-energy lines. A nonzero gap provides exponential protection. An ungapped sector can still be compatible with spectroscopy, but only if some additional mechanism suppresses either the low-energy density of states, the effective occupation, or the coupling to observed level shifts.

        The non-triviality of the bound depends explicitly on the same unresolved microscopic inputs. If the effective coupling $\lambda_n$ were itself extremely small, or if no physical process populated the internal sector above a negligible effective scale, the constraint would become correspondingly weak. The present argument therefore applies most directly to the subclass of internal-mode models in which internal excitation energy feeds into observable line shifts with a coupling that is not parametrically tiny on the relevant scales. Determining that coupling from a specific microscopic mechanism is beyond the scope of the present phenomenological note, but such a mechanism would set whether Eq.~\eqref{eq:log_bound} is restrictive or merely formal in practice.

        This framing yields a narrow and testable claim. The relevant experimental question is not whether atomic structure is ``really'' filamentary, but whether any additional internal sector activates above a threshold lying in the appendix's fiducial window,
        \begin{equation}
            10^2\,\mathrm{eV} \lesssim \Delta_K \lesssim 10^3\,\mathrm{eV},
        \end{equation}
        for the illustrative parameter choices considered there. Potential signatures would then appear not in ordinary spectroscopy, where the sector is frozen, but in threshold-like inelastic channels, anomalous broadening, or additional loss mechanisms once the excitation scale is crossed. Because this energy range overlaps ordinary inner-shell ionization and Auger backgrounds, any meaningful test would have to isolate either an anomalous rate or angular dependence not accounted for by standard atomic channels, or a species- and geometry-dependent threshold shift not aligned with known shell energies.

        The paper therefore motivates a focused search strategy: high-field or high-energy probes of bound electrons, rather than reinterpretation of standard low-energy spectroscopy. At low energy the internal sector must be silent; at sufficiently high excitation, it may become observable.

% ============================================================
        \appendix
    \section*{Appendix A: Estimate of First Kelvin Mode Energy}\label{app:first_kelvin}
        For the first mode ($m=1$) in the ground state ($n=1$), take
        \begin{equation}
            L = 2\pi a_0 \approx \SI{3.3249e-10}{m},
            \qquad
            \Gamma = \frac{h}{m_e} \approx \SI{7.2739e-4}{m^2/s},
        \end{equation}
        so that
        \begin{equation}
            k_1 = \frac{2\pi}{L} \approx \SI{1.8897e10}{m^{-1}}.
        \end{equation}
        For general regularization length $\xi$ and core constant $C_0$,
        \begin{equation}
            \omega_1(\xi,C_0,L)
            \simeq
            \frac{\Gamma}{4\pi} k_1^2
            \left[
                \ln\!\left(\frac{1}{k_1 \xi}\right) + C_0
            \right],
        \end{equation}
        and
        \begin{equation}
            E_1(\xi,C_0,L)=\hbar \omega_1(\xi,C_0,L).
        \end{equation}

        With the fiducial choice $\xi=\SI{1e-15}{m}$ and $C_0=1$, Eq.~\eqref{eq:kelvin_dispersion} yields
        \begin{equation}
            \omega_1 \approx \SI{2.45e17}{rad/s},
            \qquad
            E_1 \approx \SI{1.62e2}{eV}.
        \end{equation}

        Because the estimate depends on both the regularization scale $\xi$ and the effective loop length $L$, it is useful to display that sensitivity explicitly. For fixed $L=2\pi a_0$ and $C_0=1$:
        \begin{table}[htbp]
            \centering
            \caption{Sensitivity of the first-mode onset estimate to the regularization scale $\xi$ at fixed $L=2\pi a_0$ and $C_0=1$.}
            \begin{tabular}{ccc}
                \toprule
                $\xi$ [m] & $\ln(1/k_1\xi)+1$ & $E_1$ [eV] \\
                \midrule
                $10^{-15}$ & 11.876 & 162 \\
                $10^{-14}$ & 9.573  & 131 \\
                $10^{-13}$ & 7.271  & 99  \\
                \bottomrule
            \end{tabular}
            \label{tab:xi-sensitivity}
        \end{table}

        Likewise, at fixed $\xi=\SI{1e-15}{m}$ and $C_0=1$, shortening the effective loop length raises the onset scale:
        \begin{table}[htbp]
            \centering
            \caption{Sensitivity of the first-mode onset estimate to the effective loop length $L$ at fixed $\xi=\SI{1e-15}{m}$ and $C_0=1$.}
            \begin{tabular}{ccc}
                \toprule
                $L$ & $k_1$ [m$^{-1}$] & $E_1$ [eV] \\
                \midrule
                $2\pi a_0$      & $1.89\times 10^{10}$ & 162  \\
                $\pi a_0$       & $3.78\times 10^{10}$ & 587  \\
                $\tfrac{2\pi a_0}{3}$ & $5.67\times 10^{10}$ & 1320 \\
                \bottomrule
            \end{tabular}
            \label{tab:L-sensitivity}
        \end{table}

        For the illustrative parameter sweep reported above, the onset window may therefore be summarized as
        \begin{equation}
            \SI{1e2}{\electronvolt} \lesssim E_1 \lesssim \SI{1.3}{\kilo\electronvolt}.
        \end{equation}
        This window is not a unique prediction. It is a sensitivity range obtained from the Kelvin dispersion relation once the regularization scale $\xi$, the effective loop length $L$, and the order-unity core constant $C_0$ are specified. The fiducial choice $\xi=\SI{1e-15}{m}$ should be read only as a short-distance regularization length for the thin-filament description, chosen to remain well below the orbital scale $a_0$; it is not a claim about measured electron size. The lower edge of the window is correspondingly fragile: shortening $L$ or decreasing $\xi$ raises the onset, whereas lengthening $L$ or increasing $\xi$ softens it and can push $E_1$ back toward ordinary atomic binding energies, eventually outside the regime where the thin-filament estimate is informative. Quantitatively, for the fiducial choice $L=2\pi a_0$ and $C_0=1$, the first-mode onset falls below the hydrogen ionization energy $13.6\,\mathrm{eV}$ once $\xi \gtrsim 5.3\times 10^{-11}\,\mathrm{m}\approx a_0$; equivalently, for $\xi=\SI{1e-15}{m}$ and $C_0=1$, it falls below $13.6\,\mathrm{eV}$ once $L \gtrsim 1.21\times 10^{-9}\,\mathrm{m}\approx 3.63\,(2\pi a_0)$. These values make the domain of validity concrete: the thin-filament estimate is informative only while $\xi \ll a_0$ and the effective loop length remains of order the low-lying orbital circumference rather than many times larger. The dispersion estimate therefore identifies a fiducial onset scale together with a geometry-dependent window.
% ============================================================
% Back matter (Springer Nature)
% ============================================================
        \backmatter
        \bmhead{Declarations}

        \subsection*{Funding}
            Not applicable.

        \subsection*{Competing interests}
            The author declares no competing interests.

        \subsection*{Ethics approval}
            Not applicable.

        \subsection*{Consent to participate}
            Not applicable.

        \subsection*{Consent for publication}
            Not applicable.

        \subsection*{Data availability}
            Not applicable.

        \subsection*{Materials availability}
            Not applicable.

        \subsection*{Code availability}
            Not applicable.

        \subsection*{Author contributions}
            O.I. conceived the study, developed the analysis, performed the derivations, and wrote the manuscript.

% ============================================================
% References
% ============================================================
            \begin{thebibliography}{99}

                \bibitem{Helmholtz1858}
                H.~Helmholtz,
                ``On Integrals of the Hydrodynamical Equations Which Express Vortex Motion,''
                \emph{J. Reine Angew. Math.} \textbf{55}, 25--55 (1858).

                \bibitem{Kelvin1867}
                W.~Thomson (Lord Kelvin),
                ``On Vortex Atoms,''
                \emph{Proc. R. Soc. Edinburgh} \textbf{6}, 94--105 (1867).

                \bibitem{Onsager1949}
                L.~Onsager,
                ``Statistical Hydrodynamics,''
                \emph{Nuovo Cimento Suppl.} \textbf{6}, 279--287 (1949).

                \bibitem{Feynman1955}
                R.~P.~Feynman,
                ``Application of Quantum Mechanics to Liquid Helium,''
                in \emph{Progress in Low Temperature Physics}, Vol.~1,
                North-Holland (1955).

                \bibitem{LordKelvin1880}
                W.~Thomson (Lord Kelvin),
                ``Vibrations of a Columnar Vortex,''
                \emph{Philosophical Magazine} \textbf{10}, 155--168 (1880).

                \bibitem{Barenghi2014}
                C.~F.~Barenghi, L.~Skrbek, and K.~R.~Sreenivasan,
                ``Introduction to Quantum Turbulence,''
                \emph{Proc. Natl. Acad. Sci. USA} \textbf{111}, 4647--4652 (2014).

                \bibitem{Ricca1996}
                R.~L.~Ricca,
                ``The Contributions of Da Rios and Levi-Civita to Asymptotic Potential Theory and Vortex Filament Dynamics,''
                \emph{Fluid Dynamics Research} \textbf{18}, 245--268 (1996).

                \bibitem{Pathria2011}
                R.~K.~Pathria and P.~D.~Beale,
                \emph{Statistical Mechanics}, 3rd ed.,
                Elsevier (2011).

            \end{thebibliography}

\end{document}