
        \subsection{Finite-cell $\alpha$ coincidence and obstruction summary}
            \label{subsec:finite_cell_alpha_obstruction}

            \textbf{[DERIVED-IN-MODEL / OPEN].}
            A parameter-light finite-cell variational construction for an ideal trefoil filament
            yields a leading dimensionless scale
            \begin{align}
                \alpha^{-1}_{\mathrm{lead}}
                =
                \frac{8\pi}{3}\,\mathcal{L}_{3_1}
                \approx 137.15471,
                \label{eq:alpha_lead_finite_cell}
            \end{align}
            using the numerically computed ideal trefoil ropelength
            $\mathcal{L}_{3_1}=16.371637$ as a \emph{benchmark} topological-geometric input.
            This lies within $866$~ppm of CODATA $\alpha^{-1}=137.035999$ and is an
            $\alpha$-free sub-per-mille coincidence, not a part-per-million derivation.

            The prefactor $8\pi/3$ contains a mode-count factor $N_p=4$ derived from the
            soft sector of the spherical finite-cell surface spectrum
            $k_\ell=\ell(\ell+1)-2$ (zero and unstable modes only). The sector volume
            $4\pi/3$ and overall normalization remain partially open modelling choices.

            \textbf{[NEGATIVE / OBSTRUCTION RESULT].}
            Closing the residual to ppm accuracy is underdetermined: at fixed cell-radius
            gate the required transverse shell weight is $w_\perp=1.0675$, not the round
            value $1$ (which reaches only $10.5$~ppm). An independent Gross--Pitaevskii
            core-profile proxy returns $w_\perp\approx 2.076$, overshooting to $-157$~ppm.
            The $10.5$~ppm residual can be absorbed independently by any of five
            sub-percent coefficients (shell weight, cell-radius gate, sector volume,
            ropelength value, or a third-order term), so ppm closure carries no
            discriminating power without pinning all inputs to $\sim10^{-6}$ relative
            precision---beyond present ideal-knot ropelength certification.

            The gate hierarchy is therefore
            \begin{align}
                G_0\ (\text{input provenance})
                \longrightarrow
                G_1\ (\text{identifiability})
                \longrightarrow
                G_2\ (\text{operator Hessians})
                \longrightarrow
                G_3\ (\text{ppm closure}),
                \label{eq:finite_cell_gate_hierarchy}
            \end{align}
            with $G_0$ and $G_1$ blocking closure before Hessian-level work becomes relevant.

            \textbf{[CANON / NON-CLAIM].}
            This block does not assert a first-principles derivation of the fine-structure
            constant. The defensible content is the $\alpha$-free sub-per-mille leading
            coincidence with partially derived $N_p=4$, plus a localized obstruction to
            ppm closure. Full scripts, appendices, and audit details are in
            \texttt{finite\_cell\_obstruction.tex} and \texttt{Derive\_Constants/}.
