
    \subsection{Framed-Tube Ontology and the Attachment Gate}
        \label{subsec:framed_tube_attachment_gate}

        The particle carrier in SST is not a bare centerline knot alone. The canonical object is a framed, phase-bearing tube,
        \begin{align}
            \mathcal{K}_{\mathrm{SST}}
            =
            \big(K,\,\mathcal{F},\,\Gamma,\,\theta_{\mathrm{core}}\big),
        \end{align}
        where $K$ is the centerline knot or link, $\mathcal{F}$ is a ribbon/framing, $\Gamma$ is circulation, and $\theta_{\mathrm{core}}$ is a material or order-parameter phase attached to the core.

        The current Attachment Lemma is the statement that a local Compton/core cycle can be promoted to a globally closed framed-tube holonomy,
        \begin{align}
            \frac{1}{2\pi}\oint_K d\theta_{\mathrm{core}}
            = \chi,
            \qquad
            \chi\in\mathbb{Z}.
            \label{eq:attachment_gate_chi}
        \end{align}
        A compensated form allows local swirl-clock redistribution while preserving the exact global integer,
        \begin{align}
            \chi_{\mathrm{total}}
            =
            \chi_{\mathrm{local}}+\chi_{\mathrm{attachment}}
            = \chi,
            \qquad
            \delta Q=0.
            \label{eq:compensated_attachment_gate}
        \end{align}

        \textbf{[CANON / OPEN GATE]}: Eq.~\eqref{eq:attachment_gate_chi} is not yet a theorem of the Euler--SST dynamics. It is a load-bearing gate. Integer energy selection alone is insufficient; exact holonomy is required for canon status.

        \textbf{[CANON / NOTATION]}: the framing phase follows the Compton angular cycle $\omega_c$, while the associated local vorticity scale is $2\omega_c$. The factor of two must not be absorbed into $\chi$.


    \subsection{Particle-Candidate Mapping Layer}
        \label{subsec:integration_knotmap}

        \textbf{[SPECULATIVE]} Working dictionary: a minimal knot/composition mapping retained from earlier SST work is summarized in Table~\ref{tab:particle_candidate_mapping}. This table is organizational rather than definitive; it records current topological assignments and mechanical analogues used by the mass and taxonomy program.

        \begin{table}[h]
        \centering
        \caption{Minimal knot-class and analogue summary retained in v0.8.3, with current semantic corrections.}
        \label{tab:particle_candidate_mapping}
        \begin{tabular}{lll}
        \hline
        Carrier / composition & Candidate role & Status / interpretation \\
        \hline
        $3_1$ trefoil & electron / positron sector & baseline chiral lepton calibration; not used for fractional quark charge \\
        $T(2,5)$ or equivalent higher torus class & muon & lepton hierarchy candidate \\
        $T(2,7)$ or equivalent higher torus class & tau & lepton hierarchy candidate \\
        twist/clasp knots, quasi-unknot loops & quark-like defects & research-track fractional boundary winding candidates \\
        $5_2+5_2+6_1$ and nearby composites & baryon candidates & legacy mass-functional dictionary, still under audit \\
        triple-gear locked analogue & proton-like charged baryon analogue & mechanical model for nonzero exterior collective rotation \\
        Borromean-type analogue & neutron-like neutral baryon analogue & mechanical/topological model for zero exterior charge with internal triple linking \\
        \hline
        \end{tabular}
        \end{table}

        \textbf{[CRITICAL NOTE]}: Table~\ref{tab:particle_candidate_mapping} is a working dictionary only. Electric charge is not identified with raw Hopf helicity or pairwise linking number. The safer current placeholder is a boundary-winding charge variable $q_{\partial}$, while knot/link data supply mass, chirality, confinement, and internal topological structure.

        \textbf{[CANON / DECISION]}: The trefoil assignment is retained for the electron/positron sector only. Fractional values such as $2/3$ belong, if anywhere, to the twist-knot/quark-like boundary-winding research track rather than to the trefoil-electron calibration.
