%! Author = Omar Iskandarani
%! Title = Swirl String Theory (SST) Canon v0.4
%! Date = Sept 4, 2025
%! Affiliation = Independent Researcher, Groningen, The Netherlands
%! License = © 2025 Omar Iskandarani. All rights reserved. This manuscript is made available for academic reading and citation only. No republication, redistribution, or derivative works are permitted without explicit written permission from the author. Contact: info@omariskandarani.com
%! ORCID = 0009-0006-1686-3961
%! DOI = 10.5281/zenodo.17052966

\newcommand{\canonversion}{\textbf{v0.4.1}} % Semantic versioning: vMAJOR.MINOR.PATCH
\newcommand{\papertitle}{Swirl String Theory (SST) Canon \canonversion}
\newcommand{\paperdoi}{10.5281/zenodo.17052966}

% ==== Swirl String Theory (SST) macros ====
% Context-aware subscript symbol; uses math styles, not \scriptsize
\newcommand{\swirlarrow}{%
    \mathchoice{\mkern-2mu\scriptstyle\boldsymbol{\circlearrowleft}}%
    {\mkern-2mu\scriptstyle\boldsymbol{\circlearrowleft}}%
    {\mkern-2mu\scriptscriptstyle\boldsymbol{\circlearrowleft}}%
    {\mkern-2mu\scriptscriptstyle\boldsymbol{\circlearrowleft}}%
}
\newcommand{\swirlarrowcw}{%
    \mathchoice{\mkern-2mu\scriptstyle\boldsymbol{\circlearrowright}}%
    {\mkern-2mu\scriptstyle\boldsymbol{\circlearrowright}}%
    {\mkern-2mu\scriptscriptstyle\boldsymbol{\circlearrowright}}%
    {\mkern-2mu\scriptscriptstyle\boldsymbol{\circlearrowright}}%
}

% Canonical symbols
\newcommand{\vswirl}{\mathbf{v}_{\swirlarrow}}
\newcommand{\vswirlcw}{\mathbf{v}_{\swirlarrowcw}}
\newcommand{\SwirlClock}{S_(t)^{\swirlarrow}}
\newcommand{\SwirlClockcw}{S_(t)^{\swirlarrowcw}}
\newcommand{\omegas}{\boldsymbol{\omega}_{\swirlarrow}}  % swirl vorticity
\newcommand{\vscore}{v_{\swirlarrow}}                    % shorthand: |v_swirl| at r=r_c
\newcommand{\vnorm}{\lVert \vswirl \rVert}               % swirl speed magnitude
\newcommand{\rhof}{\rho_{\!f}}                           % effective fluid density
\newcommand{\rhoE}{\rho_{\!E}}                           % swirl energy density /c^2? (we define clearly below)
\newcommand{\rhom}{\rho_{\!m}}                           % mass-equivalent density
\newcommand{\rc}{r_c}                                    % string core radius (swirl string radius)
\newcommand{\FmaxEM}{F_{\mathrm{EM}}^{\max}}             % EM-like maximal force scale
\newcommand{\FmaxG}{F_{\mathrm{G}}^{\max}}               % G-like maximal force scale
\newcommand{\Lam}{\Lambda}                               % Swirl Coulomb constant
\newcommand{\Om}{\Omega_{\swirlarrow}}                   % swirl angular frequency profile
\newcommand{\alpg}{\alpha_g}                             % gravitational fine-structure analogue

% Policy: the golden constant is only allowed via hyperbolic functions.
% Never write (1+\sqrt{5})/2; always use \xig=\asinh(1/2), \varphi=e^{\xig}.
\newcommand{\xig}{\operatorname{asinh}\!\left(\tfrac{1}{2}\right)} % base hyperbolic scale  "golden" constant is fundamentally hyperbolic.
\newcommand{\phig}{\exp(\xig)}                                     % golden from hyperbolic
\newcommand{\phialg}{\bigl(1+\sqrt{5}\bigr)/2}                     % algebraic echo (use sparingly)
\newcommand{\xigold}{\tfrac{3}{2}\,\xig}                           % "golden rapidity" scale

% --- Display helpers (optional) ---
\newcommand{\GoldenDeclare}{%
    \textbf{Golden (hyperbolic)}:\ \(\ln\phi=\xig\), hence \(\phi=\phig\).
    \ \emph{(Equivalently, \(\phi=\phialg\); this algebraic form is derivative.)}%
}
% --- Canonical identity (hyperbolic-only proof, algebraic as corollary) ---
\newtheorem{identity}{Identity}

% Additional theorem-like environments for Canon v0.4
\newtheorem{axiom}{Axiom}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}{Definition}[section]
\newtheorem{postulate}{Postulate}

%========================================================================================
% PACKAGES AND DOCUMENT CONFIGURATION
%========================================================================================
\documentclass[11pt]{article}
\usepackage{subfiles}
\input{../template/SSTstyle.sty}
\input{../template/SST_appendix_setup.sty}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{tcolorbox}
\usetikzlibrary{knots,intersections,decorations.pathreplacing,3d,calc,arrows.meta,positioning,decorations.pathmorphing}
\usepackage{pgfmath}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{ulem}


% ==== Packages ====
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}

\geometry{margin=1in}
\usepackage{ bm, mathtools}
\usepackage{siunitx}
\sisetup{per-mode=symbol,round-mode=figures,round-precision=6}
\usepackage{physics}
\usepackage{upgreek}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue!60!black, citecolor=blue!60!black, urlcolor=blue!60!black}


% ===== Gauge sector macros =====
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\ii}{\mathrm{i}}
% Gauge fields (adjoints; indices a=1..8, i=1..3)
\newcommand{\GsA}{G^a_{\mu\nu}}
\newcommand{\WsI}{W^i_{\mu\nu}}
\newcommand{\Bmn}{B_{\mu\nu}}

%========================================================================================
% DOCUMENT START
%========================================================================================
\begin{document}

%========================================================================================
% TITLE PAGE
%========================================================================================

\titlepageOpen
\begin{abstract}

This Canon is the single source of truth for \emph{Swirl String Theory (SST)}: definitions, constants, boxed master equations, and notational conventions. It consolidates core structure and \emph{promotes five results to canonical status}:
\begin{tabular}{r@{\quad}p{0.85\linewidth}}
\textbf{I} & Swirl Coulomb constant $\Lam$ and hydrogen soft-core \\
\textbf{II} & circulation–metric corollary (frame-dragging analogue) \\
\textbf{III} & corrected swirl time-rate (Swirl Clock) law \\
\textbf{IV} & Kelvin-compatible swirl Hamiltonian density \\
\textbf{V} & swirl pressure law (Euler corollary) \\
\end{tabular}

\paragraph{Core Axioms (SST)}
    \begin{enumerate}
    \item \textbf{Swirl Medium:} Physics is formulated on $\mathbb{R}^3$ with absolute reference time. Dynamics occur in a frictionless, incompressible \emph{swirl condensate}, which serves as a universal substrate (no material dispersion, Galilean symmetry for the medium).
    \item \textbf{Swirl Strings (Circulation and Topology):} Particles and field quanta correspond to closed vortex filaments (\emph{swirl strings}). Each such loop may be linked or knotted, and the circulation of the swirl velocity around any closed loop is quantized:
    \[
        \Gamma = \oint \vswirl \cdot d\boldsymbol{\ell} = n\,\kappa,\qquad n\in\mathbb{Z},\qquad \kappa = \frac{h}{m_{\text{eff}}}.
    \]
    Equivalently, any surface spanning the loop carries an integer multiple of the circulation quantum $\kappa$. Discrete quantum numbers of an excitation (mass, charge, spin) track to the topological invariants of its swirl string (linking number, writhe, twist).
    \item \textbf{String-induced gravitation:} Macroscopic attraction emerges from coherent swirl flows and swirl-pressure gradients. In the Newtonian limit, the effective gravitational coupling $G_{\text{swirl}}$ is fixed by canonical constants so that $G_{\text{swirl}}\approx G_{\text{Newton}}$ (see Sec.~\ref{sec:master_equations}).
    \item \textbf{Swirl Clocks:} Local proper-time rate depends on tangential swirl speed. A clock comoving with swirl (tangential speed $v$) ticks slower by the factor $S_t=\sqrt{\,1-v^2/c^2\,}$ relative to an outside observer.
    \item \textbf{Dual Phases (Wave–Particle):} Each swirl string has two limiting phases: an extended \emph{R-phase} (unknotted, delocalized circulation) exhibiting wave phenomena, and a localized \emph{T-phase} (knotted soliton) carrying rest-mass. Quantum measurement corresponds to transitions $R\to T$ (collapse) or $T\to R$ (de-localization), mediated by swirl radiation.
    \item \textbf{Taxonomy:} Unknotted excitations behave as bosonic string modes; chiral hyperbolic knots map to quarks; torus knots map to leptons. Linked composite knots correspond to bound states (nuclei, molecules). The detailed particle–knot dictionary is documented separately.
    \end{enumerate}
    \footnotesize{Hydrodynamic analogy only: no mechanical “æther” is assumed in the mainstream presentation.}
\end{abstract}

\vfill
\paragraph{Versioning} Semantic versions: vMAJOR.MINOR.PATCH. This file: \canonversion.\\
    Every paper/derivation must state the Canon version it depends on.
    \titlepageClose

%================================================
\section{Classical Invariants and Swirl Quantization}
%================================================
\label{sec:classical_invariants}
Under Axiom 1 (inviscid, barotropic medium), the Euler equations hold and yield standard vortex invariants. In particular, Helmholtz/Kelvin circulation theorem ensures:

\textbf{Kelvin's circulation theorem:}
\begin{equation}
    \frac{d\Gamma}{dt}=0, \qquad \Gamma=\oint_{\mathcal{C}(t)} \vswirl\cdot d\boldsymbol{\ell}, \label{eq:kelvin}
\end{equation}

\textbf{Vorticity transport:}
\begin{equation}
    \pdv{\omegas}{t} = \nabla\times(\vswirl\times \omegas), \label{eq:vorticity-transport}
\end{equation}
\textbf{Helicity invariance:}
\begin{equation} h=\vswirl\cdot \omegas,\quad H=\int h\, dV\ \text{(constant; changes only by reconnections)~\cite{Moffatt1969}}. \label{eq:helicity}
\end{equation}
These underpin knotted swirl-string stability and reconnection energetics in SST.

\begin{axiom}[Chronos–Kelvin Invariant]
\label{ax:chronos-kelvin}
For any thin, closed swirl loop (material core radius $R(t)$) in an inviscid medium, one has the material invariant
\begin{equation}
\boxed{\;
\frac{D}{Dt}\!\Big(R^2\,\omega\Big)=0,
    \;} \qquad \text{equivalently,} \qquad
\boxed{\;
\frac{D}{Dt}\!\Big(
\frac{c}{r_c}\,R^2 \sqrt{\,1-S_t^2\,}
\Big)=0\,,
    \;}
\label{eq:CK}
\end{equation}
where $\omega=\|\omegas\|$ on the loop and $S_t=\sqrt{\,1-(\omega r_c/c)^2\,}$ is the local Swirl Clock factor. This holds in the absence of reconnections or external swirl injection.
\end{axiom}

\paragraph{Derivation (Kelvin's theorem).}
    Kelvin's theorem \ref{eq:kelvin}  implies $\frac{D}{Dt}\Gamma=0$ for any material loop in a barotropic flow【Helmholtz1858,Kelvin1869,Batchelor1967】. For a nearly solid-body core, $\Gamma = 2\pi R\, v_t = 2\pi R^2 \omega$, so $\frac{D}{Dt}(R^2 \omega)=0$. Using $v_t = \omega r_c$ and the definition of $S_t$ (Axiom 4), we get $R^2\omega=\frac{c}{r_c}R^2\sqrt{\,1-S_t^2\,}$, yielding \eqref{eq:CK}. \qed

\paragraph{Dimensional check.}
    $[R^2\omega] = \mathrm{m}^2\mathrm{s}^{-1}$, and $[\frac{c}{r_c}R^2\sqrt{1-S_t^2}] = \mathrm{s}^{-1}\cdot \mathrm{m}^2 = \mathrm{m}^2\mathrm{s}^{-1}$.

\paragraph{Clock–radius transport law (corollary).}
    From $R^2\omega=\mathrm{const}$, one finds
    \begin{equation}
    \frac{dS_t}{dt} \;=\; \frac{2(1-S_t^2)}{S_t}\,\frac{1}{R}\frac{dR}{dt}\,.
    \label{eq:clock-radius-ode}
    \end{equation}
    Thus expansion ($dR/dt>0$) drives $S_t\to 1$ (local clocks speed up), while contraction slows local clocks ($S_t\downarrow$), preserving \eqref{eq:CK}.

\paragraph{Potential-vorticity analogue.}
    With a uniform background rotation $\Omega_{\text{bg}}$ and column height $H$, the Ertel potential vorticity theorem gives the SST counterpart【Ertel1942,Batchelor1967】
    \begin{equation}
    \frac{D}{Dt}\Big(\frac{\omega + \Omega_{\text{bg}}}{H}\Big)=0\,,
    \label{eq:PV-analogue}
    \end{equation}
    directly analogous to geophysical PV invariance.

\paragraph{Conditions.}
    Inviscid, incompressible medium; barotropic swirl pressure; material loop without reconnection or external input; absolute time parameterization. These are the same assumptions under which Kelvin–Helmholtz invariants hold.

\paragraph{Limits.}
    For weak swirl ($\omega r_c\ll c$): $S_t \approx 1-\tfrac{1}{2}(\omega r_c/c)^2$ and \eqref{eq:CK} reduces to the classical invariant $R^2\omega=\text{const}$. In the core-on-axis limit ($v_t\to\vswirl$ on the symmetry axis), $S_t \to \sqrt{1-(\vswirl/c)^2}$, and \eqref{eq:CK} remains valid.

\subsection{Swirl Quantization Principle}
\label{sec:swirl_quantization}
By Axiom 2, the circulation of $\vswirl$ around any closed loop is quantized in units of $\kappa=h/m_{\text{eff}}$. Closed swirl filaments may form nontrivial knots and links, each topological class corresponding to a discrete excitation state:
\begin{equation}
\mathcal{H}_{\text{swirl}} = \{\text{trefoil knot},\; \text{figure-eight knot},\; \text{Hopf link},\;\dots\}\,.
\end{equation}
We refer to the joint discreteness of circulation and topology as the \emph{Swirl Quantization Principle}:
\[
    \Gamma = n\kappa \qquad \text{and} \qquad \text{Topology}(K)\in \mathcal{H}_{\text{swirl}} \text{ (integer knot invariants)}.
\]
This underlies both the particle spectrum and the emergence of interactions in SST.

\begin{center}\setlength{\tabcolsep}{5pt}
\begin{tabular}{|c|c|}
\hline
\textbf{Quantum Mechanics (Copenhagen)} & \textbf{Swirl String Theory (SST)} \\
\hline
Canonical quantization: & Swirl quantization principle: \\
$[x, p] = i \hbar$ & $\displaystyle \Gamma = n\,\kappa,\quad n\in\mathbb{Z}$ \\[6pt]
& $\displaystyle \mathcal{H}_{\text{swirl}} = \{\text{trefoil},\ \text{figure-eight},\ \text{Hopf link},\dots\}$ \\
\hline
Discreteness from & Discreteness from \\
non-commuting operators & circulation integrals \& knot topology \\
\hline
Particle = eigenstate of & Particle = knotted swirl state with \\
Hermitian $H$ (wavefunction) & quantized $\Gamma$ and topological invariants \\
\hline
\end{tabular}
\end{center}

%===============================================================
\section{Canonical Constants and Effective Densities}
%===============================================================
\label{sec:canonical_constants}
\subsection*{Primary SST Constants (SI units unless noted)}
    \begin{itemize}
    \item \textbf{Swirl speed scale (core):} $\vnorm = \num{1.09384563e6}\ \si{m/s}$ (tangential speed at $r=\rc$).
    \item \textbf{String core radius:} $\rc = \num{1.40897017e-15}\ \si{m}$.
    \item \textbf{Effective fluid density:} $\rhof = \num{7.0e-7}\ \si{kg/m^3}$.
    \item \textbf{Mass-equivalent density:} $\rhom = \num{3.8934358266918687e18}\ \si{kg/m^3}$.
    \item \textbf{EM-like maximal force:} $\FmaxEM = \num{2.9053507e1}\ \si{N}$.
    \item \textbf{Gravitational maximal force (ref. scale):} $\FmaxG = \num{3.02563e43}\ \si{N}$.
    \item \textbf{Golden ratio:} $\varphi = (1+\sqrt{5})/2 \approx \num{1.61803398875}$.
    \end{itemize}

\subsection*{Universal Constants}
    \begin{itemize}
    \item $c=\num{299792458}\ \si{m/s}$, \quad $t_p=\num{5.391247e-44}\ \si{s}$ (Planck time).
    \item Fine-structure constant (identified): $\alpha \approx \num{7.29735256e-3}$.
    \end{itemize}

    \paragraph{Effective densities.}
        We use $\rhof$ (effective fluid density) to avoid confusion\footnote{The canonical choice
    $\rhof = 7.0\times 10^{-7}\,\mathrm{kg/m^3}$
    is a defined calibration constant, not a measured value.
    Its magnitude is anchored to the electromagnetic permeability scale
    $\mu_0/(4\pi) = 10^{-7}$ (SI), ensuring dimensional consistency between swirl energetics and EM normalization.
    Unlike the derived high-precision values of $\rhom$ and $\rhoE$,
    the effective fluid density $\rhof$ is fixed at this tidy scale as a reference baseline.}
        with mass density; define
        \[
            \rhoE \equiv \tfrac{1}{2}\,\rhof\,\vnorm^2 \qquad (\text{swirl energy density}), \qquad
            \rho_m \equiv \frac{\rhoE}{c^2} \qquad (\text{mass-equivalent density}).
        \]
        We also introduce the \emph{swirl areal density} $\varrho_{\swirlarrow}$ as the coarse-grained number of swirl cores per unit area. Its time variation enters Faraday's law as an effective source term:
        \[
            \nabla \times \mathbf{E} = -\,\partial_t \mathbf{B} \;-\; \mathbf{b}_{\swirlarrow}, \qquad
            \mathbf{b}_{\swirlarrow} = G_{\swirlarrow}\,\partial_t \varrho_{\swirlarrow}\,.
        \]
        Here $G_{\swirlarrow}$ is the canonical swirl–EM transduction constant, identified with a flux quantum ($\Phi^* \sim h/2e$). This relation links electromotive force (voltage impulses) to reconnection dynamics, establishing a bridge between EM fields and gravity-like swirl fields.

%================================================
\section{Canon Governance and Status Taxonomy}
%================================================
\label{sec:canon_governance}
\paragraph{Formal system.}
    Let $\mathcal{S}=(\mathcal{P},\mathcal{D},\mathcal{R})$ denote the SST formal system: axioms $\mathcal{P}$, definitions $\mathcal{D}$, and admissible inference rules $\mathcal{R}$ (e.g. variational principles, Noether currents, dimensional analysis, asymptotic matching).

\paragraph{Canonical statement.}
    A statement $X$ is \emph{canonical} iff $X$ is a theorem or identity provable in $\mathcal{S}$:
    \[
        \mathcal{P},\;\mathcal{D}\;\vdash_{\mathcal{R}}\;X\,,
    \]
    and $X$ is consistent with all previously accepted canonical items in the current major version.

\paragraph{Empirical statement.}
    A statement $Y$ is \emph{empirical} iff it asserts a measured value, fit, or protocol:
    \[
        Y \equiv \text{“observable $\mathcal{O}$ has value $\hat{o}\pm \delta o$ under procedure $\Pi$.”}
    \]
    Empirical items calibrate symbols (e.g. $\vscore, \rc, \rhof$) but are not used as premises in proofs.

\subsection*{Status Classes}
\begin{itemize}
\item \textbf{Axiom/Postulate (Canonical).} Primitive assumption of SST (e.g. swirl medium, absolute time, swirl quantization).
\item \textbf{Definition (Canonical).} Introduces a symbol by construction (e.g. swirl Coulomb constant $\Lambda$ by surface integral).
\item \textbf{Theorem/Corollary (Canonical).} Proven consequence (e.g. Euler–SST radial balance; Swirl Clock time dilation).
\item \textbf{Constitutive Model (Canonical if derived; else Semi-empirical).} Relates fields/observables; canonical when deduced from $\mathcal{P},\mathcal{D}$.
\item \textbf{Calibration (Empirical).} Recommended numerical values (with uncertainties) for canonical symbols.
\item \textbf{Research Track (Non-canonical).} Conjectures or alternatives pending proof or axiomatization.
\end{itemize}

\subsection*{Canonicality Tests (all required)}
\begin{enumerate}
\item \textbf{Derivability} from $\mathcal{P},\mathcal{D}$ via $\mathcal{R}$.
\item \textbf{Dimensional consistency} (strict SI usage; correct physical limits).
\item \textbf{Symmetry compliance} (Galilean symmetry + absolute time, incompressibility).
\item \textbf{Recovery limits} (Newtonian gravity, Coulomb/Bohr, linear wave optics).
\item \textbf{Non-contradiction} with accepted canonical results.
\item \textbf{Parameter discipline} (no ad hoc fits or free parameters beyond calibrations).
\end{enumerate}

\subsection*{Examples (from this Canon)}
\begin{itemize}
\item \textit{Canonical (Definition):}\quad $\displaystyle \Lambda \equiv \int_{S_r^2} p_{\text{swirl}}(r)\,r^2\,d\Omega.$
\item \textit{Canonical (Theorem):}\quad $\displaystyle \frac{1}{\rhof}\frac{dp_{\text{swirl}}}{dr}=\frac{v_\theta(r)^2}{r}$ for steady azimuthal drift (Euler radial balance).
\item \textit{Empirical (Calibration):}\quad $\vscore = 1.09384563\times10^{6}\,\mathrm{m/s}$ with protocol $f\Delta x$ (see Sec.~\ref{sec:experiments}).
\item \textit{Consistency Check (Not a premise):}\quad Hydrogen soft-core reproduces $a_0, E_1$; this validates chosen constants but is a check, not an axiom.
\end{itemize}

%================================================
\section{What is Canonical in SST—and Why}
%================================================
\label{sec:canonical_overview}
\paragraph{[Axiom] Medium: inviscid continuum with absolute time, Euclidean space.}
    $\nabla\cdot\vswirl=0,\;\nu=0.$
    This fixes the kinematic arena and allowed inference rules (Eulerian dynamics, Galilean relativity of spatial coordinates).

\paragraph{[Definition] Vorticity, circulation, helicity.}
    $\omegas=\nabla\times \vswirl,\quad \Gamma=\oint \vswirl\!\cdot d\boldsymbol{\ell},\quad h=\vswirl\!\cdot\!\omegas,\; H=\int h\,dV.$
    Classical constructs canonized as primary SST kinematic invariants.

\paragraph{[Theorem] Kelvin’s circulation \& vorticity transport (Helmholtz).}
    For inviscid, barotropic flow:
    \[
        \frac{d\Gamma}{dt}=0,\qquad
        \pdv{\omegas}{t}=\nabla\times(\vswirl\times\omegas),\qquad
        \text{$H$ constant up to reconnections}.
    \]

\paragraph{[Definition] Swirl Coulomb constant $\Lambda$.}
    \[
        \boxed{\,\Lambda \equiv \int_{S_r^2} p_{\text{swirl}}(r)\;r^2\,d\Omega\,}, \quad [\Lambda] = \mathrm{J\,m} = \mathrm{N\,m^2}\,.
    \]
    In Canon v0.4 this evaluates to $\Lambda = 4\pi\,\rhom\,\vscore^2\,\rc^4$ (for the fundamental swirl string).

\paragraph{[Theorem] Hydrogen soft-core potential \& Coulomb limit.}
    \[
        V_{\text{SST}}(r)=-\,\frac{\Lambda}{\sqrt{r^2+\rc^2}}
        \;\xrightarrow[r\gg \rc]{}\;
        -\,\frac{\Lambda}{r}\,.
    \]
    This yields Bohr scalings
    \[
        a_0=\frac{\hbar^2}{\mu\,\Lambda}, \qquad E_n=-\,\frac{\mu\,\Lambda^2}{2\hbar^2 n^2}\,,
    \]
    correctly reproducing the hydrogen atom ($\mu$ reduced mass).

\paragraph{[Theorem] Euler–SST radial balance (swirl pressure law).}
    For a steady, purely azimuthal drift $v_\theta(r)$ with $\partial_t=0$:
    \[
        0=-\,\frac{1}{\rhof}\frac{dp_{\text{swirl}}}{dr}+\frac{v_\theta^2}{r}
        \;\;\Rightarrow\;\;
        \boxed{\,\frac{1}{\rhof}\frac{dp_{\text{swirl}}}{dr}=\frac{v_\theta(r)^2}{r}\,}\,.
    \]
    For asymptotically flat rotation ($v_\theta\to v_0$ as $r\to\infty$): $p_{\text{swirl}}(r)=p_0+\rhof v_0^2 \ln(r/r_0)$, an outward-rising pressure that provides the centripetal force for the flat curve.

\paragraph{[Definition $\to$ Corollary] Swirl analogue metric and time dilation.}
    In cylindrical coordinates $(t,r,\theta,z)$ with $v_\theta(r)$:
    \[
        ds^2 = -\big(c^2 - v_\theta^2(r)\big)dt^2 + 2\,v_\theta(r)\,r\,d\theta\,dt + dr^2 + r^2 d\theta^2 + dz^2\,.
    \]
    Co-rotating ($d\theta' = d\theta - \frac{v_\theta}{r c^2} dt$) yields $ds^2=-\,c^2\big(1 - v_\theta^2/c^2\big)dt^2+\cdots$, giving the Swirl Clock factor
    \[
        \frac{dt_{\text{local}}}{dt_{\infty}} = \sqrt{\,1-\frac{v_\theta^2}{c^2}\,}\,.
    \]

\paragraph{[Definition] SST Hamiltonian density (Kelvin-compatible).}
    \[
        \mathcal{H}_{\text{SST}} = \tfrac{1}{2}\rhof\,\|\vswirl\|^2 + \tfrac{1}{2}\rhof\,\rc^2\|\omegas\|^2 + \lambda(\nabla\cdot\vswirl)\,.
    \]

\subsection*{Empirical Calibrations (not premises, but binding numeric values)}
\begin{itemize}
\item $[\text{Empirical}] $ $\vscore = 1.09384563\times 10^6\,\mathrm{ m/s } $ (core swirl speed).
\item $[\text{Empirical}]$ $\rc = 1.40897017\times 10^{-15}\,\mathrm{m}$ (string core radius).
\item $[\text{Empirical}]$ $\rhom = 3.8934358266918687\times 10^{18}\,\mathrm{kg/m^3}$ (mass-equiv. density).
\end{itemize}

\subsection*{Non-Canonical (Research Track)}
Unproven extensions—e.g. blackbody swirl temperature, electroweak swirl couplings—remain conjectural until derived under $\mathcal{S}$.

\subsection*{Consistency \& Dimension Checks}
\[
    [\Lambda] = [\rhom][\vscore^2][\rc^4]
    = \frac{\mathrm{kg}}{\mathrm{m^3}}\cdot\frac{\mathrm{m^2}}{\mathrm{s^2}}\cdot \mathrm{m^4}
    = \frac{\mathrm{kg\,m^3}}{\mathrm{s^2}}
    = \mathrm{J\,m}\,.
\]
Soft-core Coulomb limit: $V_{\text{SST}}(r)\to -\Lambda/r$ as $r/\rc\to\infty$ (recovering Coulomb law).

%================================================
\section{Coarse-Graining Strings: Derivation of $\rhof$}
%================================================
\label{sec:canon_rhof_from_strings}
\paragraph{Setup.}
    The medium is modeled as an incompressible condensate populated by thin \emph{swirl strings}. We derive the bulk effective density $\rhof$ via coarse–graining of line-supported mass and vorticity, using Euler kinematics and Kelvin invariants.

\subsection*{Line parameters}
For a representative straight vortex string (locally solid-body core):
\begin{align}
\text{(D1)}\quad
\mu_* &:= \rhom\,\pi \rc^2
\quad\;[\mathrm{kg/m}]&& \text{(line mass per length)}, \\[1ex]
\text{(D2)}\quad
\Gamma_* &:= \oint \vswirl \cdot d\boldsymbol{\ell}
\;\approx\; 2\pi\,\rc\,\vscore
&& \text{(circulation quantum per string)}.
\end{align}
Let $\nu = N_{\text{str}}/A$ (strings per unit area). Then:
\begin{align}
\text{(C1)}\quad
\rhof &= \mu_*\,\nu, \\[1ex]
\text{(C2)}\quad
\langle \omegas \rangle &= \Gamma_*\,\nu\,\hat{\mathbf{t}}_{\text{avg}} \quad\Rightarrow\quad |\langle \omega_{\swirlarrow}\rangle| = \Gamma_*\,\nu\,,
\end{align}
where $\hat{\mathbf{t}}_{\text{avg}}$ is the average unit tangent of string orientations.

\subsection*{First–Principles Derivation}
Combining (C1)–(C2):
\begin{equation}
\boxed{\,\rhof = \mu_*\,\frac{\langle\omega_{\swirlarrow}\rangle}{\Gamma_*}
    = \frac{\rhom\,\pi \rc^2}{2\pi\,\rc\,\vscore}\,\langle\omega_{\swirlarrow}\rangle
    = \frac{\rhom\,\rc}{2\,\vscore}\,\langle\omega_{\swirlarrow}\rangle\,}\,,
\label{eq:rhof_from_omega}
\end{equation}
using $\Gamma_*=2\pi\rc\vscore$. For uniform solid rotation with angular speed $\Omega$, $\langle\omega_{\swirlarrow}\rangle = 2\,\Omega$. Then
\begin{equation}
\boxed{\,\rhof = \frac{\rhom\,\rc}{\vscore}\;\Omega\,}\,,
\label{eq:rhof_from_Omega}
\end{equation}
giving the effective bulk density in terms of a typical angular velocity $\Omega$ of the swirl-string ensemble.

\paragraph{Energy and tension scales.}
    \[
        \boxed{\,u_{\text{swirl}} = \tfrac{1}{2}\,\rhof\,\vscore^2\,}, \qquad
        \boxed{\,T_* = \tfrac{1}{2}\,\mu_*\,\vscore^2\,}\,,
    \]
    i.e. the swirl energy density and single-string tension (both on the core).

\subsection*{Numerical Calibration (Canon constants)}
With
$\rhom=3.8934358266918687\times 10^{18}\ \si{kg/m^3},\
\rc=1.40897017\times 10^{-15}\ \si{m},\
\vscore=1.09384563\times 10^{6}\ \si{m/s}$, one finds
\[
    \Gamma_* = 2\pi \rc \vscore = 9.68361920\times 10^{-9}\ \si{m^2/s}, \qquad
    T_* = 1.45267535\times 10^{1}\ \si{N}\,.
\]
From \eqref{eq:rhof_from_Omega}:
\[
    \rhof = (5.01509060\times 10^{-3})\,\Omega\,,
\]
so the baseline $\rhof = 7.0\times 10^{-7}\ \si{kg/m^3}$ occurs at
\[
    \boxed{\,\Omega_* = 1.39578735\times 10^{-4}\ \si{s^{-1}}\ \text{(period }\approx 12.5~\text{h})\,}\,.
\]

%================================================
\section{Master Equations (Boxed Canonical Relations)}
%================================================
\label{sec:master_equations}
\subsection*{Energy and Mass (Bulk)}
    \[
        \boxed{\,E_{\text{SST}}(V) = \frac{4}{\alpha\,\varphi}\left(\frac{1}{2}\,\rhof\,\vscore^2\right) V\,}\quad [\mathrm{J}],
        \qquad
        \boxed{\,M_{\text{SST}}(V) = \frac{E_{\text{SST}}(V)}{c^2}\,}\quad [\mathrm{kg}]\,.
    \]
    Numeric per unit volume: $\tfrac12\,\rhof \vscore^2 \approx 4.1877439\times10^5\ \mathrm{J/m^3}$, $\frac{4}{\alpha\varphi}\approx 3.3877162\times10^2$, so $E/V \approx 1.418688\times10^8\ \mathrm{J/m^3}$, $M/V \approx 1.57850\times10^{-9}\ \mathrm{kg/m^3}$.

\subsection*{Swirl–Gravity Coupling}
    \[
        \boxed{\,G_{\text{swirl}} = \frac{\vscore\,c^5\,t_p^2}{2\,F_{\text{EM}}^{\max}\,\rc^2}\,}\,.
    \]
    Numerically $G_{\text{swirl}}\approx 6.67430\times10^{-11}\ \mathrm{m^3/kg/s^2}$, matching Newton's $G$ to within calibration precision.

\subsection*{Topology–Driven Mass Law (Invariant Form)}
    For a torus knot $T(p,q)$ (with $n=\gcd(p,q)$ components, braid index $b=\min(|p|,|q|)$, Seifert genus $g$), using ropelength $\mathcal{L}_{\text{tot}}(T)$ and core radius $\rc$:
    \[
        \boxed{\,M\big(T(p,q)\big)
            = \left(\frac{4}{\alpha}\right) b^{-3/2}\,\varphi^{-\,g}\,n^{-1/\varphi}
            \left(\frac{1}{2}\,\rhof \vscore^2\right) \frac{\pi\,\rc^3\,\mathcal{L}_{\text{tot}}(T)}{c^2}\,}\,.
    \]
    (Dimension comes from the factor $\tfrac12\,\rhof \vscore^2$ [J/m$^3$] times a volume.)

\subsection*{Swirl Clocks (Local Time Rate)}
    \[
        \boxed{\,\frac{dt_{\text{local}}}{dt_{\infty}}
            = \sqrt{\,1 - \frac{\|\omegas\|^2\,\rc^2}{c^2}\,}
            = \sqrt{\,1 - \frac{\|\vswirl\|^2}{c^2}\,}\quad (r=\rc)\,}\,.
    \]
    \emph{Note:} An earlier variant without a length scale ($\rc$) is deprecated, retained only for historical traceability.

\subsection*{Swirl Angular Frequency Profile}
    \[
        \boxed{\,\Omega_{\text{swirl}}(r) = \frac{\vscore}{\rc}\,e^{-\,r/\rc}\,,\qquad \Omega_{\text{swirl}}(0)=\frac{\vscore}{\rc}\,}\,.
    \]

\subsection*{Vorticity Potential (Canonical Form)}
\[
	\Phi_{\text{swirl}}(\mathbf{r},\omegas) = \frac{\vscore^2}{2\,F_{\text{EM}}^{\max}}\;(\omegas\cdot \mathbf{r})\,.
\]
(Use with the SST Lagrangian so that $\rhof\,\Phi_{\text{swirl}}$ has units of energy density.)


\subsection{Empirical Anchoring of Gauge Sector (Canonical Calibration)}
The $\mathrm{SU}(3)\oplus \mathrm{SU}(2)\oplus \mathrm{U}(1)$ sector is anchored to experiment by the
following empirical values:
\begin{align}
	m_W &= 80.377~\mathrm{GeV}, \\
	m_Z &= 91.1876~\mathrm{GeV}, \\
	\sin^2\theta_W &= 0.23121 \pm 0.00004, \\
	\alpha_s(M_Z) &= 0.1181 \pm 0.0011 .
\end{align}
These imply a canonical electroweak symmetry-breaking scale
\begin{equation}
	v_\Phi^{\rm exp} = \frac{2 m_W}{g} \approx 246.22~\mathrm{GeV}.
\end{equation}
This scale is treated as an \emph{empirical calibration}. Any Swirl--String reinterpretation
in terms of fluid constants $(\rho_{\!f}, r_c, \lVert \vswirl \rVert)$ belongs to
Canon~4R (Research) until it reproduces this value.

%================================================
\section{Standard Gauge Sector (Canonical Core)}
%================================================
\label{sec:gauge_core}

\paragraph{Bundle and connections (Canonical).}
Let $P\!\to\! \mathbb{R}^{3}\times\mathbb{R}$ be a principal bundle with
$G=\mathrm{SU}(3)\times\mathrm{SU}(2)\times\mathrm{U}(1)$.
Local gauge potentials are
\[
	\mathcal{A}_\mu
	= g_s\,A^a_\mu T^a \;\oplus\; g\,W^i_\mu \tau^i \;\oplus\; g'\,B_\mu\,Y,
\]
with $T^a\in\mathfrak{su}(3)$, $\tau^i\in\mathfrak{su}(2)$, $Y\in\mathfrak u(1)$.

\paragraph{Field strengths (Canonical).}
\begin{align}
	G^a_{\mu\nu} &= \partial_\mu A^a_\nu-\partial_\nu A^a_\mu + g_s f^{abc} A^b_\mu A^c_\nu,\label{eq:Gmunu}\\
	W^i_{\mu\nu} &= \partial_\mu W^i_\nu-\partial_\nu W^i_\mu + g \epsilon^{ijk} W^j_\mu W^k_\nu,\label{eq:Wmunu}\\
	B_{\mu\nu} &= \partial_\mu B_\nu-\partial_\nu B_\mu.\label{eq:Bmunu}
\end{align}

\paragraph{Yang--Mills Lagrangian (Canonical).}
\begin{equation}
	\mathcal{L}_{\text{YM}}
	= -\frac{1}{4} \GsA \, G^{a\,\mu\nu}
	-\frac{1}{4} \WsI \, W^{i\,\mu\nu}
	-\frac{1}{4} \Bmn \, B^{\mu\nu}.
	\label{eq:YM-core}
\end{equation}
\textit{Dimensional check (natural units):} $[A_\mu]=\text{mass}$, $[F_{\mu\nu}]=\text{mass}^2$, so $[\mathcal L_{\rm YM}]=\text{mass}^4$ (SI $\to$ J/m$^3$ by \(\hbar c\)).

\paragraph{Matter, covariant derivative (Canonical).}
For any gauge-charged field $\Phi$ in representation $R$,
\begin{equation}
	D_\mu \Phi
	= \left(\partial_\mu + \ii g_s A^a_\mu T^a
	+ \ii g W^i_\mu \tau^i
	+ \ii g' B_\mu Y \right)\Phi,
	\qquad
	\mathcal{L}_{\Phi}^{\text{kin}}=(D_\mu\Phi)^\dagger (D^\mu\Phi).
	\label{eq:covder}
\end{equation}

\paragraph{Electroweak mixing and masses (Canonical).}
\begin{align}
	A_\mu &= \sin\theta_W\, W^3_\mu + \cos\theta_W\, B_\mu,\label{eq:photon}\\
	Z_\mu &= \cos\theta_W\, W^3_\mu - \sin\theta_W\, B_\mu,\qquad \tan\theta_W=\frac{g'}{g}.
\end{align}
If a scalar doublet (or SST-equivalent) develops a vacuum value $v_\Phi$ via a gauge-invariant potential $V(\Phi)$,
\begin{equation}
	m_W = \tfrac{1}{2} g v_\Phi,\qquad
	m_Z = \tfrac{1}{2}\sqrt{g^2+g'^2}\,v_\Phi,\qquad
	m_\gamma=0. \label{eq:ew_masses}
\end{equation}
\textit{Empirical anchoring:} $v_\Phi$ is fixed by data, cf. Sec.~\ref{sec:master_equations} (Empirical Anchoring).

\paragraph{Currents and anomaly constraint (Canonical).}
Noether currents:
\[
	J^{a\,\mu}_{(3)}=\sum \bar{\Psi}\gamma^\mu T^a\Psi,\quad
	J^{i\,\mu}_{(2)}=\sum \bar{\Psi}\gamma^\mu \tau^i\Psi,\quad
	J^\mu_{(1)}=\sum \bar{\Psi}\gamma^\mu Y\Psi,
\]
with minimal-coupling interaction
\(
\mathcal L_{\rm int}=- A^a_\mu J^{a\,\mu}_{(3)} - W^i_\mu J^{i\,\mu}_{(2)} - B_\mu J^\mu_{(1)}.
\)
\textbf{Anomaly cancellation} for one generation must hold; this constrains any knot\(\to\)rep mapping used elsewhere.


%================================================
\section{Unified SST Lagrangian (Definitive Form)}
%================================================
\label{sec:lagrangian}
Let $\vswirl(\mathbf{x},t)$ be the velocity, $\rhof$ constant (incompressible),
$\omegas = \nabla\times\vswirl$, and $\lambda$ enforce $\nabla\cdot\vswirl=0$. Then
\[
	\boxed{\,\mathcal{L}_{\text{SST+Gauge}}
		=
		\underbrace{\frac{1}{2}\rhof\,\|\vswirl\|^2
		- \rhof\,\Phi_{\text{swirl}}(\mathbf{r},\omegas)
			+ \lambda(\nabla\cdot\vswirl)
			+ \chi_h\,\rhof\,(\vswirl\cdot\omegas)}_{\text{SST (Kelvin-compatible, local)}}
		\;+\;
		\underbrace{\mathcal{L}_{\text{YM}}}_{\text{Yang--Mills, Eq.\,\eqref{eq:YM-core}}}
		\;+\;
		\underbrace{(D_\mu\Phi)^\dagger (D^\mu\Phi) - V(\Phi)}_{\text{Gauge-charged scalar sector}}
		\;+\;
		\underbrace{\mathcal{L}_{\text{int}}}_{\text{Minimal coupling to currents}}
		\;+\;
		\mathcal{L}_{\text{couple}}[\Gamma,\mathcal{K}]
		\,}\,.
\]
\noindent\emph{Units.} All terms carry energy-density units $\,[\mathcal L]=\mathrm{J\,m^{-3}}\,$; the helicity coupling is dimensionless $([\chi_h]=1)$. (In natural units $\hbar=c=1$, $[\mathcal L]=\text{mass}^4$.)

\noindent
\textit{Governance:} $\mathcal{L}_{\text{YM}}$, minimal coupling, and EW mixing/masses (\S\ref{sec:gauge_core}) are Canonical; any SST-specific mapping $v_\Phi(\rhof,\rc,\vnorm)$ is tracked in Canon~4R (Research).

Here $\Phi_{\text{swirl}}(\mathbf{r},\omegas)$ is a prescribed swirl potential (Sec.~\ref{sec:master_equations});
the term $\chi_h\,\rhof\,(\vswirl\cdot\omegas)$ is the local helicity density (dimensionless $\chi_h$); and $\mathcal{L}_{\text{couple}}$ encodes
coupling to quantized circulation $\Gamma$ and knot invariants $\mathcal{K}$ (linking, writhe, twist).
For the scalar sector one may take $V(\Phi)=\lambda_\Phi (|\Phi|^2 - v_\Phi^2)^2$ with
$v_\Phi$ fixed empirically (Sec.~\ref{sec:master_equations}).
\paragraph{Constraints (data).}
Running couplings $g_s,g,g'$ obey standard $\beta$ functions; numerically we anchor
$\alpha_s(M_Z)$ in Sec.~\ref{sec:master_equations}. Electroweak precision observables
(LEP/SLD) constrain $\sin^2\theta_W$ and thus the $A$–$Z$ mixing in \eqref{eq:photon}.

%================================================
\section{Wave–Particle Duality in SST}
%================================================
\label{sec:wave_particle_duality}
The dual phases introduced in Axiom 5 formalize the wave–particle duality in SST. An unknotted swirl string in R-phase behaves as a coherent circulation wave (delocalized, diffraction-capable), whereas a knotted T-phase is localized and particle-like. We outline how standard quantum phenomena emerge from these phases:

\paragraph{de Broglie relation from circulation.}
    Consider a ring-like swirl string of radius $R$ carrying circulation $\Gamma = n h/m_e$ (assuming $m_{\text{eff}}=m_e$ for an electron). The tangential momentum is $p_\theta \approx m_e v_\theta$. Quantization gives $v_\theta = n \hbar/(m_e 2\pi R)$, hence
    \[
        p_\theta = \frac{n\,h}{2\pi R}\,.
    \]
    The de Broglie wavelength $\lambda = h/p_\theta$ follows as
    \[
        \lambda = \frac{2\pi R}{n}\,,
    \]
    i.e. the circumference $2\pi R$ is an integer multiple of the wavelength, consistent with wave coherence around the loop.

\paragraph{Interference and R→T collapse.}
    In a double-slit experiment, an electron's swirl string travels in R-phase through both slits as a distributed vortex loop. The intensity pattern arises from the phase difference of the two path segments around the loop, yielding interference fringes. No \emph{which-way} information is embedded in the R-phase itself. If a detection attempt (e.g. a photon scattering) forces a T-phase localization, the swirl string knots or collapses to one side, appearing particle-like at a single slit.

\paragraph{Photon-induced collapse (measurement).}
    A photon of frequency $\omega$ impinging on an R-phase swirl loop can deposit energy $\hbar\omega$. If this matches the gap $\Delta E_{\text{eff}}$ between the delocalized state and the nearest knotted state, it triggers
    \[
        \hbar\omega \approx \Delta E_{\text{eff}}\,,
    \]
    causing the loop to knot (transition to T-phase). Thus measurements involving photons inherently induce collapse by exciting the swirl into a localized mode.

\paragraph{Fringe visibility decay.}
    Environmental interactions cause gradual swirl-string collapse. If $\Gamma_{\text{collapse}}$ is the net knotting rate (transitions per second from R to T), the interference fringe visibility decays as
    \[
        V(t) = \exp(-\,\Gamma_{\text{collapse}}\,t)\,,
    \]
    analogous to decoherence with a coherence time $\tau_c = \Gamma_{\text{collapse}}^{-1}$. Low-noise experiments correspond to $\Gamma_{\text{collapse}}\to 0$ (long-lived R-phase), preserving interference, whereas any information leak ($\Gamma_{\text{collapse}}>0$) will diminish $V$.

%================================================
\section{Notation, Ontology, and Glossary}
%================================================
\label{sec:glossary}
\begin{itemize}
\item \textbf{Absolute time (A-time):} The universal time parameter $t$ of the swirl condensate (preferred foliation).
\item \textbf{Chronos time (C-time):} Time measured at infinity or far outside any swirl field ($dt_\infty$).
\item \textbf{Swirl Clocks:} Local proper-time scale factors set by $\|\omegas\|$ or $\|\vswirl\|$ (see Sec.~\ref{sec:lagrangian}); high swirl intensity (large $\omega$) slows down these clocks relative to A-time.
\item \textbf{R-phase vs. T-phase:} ``Ring'' phase (unknotted, extended) versus ``Torus-knot'' phase (knotted, localized). R-phase excitations superpose and interfere (bosonic behavior), while T-phase excitations manifest particle individuality (fermionic behavior via topological sign rules~\cite{FinkelsteinRubinstein1968}).
\item \textbf{String taxonomy:} Leptons are associated with torus knots; quarks with chiral hyperbolic knots; gauge bosons with unknots; neutrinos with linked loops (Hopf links). Family structure and conservation laws correspond to topological properties (e.g. genus, chirality, linking number).
\item \textbf{Chirality:} Counter-clockwise (ccw) swirl orientation corresponds to matter; clockwise (cw) corresponds to antimatter, through the sign of swirl–gravity interaction.
\end{itemize}

%================================================
\section{Unknot Bosons and Lossless Swirl Radiation}
%================================================
\label{sec:bosons_photons}
\paragraph{Postulate (Topological sector).}
    Let $\mathcal{U}$ denote an \emph{unknotted} closed swirl string ($\mathcal{H}=0$ Hopf invariant). Finkelstein–Rubinstein single-valuedness on multi-string configuration space enforces integer spin for $\mathcal{U}$【FinkelsteinRubinstein1968】:
    \[
        \boxed{\,\mathcal{U} \implies \text{bosonic sector}\,.}
    \]
    (Nontrivial knot classes supply the topological phase needed for half-integer spin.)

\paragraph{Field variables and lossless propagation.}
    Introduce a transverse swirl potential $\mathbf{a}(\mathbf{x},t)$ such that
    \[
        \mathbf{v} = \partial_t \mathbf{a}, \qquad
        \mathbf{b} = \nabla\times \mathbf{a}, \qquad \nabla\cdot \mathbf{a}=0\,.
    \]
    Consider the quadratic Lagrangian
    \[
        \mathcal{L}_{\text{wave}} = \frac{\rhof}{2}\,|\mathbf{v}|^2 - \frac{\rhof c^2}{2}\,|\mathbf{b}|^2\,,
    \]
    where $c$ is the observed luminal wave speed (from Axiom 1). The Euler–Lagrange equations give a lossless wave equation:
    \[
        \boxed{\,\partial_t^2 \mathbf{a} - c^2\,\nabla\times(\nabla\times \mathbf{a}) = 0, \qquad \nabla\cdot \mathbf{a}=0\,}\,,
    \]
    with conserved energy density $u$ and Poynting flux $\mathbf{S}$:
    \[
        u = \frac{\rhof}{2}\Big(|\mathbf{v}|^2 + c^2|\mathbf{b}|^2\Big), \qquad
        \mathbf{S} = \rhof c^2\,(\mathbf{v}\times \mathbf{b}), \qquad
        \partial_t u + \nabla\cdot \mathbf{S}=0\,,
    \]
    and momentum density $\mathbf{g}=\mathbf{S}/c^2$. Inviscid, dissipation-free background (Kelvin’s theorem) means no swirl circulation is lost; the waves propagate without attenuation【Batchelor1967,Saffman1992】.

\paragraph{Photon identification.}
    We identify electromagnetic field variables by the linear mapping
    \[
        \boxed{\,\mathbf{E} = \sqrt{\frac{\rhof}{\varepsilon_0}}\,\mathbf{v}, \qquad
        \mathbf{B} = \sqrt{\frac{\rhof}{\varepsilon_0}}\,\mathbf{b}\,}\,,
    \]
    yielding
    \[
        u = \frac{\varepsilon_0}{2}|\mathbf{E}|^2 + \frac{1}{2\mu_0}|\mathbf{B}|^2, \qquad
        \mathbf{S} = \frac{1}{\mu_0}\,(\mathbf{E}\times \mathbf{B}), \qquad
        \frac{1}{\varepsilon_0 \mu_0} = c^2\,,
    \]
    exactly the Maxwell energy–momentum in vacuum【Jackson1999】. Plane- and spherical-wave solutions of $\mathcal{L}_{\text{wave}}$ thus describe \emph{photons} as \emph{delocalized}, divergence-free swirl oscillations.

\paragraph{Quantization and single-photon amplitude.}
    Quantizing a cavity mode (volume $V$, frequency $\omega$) gives the standard one-photon field amplitude
    \[
        E_{\text{rms}}^{(1)} = \sqrt{\frac{\hbar\omega}{2\varepsilon_0 V}}\,,
    \]
    hence swirl velocity amplitude
    \[
        \boxed{\,v_{\text{rms}}^{(1)} = \sqrt{\frac{\hbar\omega}{2\,\rhof\,V}}\,}\,.
    \]
    For $\lambda = 532~\mathrm{nm}$ (green, $\omega=2\pi c/\lambda$) and $\rhof=7.0\times10^{-7}\,\mathrm{kg/m^3}$:
    \[
        V=1~\mathrm{mm}^3: \quad v_{\text{rms}}^{(1)} \approx 3.27\times10^{-2}\ \mathrm{m/s}\,,
    \]
    consistent with $E_{\text{rms}}^{(1)}$ and observed cavity QED couplings【HarocheRaimond2006,ScullyZubairy1997】.

\paragraph{Radiation from bound strings (``atoms'').}
    A localized bound swirl configuration with time-varying multipole moment $\mathbf{d}(t)$ launches outward transverse $\mathbf{a}$ waves. Far from the source ($r \gg$ source size), the solution is
    \[
        \mathbf{a}(\mathbf{x},t) \;\propto\; \frac{\mathbf{e}_\perp}{r}\,\Re\!\big(e^{i(kr-\omega t)}\big), \qquad k=\omega/c\,,
    \]
    with flux $\mathbf{S}=\rhof c^2\,(\mathbf{v}\times\mathbf{b})$ directed radially and $|\mathbf{S}|\propto r^{-2}$, ensuring constant power through spheres【Jackson1999】. Thus, \emph{atoms (knotted strings) emit concentric swirl waves; the lossless medium transmits them without attenuation.}

\paragraph{Exclusion of smoke-ring photons.}
    A localized vortex-ring (smoke ring) of core radius $\rc$ and energy $E_{\text{vr}}$ carrying momentum $p_{\text{vr}}$ cannot simultaneously satisfy $E_{\text{vr}}=\hbar\omega$ and $p_{\text{vr}}=\hbar k$ with subluminal core speed【Saffman1992,Batchelor1967】. Hence, \emph{photons in vacuum are not toroidal vortex rings}, but rather extended swirl modes as above.

\paragraph{Summary.}
    \[
        \boxed{\,\mathcal{U} \ (\text{unknot}) \implies \text{boson}; \qquad
        \text{photons} = \text{delocalized, lossless swirl waves launched by bound sources.}\,}
    \]

%===========================================================
\subsection{Photon as a Pulsed Unknot with Delocalized Circulation}
%===========================================================
\label{sec:photon_pulsed_unknot}
We can model the photon as a pulsed, unknotted swirl-string $K \cong S^1$ of radius $R$ (circumference $L=2\pi R$). Unlike massive particles (localized knots with core density $\rhom$), the photon has no rest-mass contribution ($\rhom=0$); its energy resides entirely in oscillatory swirl motion within the effective fluid $\rhof$.

\paragraph{Effective 1D action.}
    Define a transverse displacement $\xi(s,t)$ along the ring (parametrized by $s\in[0,L)$) with cross-sectional area $A_{\mathrm{eff}}=\pi w^2$. The photon's delocalized mode is described by
    \[
        S[\xi] = \frac{1}{2}\rhof A_{\mathrm{eff}} \int dt \int_0^L ds\,\Big[(\partial_t \xi)^2 - c^2 (\partial_s \xi)^2\Big]\,,
    \]
    yielding the wave equation
    \[
        \partial_t^2 \xi - c^2\,\partial_s^2 \xi = 0,\qquad \xi(s+L,t) = \xi(s,t)\,.
    \]

\paragraph{Normal modes.}
    Periodic boundary conditions give discrete wavenumbers
    \[
        k_m = \frac{2\pi m}{L},\qquad \omega_m = c\,k_m,\qquad m\in\mathbb{Z}_{>0}\,.
    \]
    A single-mode solution:
    \[
        \xi_m(s,t) = a_m \cos(k_m s - \omega_m t)\,.
    \]

\paragraph{Mode energy.}
    The time-averaged energy of mode $m$ is
    \[
        E_m = \frac{1}{2}\,\rhof A_{\mathrm{eff}} L\,\omega_m^2 a_m^2\,,
    \]
    which depends on the delocalized volume $A_{\mathrm{eff}}L$ rather than a massive core. Thus, photon energy is carried by the distributed swirl field, not a localized mass density.

\paragraph{Quantization.}
    Assigning energy $\hbar \omega_m$ to each mode yields amplitude
    \[
        a_m = \sqrt{\frac{\hbar}{\rhof A_{\mathrm{eff}} L \,\omega_m}}\,.
    \]
    For a photon of wavelength $\lambda$, set $R=\lambda/(2\pi)$ so $L=\lambda$, and choose $w\sim\lambda/(2\pi)$ (so $A_{\mathrm{eff}}=\pi w^2$):
    \[
        a = \sqrt{\frac{\hbar}{\rhof\,A_{\mathrm{eff}} \,L \,\omega}} = \sqrt{\frac{\hbar}{\rhof \,\pi w^2\, \lambda \,\omega}}\,,
    \]
    with $\omega = 2\pi c/\lambda$. For $\lambda = 500\,\mathrm{nm}$ and $\rhof = 7.0 \times 10^{-7}\,\mathrm{kg/m^3}$,
    \[
        a \approx 2.0 \times 10^{-12}\,\mathrm{m}\,, \qquad E = \hbar \omega \approx 3.97 \times 10^{-19}\,\mathrm{J}\;\; (2.48\,\mathrm{eV})\,.
    \]

\paragraph{Interpretation.}
    The photon is thus a \emph{pulsed unknot swirl-string}, with vanishing rest-mass density ($\rhom=0$) but finite distributed energy density
    \[
        \rhoE = \tfrac{1}{2}\rhof\!\Big((\partial_t \xi)^2 + c^2 (\partial_s \xi)^2\Big)
    \]
    integrated over its volume. It is neither pointlike nor bound to a core, but consists of a minimal swirl loop excited to launch delocalized waves—akin to a momentarily perturbed vortex ring radiating ripples in a fluid.

%================================================
\section{Canonical Checks (Verification in Practice)}
%================================================
\label{sec:canonical_checks}
\begin{enumerate}
\item \textbf{Dimensional analysis:} Verify SI consistency for every new term and equation introduced.
\item \textbf{Limiting cases:} Show that low-swirl limits ($\|\omegas\|\to 0$) recover classical mechanics and Maxwell electrodynamics; large-scale averages reproduce Newtonian gravity with $G_{\text{swirl}}$.
\item \textbf{Numerical evaluation:} Provide numeric factors using Canon constants (Sec.~\ref{sec:canonical_constants}) for any new formula. If new constants are needed, add them to Sec.~\ref{sec:canonical_constants} for consistency.
\item \textbf{Topology–quantum mapping:} Explicitly state which knot invariants correspond to which quantum numbers and how they are normalized (linking number $\leftrightarrow$ baryon number, etc.).
\item \textbf{Citations:} Cite any non-original constructs or standard results (e.g. Kelvin’s theorem, Planck’s law) using the provided BibTeX keys.
\end{enumerate}

%================================================
\section{Swirl Hamiltonian Density (Canonical Form)}
%================================================
\label{sec:hamiltonian}
Given effective density $\rhof$ and swirl vorticity $\omegas = \nabla\times \vswirl$, a Kelvin-compatible, dimensionally consistent Hamiltonian density is:
\begin{equation}
\mathcal{H}_{\text{SST}}[\vswirl] = \frac{1}{2}\rhof\,\|\vswirl\|^2 + \frac{1}{2}\rhof\,\rc^2\,\|\omegas\|^2 + \frac{1}{2}\rhof\,\rc^4\,\|\nabla\omegas\|^2 + \lambda\,(\nabla\cdot \vswirl)\,,
\label{eq:Hamiltonian_SST}
\end{equation}
which has units of energy density (J/m$^3$). The first term is kinetic energy of swirl motion; the second term $\sim \rc^2 \|\omegas\|^2$ represents core rotational energy (rest-mass analogue); the third term $\sim \rc^4\|\nabla\omegas\|^2$ penalizes curvature of the vortex filaments (string tension). In the limit $\rc\to 0$ or for spatially uniform vorticity, the higher-order terms vanish, reducing $\mathcal{H}_{\text{SST}}$ to the usual fluid kinetic energy density $\frac{1}{2}\rhof v^2$ with incompressibility constraint.

%================================================
\section{Swirl Pressure Law (Euler Corollary)}
%================================================
\label{sec:darkpressure}
For a steady, purely azimuthal flow ($v_r=v_z=0$, $\partial_t=0$), the radial component of the Euler momentum equation ($\rhof\,v_\theta^2/r = dp_{\text{swirl}}/dr$) provides a direct relationship for the swirl pressure gradient:
\begin{equation}
\frac{1}{\rhof}\frac{dp_{\text{swirl}}}{dr} = \frac{v_\theta(r)^2}{r}\,.
\label{eq:swirl_pressure_law}
\end{equation}
This is a canonical theorem derived directly from first principles. For a system exhibiting an asymptotically flat rotation curve where $v_\theta(r) \to v_0$ for large $r$, the pressure profile is found by integration:
\begin{equation}
p_{\text{swirl}}(r) = p_0 + \rhof v_0^2 \ln\left(\frac{r}{r_0}\right)\,.
\end{equation}
Here, $p_0$ is the pressure at a reference radius $r_0$. The resulting outward-rising pressure creates an inward-pointing force ($-\nabla p_{\text{swirl}}$), providing the centripetal acceleration required to maintain the flat rotation curve.

%================================================
\section{Experimental Protocols (Canon-Ready Tests)}
%================================================
\label{sec:experiments}
\subsection*{Universality of $\vscore = f\,\Delta x$ (multi-platform metrology)}
    \textit{(From \texttt{ExperimentalValidationOfVortexCoreTangentialVelocity.tex})}—In diverse systems (magnetized plasmas, superconducting vortices, optical ring modes, acoustic vortices), measure a natural frequency $f$ and a spatial period $\Delta x$ of a standing or traveling swirl mode. Verify:
    \begin{equation}
    \boxed{\,\vscore = f\,\Delta x \approx 1.09384563\times10^{6}\ \mathrm{m/s}\,}\,. \tag{X1}
    \end{equation}
    Achieve sub-ppm agreement across platforms; report mean and standard deviation. This confirms a universal quantum of circulation speed.

\subsection*{Swirl-induced gravitational potential}
    \textit{(From \texttt{ExperimentalValidationOfGravitationalPotential.tex})}—Infer $p_{\text{swirl}}(r)$ from centripetal balance (\S\ref{sec:darkpressure}) and compare predicted forces with measured thrust or buoyancy anomalies in shielded high-voltage/coil experiments (geometry: starship/Rodin coils). Ensure dimensional consistency and calibrate only via Canon constants.

%=========================================================
\section{Critical Questions Across SST Extensions}
%=========================================================
\label{sec:critical-questions}
We collect here several forward-facing questions for Swirl–String Theory (SST), posed as critical tests or extensions. Each is answered canonically, with experimental or theoretical implications.

\subsection*{1. Is EMF quantization observable?}
    If each reconnection or knotting event releases a discrete flux impulse $\Phi^*$, then
    \[
        \Delta \Phi_{\mathcal{C}} = \int_{\Sigma(\mathcal{C})} \Delta \mathbf{B} \cdot d\mathbf{S} = m\,\Phi^*,\quad m\in\mathbb Z,
    \]
    should appear as a \emph{quantized step} in a superconducting interferometer.
    For a pickup loop of inductance $L$,
    \[
        \Delta I=\frac{\Delta\Phi}{L},\qquad V_{\textrm ind}(t)=-\frac{d\Phi}{dt}.
    \]
    A reconnection of duration $\tau$ requires bandwidth $f_{\textrm BW}\gtrsim (2\pi\tau)^{-1}$. For $\tau\sim$ ns, this is 20--200 MHz, within modern SQUID ranges. If $\Phi^*\approx\Phi_0=h/2e$, steps are resolvable.

    \paragraph{Status.} Canonical prediction: \emph{yes}, observable as quantized steps; scale of $\Phi^*$ to be calibrated empirically.

\subsection*{2. Is $R\!\to\!T$ collapse deterministic or stochastic?}
Field equations (Euler + swirl coupling) are deterministic. However, topology change occurs at core separations $\sim r_c$ with extreme sensitivity to microstates. Effective model:
\[
    \dot K=F(K)+\sqrt{2D_{\textrm env}}\,\eta(t),\qquad \text{Vis}(t)=e^{-\Gamma_{\textrm env} t},\;\Gamma_{\textrm env}\propto D_{\textrm env}.
\]
Thus: deterministic instability in the $D_{\textrm env}\!\to 0$ limit; effectively stochastic under environmental noise.

\paragraph{Status.} Collapse is \emph{deterministic at the core level}, \emph{stochastic in practice}.

\subsection*{3. Can SST replace quantum measurement postulates?}
The dual-phase picture (delocalized $R$ vs localized $T$ states) suggests an objective collapse mechanism. Collapse is driven by swirl radiation and reconnections.
Key tasks:
\begin{itemize}
\item Derive the Born rule $P\sim|\psi|^2$ from ergodic measures on swirl phase space.
\item Ensure no-signaling under nonlocal correlations of linked knots.
\end{itemize}

\paragraph{Status.} Promising realist alternative, but \emph{derivation of Born and no-signaling remains open}.

\subsection*{4. How unique is the topological decomposition?}
Different knots $K$ can share
\[
    \mathcal M(K)=b(K)^{-3/2}\,\varphi^{-g(K)}\,n(K)^{-1/\varphi}\,L_{\textrm tot}(K).
\]
Thus mass alone is degenerate. Resolution requires:
\begin{itemize}
\item Helicity $H=\int \mathbf v\!\cdot\!\boldsymbol\omega\,dV$,
\item writhe/twist spectra and normal-mode eigenfrequencies,
\item stability (lifetime) and selection rules.
\end{itemize}

\paragraph{Status.} Unique particle identity emerges only when \emph{mass, helicity, and mode spectra} are jointly enforced.

\subsection*{5. Can the swirl Lagrangian generate interactions?}
Beyond mass, interaction terms may appear via extended couplings:
\[
    \mathcal L_{\textrm couple}\;+\;\lambda_{\textrm ch}\int (\mathbf v\!\cdot\!\boldsymbol\omega)(\nabla\!\cdot\!\mathbf a)\,dV
    +\;g_c \int \mathcal C(\mathcal K_1,\mathcal K_2)\,d\Sigma.
\]
These generate parity-odd (chiral) and contact vertices, reminiscent of Yukawa/weak interactions.

\paragraph{Status.} Plausible EFT tower; \emph{explicit vertex catalogue} is an open derivation.

\subsection*{6. Is the swirl condensate Lorentz-violating?}
SST posits absolute time (preferred foliation). Microscopic frame is Galilean.
However, the photon sector Lagrangian
\[
    \partial_t^2 \mathbf a - c^2 \nabla\times(\nabla\times \mathbf a)=0,\quad \nabla\cdot\mathbf a=0
\]
is exactly Lorentz-invariant. Residual anisotropies are suppressed operators of order $\epsilon^2$ with $\epsilon=\|\mathbf u_{\textrm drift}\|/c$.
Experimental bounds: $\delta c/c \lesssim 10^{-17}$--$10^{-21}$; SST must respect these.

\paragraph{Status.} \emph{Emergent Lorentz invariance} in radiation sector; matter sector constrained to high precision.

\subsection*{Experiment table}

\begin{table}[H]
\centering
\caption{Concrete experiments to test critical SST questions.}
\begin{tabular}{lllll}
\toprule
Objective & Observable & SST control & Expected scale & Note \\
\midrule
Flux impulse & $\Delta\Phi$ steps & reconnections & $\Phi^*\sim\Phi_0$? & SQUID; $f_{\textrm BW}$ ns--µs \\
Collapse rate & vis. $\sim e^{-\Gamma t}$ & env. coupling $D_{\textrm env}$ & tunable $\Gamma$ & Kramers escape analogue \\
Identity & spectra, $H$ & knot class $K$ & discrete $\Omega_n$ & inelastic spectroscopy \\
Interactions & scattering & contact twist/link & selection rules & EFT vertex test \\
Lorentz & $\delta c/c$ & drift $\mathbf u$ & $<10^{-17}$ & cavity/clock tests \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Governance Note.}
Definitions of $\varepsilon_*$, $\mathcal B[K]$, and $S_{\textrm comp}$ are Canonical.
Their \emph{interpretation as renormalizing} $g_{2,3}$ and the representation map
$t(K)\to(\mathrm{SU}(3),\mathrm{SU}(2),Y)$ are \emph{Research} until anomaly cancellation
and empirical coupling fits are demonstrated.

\section*{Canon 4R: Research Extensions (Non-Canonical)}
The following conjectural relations are recorded for future calibration. They are
dimensionally consistent but not yet anchored to empirical values.
\begin{itemize}
	\item $v_\Phi^{\rm SST} \sim \sqrt{\rho_{\!f}}\, r_c \lVert \vswirl \rVert / \hbar$
	\item Swirl-helicity $\times$ Chern–Simons couplings
	\item Knot $\to$ gauge representation map beyond anomaly checks
\end{itemize}

% ================== Begin Operational Kinematics ==================
\subsection*{Bib\TeX (comparators)}
\begin{verbatim}
@book{Tinkham1996,
  author={Tinkham, Michael},
  title={Introduction to Superconductivity},
  edition={2}, year={1996}, publisher={McGraw--Hill}
}
@book{ClarkeBraginski2004,
  author={Clarke, John and Braginski, Alex I.},
  title={The SQUID Handbook},
  year={2004}, publisher={Wiley-VCH}
}
@article{Moffatt1969,
  author={Moffatt, H. K.},
  title={The degree of knottedness of tangled vortex lines},
  journal={J. Fluid Mech.}, year={1969}, doi={10.1017/S0022112069000225}
}
\end{verbatim}


% === Composite-knot correction (SST) ===
For a composite $K_1 \# K_2$,
\[
    u(K_1 \# K_2)
    = u(K_1) + u(K_2) - \Delta_u(K_1,K_2),
    \qquad \Delta_u \ge 0.
\]

Hence the barrier functional satisfies
\[
    \mathcal B[K_1 \# K_2]
    = \mathcal B[K_1] + \mathcal B[K_2] - \varepsilon_*\,\Delta_u.
\]

We define a dimensionless \emph{simplification index}:
\[
    S_{\textrm comp}(K_1,K_2)
    = \frac{\Delta_u}{u(K_1)+u(K_2)} \in [0,1).
\]

This index measures the degree to which composition
reduces the unknotting barrier.

\medskip

In SST taxonomy, the correction term
\[
    \Delta\mathcal B = \varepsilon_* \Delta_u
\]
acts as a \emph{nonlinear coupling},
analogous to the non-Abelian structure constants
in $\mathfrak{su}(3)\oplus\mathfrak{su}(2)\oplus\mathfrak{u}(1)$.

% ================== End Operational Kinematics ==================

% =========================================================
% SST: Invariant Mass from the Canonical Lagrangian
% =========================================================

\section*{Appendix C: Invariant Mass from the Canonical Lagrangian}

Starting from the schematic Lagrangian
\[
    \mathcal{L}_{\text{SST}}
    = \rhof\!\left(\tfrac{1}{2}\vswirl^2 - \Phi_{\text{swirl}}\right)
    + \tfrac{1}{4}F_{\mu\nu}F^{\mu\nu}
    + \big(\alpha C(K)+\beta L(K)+\gamma \mathcal{H}(K)\big)
    + \rhof \ln\!\sqrt{1-\tfrac{\|\boldsymbol\omega\|^2}{c^2}}
    + \Delta p(\text{swirl}),
\]
the \emph{mass sector} reduces, under the slender-tube approximation, to an invariant energy functional
\[
    E(K)= u\,V(K)\,\Xi_{\text{top}}(K),\qquad
    u=\tfrac{1}{2}\rho_{\text{core}}\;v_{\circlearrowleft}^{2},
\]
with $u$ the swirl energy density scale on the core, $V(K)$ the effective tube volume of the swirl string, and $\Xi_{\text{top}}(K)$ a dimensionless topological multiplier summarizing discrete combinatorial and contact/helicity corrections. In SST we adopt
\[
    V(K)\;=\;\pi r_c^2 \underbrace{\big(L_{\textrm phys}\big)}_{=\,r_c\,L_{\textrm tot}}
    \;=\;\pi r_c^3\,L_{\textrm tot},
\]
where $r_c$ is the core radius and $L_{\textrm tot}$ is the \emph{dimensionless ropelength}. The rest mass is $M=E/c^2$.

\paragraph{Canonical multiplier.}
    Guided by the EM coupling and SST’s discrete scaling rules, we take
    \[
        \Xi_{\text{top}}(K)=\frac{4}{\alpha_{\textrm fs}}\;b^{-3/2}\;\varphi^{-g}\;n^{-1/\varphi},
    \]
    where $b,g,n$ are the integer topology labels used in the Canon (e.g. torus index, layer, linkage count), $\alpha_{\textrm fs}$ is the fine-structure constant, and $\varphi$ the golden ratio. Collecting factors, the \textbf{invariant mass law} used in the code is
    \begin{equation*}
    \boxed{M(K)=\frac{4}{\alpha_{\textrm fs}}\;b^{-3/2}\;\varphi^{-g}\;n^{-1/\varphi}\;
    \frac{u\,\pi r_c^3 L_{\textrm tot}}{c^2},
        \qquad
        u=\tfrac{1}{2}\rho_{\text{core}}v_{\circlearrowleft}^2.
    }\label{eq:SST-invariant-mass}
    \end{equation*}

\paragraph{Leptons (solved $L_{\textrm tot}$).}
    For a lepton with labels $(b,g,n)$ and known mass $M_\ell^{\textrm(\exp)}$, invert \eqref{eq:SST-invariant-mass}:
    \[
        L_{\textrm tot}^{(\ell)} \;=\;
        \frac{M_\ell^{\textrm(\exp)}\,c^2}{\big(\tfrac{4}{\alpha_{\textrm fs}}\,b^{-3/2}\varphi^{-g}n^{-1/\varphi}\big)\,u\,\pi r_c^3}.
    \]

\paragraph{Baryons (exact closure).}
    Let the proton and neutron ropelengths be
    \[
        L_p=\lambda_b\,(2s_u+s_d)\,\mathcal S,\qquad
        L_n=\lambda_b\,(s_u+2s_d)\,\mathcal S,\qquad
        \mathcal S=2\pi^2\kappa_R,\;\;\kappa_R=2,
    \]
    with $(s_u,s_d)$ dimensionless sector weights and $\lambda_b$ a sector scale (set to $1$ in exact-closure).
    Imposing $M_p^{\textrm(\exp)}=M_p$ and $M_n^{\textrm(\exp)}=M_n$ in \eqref{eq:SST-invariant-mass} yields a \emph{linear} $2\times2$ system for $(s_u,s_d)$:
    \[
        \begin{bmatrix}
        2 & 1\\[2pt]
        1 & 2
        \end{bmatrix}
        \begin{bmatrix}
        s_u\\ s_d
        \end{bmatrix}

        =
        \frac{1}{K}
        \begin{bmatrix}
        M_p^{\textrm(\exp)}\\ M_n^{\textrm(\exp)}
        \end{bmatrix},
        \qquad
        K=\Big[\tfrac{4}{\alpha_{\textrm fs}}\,3^{-3/2}\,\varphi^{-2}\,3^{-1/\varphi}\Big]\frac{u\,\pi r_c^3\,\mathcal S}{c^2}.
    \]
    Solving gives
    \[
        s_u=\frac{2M_p^{\textrm(\exp)}-M_n^{\textrm(\exp)}}{3K},
        \qquad
        s_d=\frac{M_p^{\textrm(\exp)}}{K}-2s_u.
    \]

\paragraph{Composites (no binding).}
    For an atom with proton number $Z$ and neutron number $N$ (atomic mass includes $Z$ electrons),
    \[
        M_{\textrm atom}^{(\textrm pred)} = Z\,M_p+N\,M_n+Z\,M_e,\quad
        M_{\textrm mol}^{(\textrm pred)}=\sum_{\text{atoms}}M_{\textrm atom}^{(\textrm pred)}.
    \]
    Deviations from experiment in atoms/molecules correspond to \emph{binding energies} not included in this baseline (nuclear $\sim\!8\,{\textrm MeV}$ per nucleon; molecular $\sim{\textrm eV}$).

% ---------------------------------------------------------
\subsection{Benchmarks (exact\_closure mode)}
\label{sec:benchmarks-exact-closure}
The following table was generated by the Python file listed after it.
\emph{Errors in atoms/molecules = missing binding energy contribution, not model failure.}

\begin{table}[H]
\centering
\caption{Invariant-kernel mass benchmarks (exact\_closure). \emph{Errors in atoms/molecules = missing binding energy contribution, not model failure.}}
\begin{tabular}{lccc}
\toprule
Species & Known mass (kg) & Predicted mass (kg) & Error (\%)\\
\midrule
electron e- & 9.109384e-31 & 9.109384e-31 & 0.0000\\
muon $\mu$- & 1.883532e-28 & 1.883532e-28 & 0.0000\\
tau $\tau$- & 3.167540e-27 & 3.167540e-27 & 0.0000\\
proton p & 1.672622e-27 & 1.672622e-27 & 0.0000\\
neutron n & 1.674927e-27 & 1.674927e-27 & 0.0000\\
Hydrogen-1 atom & 1.673533e-27 & 1.673533e-27 & 0.0000\\
Helium-4 atom & 6.646477e-27 & 6.689952e-27 & 0.6549\\
Carbon-12 atom & 1.992647e-26 & 2.005276e-26 & 0.6330\\
Oxygen-16 atom & 2.656017e-26 & 2.674532e-26 & 0.6980\\
H$_2$ molecule & 3.367403e-27 & 3.347066e-27 & -0.6040\\
H$_2$O molecule & 2.991507e-26 & 3.009885e-26 & 0.6139\\
CO$_2$ molecule & 7.305355e-26 & 7.354340e-26 & 0.6704\\
\bottomrule
\end{tabular}\label{tab:benchmarks-exact-closure}
\end{table}

% ---------------------------------------------------------
\subsection*{Notes}
\begin{itemize}
\item Elementary entries are exact by construction in exact\_closure mode (leptons solved from $L_{\textrm tot}$; $p,n$ from closure).
\item Composite errors track omitted binding: nuclear $\mathcal O(10^{-3})$–$\mathcal O(10^{-2})$, molecular $\mathcal O(10^{-9})$.
\end{itemize}

% ---------------------------------------------------------

% === Unknotting barrier & gauge structure (SST) ===
\subsection*{From unknotting non-additivity to \(\mathfrak{su}(3)\oplus\mathfrak{su}(2)\oplus\mathfrak u(1)\) in SST}

\paragraph{Unknotting barrier functional.}
    Let \(K\subset\mathbb R^3\) be a closed swirl–string on a leaf \(\Sigma_t\).
    Define the per–crossing activation scale
    \[
        \varepsilon_*\;=\;\kappa\,\beta\,\rc\;+\;\frac{\kappa\pi}{2}\,\rhof\,\vnorm^2\,\rc^3,
        \quad \kappa=\mathcal O(1{-}10),
    \]
    and the barrier
    \[
        \mathcal B[K]\;=\;u(K)\,\varepsilon_*.
    \]
    For a connected sum \(K_1\#K_2\),
    \[
        u(K_1\#K_2)=u(K_1)+u(K_2)-\Delta_u(K_1,K_2),\qquad \Delta_u\ge 0,
    \]
    so that
    \[
        \mathcal B[K_1\#K_2]=\mathcal B[K_1]+\mathcal B[K_2]-\varepsilon_*\,\Delta_u.
    \]
    (Brittenham–Hermiller 2025 give explicit \(\Delta_u>0\) families for torus knots.)

\paragraph{Dimensionless simplification index.}
    Define
    \[
        S_{\textrm comp}(K_1,K_2):=\frac{\Delta_u(K_1,K_2)}{u(K_1)+u(K_2)}\in[0,1),
    \]
    and \(\Delta\mathcal B=\varepsilon_*\,\Delta_u\). Here \(S_{\textrm comp}\) is \emph{dimensionless}; \(\Delta\mathcal B\) has units of energy.

\paragraph{Discrete curvature on composition.}
    Let \((\mathcal K,\#)\) denote the knot configuration monoid. Non-additivity of \(u\) defines a discrete \(2\)-cocycle:
    \[
        \mathcal C(K_1,K_2):=\Delta_u(K_1,K_2).
    \]
    A minimal \emph{associator defect} (discrete curvature) for triples is
    \[
        \mathfrak{R}(K_1,K_2,K_3)\;:=\;
        \mathcal C(K_1,K_2)+\mathcal C(K_1\#K_2,K_3)
        -\mathcal C(K_2,K_3)-\mathcal C(K_1,K_2\#K_3).
    \]
    If \(\mathfrak{R}\equiv 0\) the composition is “flat” (effectively Abelian in the barrier metric); \(\mathfrak{R}\neq 0\) signals nontrivial curvature, the discrete analogue of non-Abelian structure.

\paragraph{Emergent gauge potentials from multi-director swirl.}
    Let \(\mathcal A=\big(A_\mu^{(0)},\,W_\mu^a,\,G_\mu^A\big)\) denote the swirl–gauge potentials for
    \(\mathfrak u(1)\oplus\mathfrak{su}(2)\oplus\mathfrak{su}(3)\).
    Introduce coupling functions driven by simplification statistics in a family \(\mathcal F\subset\mathcal K\):
    \[
        g_1^{-2}(\mathcal F)=g_{1,0}^{-2},\qquad
        g_2^{-2}(\mathcal F)=g_{2,0}^{-2}\Bigl[1+\lambda_2\,\langle S_{\textrm comp}\rangle_{\mathcal F}\Bigr],
        \qquad
        g_3^{-2}(\mathcal F)=g_{3,0}^{-2}\Bigl[1+\lambda_3\,\langle S_{\textrm comp}\rangle_{\mathcal F}\Bigr],
    \]
    with \(\lambda_{2,3}>0\) dimensionless and \(\langle\cdot\rangle_{\mathcal F}\) the family average.
    Thus nonzero simplification (\(\Delta_u>0\)) \emph{renormalizes} the non-Abelian sectors, while \(U(1)\) remains purely additive at leading order.

\paragraph{SST gauge Lagrangian (coupling by taxonomy).}
    With \(F_{\mu\nu}^{(0)},\,W_{\mu\nu}^a,\,G_{\mu\nu}^A\) the field strengths,
    \[
        \mathcal L_{\textrm gauge}
        =-\frac{1}{4}\frac{1}{g_1^2(\mathcal F)}\,F_{\mu\nu}^{(0)}F^{(0)\mu\nu}
        -\frac{1}{4}\frac{1}{g_2^2(\mathcal F)}\,W_{\mu\nu}^{a}W^{a\,\mu\nu}
        -\frac{1}{4}\frac{1}{g_3^2(\mathcal F)}\,G_{\mu\nu}^{A}G^{A\,\mu\nu},
    \]
    and the total selection functional acquires the barrier:
    \[
        \mathcal E_{\textrm tot}[K]=\alpha\,C(K)+\beta\,L(K)+\gamma\,\mathcal H(K)+\mathcal B[K],
        \quad
        \mathcal E_{\textrm tot}[K_1\#K_2]
        =\mathcal E_{\textrm tot}[K_1]+\mathcal E_{\textrm tot}[K_2]-\varepsilon_*\,\Delta_u.
    \]

\paragraph{Representation assignment (house mapping).}
    Adopt the Canon homomorphism \(t(K)=(L \bmod 3,\;S \bmod 2,\;\chi)\) to \(\mathfrak{su}(3)\oplus\mathfrak{su}(2)\oplus\mathfrak u(1)\):
    \[
        \begin{aligned}
        &\text{Color (SU(3)) index: } &&\mathbf 3 \text{ class determined by } (L \bmod 3),\\
        &\text{Weak (SU(2)) isospin: } &&\mathbf 2 \text{ / singlet by } (S \bmod 2),\\
        &\text{Hypercharge (U(1)): } &&Y\propto \chi\, \mathcal Q(K),
        \end{aligned}
    \]
    where \(\chi\in\{\pm1\}\) tracks chirality/mirror and \(\mathcal Q(K)\) is a chosen Abelian scalar (e.g.\ normalized circulation or writhe). This retains Abelian additivity for \(Y\) while allowing non-Abelian renormalization via \(\langle S_{\textrm comp}\rangle\).

\paragraph{Worked composite example.}
    For \(K=T(2,7)\) with \(u(K)=3\) and \(u(K\#\overline K)\le 5\),
    \[
        \Delta_u(K,\overline K)\ge 1,\qquad
        S_{\textrm comp}(K,\overline K)\ge \frac{1}{6}.
    \]
    Hence
    \[
        \Delta\mathcal B=\varepsilon_*\,\Delta_u\ge \varepsilon_*,
        \quad
        \frac{1}{g_{2,3}^2}\;\mapsto\;\frac{1}{g_{2,3}^2}\Bigl[1+\lambda_{2,3}\times\tfrac{1}{6}\Bigr]
        \ \ \text{for the family containing }K,\overline K.
    \]
    All quantities entering \(g_i(\mathcal F)\) are dimensionless (consistency check).

\paragraph{Physical interpretation.}
    Additive (\(U(1)\)) observables follow linear composition; subadditivity of \(u\) generates a discrete curvature that selectively enhances the non-Abelian sectors. Families with larger \(\langle S_{\textrm comp}\rangle\) act as stronger “non-Abelianizers” of the swirl–gauge dynamics.

% =========================
% Bibliography (non-original)
% =========================
    \begin{thebibliography}{9}
    \bibitem{BrittenhamHermiller2025}
    M.~Brittenham and S.~Hermiller,
    \emph{Unknotting number is not additive under connected sum},
    arXiv:2506.24088 (2025).
    \end{thebibliography}

%================================================
% Personas (unchanged logic, SST names)
%================================================
\section*{Appendix D: Persona Prompts}
\label{sec:personas}

\subsection*{Reviewer Persona}
    \scriptsize
    You are a peer reviewer for an SST paper. Use only the definitions and constants in the "SST Canon (\canonversion)".
    Check dimensional consistency, limiting behavior, and numerical validation. Flag any use of non-canonical
    constants or equations unless equivalence is proved. Demand explicit mapping from knot invariants (linking,
    writhe, twist) to claimed quantum numbers.

\subsection*{Theorist Persona}

    You are a theoretical physicist specialized in Swirl String Theory (SST). Base all reasoning on the attached
    "SST Canon (\canonversion)". Your task: derive the swirl-based Hamiltonian for [TARGET SYSTEM], use Sec.~\ref{sec:lagrangian},
    and verify the Swirl Clock law (Sec. \ref{sec:classical_invariants}). Provide boxed equations, dimensional checks, and a short numerical
    evaluation using the Canon constants.

\subsection*{Bridging Persona (Compare to GR/SM)}

    Work strictly within SST Canon (\canonversion). Compare [TARGET] to its GR/SM counterpart. Identify exact replacements
    (e.g., curvature → swirl), and show which terms reduce to Newtonian/Maxwellian limits. Include a correspondence
    table and any constraints needed for equivalence.


%================================================
% Session Kickoff Checklist
%================================================
    \normalsize
\section*{Appendix E: Session Kickoff Checklist}
\begin{enumerate}
\item Start new chat per task; attach this Canon first.
\item Paste a persona prompt (Sec.~\ref{sec:personas}).
\item Attach only task-relevant papers/sources.
\item State any corrections explicitly (they persist in the session).
\item At end, record Canon deltas (if any) and bump version.
\end{enumerate}


%================================================
\section*{Appendix F: Dimensional Cross-Check for \texorpdfstring{$\mathcal L_{\text{SST+Gauge}}$}{L\_\{SST+Gauge\}}}
%================================================
\label{app:dim-check}

\noindent\textbf{Unit conventions.}
We present SI checks. Where convenient, we also note the natural-unit assignment
($\hbar=c=1$), with \([A_\mu]=\text{mass}\), \([F_{\mu\nu}]=\text{mass}^2\), ensuring \([\mathcal L]=\text{mass}^4\);
conversion to SI energy density uses \(\hbar c\).

\begin{center}
	\renewcommand{\arraystretch}{1.2}
	\begin{tabular}{@{}llcl@{}}
		\toprule
		\textbf{Term} & \textbf{Expression} & \textbf{Primary units} & \textbf{Check (SI)} \\
		\midrule
		Kinetic (swirl) &
		$\displaystyle \tfrac12\,\rhof\,\|\vswirl\|^2$ &
		$[\rhof]=\mathrm{kg\,m^{-3}},\ [\vswirl]=\mathrm{m\,s^{-1}}$ &
		$\mathrm{kg\,m^{-3}}\cdot \mathrm{m^2\,s^{-2}}=\mathrm{J\,m^{-3}}$ \\

		Swirl potential &
		$\displaystyle -\,\rhof\,\Phi_{\text{swirl}}(\mathbf r,\omegas)$ &
		$[\Phi_{\text{swirl}}]=\mathrm{m^2\,s^{-2}}$ &
		$\mathrm{kg\,m^{-3}}\cdot \mathrm{m^2\,s^{-2}}=\mathrm{J\,m^{-3}}$ \\

		Incompressibility constraint &
		$\displaystyle \lambda\,(\nabla\!\cdot\!\vswirl)$ &
		$[\nabla\!\cdot\!\vswirl]=\mathrm{s^{-1}}$ &
		$[\lambda]=\mathrm{J\,s\,m^{-3}}$ so product is $\mathrm{J\,m^{-3}}$ \\

		Helicity density (local) &
		$\displaystyle \chi_h\,\rhof\,(\vswirl\!\cdot\!\omegas)$ &
		$[\omegas]=\mathrm{s^{-1}}$ &
		$\chi_h$ dimensionless; $\mathrm{kg\,m^{-3}}\cdot \mathrm{m\,s^{-1}}\cdot \mathrm{s^{-1}}=\mathrm{J\,m^{-3}}$ \\

		Yang--Mills (gauge) &
		$\displaystyle -\tfrac14 \GsA G^{a\,\mu\nu}
		-\tfrac14 \WsI W^{i\,\mu\nu}
		-\tfrac14 \Bmn B^{\mu\nu}$ &
		$\hbar=c=1:\ [F]=\text{mass}^2$ &
		$[\mathcal L_{\rm YM}]=\text{mass}^4\ \Rightarrow\ \mathrm{J\,m^{-3}}$ via $\hbar c$ \\

		Scalar kinetic &
		$\displaystyle (D_\mu\Phi)^\dagger(D^\mu\Phi)$ &
		$\hbar=c=1:\ [D_\mu]=\text{mass}$,\ $[\Phi]=\text{mass}$ &
		$\text{mass}^4\ \Rightarrow\ \mathrm{J\,m^{-3}}$ \\

		Scalar potential &
		$\displaystyle V(\Phi)=\lambda_\Phi\big(|\Phi|^2-v_\Phi^2\big)^2$ &
		$\hbar=c=1:\ [V]=\text{mass}^4$ &
		$\text{mass}^4\ \Rightarrow\ \mathrm{J\,m^{-3}}$ \\

		Minimal coupling &
		$\displaystyle \mathcal L_{\text{int}}=-A^a_\mu J_{(3)}^{a\,\mu}-W^i_\mu J_{(2)}^{i\,\mu}-B_\mu J_{(1)}^\mu$ &
		$\hbar=c=1:\ [A_\mu]=\text{mass},\ [J^\mu]=\text{mass}^3$ &
		$\text{mass}^4\ \Rightarrow\ \mathrm{J\,m^{-3}}$ \\
		\bottomrule
	\end{tabular}
\end{center}

\paragraph{Notes for reviewers.}
\begin{itemize}
	\item \textbf{Helicity term:} since $[\vswirl\!\cdot\!\omegas]=\mathrm{m\,s^{-2}}$, multiplying by $\rhof$ gives $\mathrm{J\,m^{-3}}$, so $[\chi_h]=1$.
	\item \textbf{Constraint multiplier:} with $(\nabla\!\cdot\!\vswirl)$ in $\mathrm{s^{-1}}$, the Lagrange multiplier has units $[\lambda]=\mathrm{Pa\cdot s}=\mathrm{J\,s\,m^{-3}}$. In Euler–Lagrange equations, its \emph{spatial} gradient divided by time (or $\partial_t\lambda$) plays the role of a pressure field.
	\item \textbf{Swirl potential:} the canonical choice $\Phi_{\text{swirl}}=\frac{\vscore^{2}}{2\,\FmaxEM}(\omegas\!\cdot\!\mathbf r)$ has $[\Phi_{\text{swirl}}]=\mathrm{m^2\,s^{-2}}$ provided $\FmaxEM$ carries force units, consistent with Table entries.
	\item \textbf{Gauge block:} all gauge-sector rows are standard; in natural units they produce mass$^4$, hence energy density after restoring $\hbar,c$.
\end{itemize}

\noindent\textbf{Summary.} Each addend in $\mathcal L_{\text{SST+Gauge}}$ carries $\mathrm{J\,m^{-3}}$ in SI; coupling constants \((g_s,g,g',\chi_h)\) are dimensionless; the incompressibility multiplier has $[\lambda]=\mathrm{Pa\cdot s}$ under the present choice of constraint.

%================================================
% References
%================================================
\nocite{*}
\bibliographystyle{unsrt}
\bibliography{canon_swirl_string_theory}
\end{document}